### 2011-02-10 background_and_systematic.tex
First commit

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, year-dependent
shifts in the missing-mass event distributions and various detector and binning
effects determined as in Ref\blue{s}.~\cite{2009a,HERMESCollaboration2008}. The
\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which} was eliminated for the 2006-2007 data sample. Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production. The procedure is described in detail in Refs.~\cite{2009a,HERMESCollaboration2008} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}. The largest \blue{contamination in} the data sample is expected to come from the \blue{excitation of a target proton to a $\Delta^+$ resonance. The separation of these events from the elastic sample is nto feasible because the recoiling proton is not detected. No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal}. A Monte Carlo calculation based on the parameterisation of Ref.~\cite{brasse} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform the estimation is described in detail in
Ref.~\cite{HERMESCollaboration2008}.

Another \blue{contribution to the} systematic uncertainty comes from the relative shift of the
missing-mass distribution\blue{s} between the electron and positron data
samples~\cite{Burnsth2010,Zeiler2009}. The exclusive region in the missing-mass
distribution is adjusted for each calorimeter calibration period for data
collected in 2007 to account for the observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects \blue{due to detector resolution and radiative processes}, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, DVCS/BH events were generated using a Monte Carlo simulation of
the spectrometer that included these effects. The simulation used an event
generator based on the GPD model described in Ref.~\cite{Guzey2006} because it describes the data well and to keep consistency with Ref.~\cite{2009a}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data.  In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated DVCS/BH data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. These contributions are \blue{summarised} in Table
\ref{table_systematic_contributions_0607}.

\begin{table}[H]
 \begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|c|}
  \hline
 & Background & Missing-Mass Shift & Detector Effects & & Total \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & 0.005 & 0.005 & 0.025 & & 0.026 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005 & 0.001 & 0.002 & & 0.006 \\
  \hline
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$  & 0.004 & 0.007 & 0.001 & & 0.008 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & 0.001 & 0.004 & 0.007 & & 0.008 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.002 & 0.001 & 0.002 & & 0.003 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & 0.001 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.000 & 0.001 & 0.001 & & 0.001 \\
  \hline
 \end{tabular}
}
  \caption{The contributions to systematic uncertainty due to the
background correction, the time-dependence of the missing-mass
distributions and detector effects for the 2006-2007 data to the total
systematic uncertainty. The total systematic uncertainties, shown in the
right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}

### 2011-02-10 experiment_and_data.tex
First commit

\section{Experiment and Data Selection}
The data were collected in 2006 and 2007 with the H{\sc ermes}
spectrometer \cite{Ackerstaff1998} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the HERA lepton storage ring at DESY. The integrated
luminosities of the electron and positron data samples respectively are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{2001}. The procedure used to select events is identical to that used in Ref.~\cite{2009a}.
A brief summary of this procedure is outlined in the following; consult
Refs.~\cite{Burnsth2010,Zeiler2009} for more details. An event
was selected as having exactly one photon and one lepton
track detected within the acceptance of the spectrometer.

The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35, $W^{2}$ $>$
9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
rest frame. The polar angle between the virtual and real photons was required to
be within the limits 5 mrad $<$
$\theta_{\gamma^{*}\gamma}$ $<$ 45 mrad.

An ``exclusive'' event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon that mediates the lepton-proton scattering process, $p$ is the four-momentum of the target proton and $q'$ is the four momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{2009a}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Burnsth2010}.

\section{Experimental Extraction of Asymmetry Amplitudes}

The expectation value of the experimental yield $N$ is parameterised as
\begin{equation}
 \langle N(e_{\ell},P_{\ell},\phi)\rangle =
\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{UU}
(\phi)\times
[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
(\phi)],
\end{equation}
where $\mathcal{L}$ is the integrated luminosity, $\eta$ the detection
efficiency and d$\sigma_{UU}$ denotes the
cross section for an unpolarised target integrated over both beam charges and
beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
$\phi$ as
\begin{equation}
\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi),
\label{alui_asym}
\end{equation}
\begin{equation}
 \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq \sum^{2}_{n=1}
A_{\textrm{LU,DVCS}}^{\sin(n\phi)}\sin(n\phi) 
+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi),
\label{aludvcs_asym}
\end{equation}
\begin{equation}
\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
+ A_{\textrm{C}}^{\sin\phi}\sin\phi,
\label{ac_asym}
\end{equation}
where the approximation is due to the truncation of the infinite Fourier series
caused by the azimuthal dependencies in the denominators from
Eqs.~\ref{e:alui}-\ref{e:ac}. Only the $\sin(n\phi)$ terms of the
$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
are included as both a consistency check for extraneous harmonics caused
by the denominators in Eqs.~\ref{e:alui}-\ref{e:ac} and as a test of the
normalisation of the fit. These terms are expected to be small.

A maximum-likelihood fitting technique \cite{Barlow1990} was used to
extract the asymmetry amplitudes in \blue{each} kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
This method, described in Ref.~\cite{HERMESCollaboration2008}, fits the expected
\blue{azimuthal} distribution function to the data without introducing binning effects in $\phi$.
Weights are introduced per event in the fitting procedure to account for
luminosity imbalances with respect to the beam charge and polarisation.

The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes may also be affected by the lepton progopagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients are \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} $\mathcal{C}$-function is a combination of complex Compton Form Factors. \blue{A CFF is a convolution of a GPD with a hard scattering kernel}. \blue{Contributions of GPDs to the cross section may ne relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears. Leading twist is twist-2. Typically, the contribution of a \blue{twist-$n$} GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$. \blue{Table~\ref{tab_amplitudes} presents t}he asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression\blue{.}

At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$. These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$. Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
\begin{center}
\begin{equation}
 s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:s1}
\end{equation}
\end{center}
\begin{center}
\begin{equation}
 c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
\label{eq:c1}
\end{equation}
\end{center}
where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
written
\cite{Belitsky2002} 
\begin{equation}
 \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
\label{Eq_cunp}
\end{equation}
where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
are kinematically suppressed by an order of magnitude or more.
Hence, \blue{in this} approximation, the behaviour of
$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
and therefore GPD $H$. Using this dependence, $H$ can be constrained through
measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
upon this $\mathcal{C}$-function. However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, whereas the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
twist level (see Table~\ref{tab_amplitudes}).

The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a dominant
contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ function,
which is bilinear in CFFs. \blue{However, the amplitude is suppressed by the larger BH contribution in the denominator of Eq.~\ref{e:aludvcs}. As a result of
the more complicated dependence on the CFFs and th\blue{is} suppression, it
will be more difficult to extract useful information for the constraint of GPDs
from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than f\blue{rom} the
kinematically-unsuppressed leading-twist amplitudes.}

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
$\mathcal{C}$-function receives contributions from both the BH and DVCS
processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
\begin{table}[H]
\begin{center}
\resizebox{16cm}{!} {
 \begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Suppression \\
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & $n$ = 2\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $n$ = 3\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3& $n$
= 3 \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & $n$ = 2
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $n$ = 3 \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $n$ = 2, $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Belitsky2002}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-02-10 frame.tex
First commit

\documentclass{elsart}
\usepackage[pdftex]{hyperref}
\usepackage{amstext,amsmath,amsfonts,amssymb}
\usepackage{bm}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{vruler}
\usepackage{color}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{float}
\usepackage{rotating}
\textwidth 17.0cm
\oddsidemargin 0.0cm
\evensidemargin 0.0cm
\topmargin 0.5cm
% ===========================================================================

\begin{document}
\newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
\newcommand{\red}[1]{{\color{red}{#1}\color{black}}}

\newcommand{\green}[1]{{\color{green}{#1}\color{black}}}
\newcommand{\yellow}[1]{{\color{yellow}{#1}\color{black}}}
\newcommand{\darkblue}[1]{{\color{darkblue}{#1}\color{black}}}
\newcommand{\darkgreen}[1]{{\color{darkgreen}{#1}\color{black}}}
\newcommand{\darkred}[1]{{\color{darkred}{#1}\color{black}}}
\newcommand{\lightred}[1]{{\color{lightred}{#1}\color{black}}}
\newcommand{\pink}[1]{{\color{pink}{#1}\color{black}}}
\newcommand{\gray}[1]{{\color{gray}{#1}\color{black}}}
\newcommand{\black}[1]{{\color{black}{#1}\color{black}}}
\newcommand{\magenta}[1]{\color{magenta}{#1}\color{black}}
\newcommand{\darkmag}[1]{\color{darkmag}{#1}\color{black}}

\def\CalT{\mathcal{T}}
\def\rmBH{\mathrm{BH}}
\def\rmDVCS{\mathrm{DVCS}}
\def\CalI{\mathcal{I}}
\def\rmunp{\mathrm{unp}}
\def\rmTP{\mathrm{TP}}
\def\rmRe{\mathrm{Re}}
\def\rmIm{\mathrm{Im}}

\def\xbj{x_{B}}
\def\qsr{Q^{2}}

\def\gpdH{\emph{H}}
\def\gpdE{\emph{E}}
\def\gpdHtil{\widetilde{H}}
\def\gpdEtil{\widetilde{E}}

\def\CalH{\mathcal{H}}
\def\CalE{\mathcal{E}}
\def\CalHtil{\widetilde{\mathcal{H}}}
\def\CalEtil{\widetilde{\mathcal{E}}}

\def\CalN{\mathcal{N}}
\def\CUU{\sigma_{U}}
\def\Lumi{\mathcal{L}\,}
\def\xx{\bm{x}}
\def\tt{\bm{\eta}}
\def\AC{A_C}
\def\AUT{A_{UT}}
\def\AUTDVCS{A_{UT,\rmDVCS}}
\def\AUTI{A_{UT,\CalI}}
\def\desy{{\sc desy}}

 \begin{frontmatter}

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.5)}
        \underline{Drafting Committee: DC90 (\today)}
}

\collab{HERMES Collaboration}
\begin{abstract}
Beam\blue{-}helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target \blue{by} a 27.6\,GeV lepton beam 
are extracted from the HERMES unpolarised data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. \blue{Results from both data sets are found to be} compatible with each other. Combined results from these data sets are extracted and are the statistically most precise asymmetry amplitude measurements available in the HERMES kinematic region.
\end{abstract}

\end{frontmatter}
% 
\setvruler[15pt][1][1][3][1][30pt][30pt][-42pt]
\include{theory}
\include{experiment_and_data}
\include{background_and_systematic}
\include{results}
\include{summary}
\include{append}
% this is a test comment to test the pull push mechanism
\bibliographystyle{ieeetr}
\bibliography{jburnsref}
\end{document}

### 2011-02-10 results.tex
First commit

\section{Results}
\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005~\cite{2009a} and the new 2006-2007 hydrogen data sets, are presented in Figs. \ref{release_bsa_0607} and \ref{release_bca_0607}. The asymmetry amplitudes extracted from the combined 1996-2007 hydrogen data set are shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``assoc. fraction''), which} is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data.   
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \blue{im}precision of
the beam polarisation measurement. The inner error bars represent the statistical uncertainties\blue{, while} total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}
A \blue{statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. The results} show that the \blue{the two} data sets are \blue{not incompatible}. The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties\blue{, while t}he total error bars denote the statistical and systematic uncertainties added in quadrature. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. Theoretical calculations from the model described in \cite{Kumericki} are shown as solid and dashed lines. See text for details. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ \blue{beam-charge} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \cite{Kumericki} are shown as solid and dashed lines. See text for details. The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
  \label{bca_xbjrange}
 \end{center}
\end{figure}
The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable DVCS/BH events available from the 2006-2007 data set \blue{(XXXXX)} is approximately three times greater than the number events recorded in the 1996-2005 sample \blue{(XXXX)}. The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result. \blue{This is most noticeable in the set of beam-charge asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007}.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at low $t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes dependent on the squared DVCS term. These are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither of these amplitudes show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{UNP}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{UNP}}$ via the kinematic factor $k$ introduced in Eq~\ref{eq:c1}. These amplitudes diverge with opposite sign from zero at increasing values of $-t$ but they
have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The amplitude $A_{C}^{\cos(2\phi)}$ is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.

The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data\cite{Kumericki}. The basic model is based on a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model \blue{fit} without data from the experiment \cite{Girod2007} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves incorporates this data in the fit for an extraction of the GPDs. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is well described by the model. \blue{Both the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes favour the GPD fit that did not include the Hall A data.}

The asymmetry amplitudes shown in Figs.~\ref{release_bsa_0607} and \ref{release_bca_0607} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$. There was no observed dependence of any of the amplitudes with this two dimensional binning.

### 2011-02-10 summary.tex
First commit

\section{Summary}

Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.  This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{2009a}.

A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 DVCS/BH event sample. The \blue{resulting} asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data. \blue{These model fits all include the H{\sc ermes} data set from 1996-2005. One fitted model achieve good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. One leading-twist model shows good agreement with the asymmetry amplitudes that it can be used to calculate. }

### 2011-02-10 theory.tex
First commit

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mueller1994,Ji1997a,Radyushkin1996} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{2009a,2010,CollaborationPhys.Rev.D75:0111032007,HERMEScollaboration2010,HERMESCollaborationPhys.Rev.Lett.87:1820012001} on
the leptoproduction of real photons from a nucleon that can be used to
constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
hard scattering kernel with a GPD \blue{that} describes a soft part of the scattering
process.

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the exchanged virtual photon's
four-momentum $q$. In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{$\gamma^\ast$)}. The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}. The quark is absorbed by the nucleon with fraction $x-\xi$. Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

Leptoproduction of real photons \blue{($ep\rightarrow ep\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
emission of a real photon by a quark from the nucleon\blue{,} and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
emission of a Bremsstrahlung photon by the lepton. 
The BH process is calculable in the QED framework; this process is
dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
scattering amplitudes of the two processes interfere and the large BH amplitude
amplifies the contribution of the DVCS amplitude to the interference term. 
It is through the study of this interference term at H{\sc ermes} that
useful information for the constraint of certain GPDs can be obtained.

The differential four-fold cross section for the leptoproduction of real photons
from an unpolarised target can be written \cite{Belitsky2002}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the nucleon mass and $\phi$ is the
azimuthal angle between the scattering and production planes REF\_TRENTO.
The scattering amplitude $\tau$ can be written
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and the interference term (I). These
contributions can be written 
\begin{equation}
 |\tau_{\textrm{BH}}|^{2} =
\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\left(c_{0}^{
\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
\label{e:tbh}
\end{equation}
\begin{equation}
 \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1}^{\textrm{DVCS}}\sin\phi\right),
\label{e:tdvcs}
\end{equation}
\begin{equation}
\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
I}}
+
\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)\right),
\label{e:ti}
\end{equation}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process and $\lambda$ and $e_\ell$ are respectively the
helicity and unit charge of the lepton beam.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_n^V,s_n^W$]
\blue{(}$V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$\blue{)} can be
found in
Ref.~\cite{Belitsky2002}.

This paper provides a set of results analogous to those reported in
Ref.~\cite{2009a}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment \blue{(i.e. uses a missing-mass technique for event selection)}, but represent the largest DVCS data set that will
be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
the reader is referred to Ref.~\cite{2009a}.

There are two sets of asymmetries that are measured at H{\sc
ermes} with an unpolarised target and a polarised electron or positron beam:
beam-helicity asymmetries and beam-charge asymmetries. It is possible to
disentangle the DVCS and interference contributions to the beam-helicity
asymmetry due to the beam-charge dependence of the interference term, so that
this paper, as Ref.~\cite{2009a}, presents results on the following asymmetries:
\begin{align}
\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{
2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
\label{e:alui}
\end{align}

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{K_{\textrm{DVCS}}
s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},&
\label{e:aludvcs}
\end{align}

\begin{align}
\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^3
c_{n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_
{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)} ,&
\label{e:ac}
\end{align}
where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
cross sections with positive (negative) beam charge and
$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
to cross sections taken with beam spin parallel and anti-parallel with the
beam momentum.

### 2011-02-11 theory.tex
includes new references

@@
 Generalised Parton Distributions (GPDs)
-\cite{Mueller1994,Ji1997a,Radyushkin1996} encompass the familiar parton
+\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
 distribution functions (PDFs) and nucleon form factors to provide a
@@
 collaboration has previously published results
-\cite{2009a,2010,CollaborationPhys.Rev.D75:0111032007,HERMEScollaboration2010,HERMESCollaborationPhys.Rev.Lett.87:1820012001} on
+\cite{Air06,Air08,Air09,Air10,Air10a} on
 the leptoproduction of real photons from a nucleon that can be used to
@@
 \caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
-which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{$\gamma^\ast$)}.
+which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}.
 The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}.
@@
 The differential four-fold cross section for the leptoproduction of real photons
-from an unpolarised target can be written \cite{Belitsky2002}
+from an unpolarised target can be written \cite{Bel02b}
 \begin{center}
@@
 the nucleon mass and $\phi$ is the
-azimuthal angle between the scattering and production planes REF\_TRENTO.
+azimuthal angle between the scattering and production planes \cite{Tre04}.
 The scattering amplitude $\tau$ can be written
@@
 found in
-Ref.~\cite{Belitsky2002}.
+Ref.~\cite{Bel02b}.
 
 This paper provides a set of results analogous to those reported in
-Ref.~\cite{2009a}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
+Ref.~\cite{Air09}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
 The results in this paper do not make use of any of the information from the
@@
 be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
-the reader is referred to Ref.~\cite{2009a}.
+the reader is referred to Ref.~\cite{Air09}.
 
@@
 asymmetry due to the beam-charge dependence of the interference term, so that
-this paper, as Ref.~\cite{2009a}, presents results on the following asymmetries:
+this paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
 \begin{align}

### 2011-02-11 experiment_and_data.tex
new references included

@@
 The data were collected in 2006 and 2007 with the H{\sc ermes}
-spectrometer \cite{Ackerstaff1998} using the longitudinally polarised 27.6\,GeV
+spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
 electron and positron beams incident upon an unpolarised hydrogen gas
@@
 luminosities of the electron and positron data samples respectively are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{2001}.
-The procedure used to select events is identical to that used in Ref.~\cite{2009a}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}.
+The procedure used to select events is identical to that used in Ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult
-Refs.~\cite{Burnsth2010,Zeiler2009} for more details. An event
+Refs.~\cite{Zei09,Bur10} for more details. An event
 was selected as having exactly one photon and one lepton
@@
 Here, $q$ is the four-momentum of the virtual photon that mediates the lepton-proton scattering process, $p$ is the four-momentum of the target proton and $q'$ is the four momentum of the produced photon.
-The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{2009a}.
-This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Burnsth2010}.
+The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
+This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Bur10}.
 
@@
 
-A maximum-likelihood fitting technique \cite{Barlow1990} was used to
+A maximum-likelihood fitting technique \cite{Bar90} was used to
 extract the asymmetry amplitudes in \blue{each} kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-This method, described in Ref.~\cite{HERMESCollaboration2008}, fits the expected
+This method, described in Ref.~\cite{Air08}, fits the expected
 \blue{azimuthal} distribution function to the data without introducing binning effects in $\phi$.
@@
 written
-\cite{Belitsky2002} 
+\cite{Bel02b} 
 \begin{equation}
@@
 be extracted from the available data set, the related Fourier coefficients,
- the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Belitsky2002}.}
+ the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-02-11 background_and_systematic.tex
new references included

@@
 shifts in the missing-mass event distributions and various detector and binning
-effects determined as in Ref\blue{s}.~\cite{2009a,HERMESCollaboration2008}. The
+effects determined as in Ref\blue{s}.~\cite{Air08,Air09}. The
 \blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which} was eliminated for the 2006-2007 data sample.
 Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production.
-The procedure is described in detail in Refs.~\cite{2009a,HERMESCollaboration2008} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}.
+The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}.
 The largest \blue{contamination in} the data sample is expected to come from the \blue{excitation of a target proton to a $\Delta^+$ resonance.
-The separation of these events from the elastic sample is nto feasible because the recoiling proton is not detected.
+The separation of these events from the elastic sample is not feasible because the recoiling proton is not detected.
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal}.
-A Monte Carlo calculation based on the parameterisation of Ref.~\cite{brasse} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
+A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
 The results, denoted associated fraction and labelled ``assoc.
@@
 The method used to perform the estimation is described in detail in
-Ref.~\cite{HERMESCollaboration2008}.
+Ref.~\cite{Air08}.
 
@@
 missing-mass distribution\blue{s} between the electron and positron data
-samples~\cite{Burnsth2010,Zeiler2009}. The exclusive region in the missing-mass
+samples~\cite{Zei09,Bur10}. The exclusive region in the missing-mass
 distribution is adjusted for each calorimeter calibration period for data
@@
 the spectrometer that included these effects. The simulation used an event
-generator based on the GPD model described in Ref.~\cite{Guzey2006} because it describes the data well and to keep consistency with Ref.~\cite{2009a}.
+generator based on the GPD model described in Ref.~\cite{Guz06} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis

### 2011-02-11 results.tex
new reference and event numbers included

@@
 \section{Results}
-\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005~\cite{2009a} and the new 2006-2007 hydrogen data sets, are presented in Figs.
+\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005~\cite{Air09} and the new 2006-2007 hydrogen data sets, are presented in Figs.
 \ref{release_bsa_0607} and \ref{release_bca_0607}.
@@
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``assoc.
+All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``Assoc.
 fraction''), which} is shown in the bottom row of each figure.
@@
 (systematic) uncertainties.
-Theoretical calculations from the model described in \cite{Kumericki} are shown as solid and dashed lines.
+Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in \cite{Kumericki} are shown as solid and dashed lines.
+Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
 The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
-The number of analysable DVCS/BH events available from the 2006-2007 data set \blue{(XXXXX)} is approximately three times greater than the number events recorded in the 1996-2005 sample \blue{(XXXX)}.
+The number of analysable DVCS/BH events available from the 2006-2007 data set \blue{(67815)} is approximately three times greater than the number events recorded in the 1996-2005 sample \blue{(24817)}.
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result.
@@
 
-The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data\cite{Kumericki}.
+The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data\cite{Kum09}.
 The basic model is based on a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences.
 In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence.
-The solid curves represent the model \blue{fit} without data from the experiment \cite{Girod2007} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves incorporates this data in the fit for an extraction of the GPDs.
+The solid curves represent the model \blue{fit} without data from the experiment \cite{Gir08,Cam06} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves incorporates this data in the fit for an extraction of the GPDs.
 Both fits include the 1996-2005 H{\sc ermes} data.

### 2011-02-11 summary.tex
new refs removed last sentence

@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{2009a}.
+This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{Air09}.
 
@@
 \blue{These model fits all include the H{\sc ermes} data set from 1996-2005.
-One fitted model achieve good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
-One leading-twist model shows good agreement with the asymmetry amplitudes that it can be used to calculate.
-}
+One fitted model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}

### 2011-02-11 background_and_systematic.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

@@
 The extracted asymmetry amplitudes are subject to systematic uncertainties that
-result from a combination of background processes, year-dependent
+result from a combination of background processes, 
 shifts in the missing-mass event distributions and various detector and binning
 effects determined as in Ref\blue{s}.~\cite{Air08,Air09}. The
-\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which} was eliminated for the 2006-2007 data sample.
+\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which has been} eliminated for the 2006-2007 data sample.
 Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production.
 The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}.
-The largest \blue{contamination in} the data sample is expected to come from the \blue{excitation of a target proton to a $\Delta^+$ resonance.
+The largest \blue{contamination in} the data sample is expected to come from the \blue{events involving the excitation of a target proton to a $\Delta^+$ resonance.
 The separation of these events from the elastic sample is not feasible because the recoiling proton is not detected.
@@
 these effects, DVCS/BH events were generated using a Monte Carlo simulation of
-the spectrometer that included these effects. The simulation used an event
+the spectrometer that included \blue{them}. The simulation used an event
 generator based on the GPD model described in Ref.~\cite{Guz06} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.

### 2011-02-11 experiment_and_data.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

@@
 approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}.
-The procedure used to select events is identical to that used in Ref.~\cite{Air09}.
+The procedure used to select events is \blue{similar} to that used in Ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult
@@
 The asymmetry amplitudes may also be affected by the lepton progopagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients are \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} $\mathcal{C}$-function is a combination of complex Compton Form Factors.
+The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} is a combination of complex Compton Form Factors.
 \blue{A CFF is a convolution of a GPD with a hard scattering kernel}.
-\blue{Contributions of GPDs to the cross section may ne relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears.
+\blue{Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears.
 Leading twist is twist-2.
@@
 upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, whereas the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
+However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, \blue{and} the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
 twist level (see Table~\ref{tab_amplitudes}).
@@
 \hline
-Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Suppression \\
+Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & \blue{Relative} Suppression \\
 \hline
@@
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
-&  2 & $n$ = 2\\
+&  2 & --\\
 \hline
@@
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
-&  3 & $n$ = 3\\
+&  3 & $1/Q$\\
 \hline
@@
 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
-$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3& $n$
-= 3 \\
+$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
 \hline
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $n$ = 2
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& --
 \\
@@
 $A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & $n$ = 2
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
 \\
@@
 $A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $n$ = 3 \\
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
 \hline
 $A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
-$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $n$ = 2, $\alpha_{\textrm{S}}/\pi$ \\
+$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
 \hline

### 2011-02-11 results.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

@@
 \section{Results}
-\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005~\cite{Air09} and the new 2006-2007 hydrogen data sets, are presented in Figs.
+\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
 \ref{release_bsa_0607} and \ref{release_bca_0607}.
-The asymmetry amplitudes extracted from the combined 1996-2007 hydrogen data set are shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
  \end{figure}
+
 A \blue{statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets.
@@
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at low $t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}.
+This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at \blue{small} $-t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes dependent on the squared DVCS term.
-These are shown in the second row of Fig.~\ref{bsa_xbjrange}.
-Neither of these amplitudes show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes\blue{, which are} dependent on the squared DVCS term.
+These \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes} are shown in the second row of Fig.~\ref{bsa_xbjrange}.
+Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
 The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.
@@
 
-The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data\cite{Kum09}.
-The basic model is based on a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences.
+The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
+The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences.
 In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence.
-The solid curves represent the model \blue{fit} without data from the experiment \cite{Gir08,Cam06} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves incorporates this data in the fit for an extraction of the GPDs.
+The solid curves represent the model \blue{fit} without data from experiment\blue{s} \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves \blue{includes} this data.
 Both fits include the 1996-2005 H{\sc ermes} data.
@@
 
-The asymmetry amplitudes shown in Figs.~\ref{release_bsa_0607} and \ref{release_bca_0607} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$.
+The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$.
 There was no observed dependence of any of the amplitudes with this two dimensional binning.

### 2011-02-11 theory.tex
Penultimate reading of the paper before circulation to the drafting committee. Fixed a few typos, re-flowed a couple of sentences to improve coherency with previous changes. Swapped a couple of the references around.

@@
 \caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
-which an electron/positron \blue{($e,e^\prime$)}interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}.
+which an electron/positron \blue{($e,e^\prime$)} interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}.
 The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}.
@@
 
-Leptoproduction of real photons \blue{($ep\rightarrow ep\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
+Leptoproduction of real photons \blue{($e\,p\,\rightarrow\,e\,p\,\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
 emission of a real photon by a quark from the nucleon\blue{,} and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
@@
 The results in this paper do not make use of any of the information from the
-upgraded detector equipment \blue{(i.e. uses a missing-mass technique for event selection)}, but represent the largest DVCS data set that will
-be published by H{\sc ermes}. For more details on the physics implications and general experimental technique,
-the reader is referred to Ref.~\cite{Air09}.
+upgraded detector equipment \blue{(i.e. a missing-mass technique for event selection is used)}, but represent the largest DVCS data set that will
+be published by H{\sc ermes}.
 
@@
 asymmetry due to the beam-charge dependence of the interference term, so that
-this paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
+this paper \blue{(like} Ref.~\cite{Air09}\blue{)}, presents results on the following asymmetries:
 \begin{align}

### 2011-02-11 results.tex
Changed a typo

@@
 Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used \blue{used in the various stages} of the H{\sc ermes} experiment.
+The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment \blue{used in the various stages} of the H{\sc ermes} experiment.
 

### 2011-02-21 theory.tex
update theory.tex from drafting meeting

@@
 \cite{Air06,Air08,Air09,Air10,Air10a} on
-the leptoproduction of real photons from a nucleon that can be used to
+the leptoproduction of real photons from a \blue{nucleus} that can be used to
 constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
-hard scattering kernel with a GPD \blue{that} describes a soft part of the scattering
+hard scattering kernel with a GPD that describes a soft part of the scattering
 process.
@@
 active quark at the start and end of the process, written as the skewness
-variable $\xi$; and the square $-Q^2=q^2$ of the exchanged virtual photon's
-four-momentum $q$. In the Bjorken limit of $Q^2\rightarrow\infty$ with
+variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.}.
+In the Bjorken limit of $Q^2\rightarrow\infty$ with
 fixed $t$, $\xi$ is related to the Bjorken variable
@@
 \caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
-which an electron/positron \blue{($e,e^\prime$)} interacts with a quark in the nucleon \blue{($P$)} via a virtual photon \blue{($\gamma^\ast$)}.
-The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon \blue{($\gamma$)}.
+which an electron/positron ($e,e^\prime$) interacts with a quark in the nucleon \ ($P$) via a virtual photon ($\gamma^\ast$).
+The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon ($\gamma$).
 The quark is absorbed by the nucleon with fraction $x-\xi$.
@@
 
-Leptoproduction of real photons \blue{($e\,p\,\rightarrow\,e\,p\,\gamma$)} can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
-emission of a real photon by a quark from the nucleon\blue{,} and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
+Leptoproduction of real photons ($e\,p\,\rightarrow\,e\,p\,\gamma$) can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
+emission of a real photon by a quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
 emission of a Bremsstrahlung photon by the lepton. 
@@
 explanation of the Fourier coefficients [$c_n^V,s_n^W$]
-\blue{(}$V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$\blue{)} can be
+($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be
 found in
 Ref.~\cite{Bel02b}.
-
-This paper provides a set of results analogous to those reported in
-Ref.~\cite{Air09}. The analysis presented here \blue{additionally includes} a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
-The results in this paper do not make use of any of the information from the
-upgraded detector equipment \blue{(i.e. a missing-mass technique for event selection is used)}, but represent the largest DVCS data set that will
-be published by H{\sc ermes}.
 
@@
 asymmetry due to the beam-charge dependence of the interference term, so that
-this paper \blue{(like} Ref.~\cite{Air09}\blue{)}, presents results on the following asymmetries:
+this paper (like Ref.~\cite{Air09}), presents results on the following asymmetries:
 \begin{align}
@@
 beam momentum.
+
+\blue{This paper provides a set of results analogous to those reported in
+Ref.~\cite{Air09}. The analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
+The results in this paper do not make use of any of the information from the
+upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will
+be published by H{\sc ermes}.}

### 2011-02-21 experiment_and_data.tex
updated experiment_and_data.tex from drafting committee

@@
 luminosities of the electron and positron data samples respectively are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$\blue{,} with average beam polarisation\blue{s} of 30.3\,\% and 39.2\% \cite{Ben01}.
-The procedure used to select events is \blue{similar} to that used in Ref.~\cite{Air09}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult
@@
 
-An ``exclusive'' event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
-Here, $q$ is the four-momentum of the virtual photon that mediates the lepton-proton scattering process, $p$ is the four-momentum of the target proton and $q'$ is the four momentum of the produced photon.
+An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
+Here, $q$ is the four-momentum of the virtual photon, $p$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
 The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
-This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 dataset \cite{Bur10}.
+This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.
 
@@
 A maximum-likelihood fitting technique \cite{Bar90} was used to
-extract the asymmetry amplitudes in \blue{each} kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+extract the asymmetry amplitudes in each kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
 This method, described in Ref.~\cite{Air08}, fits the expected
-\blue{azimuthal} distribution function to the data without introducing binning effects in $\phi$.
+azimuthal distribution function to the data without introducing binning effects in $\phi$.
 Weights are introduced per event in the fitting procedure to account for
@@
 coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The asymmetry amplitudes may also be affected by the lepton progopagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients \blue{depend on}  ``$\mathcal{C}$-functions''\blue{,} each \blue{of which} is a combination of complex Compton Form Factors.
-\blue{A CFF is a convolution of a GPD with a hard scattering kernel}.
-\blue{Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.} The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears.
+The asymmetry amplitudes may also be affected by the lepton \blue{propagators} and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
+The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients depend on ``$\mathcal{C}$-functions'', each of which is a combination of complex Compton Form Factors.
+A CFF is a convolution of a GPD with a hard scattering kernel.
+Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.
+The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears.
 Leading twist is twist-2.
-Typically, the contribution of a \blue{twist-$n$} GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$.
-\blue{Table~\ref{tab_amplitudes} presents t}he asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression\blue{.}
+Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression.
 
-At H{\sc ermes} kinematic\blue{ conditions}, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
+At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
 These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
@@
 $\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
-conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), \blue{to first approximation} the
+conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), to first approximation the
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
@@
 are kinematically suppressed by an order of magnitude or more.
-Hence, \blue{in this} approximation, the behaviour of
+Hence, in this approximation, the behaviour of
 $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
@@
 upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ \blue{amplitude} is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, \blue{and} the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ \blue{amplitudes} enter the cross section at a higher
+However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
 twist level (see Table~\ref{tab_amplitudes}).
 
-The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a dominant
+The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
 contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ function,
-which is bilinear in CFFs. \blue{However, the amplitude is suppressed by the larger BH contribution in the denominator of Eq.~\ref{e:aludvcs}. As a result of
-the more complicated dependence on the CFFs and th\blue{is} suppression, it
+which is bilinear in CFFs.
+\blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the $s_{1}^{\textrm{I}}$ coefficient.} As a result of
+the more complicated dependence on the CFFs and this suppression, it
 will be more difficult to extract useful information for the constraint of GPDs
-from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than f\blue{rom} the
-kinematically-unsuppressed leading-twist amplitudes.}
+from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
+kinematically-unsuppressed leading-twist amplitudes.
 
@@
 processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
-in this function are \blue{of} leading twist, they relate to gluon helicity\blue{-}flip GPDs and are \blue{thus} suppressed by \blue{$\alpha_{\textrm{S}}/\pi$}.
+in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$.
 \begin{table}[H]
@@
 \hline
-Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & \blue{Relative} Suppression \\
+Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Relative Suppression \\
 \hline
@@
 be extracted from the available data set, the related Fourier coefficients,
- the $\mathcal{C}$-functions, the twist level and the suppression \blue{at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
+ the $\mathcal{C}$-functions, the twist level and the suppression at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-02-21 background_and_systematic.tex
text updates background_and_systematic.tex from drafitng meeting

--- 2011-02-11 background_and_systematic.tex
@@
 The extracted asymmetry amplitudes are subject to systematic uncertainties that
-result from a combination of background processes, year-dependent
+result from a combination of background processes, 
 shifts in the missing-mass event distributions and various detector and binning
-effects determined as in Ref\blue{s}.~\cite{Air08,Air09}. The
-\blue{1996-2005} data sample also has a systematic uncertainty from misalignment of the spectrometer\blue{, which} was eliminated for the 2006-2007 data sample.
-Contributions to the uncertainties on the amplitude measurements arise from \blue{background in the data from} events that include neutral meson production.
-The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607}.
-The largest \blue{contamination in} the data sample is expected to come from the \blue{excitation of a target proton to a $\Delta^+$ resonance.
-The separation of these events from the elastic sample is not feasible because the recoiling proton is not detected.
-No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal}.
-A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
-The results, denoted associated fraction and labelled ``assoc.
-fraction'', are shown in the last row of each figure in the results section.
-The method used to perform the estimation is described in detail in
-Ref.~\cite{Air08}.
+effects determined as in Refs.~\cite{Air08,Air09}. The
+1996-2005 elastic sample also has a systematic uncertainty from misalignment of the spectrometer, which has been eliminated for the 2006-2007 data sample.
+Contributions to the uncertainties on the amplitude measurements arise from background in the data from events that include neutral meson production.
+The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} \blue{for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region}.
 
-Another \blue{contribution to the} systematic uncertainty comes from the relative shift of the
-missing-mass distribution\blue{s} between the electron and positron data
+Another contribution to the systematic uncertainty comes from the relative shift of the
+missing-mass distributions between the electron and positron data
 samples~\cite{Zei09,Bur10}. The exclusive region in the missing-mass
@@
 The predominant contribution to the systematic uncertainty arises from detector
-effects, including the acceptance of the spectrometer, smearing effects \blue{due to detector resolution and radiative processes}, and
+effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
 finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
 these effects, DVCS/BH events were generated using a Monte Carlo simulation of
-the spectrometer that included these effects. The simulation used an event
-generator based on the GPD model described in Ref.~\cite{Guz06} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.
+the spectrometer that included them. \blue{An event
+generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis
@@
 background corrections, detector effects and missing-mass shift
-uncertainties added in quadrature. These contributions are \blue{summarised} in Table
+uncertainties added in quadrature. These contributions are summarised in Table
 \ref{table_systematic_contributions_0607}.
@@
 }
-  \caption{The contributions to systematic uncertainty due to the
-background correction, the time-dependence of the missing-mass
+  \caption{The contributions to \blue{the} systematic uncertainty due to the
+background correction, the time-dependenc\blue{t shifts} of the missing-mass
 distributions and detector effects for the 2006-2007 data to the total
@@
 \end{table}
+
+\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
+As the recoiling proton is not detected the separation of the latter events is not possible.}
+No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
+A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
+The results, denoted associated fraction and labelled ``\blue{A}ssoc.
+fraction'', are shown in the last row of each figure in the results section.
+The method used to perform the estimation is described in detail in
+Ref.~\cite{Air08}.

### 2011-02-21 results.tex
updates results.tex from drafting committee

@@
 \section{Results}
-\blue{R}esults \blue{for} the beam-helicity and beam-charge asymmetry \blue{amplitudes} extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
 \ref{release_bsa_0607} and \ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-All of the extracted asymmetry amplitudes \blue{are subject to} a \blue{fractional} contribution to the event yield from associated \blue{production (``Assoc.
-fraction''), which} is shown in the bottom row of each figure.
+All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc.
+fraction''), which is shown in the bottom row of each figure.
 The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
@@
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the \blue{im}precision of
+2006-2007 data respectively is present in the amplitudes due to the imprecision of
 the beam polarisation measurement.
-The inner error bars represent the statistical uncertainties\blue{, while} total error bars denote the statistical and systematic uncertainties added in quadrature.
-The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
+The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{release_bsa_0607}
@@
 
-A \blue{statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets.
+A statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets.
 Only the statistical uncertainties were employed in this test.
-The results} show that the \blue{the two} data sets are \blue{not incompatible}.
+The results show that the two data sets are not incompatible.
 The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
@@
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
-The inner error bars represent the statistical uncertainties\blue{, while t}he total error bars denote the statistical and systematic uncertainties added in quadrature.
-The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
+The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{release_bca_0607}
@@
 See text for details.
-The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
   \label{bsa_xbjrange}
@@
     \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
-    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ \blue{beam-charge} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
 The error bars (bands) represent the statistical (systematic) uncertainties.
@@
 See text for details.
-The \blue{simulated fractional} contribution \blue{from associated production} to the yield in each kinematic bin is shown in the bottom row.}
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
   \label{bca_xbjrange}
@@
 The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
-The number of analysable DVCS/BH events available from the 2006-2007 data set \blue{(67815)} is approximately three times greater than the number events recorded in the 1996-2005 sample \blue{(24817)}.
+The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number \blue{of} events recorded in the 1996-2005 sample (24817).
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result.
-\blue{This is most noticeable in the set of beam-charge asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007}.
+\blue{This is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.
 
@@
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish at \blue{small} $-t$ values due to the dependence of the amplitude on the factor $k$ from in Eq.~\ref{eq:s1}.
+This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish \blue{in this $-t$ region} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes are compatible with zero, as are the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes\blue{, which are} dependent on the squared DVCS term.
-These \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes} are shown in the second row of Fig.~\ref{bsa_xbjrange}.
-Neither the \blue{$A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitudes} show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment \blue{used in the various stages} of the H{\sc ermes} experiment.
+The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude \blue{is} compatible with zero, as \blue{is} the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes are shown in the second row of Fig.~\ref{bsa_xbjrange}.
+Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
 
@@
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{UNP}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{UNP}}$ via the kinematic factor $k$ introduced in Eq~\ref{eq:c1}.
+There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{UNP}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{UNP}}$ via the kinematic factor $k$ \blue{from} Eq.~\ref{eq:c1}.
 These amplitudes diverge with opposite sign from zero at increasing values of $-t$ but they
@@
 The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
-The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewedness and $t$ dependences.
+The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled \blue{skewness} and $t$ dependences.
 In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence.
-The solid curves represent the model \blue{fit} without data from experiment\blue{s} \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model \blue{fit} represented by the dashed curves \blue{includes} this data.
+The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data.
 Both fits include the 1996-2005 H{\sc ermes} data.
 The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
-The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is well described by the model.
-\blue{Both the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes favour the GPD fit that did not include the Hall A data.}
+\blue{All of the amplitudes are well described by the model.}
 

### 2011-02-21 summary.tex
updated summary.tex drafting committee

@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-This new data set is larger than the previously publised 1996-2005 data set Ref.~\cite{Air09}.
 
-A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 DVCS/BH event sample.
-The \blue{resulting} asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
+A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
+The \blue{resulting} \blue{beam charge} asymmetry amplitudes represent the statistically \blue{most} precise DVCS result that will be published by the H{\sc ermes} collaboration.
 The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry.
@@
 The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data.
-\blue{These model fits all include the H{\sc ermes} data set from 1996-2005.
-One fitted model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}
+\blue{This model fit ~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}.
+\blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}

### 2011-02-22 background_and_systematic.tex
new column in table

@@
 \resizebox{16cm}{!} {
- \begin{tabular}{|c|c|c|c|c|c|}
+ \begin{tabular}{|c|c|c|c|c|c|c|}
   \hline
- & Background & Missing-Mass Shift & Detector Effects & & Total \\
+ & $A$ $\pm \delta_{stat.}$ $\pm \delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
   \hline
   \hline
-  $A_{\textrm{LU,I}}^{\sin\phi}$ & 0.005 & 0.005 & 0.025 & & 0.026 \\
+  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
   \hline
-  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005 & 0.001 & 0.002 & & 0.006 \\
+  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
+  \hline
+  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
   \hline
   \hline
-  $A_{\textrm{LU,DVCS}}^{\sin\phi}$  & 0.004 & 0.007 & 0.001 & & 0.008 \\
+  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
   \hline
+  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
   \hline
-  $A_{\textrm{C}}^{\cos(0\phi)}$ & 0.001 & 0.004 & 0.007 & & 0.008 \\
+  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
   \hline
-  $A_{\textrm{C}}^{\cos\phi}$ & 0.002 & 0.001 & 0.002 & & 0.003 \\
-  \hline
-  $A_{\textrm{C}}^{\cos(2\phi)}$ & 0.001 & 0.001 & 0.001 & & 0.002 \\
-  \hline
-  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.000 & 0.001 & 0.001 & & 0.001 \\
+  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
   \hline
@@
   \caption{The contributions to \blue{the} systematic uncertainty due to the
-background correction, the time-dependenc\blue{t shifts} of the missing-mass
+background correction, the time-dependen\blue{t shifts} of the missing-mass
 distributions and detector effects for the 2006-2007 data to the total

### 2011-02-22 theory.tex
added additional paper references

@@
 collaboration has previously published results
-\cite{Air06,Air08,Air09,Air10,Air10a} on
+\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
 the leptoproduction of real photons from a \blue{nucleus} that can be used to

### 2011-02-22 results.tex
added new 2d plots

@@
 the 1996-2005 (open triangles) and 2006-2007 (filled squares)
-hydrogen data.   
+hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
 2006-2007 data respectively is present in the amplitudes due to the imprecision of
-the beam polarisation measurement.
-The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.
-The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{release_bsa_0607}
@@
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity \blue{asymmetry} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
 from 1996 until 2007. The error bars (bands) represent the statistical
-(systematic) uncertainties.
-Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
+(systematic) uncertainties. \blue{An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
+the beam polarisation measurement.} Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
     \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
-    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge \blue{asymmetry} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
 The error bars (bands) represent the statistical (systematic) uncertainties.
@@
 \end{figure}
+
+\begin{figure}
+ \begin{center}
+ \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
+  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
+from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
+(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
+the beam polarisation measurement.}}
+  \label{bsa_xbjrange}
+ \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
+    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+The error bars (bands) represent the statistical (systematic) uncertainties.
+Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
+See text for details.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
+  \label{bca_xbjrange}
+ \end{center}
+\end{figure}
+
 The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.

### 2011-02-22 results.tex
added 2d description

@@
 the beam polarisation measurement.}}
-  \label{bsa_xbjrange}
+  \label{bsa_xbjrange2}
  \end{center}
@@
 The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
-  \label{bca_xbjrange}
+  \label{bca_xbjrange2}
  \end{center}
@@
 
-The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$.
-There was no observed dependence of any of the amplitudes with this two dimensional binning.
+\blue{Calculations from a fit of GPDs to all existing DVCS data can be used as an alternative to comparing experimental results with existing models.
+The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}, extracted from H{\sc ermes} hydrogen data, can be described by a fit to other DVCS results.
+In order to provide more detailed information for future fits, in particular for the entanglement  and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+There is no observed $-t$ dependnece on any of the $A_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
+Also no additional features or $-t$ dependencies are observed for the $A_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.}

### 2011-02-24 background_and_systematic.tex
Fixed some typos and rewrote some parts for clarification

@@
 \blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
-As the recoiling proton is not detected the separation of the latter events is not possible.}
+As the recoiling proton is not detected, separation of the latter events from the data sample is not possible.}
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.

### 2011-02-24 experiment_and_data.tex
Fixed some typos and rewrote some parts for clarification

@@
 which is bilinear in CFFs.
-\blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the $s_{1}^{\textrm{I}}$ coefficient.} As a result of
+\blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}}.
+As a result of
 the more complicated dependence on the CFFs and this suppression, it

### 2011-02-24 results.tex
sentence removed
Fixed some typos and rewrote some parts for clarification

--- 2011-02-22 results.tex
@@
     \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
-The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
-See text for details.
-The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
-  \label{bca_xbjrange}
+The error bars (bands) represent the statistical (systematic) uncertainties.}}
+  \label{bca_xbjrange2}
  \end{center}
@@
 
-The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$.
-There was no observed dependence of any of the amplitudes with this two dimensional binning.
+\blue{In order to provide more detailed information for future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+There is no observed $-t$ dependnece on any of the $A_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
+Also no additional features or $-t$ dependencies are observed for the $A_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.}

### 2011-02-24 theory.tex
Fixed some typos and rewrote some parts for clarification

@@
 active quark at the start and end of the process, written as the skewness
-variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.}.
-In the Bjorken limit of $Q^2\rightarrow\infty$ with
+variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.} In the Bjorken limit of $Q^2\rightarrow\infty$ with
 fixed $t$, $\xi$ is related to the Bjorken variable

### 2011-02-24 background_and_systematic.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

--- 2011-02-22 background_and_systematic.tex
@@
 finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
-these effects, DVCS/BH events were generated using a Monte Carlo simulation of
+these effects, events were generated using a Monte Carlo simulation of
 the spectrometer that included them. \blue{An event
@@
 bin, the systematic uncertainty was determined as the difference between the
-asymmetry amplitude reconstructed from the simulated DVCS/BH data and that
+asymmetry amplitude reconstructed from the simulated data and that
 calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
@@
 \ref{table_systematic_contributions_0607}.
+
+\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
+As the recoiling proton is not detected, separation of the latter events from rest of the data sample is not possible due to the experimental technique.}
+No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
+A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
+The results, denoted associated fraction and labelled ``\blue{A}ssoc.
+fraction'', are shown in the last row of each figure in the results section.
+The method used to perform the estimation is described in detail in
+Ref.~\cite{Air08}.
 
@@
 \end{table}
-
-\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
-As the recoiling proton is not detected the separation of the latter events is not possible.}
-No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
-A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
-The results, denoted associated fraction and labelled ``\blue{A}ssoc.
-fraction'', are shown in the last row of each figure in the results section.
-The method used to perform the estimation is described in detail in
-Ref.~\cite{Air08}.

### 2011-02-24 results.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

@@
 
-A statistical test was applied in order to check for possible incompatiability between the asymmetry amplitudes extracted from both data sets.
+A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets.
 Only the statistical uncertainties were employed in this test.
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result.
-\blue{This is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.
+\blue{This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.
 
@@
 The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude \blue{is} compatible with zero, as \blue{is} the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term.
-The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitudes are shown in the second row of Fig.~\ref{bsa_xbjrange}.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}.
 Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands of the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
+The systematic error bands \blue{associated with} the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
 

### 2011-02-24 summary.tex
Fixed some typos and rewrote some parts for clarification
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-
 A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
@@
 The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data.
-\blue{This model fit ~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}.
-\blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}
+\blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}.
+\blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
+All amplitudes are also presented projected in $x_{\textrm{B}}$ in bins of $-t$.
+No localised features are observed in any particular $t$-bin.}

### 2011-02-24 theory.tex
Rephrased and rewrote a couple of sections for greater emphasis and to bring in line with more of the DCs suggestions.

@@
 \cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
-the leptoproduction of real photons from a \blue{nucleus} that can be used to
-constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
-hard scattering kernel with a GPD that describes a soft part of the scattering
-process.
+the leptoproduction of real photons from a nucleon \blue{or nucleus} that can be used to constrain GPDs via Compton Form Factors (CFFs).
+Each CFF is a convolution of a hard scattering kernel with a GPD that describes a soft part of the scattering process.
 

### 2011-02-24 background_and_systematic.tex
minor update

@@
 the spectrometer that included them. \blue{An event
-generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.
+generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well \blue{and is consistent with} Ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis

### 2011-02-24 theory.tex
minor update

@@
 transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
-representing the initial (final) four momentum of the proton; the average
+representing the initial (final) four-momentum of the proton; the average
 fraction $x$ of the nucleon's longitudinal momentum carried by the active

### 2011-02-24 frame.tex
v0.5 -> v0.6
0.6 - 0.7 removed blue font

@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS (v0.5)}
+  	\underline{Paper Tag: PDVCS (v0.7)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 \begin{abstract}
-Beam\blue{-}helicity and charge asymmetries in the hard exclusive leptoproduction of
-real photons from an unpolarised proton target \blue{by} a 27.6\,GeV lepton beam 
+Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
+real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
 are extracted from the HERMES unpolarised data set of 2006-2007 using a
@@
 The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
-\blue{Results from both data sets are found to be} compatible with each other.
+Results from both data sets are found to be compatible with each other.
 Combined results from these data sets are extracted and are the statistically most precise asymmetry amplitude measurements available in the HERMES kinematic region.

### 2011-03-01 frame.tex
updates from drafting meeting

@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS (v0.7)}
+  	\underline{Paper Tag: PDVCS (v0.8)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
-are extracted from the HERMES unpolarised data set of 2006-2007 using a
+are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a
 missing-mass event selection technique.
 The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
-Results from both data sets are found to be compatible with each other.
-Combined results from these data sets are extracted and are the statistically most precise asymmetry amplitude measurements available in the HERMES kinematic region.
+Results from \blue{the two} data sets are found to be compatible with each other.
+Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
 \end{abstract}

### 2011-03-01 theory.tex
updates of theory from drafting committee

--- 2011-02-24 theory.tex
@@
 \cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
-the leptoproduction of real photons from a \blue{nucleus} that can be used to
-constrain GPDs via Compton Form Factors (CFFs). Each CFF is a convolution of a
-hard scattering kernel with a GPD that describes a soft part of the scattering
-process.
+the leptoproduction of real photons from a nucleon or nucleus that can be used to constrain GPDs via Compton Form Factors (CFFs).
+Each CFF is a convolution of a hard scattering kernel with a GPD that describes a soft part of the scattering process.
 
 Generalised parton distributions depend upon four kinematic variables: the
-Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
-transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
-representing the initial (final) four momentum of the proton; the average
+Mandelstam variable $t=(\blue{P-P^{\prime}})^2$, which is the squared momentum
+transfer to the target nucleon in the scattering process with \blue{$P$ ($P^{\prime}$})
+representing the initial (final) four-momentum of the proton; the average
 fraction $x$ of the nucleon's longitudinal momentum carried by the active
@@
 active quark at the start and end of the process, written as the skewness
-variable $\xi$; and the square $-Q^2=q^2$ of the \blue{of the four-momentum of the virtual photon that mediates the lepton-proton scattering process.} In the Bjorken limit of $Q^2\rightarrow\infty$ with
+variable $\xi$; and the square $-Q^2=q^2$ of the four-momentum of the virtual photon that mediates the lepton-proton scattering process. In the Bjorken limit of $Q^2\rightarrow\infty$ with
 fixed $t$, $\xi$ is related to the Bjorken variable
-$x_{\textrm{B}}=\frac{-q^2}{2p.q}$ as
+$x_{\textrm{B}}=\frac{-q^2}{2\blue{P}.q}$ as
 $\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
@@
 \subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
-\caption[DVCS and Bethe Heitler hand bag diagram.]{Left: The DVCS process in
-which an electron/positron ($e,e^\prime$) interacts with a quark in the nucleon \ ($P$) via a virtual photon ($\gamma^\ast$).
+\caption[DVCS and Bethe Heitler hand bag diagram.]{\blue{(a)}: The DVCS process in
+which an electron/positron (\blue{$e$}) interacts with a quark in the nucleon \ \blue{($p$)} via a virtual photon ($\gamma^\ast$).
 The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon ($\gamma$).
 The quark is absorbed by the nucleon with fraction $x-\xi$.
-Right: The Bethe-Heitler process which has the same initial and final states as DVCS.}
+\blue{(b)}: The Bethe-Heitler process which has the same initial and final states as DVCS.}
 \label{spin}
@@
 
-Leptoproduction of real photons ($e\,p\,\rightarrow\,e\,p\,\gamma$) can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
+Leptoproduction of real photons ($e\,p\,\rightarrow\,e'\,p'\,\gamma$) can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
 emission of a real photon by a quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
@@
 It is through the study of this interference term at H{\sc ermes} that
-useful information for the constraint of certain GPDs can be obtained.
+useful information for the constraint of certain GPDs can be obtained \blue{\cite{Bel02b}}.
 
@@
 ermes} with an unpolarised target and a polarised electron or positron beam:
-beam-helicity asymmetries and beam-charge asymmetries. It is possible to
-disentangle the DVCS and interference contributions to the beam-helicity
-asymmetry due to the beam-charge dependence of the interference term, so that
-this paper (like Ref.~\cite{Air09}), presents results on the following asymmetries:
+beam-helicity asymmetries and beam-charge asymmetries. \blue{In order to disentangle the DVCS and interference contributions
+to the cross section via the beam-charge dependence of the
+interference term this paper, as in Ref.~\cite{Air09}, presents} results on the following asymmetries:
 \begin{align}
@@
 $\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
-to cross sections taken with beam spin parallel and anti-parallel with the
+to cross sections taken with beam spin parallel \blue{(anti-parallel)} with the
 beam momentum.
 
-\blue{This paper provides a set of results analogous to those reported in
+This paper provides a set of results analogous to those reported in
 Ref.~\cite{Air09}. The analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
@@
 upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will
-be published by H{\sc ermes}.}
+be published by H{\sc ermes}.

### 2011-03-01 experiment_and_data.tex
updates of experiment and data selection section

@@
 A brief summary of this procedure is outlined in the following; consult
-Refs.~\cite{Zei09,Bur10} for more details. An event
+Refs.~\cite{Zei09,Bur10} for more details.
+
+An event
 was selected as having exactly one photon and one lepton
 track detected within the acceptance of the spectrometer.
-
 The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
@@
 
-An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+p-q')^{2}$ of the $ep \rightarrow e\gamma \textrm{X}$ measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
-Here, $q$ is the four-momentum of the virtual photon, $p$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
+An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
+Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
 The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.

### 2011-03-01 experiment_and_data.tex
updated experiemnt and data selection

@@
  \langle N(e_{\ell},P_{\ell},\phi)\rangle =
-\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{UU}
+\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\blue{\textrm{UU}}}
 (\phi)\times
@@
 \end{equation}
-where $\mathcal{L}$ is the integrated luminosity, $\eta$ the detection
-efficiency and d$\sigma_{UU}$ denotes the
+where $\mathcal{L}$ is the integrated luminosity, $\eta$ \blue{is} the detection
+efficiency and d$\sigma_{\blue{\textrm{UU}}}$ denotes the
 cross section for an unpolarised target integrated over both beam charges and
@@
 coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The asymmetry amplitudes may also be affected by the lepton \blue{propagators} and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
+The asymmetry amplitudes may also be affected by the lepton propagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
 The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients depend on ``$\mathcal{C}$-functions'', each of which is a combination of complex Compton Form Factors.
@@
 Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.
-The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross-section in which the amplitude appears.
+The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross section in which the amplitude appears.
 Leading twist is twist-2.
@@
 At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
-These asymmetry amplitudes for an unpolarised target are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+These asymmetry amplitudes\blue{,} for an unpolarised target\blue{,} are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
 Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
@@
 which is bilinear in CFFs.
-\blue{However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}}.
+However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of
@@
 processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
-in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$.
+in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
+\blue{where $\alpha_{\textrm{S}}$ is the fine structue constant}.
 \begin{table}[H]
@@
 be extracted from the available data set, the related Fourier coefficients,
- the $\mathcal{C}$-functions, the twist level and the suppression at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
+ the $\mathcal{C}$-functions, the twist level and the suppression~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-03-01 background_and_systematic.tex
updated background_and_systematic

--- 2011-02-24 background_and_systematic.tex
@@
 result from a combination of background processes, 
-shifts in the missing-mass event distributions and various detector and binning
-effects determined as in Refs.~\cite{Air08,Air09}. The
-1996-2005 elastic sample also has a systematic uncertainty from misalignment of the spectrometer, which has been eliminated for the 2006-2007 data sample.
-Contributions to the uncertainties on the amplitude measurements arise from background in the data from events that include neutral meson production.
-The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} \blue{for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region}.
+shifts in the missing-mass distributions and various detector and binning
+effects determined as in Refs.~\cite{Air08,Air09}.
+Contributions to the uncertainties on the amplitude measurements arise from background in the data from neutral meson production.
+The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region.
 
 Another contribution to the systematic uncertainty comes from the relative shift of the
-missing-mass distributions between the electron and positron data
-samples~\cite{Zei09,Bur10}. The exclusive region in the missing-mass
-distribution is adjusted for each calorimeter calibration period for data
-collected in 2007 to account for the observed time dependence. One
+missing-mass distributions. \blue{There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}}. \blue{The missing-mass
+distribution is also adjusted for each calorimeter calibration period of data
+collected in 2007 to account for the observed time dependence.} One
 quarter of the difference between the asymmetries extracted using the standard
@@
 these effects, events were generated using a Monte Carlo simulation of
-the spectrometer that included them. \blue{An event
-generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation} because it describes the data well and to keep consistency with Ref.~\cite{Air09}.
+the spectrometer that included them. An event
+generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis
@@
 background corrections, detector effects and missing-mass shift
-uncertainties added in quadrature. These contributions are summarised in Table
+uncertainties added in quadrature. 
+\blue{The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
+which has been eliminated for the 2006-2007 data sample.}
+These contributions are summarised in Table
 \ref{table_systematic_contributions_0607}.
 
-\blue{The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
-As the recoiling proton is not detected, separation of the latter events from rest of the data sample is not possible due to the experimental technique.}
+The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
+\blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample is not possible due to the experimental technique.
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
-A Monte Carlo calculation based on the parameterisation of Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
-The results, denoted associated fraction and labelled ``\blue{A}ssoc.
+A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
+The results, denoted associated fraction and labelled ``Assoc.
 fraction'', are shown in the last row of each figure in the results section.
-The method used to perform the estimation is described in detail in
+The method used to perform \blue{this} estimation is described in detail in
 Ref.~\cite{Air08}.
@@
   \hline
- & $A$ $\pm \delta_{stat.}$ $\pm \delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
+ & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift & Detector Effects & & Total \\
   \hline
@@
 }
-  \caption{The contributions to \blue{the} systematic uncertainty due to the
-background correction, the time-dependen\blue{t shifts} of the missing-mass
+  \caption{The contributions to the systematic uncertainty due to the
+background correction, the time-dependent shifts of the missing-mass
 distributions and detector effects for the 2006-2007 data to the total

### 2011-03-01 results.tex
updated results

@@
 Only the statistical uncertainties were employed in this test.
-The results show that the two data sets are not incompatible.
-The $A_{\textrm{LU,I}}$, $A_{\textrm{LU,DVCS}}$ and $A_{\textrm{C}}$ asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
+\blue{This test revealed no significant evidence for incompatibility between the data sets.} The \blue{beam-helicity and beam-charge} asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
 \begin{figure}
@@
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity \blue{asymmetry} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
 from 1996 until 2007. The error bars (bands) represent the statistical
-(systematic) uncertainties. \blue{An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
-the beam polarisation measurement.} Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
+(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
+the beam polarisation measurement.
+Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
     \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
-    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge \blue{asymmetry} amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
 The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines.
+Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
  \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
-  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
+  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
@@
 (systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
-the beam polarisation measurement.}}
+the beam polarisation measurement.}
   \label{bsa_xbjrange2}
@@
     \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
-    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
-The error bars (bands) represent the statistical (systematic) uncertainties.}}
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+The error bars (bands) represent the statistical (systematic) uncertainties.}
   \label{bca_xbjrange2}
@@
 The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
-The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number \blue{of} events recorded in the 1996-2005 sample (24817).
+The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result.
-\blue{This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes} because the beam polarisation was lower in 2006 and 2007.
+This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.
 
 The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
-sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
+sensitive to the interference term in the scattering amplitude, \blue{is} shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish \blue{in this $-t$ region} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
+This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish in this $-t$ region due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude \blue{is} compatible with zero, as \blue{is} the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term.
+The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude is compatible with zero, as is the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term.
 The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}.
 Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands \blue{associated with} the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
+The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
 
@@
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{UNP}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{UNP}}$ via the kinematic factor $k$ \blue{from} Eq.~\ref{eq:c1}.
+There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
 These amplitudes diverge with opposite sign from zero at increasing values of $-t$ but they
@@
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-The amplitude $A_{C}^{\cos(2\phi)}$ is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
-Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.
+The $A_{C}^{\cos(2\phi)}$ \blue{amplitude} is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
+Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading\blue{-}twist amplitudes.
 
 The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
-The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled \blue{skewness} and $t$ dependences.
+The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
 In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence.
@@
 The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
-\blue{All of the amplitudes are well described by the model.}
+All of the amplitudes are well described by the model.
 
-\blue{In order to provide more detailed information for future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-There is no observed $-t$ dependnece on any of the $A_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
-Also no additional features or $-t$ dependencies are observed for the $A_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.}
+In order to provide more detailed information \blue{that will be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
+Also no additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-03-01 summary.tex
updated summary

--- 2011-02-21 summary.tex
@@
 
-Beam helicity and beam charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
+Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-
+\blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained 1996-2005 experimental period \blue{described in} Ref.~\cite{Air09}}.
 A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The \blue{resulting} \blue{beam charge} asymmetry amplitudes represent the statistically \blue{most} precise DVCS result that will be published by the H{\sc ermes} collaboration.
-The result of this simultaneous extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam helicity asymmetry.
-There are also non zero amplitudes in the zeroth and first harmonic of the beam charge asymmetry.
+The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
+The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry.
+There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry.
 Each of the other higher order asymmetry amplitudes are consistent with zero.
-The combined results are \blue{compared to} calculations from ongoing work to fit GPD models to experimental data.
-\blue{This model fit ~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 Ref.~\cite{Air09}.
-\blue{The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.}
+The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
+\blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}.
+The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
+All amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
+No localised features are observed in any particular $t$-bin.

### 2011-03-28 results.tex
Added description of models

@@
 
-The curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
+The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
@@
 
-In order to provide more detailed information \blue{that will be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations made from a hybrid quark-diquark model with a Regge term that is included to accurately describe parton distribution functions at low $x$ values.
+The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence).
+The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region.
+The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.
+
+The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005).
+The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain.
+The presented data is well described by the calculations.
+
+In order to provide more detailed information \blue{that can be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
 There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.

### 2011-03-29 background_and_systematic.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
-\blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample is not possible due to the experimental technique.
+\blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.

### 2011-03-29 experiment_and_data.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 
-An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
-Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
+An event sample was selected using a missing-mass technique requiring
+that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$
+of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement
+corresponded to the square of the proton mass within the limits of the
+energy resolution of the \blue{H{\sc ermes}} calorimeter.
+Here, $q$ is the four-momentum of the virtual photon, $p$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
 The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.

### 2011-03-29 frame.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 \usepackage{float}
+%\usepackage{superscriptaddress}
 \usepackage{rotating}
@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS (v0.8)}
+  	\underline{Paper Tag: PDVCS (v0.9)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 
+% List of Institute Addresses 
 \collab{HERMES Collaboration}
@@
 missing-mass event selection technique.
-The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
+The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
 Results from \blue{the two} data sets are found to be compatible with each other.

### 2011-03-29 results.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
-sensitive to the interference term in the scattering amplitude, \blue{is} shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
+sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set.
@@
 
-The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations made from a hybrid quark-diquark model with a Regge term that is included to accurately describe parton distribution functions at low $x$ values.
+\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values.
 The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence).
@@
 The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain.
-The presented data is well described by the calculations.
+The presented data is well described by the calculations.}
 
@@
 There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
-Also no additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.
+No additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-03-29 summary.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-\blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained 1996-2005 experimental period \blue{described in} Ref.~\cite{Air09}}.
-A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
+\blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}.
+A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
 The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
@@
 The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
-\blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}.
+\blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}.
 The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
-All amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
+\blue{The other model fit does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data accurately.
+A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points.
+The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005.
+The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
 No localised features are observed in any particular $t$-bin.

### 2011-03-29 theory.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

@@
 Generalised parton distributions depend upon four kinematic variables: the
-Mandelstam variable $t=(\blue{P-P^{\prime}})^2$, which is the squared momentum
-transfer to the target nucleon in the scattering process with \blue{$P$ ($P^{\prime}$})
+Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
+transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
 representing the initial (final) four-momentum of the proton; the average
@@
 fixed $t$, $\xi$ is related to the Bjorken variable
-$x_{\textrm{B}}=\frac{-q^2}{2\blue{P}.q}$ as
+$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
 $\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
@@
 charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
-the nucleon mass and $\phi$ is the
+the nucleon mass\blue{,} and $\phi$ is the
 azimuthal angle between the scattering and production planes \cite{Tre04}.
@@
 c_{n}^{\textrm{BH}}\cos(n\phi) + 
-K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},&
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
+c_{n}^{\textrm{DVCS}}\cos(n\phi)} \blue{\textrm{\,\,and}}&
 \label{e:aludvcs}
@@
 $\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
-to cross sections taken with beam spin parallel \blue{(anti-parallel)} with the
+to cross sections taken with beam spin parallel \blue{(anti-parallel)} \blue{to} the
 beam momentum.
 
-This paper provides a set of results analogous to those reported in
-Ref.~\cite{Air09}. The analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
-The results in this paper do not make use of any of the information from the
+The analysis presented here additionally includes a larger,
+independent data set taken during the years 2006 and 2007 after the
+experiment was upgraded in the target region. The results in this paper do not make use of any of the information from the
 upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will

### 2011-03-29 bsadvcsplots_eml_par13_bin6_9607_release.C
added root macros

@@ -1,0 +1,4044 @@
+/* 
+Macro for displaying values for BSA vs standard kinematics
+
+
+STAND-ALONE PROGRAM. Compile and run with links to ROOT libraries.
+Use root-compile.sh shell script
+
+
+*/
+
+#include "Riostream.h"
+#include "TROOT.h"
+#include "TTree.h"
+#include "TGraph.h"
+#include "TMinuit.h"
+#include "TCanvas.h"
+#include "TLegend.h"
+#include "TLine.h"
+#include "TGraphErrors.h"
+#include "TStyle.h"
+#include "TSystem.h"
+#include "TPad.h"
+#include "TVirtualPad.h"
+#include "TAxis.h"
+#include "TH1.h"
+#include "TPolyLine.h"
+#include "TAttFill.h"
+#include "TLatex.h"
+
+#define bins 9
+#define pup 1.2
+#define plo 0
+
+#define std_title_size 0.05
+#define std_title_offset 0.9
+
+
+
+int main(){
+
+  //gROOT->Reset();
+
+  gStyle->SetOptStat(0);
+  gStyle->SetOptFit(0);
+  gStyle->SetStatX(0.9); 
+  gStyle->SetStatY(0.9);
+  gStyle->SetStatW(0.4);
+  gStyle->SetStatH(0.26);
+  gStyle->SetStatBorderSize(1);
+  gStyle->SetStatColor(0);
+  gStyle->SetTitleFillColor(0);
+  //gStyle->SetTitleXOffset(100);
+  //gStyle->SetTitleYOffset(100);
+  gStyle->SetTitleBorderSize(1);
+  //gStyle->SetTitleY(0.9);
+  //gStyle->SetTitleX(0.1);
+  gStyle->SetCanvasBorderMode(0);
+  gStyle->SetCanvasColor(0);
+  gStyle->SetPadBorderMode(0);
+
+
+  gStyle->SetFrameBorderMode(0);
+  gStyle->SetFrameFillStyle(0);
+  gStyle->SetFillStyle(0);
+
+
+
+  /** LOAD DATA **/
+
+ /* Reading values from pi0 Q2, xB, tc .txt files */
+  /*********************************************************************************************************
[…]

### 2011-03-29 background_and_systematic.tex
Added the JHEP style

@@
 
-The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state.
-\blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample.
+The data sample in the exclusive region contains events involving both
+production of real photons in which the proton remains intact and
+events involving the excitation of the target proton to a $\Delta^+$
+resonant state. \blue{The} recoiling proton is not detected \blue{and
+  the calorimeter resolution does not allow} separation of the latter events from rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
@@
 
-\begin{table}[H]
+\begin{table}
  \begin{center}

### 2011-03-29 frame.tex
Added the JHEP style

@@
-\documentclass{elsart}
-\usepackage[pdftex]{hyperref}
-\usepackage{amstext,amsmath,amsfonts,amssymb}
-\usepackage{bm}
+\documentclass[11pt,a4paper]{article}
+\usepackage{jheppub}
+\pdfoutput=1
+\toccontinuoustrue
 \usepackage{lscape}
-\usepackage{graphicx}
 \usepackage{vruler}
-\usepackage{color}
 \usepackage{subfigure}
-\usepackage{mathrsfs}
-\usepackage{eufrak}
-\usepackage{float}
-%\usepackage{superscriptaddress}
-\usepackage{rotating}
-\textwidth 17.0cm
-\oddsidemargin 0.0cm
-\evensidemargin 0.0cm
-\topmargin 0.5cm
-% ===========================================================================
+\usepackage{appendix}
+
+\newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
+\def\desy{{\sc desy}}
 
 \begin{document}
-\newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
-\newcommand{\red}[1]{{\color{red}{#1}\color{black}}}
-
-\newcommand{\green}[1]{{\color{green}{#1}\color{black}}}
-\newcommand{\yellow}[1]{{\color{yellow}{#1}\color{black}}}
-\newcommand{\darkblue}[1]{{\color{darkblue}{#1}\color{black}}}
-\newcommand{\darkgreen}[1]{{\color{darkgreen}{#1}\color{black}}}
-\newcommand{\darkred}[1]{{\color{darkred}{#1}\color{black}}}
-\newcommand{\lightred}[1]{{\color{lightred}{#1}\color{black}}}
-\newcommand{\pink}[1]{{\color{pink}{#1}\color{black}}}
-\newcommand{\gray}[1]{{\color{gray}{#1}\color{black}}}
-\newcommand{\black}[1]{{\color{black}{#1}\color{black}}}
-\newcommand{\magenta}[1]{\color{magenta}{#1}\color{black}}
-\newcommand{\darkmag}[1]{\color{darkmag}{#1}\color{black}}
-
-\def\CalT{\mathcal{T}}
-\def\rmBH{\mathrm{BH}}
-\def\rmDVCS{\mathrm{DVCS}}
-\def\CalI{\mathcal{I}}
-\def\rmunp{\mathrm{unp}}
-\def\rmTP{\mathrm{TP}}
-\def\rmRe{\mathrm{Re}}
-\def\rmIm{\mathrm{Im}}
-
-\def\xbj{x_{B}}
-\def\qsr{Q^{2}}
-
-\def\gpdH{\emph{H}}
-\def\gpdE{\emph{E}}
-\def\gpdHtil{\widetilde{H}}
-\def\gpdEtil{\widetilde{E}}
-
-\def\CalH{\mathcal{H}}
-\def\CalE{\mathcal{E}}
-\def\CalHtil{\widetilde{\mathcal{H}}}
-\def\CalEtil{\widetilde{\mathcal{E}}}
-
-\def\CalN{\mathcal{N}}
-\def\CUU{\sigma_{U}}
-\def\Lumi{\mathcal{L}\,}
-\def\xx{\bm{x}}
-\def\tt{\bm{\eta}}
-\def\AC{A_C}
-\def\AUT{A_{UT}}
-\def\AUTDVCS{A_{UT,\rmDVCS}}
-\def\AUTI{A_{UT,\CalI}}
-\def\desy{{\sc desy}}
-
- \begin{frontmatter}
-
-\title{
-	Beam-Helicity and Charge Asymmetries \\
+\title{Beam-Helicity and Charge Asymmetries \\
         in the Bethe-Heitler and DVCS processes on \\
@@
 % List of Institute Addresses 
-\collab{HERMES Collaboration}
-\begin{abstract}
-Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
-real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
-are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a
-missing-mass event selection technique.
+\collaboration{The HERMES Collaboration}
+\collaborationImg{\includegraphics{hermeslogo.pdf}}
+
+\author[12]{A.~Airapetian}
+\author[26]{N.~Akopov}
+\author[5]{Z.~Akopov}
+\author[6]{E.C.~Aschenauer}
+\author[25]{W.~Augustyniak}
+\author[26]{R.~Avakian}
+\author[26]{A.~Avetissian}
+\author[5]{E.~Avetisyan}
+\author[15]{B.~Ball}
+\author[18]{S.~Belostotski}
+\author[10]{N.~Bianchi}
+\author[17,24]{H.P.~Blok}
+\author[6]{H.~B\"ottcher}
+\author[5]{A.~Borissov}
+\author[13]{J.~Bowles}
+\author[12]{I.~Brodski}
+\author[19]{V.~Bryzgalov}
+\author[13]{J.~Burns}
+\author[9]{M.~Capiluppi}
+\author[10]{G.P.~Capitani}
+\author[21]{E.~Cisbani}
+\author[9]{G.~Ciullo}
+\author[9]{M.~Contalbrigo}
+\author[9]{P.F.~Dalpiaz}
+\author[5]{W.~Deconinck}
+\author[2]{R.~De~Leo}
+\author[5,22]{L.~De~Nardo}
+\author[10]{E.~De~Sanctis}
+\author[8]{M.~Diefenthaler}
+\author[10]{P.~Di~Nezza}
+\author[17]{J.~Dreschler}
+\author[12]{M.~D\"uren}
+\author[12]{M.~Ehrenfried}
+\author[26]{G.~Elbakian}
+\author[4]{F.~Ellinghaus}
+\author[6]{R.~Fabbri}
+\author[10]{A.~Fantoni}
+\author[22]{L.~Felawka}
+\author[21]{S.~Frullani}
+\author[6]{D.~Gabbert}
+\author[19]{G.~Gapienko}
+\author[19]{V.~Gapienko}
+\author[21]{F.~Garibaldi}
+\author[5,18,22]{G.~Gavrilov}
+\author[26]{V.~Gharibyan}
+\author[9]{F.~Giordano}
+\author[15]{S.~Gliske}
+\author[5]{M.~Golembiovskaya}
+\author[10]{C.~Hadjidakis}
+\author[5]{M.~Hartig}
+\author[10]{D.~Hasch}
+\author[23]{T.~Hasegawa}
+\author[13]{G.~Hill}
+\author[6]{A.~Hillenbrand}
+\author[13]{M.~Hoek}
+\author[5]{Y.~Holler}
+\author[6]{I.~Hristova}
+\author[23]{Y.~Imazu}
+\author[19]{A.~Ivanilov}
+\author[18]{A.~Izotov}
+\author[1]{H.E.~Jackson}
+\author[18]{A.~Jgoun}
+\author[11]{H.S.~Jo}
+\author[14]{S.~Joosten}
+\author[13]{R.~Kaiser}
+\author[26]{G.~Karyan}
+\author[12]{T.~Keri}
+\author[4]{E.~Kinney}
+\author[18]{A.~Kisselev}
+\author[23]{N.~Kobayashi}
+\author[19]{V.~Korotkov}
+\author[16]{V.~Kozlov}
+\author[18]{P.~Kravchenko}
+\author[7]{V.G.~Krivokhijine}
+\author[2]{L.~Lagamba}
+\author[14]{R.~Lamb}
+\author[17]{L.~Lapik\'as}
+\author[13]{I.~Lehmann}
+\author[9]{P.~Lenisa}
+\author[14]{L.A.~Linden-Levy}
+\author[11]{A.~L\'opez~Ruiz}
+\author[15]{W.~Lorenzon}
+\author[5]{X.-G.~Lu}
+\author[23]{X.-R.~Lu}
+\author[3]{B.-Q.~Ma}
+\author[13]{D.~Mahon}
+\author[14]{N.C.R.~Makins}
+\author[18]{S.I.~Manaenkov}
+\author[21]{L.~Manfr\'e}
+\author[3]{Y.~Mao}
+\author[25]{B.~Marianski}
+\author[4]{A.~Martinez de la Ossa}
+\author[26]{H.~Marukyan}
+\author[22]{C.A.~Miller}
+\author[23]{Y.~Miyachi}
+\author[26]{A.~Movsisyan}
+\author[10]{V.~Muccifora}
+\author[13]{M.~Murray}
+\author[8]{A.~Mussgiller}
+\author[2]{E.~Nappi}
+\author[18]{Y.~Naryshkin}
+\author[8]{A.~Nass}
+\author[6]{M.~Negodaev}
+\author[6]{W.-D.~Nowak}
+\author[9]{L.L.~Pappalardo}
+\author[12]{R.~Perez-Benito}
+\author[8]{N.~Pickert}
+\author[8]{M.~Raithel}
+\author[1]{P.E.~Reimer}
+\author[10]{A.R.~Reolon}
+\author[6]{C.~Riedl}
+\author[8]{K.~Rith}
+\author[13]{G.~Rosner}
+\author[5]{A.~Rostomyan}
+\author[14]{J.~Rubin}
+\author[11]{D.~Ryckbosch}
+\author[19]{Y.~Salomatin}
+\author[20]{F.~Sanftl}
+\author[20]{A.~Sch\"afer}
+\author[11]{G.~Schnell}
+\author[5]{K.P.~Sch\"uler}
+\author[13]{B.~Seitz}
+\author[23]{T.-A.~Shibata}
+\author[7]{V.~Shutov}
+\author[9]{M.~Stancari}
+\author[9]{M.~Statera}
+\author[8]{E.~Steffens}
+\author[17]{J.J.M.~Steijger}
+\author[12]{H.~Stenzel}
+\author[6]{J.~Stewart}
+\author[8]{F.~Stinzing}
+\author[26]{S.~Taroian}
+\author[16]{A.~Terkulov}
+\author[25]{A.~Trzcinski}
+\author[11]{M.~Tytgat}
+\author[11]{A.~Vandenbroucke}
+\author[17]{P.B.~van~der~Nat}
+\author[11]{Y.~Van~Haarlem}
+\author[11]{C.~Van~Hulse}
+\author[5]{M.~Varanda}
+\author[18]{D.~Veretennikov}
+\author[18]{V.~Vikhrov}
+\author[2]{I.~Vilardi}
+\author[8]{C.~Vogel}
+\author[3]{S.~Wang}
+\author[8]{S.~Yaschenko}
+\author[3]{H.~Ye}
+\author[5]{Z.~Ye}
+\author[22]{S.~Yen}
+\author[12]{W.~Yu}
+\author[8]{D.~Zeiler}
+\author[5]{B.~Zihlmann}
+\author[25]{P.~Zupranski}
+
+\affiliation[1]{Physics Division, Argonne National Laboratory, Argonne, Illinois 60439-4843, USA}
+\affiliation[2]{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70124 Bari, Italy}
+\affiliation[3]{School of Physics, Peking University, Beijing 100871, China}
+\affiliation[4]{Nuclear Physics Laboratory, University of Colorado, Boulder, Colorado 80309-0390, USA}
+\affiliation[5]{DESY, 22603 Hamburg, Germany}
+\affiliation[6]{DESY, 15738 Zeuthen, Germany}
+\affiliation[7]{Joint Institute for Nuclear Research, 141980 Dubna, Russia}
+\affiliation[8]{Physikalisches Institut, Universit\"at Erlangen-N\"urnberg, 91058 Erlangen, Germany}
+\affiliation[9]{Istituto Nazionale di Fisica Nucleare, Sezione di Ferrara and Dipartimento di Fisica, Universit\`a di Ferrara, 44100 Ferrara, Italy}
+\affiliation[10]{Istituto Nazionale di Fisica Nucleare, Laboratori Nazionali di Frascati, 00044 Frascati, Italy}
+\affiliation[11]{Department of Subatomic and Radiation Physics, University of Gent, 9000 Gent, Belgium}
+\affiliation[12]{Physikalisches Institut, Universit\"at Gie{\ss}en, 35392 Gie{\ss}en, Germany}
+\affiliation[13]{SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, United Kingdom}
+\affiliation[14]{Department of Physics, University of Illinois, Urbana, Illinois 61801-3080, USA}
+\affiliation[15]{Randall Laboratory of Physics, University of Michigan, Ann Arbor, Michigan 48109-1040, USA }
+\affiliation[16]{Lebedev Physical Institute, 117924 Moscow, Russia}
+\affiliation[17]{National Institute for Subatomic Physics (Nikhef), 1009 DB Amsterdam, The Netherlands}
+\affiliation[18]{Petersburg Nuclear Physics Institute, Gatchina, Leningrad region, 188300 Russia}
+\affiliation[19]{Institute for High Energy Physics, Protvino, Moscow region, 142281 Russia}
+\affiliation[20]{Institut f\"ur Theoretische Physik, Universit\"at Regensburg, 93040 Regensburg, Germany}
+\affiliation[21]{Istituto Nazionale di Fisica Nucleare, Sezione Roma 1, Gruppo Sanit\`a and Physics Laboratory, Istituto Superiore di Sanit\`a, 00161 Roma, Italy}
+\affiliation[22]{TRIUMF, Vancouver, British Columbia V6T 2A3, Canada}
+\affiliation[23]{Department of Physics, Tokyo Institute of Technology, Tokyo 152, Japan}
+\affiliation[24]{Department of Physics and Astronomy, Vrije Universiteit, 1081 HV Amsterdam, The Netherlands}
+\affiliation[25]{Andrzej Soltan Institute for Nuclear Studies, 00-689 Warsaw, Poland}
+\affiliation[26]{Yerevan Physics Institute, 375036 Yerevan, Armenia}
+
+\abstract{
+Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
+are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a missing-mass event selection technique.
 The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
@@
 Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
-\end{abstract}
+}
+\keywords{lepton-nucleon scattering}
 
-\end{frontmatter}
-% 
 \setvruler[15pt][1][1][3][1][30pt][30pt][-42pt]
+\maketitle
+
 \include{theory}
@@
 \include{append}
-% this is a test comment to test the pull push mechanism
-\bibliographystyle{ieeetr}
+\bibliographystyle{natbib}
 \bibliography{jburnsref}

### 2011-03-29 summary.tex
Added the JHEP style

@@
 No localised features are observed in any particular $t$-bin.
+
+\acknowledgments
+We gratefully acknowledge the \desy\ management for its support and the staff
+at \desy\ and the collaborating institutions for their significant effort.
+This work was supported by 
+the Ministry of Economy and the Ministry of Education and Science of Armenia;
+the FWO-Flanders and IWT, Belgium;
+the Natural Sciences and Engineering Research Council of Canada;
+the National Natural Science Foundation of China;
+the Alexander von Humboldt Stiftung,
+the German Bundesministerium f\"ur Bildung und Forschung (BMBF), and
+the Deutsche Forschungsgemeinschaft (DFG);
+the Italian Istituto Nazionale di Fisica Nucleare (INFN);
+the MEXT, JSPS, and G-COE of Japan;
+the Dutch Foundation for Fundamenteel Onderzoek der Materie (FOM);
+the Russian Academy of Science and the Russian Federal Agency for 
+Science and Innovations;
+the U.K.~Engineering and Physical Sciences Research Council, 
+the Science and Technology Facilities Council,
+and the Scottish Universities Physics Alliance;
+the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
+and the European Community Research Infrastructure Integrating Activity
+under the FP7 "Study of strongly interacting matter (HadronPhysics2, Grant
+Agreement number 227431)".

### 2011-03-29 bcaplots_eml_par13_bin6_all_release_withassoc.C
removed old macros

@@ -1,4421 +1,0 @@
-/* 
-Macro for displaying values for BSA vs standard kinematics
-
-
-STAND-ALONE PROGRAM. Compile and run with links to ROOT libraries.
-Use root-compile.sh shell script
-
-
-*/
-
-#include "Riostream.h"
-#include "TROOT.h"
-#include "TTree.h"
-#include "TGraph.h"
-#include "TMinuit.h"
-#include "TCanvas.h"
-#include "TLegend.h"
-#include "TLine.h"
-#include "TGraphErrors.h"
-#include "TStyle.h"
-#include "TSystem.h"
-#include "TPad.h"
-#include "TVirtualPad.h"
-#include "TAxis.h"
-#include "TH1.h"
-#include "TPolyLine.h"
-#include "TAttFill.h"
-#include "TLatex.h"
-
-#define bins 9
-#define pup 1.2
-#define plo 0
-
-#define std_title_size 0.05
-#define std_title_offset 0.9
-
-
-
-int main(){
-
-  //gROOT->Reset();
-
-  gStyle->SetOptStat(0);
-  gStyle->SetOptFit(0);
-  gStyle->SetStatX(0.9); 
-  gStyle->SetStatY(0.9);
-  gStyle->SetStatW(0.4);
-  gStyle->SetStatH(0.26);
-  gStyle->SetStatBorderSize(1);
-  gStyle->SetStatColor(0);
-  gStyle->SetTitleFillColor(0);
-  //gStyle->SetTitleXOffset(100);
-  //gStyle->SetTitleYOffset(100);
-  gStyle->SetTitleBorderSize(1);
-  //gStyle->SetTitleY(0.9);
-  //gStyle->SetTitleX(0.1);
-  gStyle->SetCanvasBorderMode(0);
-  gStyle->SetCanvasColor(0);
-  gStyle->SetPadBorderMode(0);
-
-
-  gStyle->SetFrameBorderMode(0);
-  gStyle->SetFrameFillStyle(0);
-  gStyle->SetFillStyle(0);
-
-
-
-  /** LOAD DATA **/
-
- /* Reading values from pi0 Q2, xB, tc .txt files */
-  /*********************************************************************************************************
[…]

### 2011-03-29 bsadvcsplots_eml_par13_bin6_9607_release.C

@@ -1,4044 +1,0 @@
-/* 
-Macro for displaying values for BSA vs standard kinematics
-
-
-STAND-ALONE PROGRAM. Compile and run with links to ROOT libraries.
-Use root-compile.sh shell script
-
-
-*/
-
-#include "Riostream.h"
-#include "TROOT.h"
-#include "TTree.h"
-#include "TGraph.h"
-#include "TMinuit.h"
-#include "TCanvas.h"
-#include "TLegend.h"
-#include "TLine.h"
-#include "TGraphErrors.h"
-#include "TStyle.h"
-#include "TSystem.h"
-#include "TPad.h"
-#include "TVirtualPad.h"
-#include "TAxis.h"
-#include "TH1.h"
-#include "TPolyLine.h"
-#include "TAttFill.h"
-#include "TLatex.h"
-
-#define bins 9
-#define pup 1.2
-#define plo 0
-
-#define std_title_size 0.05
-#define std_title_offset 0.9
-
-
-
-int main(){
-
-  //gROOT->Reset();
-
-  gStyle->SetOptStat(0);
-  gStyle->SetOptFit(0);
-  gStyle->SetStatX(0.9); 
-  gStyle->SetStatY(0.9);
-  gStyle->SetStatW(0.4);
-  gStyle->SetStatH(0.26);
-  gStyle->SetStatBorderSize(1);
-  gStyle->SetStatColor(0);
-  gStyle->SetTitleFillColor(0);
-  //gStyle->SetTitleXOffset(100);
-  //gStyle->SetTitleYOffset(100);
-  gStyle->SetTitleBorderSize(1);
-  //gStyle->SetTitleY(0.9);
-  //gStyle->SetTitleX(0.1);
-  gStyle->SetCanvasBorderMode(0);
-  gStyle->SetCanvasColor(0);
-  gStyle->SetPadBorderMode(0);
-
-
-  gStyle->SetFrameBorderMode(0);
-  gStyle->SetFrameFillStyle(0);
-  gStyle->SetFillStyle(0);
-
-
-
-  /** LOAD DATA **/
-
- /* Reading values from pi0 Q2, xB, tc .txt files */
-  /*********************************************************************************************************
[…]

### 2011-03-30 results.tex
Added citations to Liuti and Guidal

@@
 
-\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values.
+\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence).
@@
 
-The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005).
+The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}.
 The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain.

### 2011-03-30 summary.tex
Added citations to Liuti and Guidal

@@
 The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
-\blue{The other model fit does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data accurately.
-A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points.
+\blue{The other model fit~\cite{Liu11} does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data as accurately.
+A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points~\cite{Gui11}.
 The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005.

### 2011-03-30 results.tex
Changed the description of simonettas model

@@
 
-\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+\blue{The dash-dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence).
 The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region.
-The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not well described.
 

### 2011-03-30 summary.tex
Changed the description of simonettas model

@@
 The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
-\blue{The other model fit~\cite{Liu11} does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data as accurately.
+\blue{The other model fit~\cite{Liu11} does not include the H{\sc ermes} data from 1996-2005 and describes the $t$-projection of the $A^{\sin\phi}_{\textrm{LU}}$ well.
 A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points~\cite{Gui11}.

### 2011-04-01 results.tex
updated 2d plots figs 6 and 7
Made changes suggested by Delia

--- 2011-03-29 results.tex
@@
 the beam polarisation measurement.
-Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines.
-See text for details.
+\blue{Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.} See text for details.
 The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines.
+Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines and amplitude values calculated from fits to data from Ref.~\cite{Gui11} are shown as open crosses.
 See text for details.
@@
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
-from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
-(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
-the beam polarisation measurement.}
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+The error bars (bands) represent the statistical (systematic) uncertainties.
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of the beam polarisation measurement.}
   \label{bsa_xbjrange2}
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
+    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_release_pic_update}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
@@
 
-The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09}.
+The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from the colliders at H{\sc era} and H{\sc ermes} and Jefferson Lab.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
@@
 
-\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values.
-The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence).
-The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region.
-The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.
+\blue{The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD.
+The model incorporates fits to global deep-inelastic scattering and elastic data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from H{\sc ermes} and Jefferson Lab (to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.}
 
-The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005).
-The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain.
+\blue{The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}.
+The extraction of the Compton Form Factors is independent of assumptions made about the shape of the underlying CFFs, but cannot be simply extended beyond the H{\sc ermes} kinematic domain.
 The presented data is well described by the calculations.}

### 2011-04-01 summary.tex
Made changes suggested by Delia

--- 2011-03-29 summary.tex
@@
 The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
-\blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}.
-The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes.
-\blue{The other model fit does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data accurately.
-A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points.
-The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005.
-The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
+All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
 No localised features are observed in any particular $t$-bin.

### 2011-04-01 background_and_systematic.tex
Removed blue text

@@
 Another contribution to the systematic uncertainty comes from the relative shift of the
-missing-mass distributions. \blue{There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}}. \blue{The missing-mass
+missing-mass distributions. There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}. The missing-mass
 distribution is also adjusted for each calorimeter calibration period of data
-collected in 2007 to account for the observed time dependence.} One
+collected in 2007 to account for the observed time dependence. One
 quarter of the difference between the asymmetries extracted using the standard
@@
 uncertainties added in quadrature. 
-\blue{The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
-which has been eliminated for the 2006-2007 data sample.}
+The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
+which has been eliminated for the 2006-2007 data sample.
 These contributions are summarised in Table
@@
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state. \blue{The} recoiling proton is not detected \blue{and
-  the calorimeter resolution does not allow} separation of the latter events from rest of the data sample.
+resonant state. The recoiling proton is not detected and
+  the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
-A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
+A Monte Carlo calculation based on the parameterisation from Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
 The results, denoted associated fraction and labelled ``Assoc.
 fraction'', are shown in the last row of each figure in the results section.
-The method used to perform \blue{this} estimation is described in detail in
+The method used to perform this estimation is described in detail in
 Ref.~\cite{Air08}.
@@
  \begin{center}
-\resizebox{16cm}{!} {
+\resizebox{\textwidth}{!} {
  \begin{tabular}{|c|c|c|c|c|c|c|}

### 2011-04-01 experiment_and_data.tex
Added the JHEP style
Removed blue text

--- 2011-03-01 experiment_and_data.tex
@@
 
-An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter.
-Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon.
+An event sample was selected using a missing-mass technique requiring
+that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
+of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
+corresponded to the square of the proton mass within the limits of the
+energy resolution of the H{\sc ermes} calorimeter.
+Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon.
 The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
@@
  \langle N(e_{\ell},P_{\ell},\phi)\rangle =
-\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\blue{\textrm{UU}}}
+\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
 (\phi)\times
@@
 \end{equation}
-where $\mathcal{L}$ is the integrated luminosity, $\eta$ \blue{is} the detection
-efficiency and d$\sigma_{\blue{\textrm{UU}}}$ denotes the
+where $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
+efficiency and d$\sigma_{\textrm{UU}}$ denotes the
 cross section for an unpolarised target integrated over both beam charges and
@@
 At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
-These asymmetry amplitudes\blue{,} for an unpolarised target\blue{,} are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
 Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-\blue{where $\alpha_{\textrm{S}}$ is the fine structue constant}.
-\begin{table}[H]
+where $\alpha_{\textrm{S}}$ is the fine structue constant.
+\begin{table}
 \begin{center}
-\resizebox{16cm}{!} {
+\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c|c|c|c|}
 \hline
-Asymmetry Amplitude & Fourier Coefficient& Dominant CFF Dependence & Twist Level  & Relative Suppression \\
+Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
 \hline

### 2011-04-01 frame.tex
Removed blue text

@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS (v0.9)}
+  	\underline{Paper Tag: PDVCS0607 (v1.0)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
-are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a missing-mass event selection technique.
-The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
-Results from \blue{the two} data sets are found to be compatible with each other.
-Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
+are extracted from the H{\sc ermes} data set of 2006-2007 using a missing-mass event selection technique.
+The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from the earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
+Results from the two data sets are found to be compatible with each other.
+Combined results from these data sets are extracted and represent the statistically most precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
 }

### 2011-04-01 results.tex
Removed blue text

@@
 Only the statistical uncertainties were employed in this test.
-\blue{This test revealed no significant evidence for incompatibility between the data sets.} The \blue{beam-helicity and beam-charge} asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
+This test revealed no significant evidence for incompatibility between the data sets.
+The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
 \begin{figure}
@@
 the beam polarisation measurement.
-\blue{Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.} See text for details.
+Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.
+See text for details.
 The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in \blue{Ref.} \cite{Kum09} are shown as solid and dashed lines and amplitude values calculated from fits to data from Ref.~\cite{Gui11} are shown as open crosses.
+Theoretical calculations from the model described in Ref.
+\cite{Kum09} are shown as solid and dashed lines and amplitude values calculated from fits to data from Ref.~\cite{Gui11} are shown as open crosses.
 See text for details.
@@
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-The $A_{C}^{\cos(2\phi)}$ \blue{amplitude} is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
-Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading\blue{-}twist amplitudes.
+The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
+Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.
 
@@
 
-\blue{The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD.
 The model incorporates fits to global deep-inelastic scattering and elastic data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from H{\sc ermes} and Jefferson Lab (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.}
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.
 
-\blue{The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}.
+The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}.
 The extraction of the Compton Form Factors is independent of assumptions made about the shape of the underlying CFFs, but cannot be simply extended beyond the H{\sc ermes} kinematic domain.
-The presented data is well described by the calculations.}
+The presented data is well described by the calculations.
 
-In order to provide more detailed information \blue{that can be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
-No additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.
+In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+There is no observed $-t$ dependence on any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
+No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-04-01 summary.tex
Removed blue text

@@
 
-Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
+Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-\blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}.
-A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
-The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry.
-There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry.
+An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
+A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
+The resulting beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
+The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
+There are also non zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
 Each of the other higher order asymmetry amplitudes are consistent with zero.
 The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
-All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$.
+All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
 No localised features are observed in any particular $t$-bin.

### 2011-04-01 theory.tex
Removed blue text

@@
 \subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
-\caption[DVCS and Bethe Heitler hand bag diagram.]{\blue{(a)}: The DVCS process in
-which an electron/positron (\blue{$e$}) interacts with a quark in the nucleon \ \blue{($p$)} via a virtual photon ($\gamma^\ast$).
+\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
+which an electron/positron ($e$) interacts with a quark in the nucleon ($p$) via a virtual photon ($\gamma^\ast$).
 The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon ($\gamma$).
 The quark is absorbed by the nucleon with fraction $x-\xi$.
-\blue{(b)}: The Bethe-Heitler process which has the same initial and final states as DVCS.}
+(b): The Bethe-Heitler process which has the same initial and final states as DVCS.}
 \label{spin}
@@
 It is through the study of this interference term at H{\sc ermes} that
-useful information for the constraint of certain GPDs can be obtained \blue{\cite{Bel02b}}.
+useful information for the constraint of certain GPDs can be obtained \cite{Bel02b}.
 
@@
 charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
-the nucleon mass\blue{,} and $\phi$ is the
+the nucleon mass, and $\phi$ is the
 azimuthal angle between the scattering and production planes \cite{Tre04}.
@@
 ermes} with an unpolarised target and a polarised electron or positron beam:
-beam-helicity asymmetries and beam-charge asymmetries. \blue{In order to disentangle the DVCS and interference contributions
+beam-helicity asymmetries and beam-charge asymmetries. In order to disentangle the DVCS and interference contributions
 to the cross section via the beam-charge dependence of the
-interference term this paper, as in Ref.~\cite{Air09}, presents} results on the following asymmetries:
+interference term this paper, as in Ref.~\cite{Air09}, presents results on the following asymmetries:
 \begin{align}
@@
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi)} \blue{\textrm{\,\,and}}&
+c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\,\,and}&
 \label{e:aludvcs}
@@
 $\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
-to cross sections taken with beam spin parallel \blue{(anti-parallel)} \blue{to} the
+to cross sections taken with beam spin parallel (anti-parallel) to the
 beam momentum.

### 2011-05-31 experiment_and_data.tex
Updating from collab

@@
 electron and positron beams incident upon an unpolarised hydrogen gas
-target internal to the HERA lepton storage ring at DESY. The integrated
-luminosities of the electron and positron data samples respectively are
+target internal to the \red{H\sc{era}} lepton storage ring at \red{D\sc{esy}}. The integrated
+luminosities of the electron and positron data samples\red{,} respectively\red{,} are
 approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
@@
 The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
-Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35, $W^{2}$ $>$
+Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
+\red{$0.0$\,GeV$^2 < -t < 0.7$\,GeV$^2$,} $W^{2}$ $>$
 9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
@@
 Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon.
-The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
+The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
 This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.
@@
 \end{equation}
-where $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
+where \red{$P_\ell$ is the beam polarisation, }$\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
 efficiency and d$\sigma_{\textrm{UU}}$ denotes the
@@
 \begin{equation}
- \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq \sum^{2}_{n=1}
-A_{\textrm{LU,DVCS}}^{\sin(n\phi)}\sin(n\phi) 
+ \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
+A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
 + \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
@@
 \end{equation}
-where the approximation is due to the truncation of the infinite Fourier series
-caused by the azimuthal dependencies in the denominators from
-Eqs.~\ref{e:alui}-\ref{e:ac}. Only the $\sin(n\phi)$ terms of the
+where the approximation is due to the truncation of the infinite
+Fourier series \red{that would describe the fitted distribution
+  perfectly}. Only the $\sin(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
-are included as both a consistency check for extraneous harmonics caused
-by the denominators in Eqs.~\ref{e:alui}-\ref{e:ac} and as a test of the
-normalisation of the fit. These terms are expected to be small.
+are included as both a consistency check for \red{any off-phase}
+extraneous harmonics \red{in the data} and as a test of the
+normalisation of the fit. These terms are expected to be
+\red{consistent with zero}.
 
@@
 azimuthal distribution function to the data without introducing binning effects in $\phi$.
-Weights are introduced per event in the fitting procedure to account for
+\red{Event w}eights are introduced in the fitting procedure to account for
 luminosity imbalances with respect to the beam charge and polarisation.
@@
 $A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
-coefficients $s_{n}^{W}$ and $c_{n}^{V}$ from the interference and DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The asymmetry amplitudes may also be affected by the lepton propagators and the other $\phi$-dependent terms in the denominators in Eqs.~\ref{e:alui}-\ref{e:ac}.
-The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier coefficients depend on ``$\mathcal{C}$-functions'', each of which is a combination of complex Compton Form Factors.
+coefficients $s_{n}^{W}$ and $c_{n}^{I}$ from the interference and
+DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+may also be affected by the lepton propagators and the other
+$\phi$-dependent terms in the denominators in
+Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier
+coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
+combination of complex Compton Form Factors (CFF).
 A CFF is a convolution of a GPD with a hard scattering kernel.
@@
 $\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
-conditions (where $x_{\textrm{B}}$ and $\frac{t}{4M^2}$ are of order 0.1), to first approximation the
+conditions (where $x_{\textrm{B}}$ and $\frac{\red{-}t}{4M^2}$ are of order 0.1), the
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in Eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ since they
+neglected in Eq.~\ref{Eq_cunp} \red{(in first approximation)} with respect to $\mathcal{H}$ since they
 are kinematically suppressed by an order of magnitude or more.
@@
 $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
-and therefore GPD $H$. Using this dependence, $H$ can be constrained through
+and therefore GPD $H$. \red{Therefore}, $H$ can be constrained through
 measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
@@
 which is bilinear in CFFs.
-However, this amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this \red{twist-3} amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of
 the more complicated dependence on the CFFs and this suppression, it
-will be more difficult to extract useful information for the constraint of GPDs
+\red{is} more difficult to \red{constrain} GPDs
 from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-where $\alpha_{\textrm{S}}$ is the fine structue constant.
+where $\alpha_{\textrm{S}}$ is the\red{strong} constant.
 \begin{table}
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& --
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&\red{kinematic}
 \\
@@
 be extracted from the available data set, the related Fourier coefficients,
- the $\mathcal{C}$-functions, the twist level and the suppression~\cite{Bel02b}.}
+ the $\mathcal{C}$-functions, the twist level and the suppression
+ \red{relative to the leading amplitudes at H\sc{ermes} kinematic conditions}~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-05-31 frame.tex
Updating from collab

@@
 \newcommand{\blue}[1]{{\color{blue}{#1}\color{black}}}
+\newcommand{\red}[1]{{\color{red}{#1}\color{black}}}
+
 \def\desy{{\sc desy}}
@@
 \begin{document}
-\title{Beam-Helicity and Charge Asymmetries \\
+\title{Beam-Helicity and Beam-Charge Asymmetries \\
         in the Bethe-Heitler and DVCS processes on \\
@@
 \abstract{
-Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
+Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
 are extracted from the H{\sc ermes} data set of 2006-2007 using a missing-mass event selection technique.

### 2011-05-31 theory.tex
Updating from collab

@@
 \cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
-the leptoproduction of real photons from a nucleon or nucleus that can be used to constrain GPDs via Compton Form Factors (CFFs).
-Each CFF is a convolution of a hard scattering kernel with a GPD that describes a soft part of the scattering process.
+the leptoproduction of real photons from a nucleon or nucleus that can
+be used to constrain GPDs via Compton Form Factors (CFFs).\red{ A thorough
+desccription of the nucleon in terms of GPDs would allow a description
+of the total angular momentum of partons in the nucleon as wall as a
+longitudinal-momentum dissected transverse spatial map of parton positions.}
 
@@
 fraction $x$ of the nucleon's longitudinal momentum carried by the active
-quark throughout the scattering process; half the difference in the
-change of the fraction of the nucleon's longitudinal momentum carried by the
-active quark at the start and end of the process, written as the skewness
-variable $\xi$; and the square $-Q^2=q^2$ of the four-momentum of the virtual photon that mediates the lepton-proton scattering process. In the Bjorken limit of $Q^2\rightarrow\infty$ with
-fixed $t$, $\xi$ is related to the Bjorken variable
+quark throughout the scattering process; half the difference \red{of
+  the} fraction\red{s} of the nucleon's longitudinal momentum carried
+by the active quark at the start and end of the process, written as
+the skewness $\xi$; and the square $-Q^2=q^2$ of the four-momentum of
+the virtual photon that mediates the lepton-proton scattering
+process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
+$t$, \red{the skewness} $\xi$ is related to the Bjorken variable
 $x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
 $\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
-against $x_{\textrm{B}}$ because there is no consensus on an experimentally
+\red{as a function of} $x_{\textrm{B}}$ because there is no consensus on an experimentally
 observable representation of $\xi$.
@@
 \caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
-which an electron/positron ($e$) interacts with a quark in the nucleon ($p$) via a virtual photon ($\gamma^\ast$).
-The quark is found in the nucleon with longitudinal momentum fraction $x+\xi$ and emits a real photon ($\gamma$).
-The quark is absorbed by the nucleon with fraction $x-\xi$.
-(b): The Bethe-Heitler process which has the same initial and final states as DVCS.}
+which an electron/positron ($e$) interacts with a quark in the nucleon
+($p$) via a virtual photon ($\gamma^\ast$). The quark is found in the
+nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
+photon ($\gamma$). The quark is absorbed by the nucleon with
+longitudinal momentum fraction
+$x-\xi$. (b): The emission of a real photon from the scattering or
+scattered lepton, called the Bethe-Heitler process. It has the same initial and final states as DVCS.}
 \label{spin}
@@
 
-Leptoproduction of real photons ($e\,p\,\rightarrow\,e'\,p'\,\gamma$) can be described in terms of the two experimentally indistinguishable processes shown in Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process, which is the
-emission of a real photon by a quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
+\red{Exclusive l}eptoproduction of real photons
+($e\,p\,\rightarrow\,e'\,p'\,\gamma$) \red{arises from}
+two experimentally indistinguishable processes shown in
+Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
+which is the emission of a real photon by \red{the active} quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
 emission of a Bremsstrahlung photon by the lepton. 
@@
 
-The differential four-fold cross section for the leptoproduction of real photons
-from an unpolarised target can be written \cite{Bel02b}
+The four-fold \red{differential} cross section for the leptoproduction of real photons
+from an unpolarised target can be written \red{as} \cite{Bel02b}
 \begin{center}
@@
 azimuthal angle between the scattering and production planes \cite{Tre04}.
-The scattering amplitude $\tau$ can be written
+The {square of the} scattering amplitude $|\tau|^2$ can be written \red{as}
 \begin{center}
@@
 the DVCS process
-($\tau_{\textrm{DVCS}}$) and the interference term (I). These
-contributions can be written 
+($\tau_{\textrm{DVCS}}$) and the interference term (I) \red{from both processes}. These
+contributions can be written \red{as}
 \begin{equation}
@@
 where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
-of the BH process and $\lambda$ and $e_\ell$ are respectively the
-helicity and unit charge of the lepton beam.  The
+of the BH process\red{,} $\lambda$ \red{is}
+helicity of the lepton beam \red{and $e_\ell$ is the unit charge on
+  the lepton}.  The
 quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
@@
 
-There are two sets of asymmetries that are measured at H{\sc
-ermes} with an unpolarised target and a polarised electron or positron beam:
-beam-helicity asymmetries and beam-charge asymmetries. In order to disentangle the DVCS and interference contributions
-to the cross section via the beam-charge dependence of the
-interference term this paper, as in Ref.~\cite{Air09}, presents results on the following asymmetries:
+\red{T}wo sets of asymmetries measured at H{\sc
+ermes} with an unpolarised target and a polarised electron or positron
+beam \red{are considered here}:
+beam-helicity asymmetries and beam-charge asymmetries. \red{T}his paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
 \begin{align}
@@
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\,\,and}&
+c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\,\,\red{,}and}&
 \label{e:aludvcs}

### 2011-05-31 results.tex
Adding comments from the first circulation

@@
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the imprecision of
+2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
 the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets.
-Only the statistical uncertainties were employed in this test.
+Only the statistical uncertainties were employed in this test \red{as the largest contributions to the systematic uncertainties are largely correlated}.
 This test revealed no significant evidence for incompatibility between the data sets.
@@
 the beam polarisation measurement.
-Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.
+Solid and dashed lines show model calculations from~\cite{Kum09}; calculations \red{from} Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.
 See text for details.
@@
 The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
-The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result.
-This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.
+The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result.
+This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.
 
@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
-The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish in this $-t$ region due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
+The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest \red{magnitude} of any of the amplitudes when extracted in a single bin from the entire data set.
+This amplitude \red{shows} no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must \red{approach zero as $-t$ approaches zero} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude is compatible with zero, as is the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term.
-The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}.
-Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry is} shown in the second row of Fig.~\ref{bsa_xbjrange}.
+\red{Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows} any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
@@
 
-The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from the colliders at H{\sc era} and H{\sc ermes} and Jefferson Lab.
+\red{The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.} The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from \red{H{\sc ermes} and Jefferson Laboratory,} and the collider \red{experiments} at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
-In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data.
+In the model, the $t$ dependence is approximated by a physically motivated Regge dependence.
+The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A \red{of} Jefferson Laboratory; the model fit represented by the dashed curves includes \red{these} data.
 Both fits include the 1996-2005 H{\sc ermes} data.
-The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
+The model incorporates only twist-2 GPDs and so can provide \red{results} only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
 All of the amplitudes are well described by the model.
 
-The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{based on} a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic scattering and elastic data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from H{\sc ermes} and Jefferson Lab (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.
+The model incorporates fits to global deep-inelastic and elastic \red{scattering} data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson \red{Laboratory} (to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well \red{in the H{\sc ermes} kinematic region}, but the projections in the other kinematic variables are not as well described.
 
@@
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-There is no observed $-t$ dependence on any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$.
+There is no observed $-t$ dependence o\red{f} any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in \red{any} of the distinct ranges of $x_{\textrm{B}}$.
 No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-05-31 summary.tex
Adding comments from the first circulation

@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
-A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The resulting beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
-The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
-There are also non zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
-Each of the other higher order asymmetry amplitudes are consistent with zero.
+An analogous set of asymmetry amplitudes \red{was} extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
+A comparison of the amplitudes extracted from these independent data sets \red{has} shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
+The \red{extracted} asymmetry amplitudes show a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
+The beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
+There are non\red{-}zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
+Each of the higher order asymmetry amplitudes \red{is} consistent with zero.
 The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
 All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
-No localised features are observed in any particular $t$-bin.
+No \red{additional} features are observed in any particular $\red{x_{\textrm{B}}}$-bin.
 

### 2011-06-13 background_and_systematic.tex
Clarified the background section including some of the collaborations comments. Mostly cleaned up the structure and made a clear ordering of systematic effects.

@@
 shifts in the missing-mass distributions and various detector and binning
-effects determined as in Refs.~\cite{Air08,Air09}.
-Contributions to the uncertainties on the amplitude measurements arise from background in the data from neutral meson production.
-The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region.
+effects determined in \red{the same manner as in} Refs.~\cite{Air08,Air09}.
 
-Another contribution to the systematic uncertainty comes from the relative shift of the
-missing-mass distributions. There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}. The missing-mass
-distribution is also adjusted for each calorimeter calibration period of data
-collected in 2007 to account for the observed time dependence. One
+The contribution to the uncertainties on the amplitude measurements
+\red{arising} from background in the data from neutral meson
+production \red{is predominantly due to the misidentification of
+  $\pi^0$ mesons}. The procedure is described in detail in
+Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
+the measurements addressed here are given in
+Table~\ref{table_systematic_contributions_0607} for the amplitudes
+extracted in a single bin in the H{\sc ermes} kinematic
+region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
+  $Q^{2}$ projections has this uncertainty included as part of the
+  total systematic uncertainty.}
+
+\red{The} contribution to the systematic uncertainties from the relative shift of the
+missing-mass distributions \red{arises due to} shifts in the
+distributions \red{between} electron and positron data~\cite{Zei09,Bur10}. The
+missing-mass distribution is also adjusted for each calorimeter calibration period of data
+collected in 2007 to account for \red{an} observed time dependence. One
 quarter of the difference between the asymmetries extracted using the standard
 and shifted missing-mass windows is taken as the corresponding systematic
-uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
-which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty.
+uncertainty.
 
 The predominant contribution to the systematic uncertainty arises from detector
-effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
-finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
+effects, including the acceptance of the spectrometer, smearing
+effects due to detector resolution and radiative processes, and
+\red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
 these effects, events were generated using a Monte Carlo simulation of
 the spectrometer that included them. An event
-generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}.
-Asymmetry amplitudes were extracted from these simulated events using the same analysis
-procedure used to extract amplitudes from experimental data. In each kinematic
-bin, the systematic uncertainty was determined as the difference between the
-asymmetry amplitude reconstructed from the simulated data and that
+generator based on the GPD model described in Ref.~\cite{Guz06} was
+used for the simulation because it describes the data well and is
+consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted
+from these simulated events using the same analysis procedure used to
+extract amplitudes from experimental data. In each kinematic bin, the
+systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
 calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
 $Q^{2}$ value for that bin.
+
 The total systematic uncertainty for the 2006-2007 data sample was
 determined for each kinematic bin from the uncertainty contributions of the
-background corrections, detector effects and missing-mass shift
-uncertainties added in quadrature. 
-The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
-which has been eliminated for the 2006-2007 data sample.
-These contributions are summarised in Table
-\ref{table_systematic_contributions_0607}.
+background correction, missing-mass shift, and detector effect
+uncertainties added in quadrature.  The 1996-2005 sample also has a
+systematic uncertainty from misalignment of the
+spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
+  surveying measurements of the spectrometer~\cite{Bur10}. The contribution from
+each uncertainty to each amplitude extracted in a single kinematic bin
+from the 2006-07 data  is summarised in Table
+\ref{table_systematic_contributions_0607}.}
+
+The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
+which is present in the beam-helicity amplitudes and is quoted as an
+independent scale uncertainty. \red{The systematic uncertainty quoted for each
+  amplitude measurement therefore does not include any uncertainty due to the
+  measurement of the beam polarisation.}
 

### 2011-06-14 background_and_systematic.tex
Fixed typos and removed reference to Guidal.

@@
-\section{Background Corrections and Systematic Uncertainties}
+\section{Background Corrections and Systematic Uncertainties for the
+  2006-2007 Data}
 The extracted asymmetry amplitudes are subject to systematic uncertainties that
@@
 production \red{is predominantly due to the misidentification of
-  $\pi^0$ mesons}. The procedure is described in detail in
+  $\pi^0$ mesons}. The procedure \red{for estimating the corresponding
+uncertainty on the measured amplitude values} is described in detail in
 Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
@@
 region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
-  $Q^{2}$ projections has this uncertainty included as part of the
+  $Q^{2}$ projections has this uncertainty, which is estimated at the
+  centre of the relevant kinematic bin, included as part of the
   total systematic uncertainty.}
 
-\red{The} contribution to the systematic uncertainties from the relative shift of the
+\red{The} contribution to the systematic uncertainties\red{of the
+  measured amplitudes} from the relative shift of the
 missing-mass distributions \red{arises due to} shifts in the
@@
 effects, including the acceptance of the spectrometer, smearing
-effects due to detector resolution and radiative processes, and
+effects due to detector resolution and radiative processes \red{during
+  detection, (e.g. of the photon in the calorimeter \cite{Bur10})}, and
 \red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
@@
 systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
-calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
+\red{input} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
 $Q^{2}$ value for that bin.
@@
 The total systematic uncertainty for the 2006-2007 data sample was
-determined for each kinematic bin from the uncertainty contributions of the
-background correction, missing-mass shift, and detector effect
-uncertainties added in quadrature.  The 1996-2005 sample also has a
+determined for each kinematic bin \red{by adding in quadrature the
+  uncertainties arising from the background correction, the
+  missing-mass shifts, and the detector effects}.  The 1996-2005 sample also has a
 systematic uncertainty from misalignment of the
 spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
-  surveying measurements of the spectrometer~\cite{Bur10}. The contribution from
+  surveying measurements~\cite{Bur10}. The contribution from
 each uncertainty to each amplitude extracted in a single kinematic bin
-from the 2006-07 data  is summarised in Table
+from the 2006-2007 data  is summarised in Table
 \ref{table_systematic_contributions_0607}.}
@@
 which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty. \red{The systematic uncertainty quoted for each
+independent scale uncertainty. \red{The systematic uncertainty shown for each
   amplitude measurement therefore does not include any uncertainty due to the
@@
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state. The recoiling proton is not detected and
+resonant state \red{(``associated production'')}. The recoiling proton is not detected and
   the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
-No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal.
-A Monte Carlo calculation based on the parameterisation from Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin.
-The results, denoted associated fraction and labelled ``Assoc.
+No systematic uncertainty is assigned for the contribution from these
+events; they are treated as part of the signal. A Monte Carlo
+calculation based on the parameterisation from Ref.~\cite{Bra76} is
+used to estimate the contribution to the event sample from resonant
+production in each kinematic bin.
+The results, \red{called the associated fractions} and labelled ``Assoc.
 fraction'', are shown in the last row of each figure in the results section.

### 2011-06-14 experiment_and_data.tex
Fixed typos and removed reference to Guidal.

@@
 \section{Experiment and Data Selection}
-The data were collected in 2006 and 2007 with the H{\sc ermes}
+The \red{new} data \red{presented in this work were} collected in 2006 and 2007 with the H{\sc ermes}
 spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
@@
 normalisation of the fit. These terms are expected to be
-\red{consistent with zero}.
+\red{consistent with zero and are found to be so}.
 
@@
 $A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
-coefficients $s_{n}^{W}$ and $c_{n}^{I}$ from the interference and
+coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
 DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
@@
 $\phi$-dependent terms in the denominators in
-Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n}^{W}$ and $c_{n}^{V}$ Fourier
+Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
@@
 Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$.
-Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and levels of suppression.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
 
@@
 \end{center}
-where the kinematic factor $k \propto \sqrt{-t}/Q$ originates from the BH
-propagators. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
+where the \red{definition of the} kinematic factor $k$ \red{is found
+  in Ref.\cite{Bel02b}}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
 written
@@
 are kinematically suppressed by an order of magnitude or more.
-Hence, in this approximation, the behaviour of
+Hence, the behaviour of
 $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
-and therefore GPD $H$. \red{Therefore}, $H$ can be constrained through
+and therefore GPD $H$ can be constrained through
 measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-where $\alpha_{\textrm{S}}$ is the\red{strong} constant.
+where $\alpha_{\textrm{S}}$ is the \red{strong coupling} constant.
 \begin{table}
@@
  the $\mathcal{C}$-functions, the twist level and the suppression
- \red{relative to the leading amplitudes at H\sc{ermes} kinematic conditions}~\cite{Bel02b}.}
+ \red{relative to the leading amplitudes at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-06-14 frame.tex
Fixed typos and removed reference to Guidal.

@@
 Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
-are extracted from the H{\sc ermes} data set of 2006-2007 using a missing-mass event selection technique.
-The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from the earlier data set of 1996-2005 previously analysed in the same manner by the collaboration.
-Results from the two data sets are found to be compatible with each other.
-Combined results from these data sets are extracted and represent the statistically most precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
+are extracted from the H{\sc ermes} data set of 2006-2007 using a
+missing-mass event selection technique. The beam-charge asymmetry
+amplitudes extracted from the new data set are more
+\red{statistically} precise than those extracted from the earlier data
+set of 1996-2005 previously analysed in the same manner by the
+collaboration. Results from the two data sets are found to be
+compatible with each other. Combined results from these data sets are
+extracted and represent the most \red{statistically} precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
 }

### 2011-06-14 results.tex
Fixed typos and removed reference to Guidal.

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from \red{the} previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
 \ref{release_bsa_0607} and \ref{release_bca_0607}.
@@
 the beam polarisation measurement.
-Solid and dashed lines show model calculations from~\cite{Kum09}; calculations \red{from} Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses.
+Solid and dashed lines show model calculations from~\cite{Kum09}; calculations \red{from} Ref.~\cite{Liu11} are shown as dashed-dotted lines.
 See text for details.
@@
 Theoretical calculations from the model described in Ref.
-\cite{Kum09} are shown as solid and dashed lines and amplitude values calculated from fits to data from Ref.~\cite{Gui11} are shown as open crosses.
+\cite{Kum09} are shown as solid and dashed lines.
 See text for details.
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result.
-This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.
+This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 \red{than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit}.
 
@@
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
+\red{Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
+4 were completed.
+The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.}
 
@@
 Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.
+\red{The systematic uncertainties are extimated in a similar procedure as for those for the beam-helicity asymmetries.}
 
@@
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
-In the model, the $t$ dependence is approximated by a physically motivated Regge dependence.
+In th\red{is} model, the $t$ dependence is approximated by a physically motivated Regge dependence.
 The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A \red{of} Jefferson Laboratory; the model fit represented by the dashed curves includes \red{these} data.
@@
 
-The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted from experimental data (including the H{\sc ermes} data from 1996-2005)~\cite{Gui11}.
-The extraction of the Compton Form Factors is independent of assumptions made about the shape of the underlying CFFs, but cannot be simply extended beyond the H{\sc ermes} kinematic domain.
-The presented data is well described by the calculations.
-
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.

### 2011-06-14 summary.tex
Fixed typos and removed reference to Guidal.

@@
 Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
-These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}.
-An analogous set of asymmetry amplitudes \red{was} extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
+These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period\red{s} of H{\sc ermes}.
+Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
 A comparison of the amplitudes extracted from these independent data sets \red{has} shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.

### 2011-06-14 theory.tex
Fixed typos and removed reference to Guidal.

@@
 be used to constrain GPDs via Compton Form Factors (CFFs).\red{ A thorough
-desccription of the nucleon in terms of GPDs would allow a description
-of the total angular momentum of partons in the nucleon as wall as a
+desccription of the nucleon in terms of GPDs would allow the deduction
+of the total angular momentum of partons in the nucleon and the
+construction of a 
 longitudinal-momentum dissected transverse spatial map of parton positions.}
@@
 longitudinal momentum fraction
-$x-\xi$. (b): The emission of a real photon from the scattering or
-scattered lepton, called the Bethe-Heitler process. It has the same initial and final states as DVCS.}
+$x-\xi$. (b): \red{The Bethe-Hietler process, i.e. the} emission of a real photon from the scattering or
+scattered lepton. It has the same initial and final states as DVCS.}
 \label{spin}
@@
 \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
-\left(c_{0}^{
-\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
+\left(c_{0,\textrm{unp}}^{
+\textrm{BH}} + \sum_{n=1}^2 c_{n,\textrm{unp}}^{\textrm{BH}}\cos(n\phi)\right),
 \label{e:tbh}
@@
  \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
-K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
+K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
 \sum_{n=1}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
-s_{1}^{\textrm{DVCS}}\sin\phi\right),
+c_{n,\textrm{unp}}^{\textrm{DVCS}}\cos(n\phi) + \lambda
+s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right),
 \label{e:tdvcs}
@@
 \hspace{3.7cm} \textrm{I} = \frac{- e_\ell
-K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
+K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
 I}}
 +
-\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
-s_{n}^{\textrm{I}}\sin(n\phi)\right),
+\sum_{n=1}^3 c_{n,\textrm{unp}}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
+s_{n,\textrm{unp}}^{\textrm{I}}\sin(n\phi)\right),
 \label{e:ti}
@@
 where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
-of the BH process\red{,} $\lambda$ \red{is}
+of the BH process\red{,} $\lambda$ \red{is the}
 helicity of the lepton beam \red{and $e_\ell$ is the unit charge on
@@
 the target rest frame. A full
-explanation of the Fourier coefficients [$c_n^V,s_n^W$]
+explanation of the Fourier coefficients [$c_{n,\textrm{unp}}^V,s_{n,\textrm{unp}}^W$]
 ($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be
@@
 
-The analysis presented here additionally includes a larger,
+\red{Compared to the analysis in ref.~\cite{Air09}, t}he analysis presented here additionally includes a larger,
 independent data set taken during the years 2006 and 2007 after the
-experiment was upgraded in the target region. The results in this paper do not make use of any of the information from the
-upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will
-be published by H{\sc ermes}.
+experiment was upgraded in the target region. \red{The work covered
+  in this publication combines the data taken in 1996-2005 with this
+  new data set to produce a comprehensive set of asymmetry results.}
+The results in this paper make use \red{of} a missing-mass technique for event
+selection \red{and} represent the largest DVCS data set that will be published by H{\sc ermes}.

### 2011-06-28 results.tex
updated figures

@@
 \begin{center}
-\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
+\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster}
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
@@
 \begin{center}
- \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
+ \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc}
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
+ \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_update}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
+    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.

### 2011-06-28 results.tex
updated 2d plots from cluster

@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
+ \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_cluster}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_release_pic_update}
+    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_9607_pic_cluster}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.

### 2011-07-06 results_dual.tex
dual version of the paper

--- 2011-06-14 results.tex
@@
 \begin{center}
-\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
+\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
@@
 \begin{center}
- \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
+ \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual}
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
+ \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_update_withassoc}
+    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
+ \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_release_pic_update}
+    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_dual}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
@@
 The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
-The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
+The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result.

### 2011-07-08 background_and_systematic_dual.tex
dual version of the paper
minor text and plot updates

--- 2011-06-14 background_and_systematic.tex
@@
 the spectrometer that included them. An event
-generator based on the GPD model described in Ref.~\cite{Guz06} was
+generator based on the GPD model described in Ref.~\cite{Van99,Goe01} was
 used for the simulation because it describes the data well and is
@@
   \hline
-  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.209  $\pm$  0.026  $\pm$   0.026 & 0.005 & 0.005 & 0.025 & & 0.026 \\
+  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.055 \\
   \hline
-  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & -0.015  $\pm$  0.026  $\pm$  0.008 & 0.004 & 0.007 & 0.001 & & 0.008 \\
+  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  $\pm$  0.003 & 0.002 & 0.002 & 0.001 & & 0.003 \\
   \hline
-  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.025  $\pm$   0.005 & 0.005 & 0.001 & 0.002 & & 0.006 \\
+  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  $\pm$   0.003 & 0.003 & 0.001 & 0.001 & & 0.003 \\
   \hline
   \hline
-  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.039 $\pm$  0.004 $\pm$  0.008 & 0.001 & 0.004 & 0.007 & & 0.008 \\
+  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 $\pm$  0.011 & 0.001 & 0.003 & 0.010 & & 0.011 \\
   \hline
-  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.003 & 0.002 & 0.001 & 0.002 & & 0.003 \\
+  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.002 & 0.002 & 0.001 & 0.001 & & 0.002 \\
   \hline
-  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.007  $\pm$  0.006  $\pm$   0.002 & 0.001 & 0.001 & 0.001 & & 0.002 \\
+  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005  $\pm$   0.014 & 0.001 & 0.000 & 0.014 & & 0.014 \\
   \hline
-  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.009  $\pm$   0.006   $\pm$   0.001 & 0.000 & 0.001 & 0.001 & & 0.001 \\
+  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005   $\pm$   0.004 & 0.000 & 0.001 & 0.003 & & 0.004 \\
   \hline

### 2011-07-08 results.tex
minor text and plot updates

@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_update}
+ \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_update2}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_cluster}
+ \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update_2}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_eml_par13_bin6_9607_pic_cluster}
+    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_cluster}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.

### 2011-07-22 background_and_systematic_dual.tex
Implemented Andy's comments to v1.1

@@
 shifts in the missing-mass distributions and various detector and binning
-effects determined in \red{the same manner as in} Refs.~\cite{Air08,Air09}.
+effects determined in the same manner as in refs.~\cite{Air08,Air09}.
 
 The contribution to the uncertainties on the amplitude measurements
-\red{arising} from background in the data from neutral meson
-production \red{is predominantly due to the misidentification of
-  $\pi^0$ mesons}. The procedure \red{for estimating the corresponding
-uncertainty on the measured amplitude values} is described in detail in
-Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
-the measurements addressed here are given in
-Table~\ref{table_systematic_contributions_0607} for the amplitudes
-extracted in a single bin in the H{\sc ermes} kinematic
-region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
-  $Q^{2}$ projections has this uncertainty, which is estimated at the
-  centre of the relevant kinematic bin, included as part of the
-  total systematic uncertainty.}
+arising from background in the data from neutral meson
+production is predominantly due to the failure to identify one photon from the decay of $\pi^0$ mesons. The procedure for estimating the corresponding
+uncertainty on the measured amplitude values is described in detail in
+refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
+  $Q^{2}$ projections has this uncertainty estimated at the
+  centre of the relevant kinematic bin \red{and} included as part of the
+  total systematic uncertainty.
 
-\red{The} contribution to the systematic uncertainties\red{of the
-  measured amplitudes} from the relative shift of the
-missing-mass distributions \red{arises due to} shifts in the
-distributions \red{between} electron and positron data~\cite{Zei09,Bur10}. The
-missing-mass distribution is also adjusted for each calorimeter calibration period of data
-collected in 2007 to account for \red{an} observed time dependence. One
+\red{A} contribution to the systematic uncertainties of the
+  measured amplitudes \red{arises} from shift\red{s in}  the
+missing-mass distributions\red{.
+Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}.
+The missing-mass distribution is also adjusted for each calorimeter calibration period of data
+collected in 2007 to account for an observed time dependence. One
 quarter of the difference between the asymmetries extracted using the standard
@@
 effects, including the acceptance of the spectrometer, smearing
-effects due to detector resolution and radiative processes \red{during
-  detection, (e.g. of the photon in the calorimeter \cite{Bur10})}, and
-\red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
-these effects, events were generated using a Monte Carlo simulation of
-the spectrometer that included them. An event
-generator based on the GPD model described in Ref.~\cite{Van99,Goe01} was
-used for the simulation because it describes the data well and is
-consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted
+effects due to detector resolution and radiative processes during
+  detection, (e.g. of the photon in the calorimeter \cite{Bur10}), and
+the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
+An event
+generator based on the GPD model described in ref.~\cite{Van99,Goe01} was
+used for the simulation because it describes the data well and \red{was employed in r}ef.~\cite{Air09}. Asymmetry amplitudes were extracted
 from these simulated events using the same analysis procedure used to
@@
 systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
-\red{input} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
+input from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
 $Q^{2}$ value for that bin.
@@
 The total systematic uncertainty for the 2006-2007 data sample was
-determined for each kinematic bin \red{by adding in quadrature the
+determined for each kinematic bin by adding in quadrature the
   uncertainties arising from the background correction, the
-  missing-mass shifts, and the detector effects}.  The 1996-2005 sample also has a
+  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
 systematic uncertainty from misalignment of the
-spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
+spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
   surveying measurements~\cite{Bur10}. The contribution from
@@
 from the 2006-2007 data  is summarised in Table
-\ref{table_systematic_contributions_0607}.}
+\ref{table_systematic_contributions_0607}.
 
@@
 which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty. \red{The systematic uncertainty shown for each
+independent scale uncertainty. The systematic uncertainty shown for each
   amplitude measurement therefore does not include any uncertainty due to the
-  measurement of the beam polarisation.}
+  measurement of the beam polarisation.
 
@@
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state \red{(``associated production'')}. The recoiling proton is not detected and
-  the calorimeter resolution does not allow separation of the latter events from rest of the data sample.
+resonant state (``associated production''). The recoiling proton is not detected and
+  the calorimeter resolution does not allow separation of the latter events from \red{the} rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
 events; they are treated as part of the signal. A Monte Carlo
-calculation based on the parameterisation from Ref.~\cite{Bra76} is
+calculation based on the parameterisation from ref.~\cite{Bra76} is
 used to estimate the contribution to the event sample from resonant
 production in each kinematic bin.
-The results, \red{called the associated fractions} and labelled ``Assoc.
+The results, called the associated fractions and labelled ``Assoc.
 fraction'', are shown in the last row of each figure in the results section.
 The method used to perform this estimation is described in detail in
-Ref.~\cite{Air08}.
+ref.~\cite{Air08}.
 

### 2011-07-22 experiment_and_data.tex
Implemented Andy's comments to v1.1

@@
 \section{Experiment and Data Selection}
-The \red{new} data \red{presented in this work were} collected in 2006 and 2007 with the H{\sc ermes}
+The new data presented in this work were collected in 2006 and 2007\red{. As in ref.~\cite{Air09}, the data were collected} with the H{\sc ermes}
 spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
 electron and positron beams incident upon an unpolarised hydrogen gas
-target internal to the \red{H\sc{era}} lepton storage ring at \red{D\sc{esy}}. The integrated
-luminosities of the electron and positron data samples\red{,} respectively\red{,} are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in Ref.~\cite{Air09}.
+target internal to the H\sc{era} lepton storage ring at {D\sc{esy}. The integrated luminosities of the electron and positron data samples, respectively, are
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult
-Refs.~\cite{Zei09,Bur10} for more details.
+refs.~\cite{Zei09,Bur10} for more details.
 
@@
 Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
-\red{$0.0$\,GeV$^2 < -t < 0.7$\,GeV$^2$,} $W^{2}$ $>$
+$0.0$\,GeV$^2 < -t < 0.7$\,GeV$^2$, $W^{2}$ $>$
 9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
@@
 Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon.
-The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}.
+The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in ref.~\cite{Air09}.
 This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.
@@
 \end{equation}
-where \red{$P_\ell$ is the beam polarisation, }$\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
+where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
 efficiency and d$\sigma_{\textrm{UU}}$ denotes the
@@
 where the approximation is due to the truncation of the infinite
-Fourier series \red{that would describe the fitted distribution
-  perfectly}. Only the $\sin(n\phi)$ terms of the
+Fourier series that would describe the fitted distribution
+  perfectly. Only the $\sin(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
-are included as both a consistency check for \red{any off-phase}
-extraneous harmonics \red{in the data} and as a test of the
+are included as both a consistency check for any off-phase
+extraneous harmonics in the data and as a test of the
 normalisation of the fit. These terms are expected to be
-\red{consistent with zero and are found to be so}.
+consistent with zero and are found to be so.
 
@@
 extract the asymmetry amplitudes in each kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-This method, described in Ref.~\cite{Air08}, fits the expected
+This method, described in ref.~\cite{Air08}, fits the expected
 azimuthal distribution function to the data without introducing binning effects in $\phi$.
-\red{Event w}eights are introduced in the fitting procedure to account for
+Event weights are introduced in the fitting procedure to account for
 luminosity imbalances with respect to the beam charge and polarisation.
@@
 Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.
-The access from each asymmetry amplitude to a GPD is called twist-$n$ depending upon the part of the twist-decomposed cross section in which the amplitude appears.
 Leading twist is twist-2.
@@
 \end{center}
-where the \red{definition of the} kinematic factor $k$ \red{is found
-  in Ref.\cite{Bel02b}}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
+where the definition of the kinematic factor $k$ is found
+  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
 written
@@
 $\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
-conditions (where $x_{\textrm{B}}$ and $\frac{\red{-}t}{4M^2}$ are of order 0.1), the
+conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in Eq.~\ref{Eq_cunp} \red{(in first approximation)} with respect to $\mathcal{H}$ since they
+neglected in Eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
 are kinematically suppressed by an order of magnitude or more.
@@
 upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes enter the cross section at a higher
-twist level (see Table~\ref{tab_amplitudes}).
+However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes \red{are} higher
+twist \red{quantities} (see Table~\ref{tab_amplitudes}).
 
@@
 which is bilinear in CFFs.
-However, this \red{twist-3} amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of
 the more complicated dependence on the CFFs and this suppression, it
-\red{is} more difficult to \red{constrain} GPDs
-from the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
+is more difficult to constrain GPDs
+\red{via} the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
 kinematically-unsuppressed leading-twist amplitudes.
@@
 $c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
-$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. This
-$\mathcal{C}$-function receives contributions from both the BH and DVCS
-processes and therefore depends on $F_{1}$, $F_{2}$ and CFFs. Although the CFFs
+$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. Although the CFFs
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-where $\alpha_{\textrm{S}}$ is the \red{strong coupling} constant.
+where $\alpha_{\textrm{S}}$ is the strong coupling constant.
 \begin{table}
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&\red{kinematic}
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&kinematic
 \\
@@
  the $\mathcal{C}$-functions, the twist level and the suppression
- \red{relative to the leading amplitudes at H{\sc ermes} kinematic conditions}~\cite{Bel02b}.}
+ relative to the leading amplitudes at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
 \label{tab_amplitudes}

### 2011-07-22 frame_dual.tex
minor text and plot updates
Implemented Andy's comments to v1.1

--- 2011-06-14 frame.tex
@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v1.0)}
+  	\underline{Paper Tag: PDVCS0607 (v1.2)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 amplitudes extracted from the new data set are more
-\red{statistically} precise than those extracted from the earlier data
+precise than those extracted from the earlier data
 set of 1996-2005 previously analysed in the same manner by the
@@
 \include{experiment_and_data}
-\include{background_and_systematic}
-\include{results}
+\include{background_and_systematic_dual}
+\include{results_dual}
 \include{summary}
-\include{append}
+\include{append_dual}
 \bibliographystyle{natbib}

### 2011-07-22 results_dual.tex
Implemented Andy's comments to v1.1

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from \red{the} previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
-\ref{release_bsa_0607} and \ref{release_bca_0607}.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
+2006-2007 data respectively is present in the amplitudes due to the \red{imprecision} of
 the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 
-A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets.
-Only the statistical uncertainties were employed in this test \red{as the largest contributions to the systematic uncertainties are largely correlated}.
+A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from \red{the two} data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated.
 This test revealed no significant evidence for incompatibility between the data sets.
@@
 the beam polarisation measurement.
-Solid and dashed lines show model calculations from~\cite{Kum09}; calculations \red{from} Ref.~\cite{Liu11} are shown as dashed-dotted lines.
+Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines.
 See text for details.
@@
 The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
-The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result.
-This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 \red{than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit}.
+The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
+This resemblance to the 2006-2007 result is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit.
 
@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
-The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest \red{magnitude} of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude \red{shows} no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must \red{approach zero as $-t$ approaches zero} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
+The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry is} shown in the second row of Fig.~\ref{bsa_xbjrange}.
-\red{Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows} any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}.
+Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
-\red{Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
+Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
 4 were completed.
-The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.}
+The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.
 
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}.
+The systematic uncertainties are estimated in a similar procedure as for those for the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is a relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
-These amplitudes diverge with opposite sign from zero at increasing values of $-t$ but they
+There is a\red{n expected} relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
+These amplitudes \red{are found to} diverge with opposite sign from zero at increasing values of $-t$ but they
 have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
@@
 Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.
-\red{The systematic uncertainties are extimated in a similar procedure as for those for the beam-helicity asymmetries.}
 
-\red{The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.} The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from \red{H{\sc ermes} and Jefferson Laboratory,} and the collider \red{experiments} at H{\sc era}.
+The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.
+The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
-In th\red{is} model, the $t$ dependence is approximated by a physically motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A \red{of} Jefferson Laboratory; the model fit represented by the dashed curves includes \red{these} data.
+In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
+The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.
-The model incorporates only twist-2 GPDs and so can provide \red{results} only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
-All of the amplitudes are well described by the model.
+The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
+All of the \red{relevant} amplitudes \red{reported here} are well described by the model.
 
-The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{based on} a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
-The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic \red{scattering} data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson \red{Laboratory} (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well \red{in the H{\sc ermes} kinematic region}, but the projections in the other kinematic variables are not as well described.
+The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{from a fit} based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The ``Regge'' term \red{is extended to include} contributions that determine the $t$-dependence of the corresponding GPD.
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson Laboratory (to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude \red{reported here} well, but the projections in the other kinematic variables are not as well described.
 
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-There is no observed $-t$ dependence o\red{f} any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in \red{any} of the distinct ranges of $x_{\textrm{B}}$.
+There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.
 No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-07-22 summary.tex
Implemented Andy's comments to v1.1

@@
 Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
-These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period\red{s} of H{\sc ermes}.
+These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
 Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
-A comparison of the amplitudes extracted from these independent data sets \red{has} shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The \red{extracted} asymmetry amplitudes show a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
-The beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration.
-There are non\red{-}zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
-Each of the higher order asymmetry amplitudes \red{is} consistent with zero.
+A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
+\red{The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}.
+There is} a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
+There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
+Each of the higher order asymmetry amplitudes is consistent with zero.
 The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
 All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
-No \red{additional} features are observed in any particular $\red{x_{\textrm{B}}}$-bin.
+No additional features are observed in any particular $\red{x_{\textrm{B}}}$-bin.
 

### 2011-07-22 theory.tex
Implemented Andy's comments to v1.1

@@
 the leptoproduction of real photons from a nucleon or nucleus that can
-be used to constrain GPDs via Compton Form Factors (CFFs).\red{ A thorough
+be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
 desccription of the nucleon in terms of GPDs would allow the deduction
-of the total angular momentum of partons in the nucleon and the
-construction of a 
-longitudinal-momentum dissected transverse spatial map of parton positions.}
+of the total angular momentum of partons in the nucleon\red{,} and the
+construction of a longitudinal-momentum\red{-}dissected transverse spatial map of parton positions.
 
@@
 fraction $x$ of the nucleon's longitudinal momentum carried by the active
-quark throughout the scattering process; half the difference \red{of
-  the} fraction\red{s} of the nucleon's longitudinal momentum carried
+quark throughout the scattering process; half the difference of
+  the fractions of the nucleon's longitudinal momentum carried
 by the active quark at the start and end of the process, written as
@@
 process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
-$t$, \red{the skewness} $\xi$ is related to the Bjorken variable
+$t$, the skewness $\xi$ is related to the Bjorken variable
 $x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
 $\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
-\red{as a function of} $x_{\textrm{B}}$ because there is no consensus on an experimentally
-observable representation of $\xi$.
+as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$.
 
@@
 
-\red{Exclusive l}eptoproduction of real photons
-($e\,p\,\rightarrow\,e'\,p'\,\gamma$) \red{arises from}
+Exclusive leptoproduction of real photons
+($e\,p\,\rightarrow\,e'\,p'\,\gamma$) arises from
 two experimentally indistinguishable processes shown in
 Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by \red{the active} quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
+which is the emission of a real photon by \red{the struck} quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
 emission of a Bremsstrahlung photon by the lepton. 
@@
 
-The four-fold \red{differential} cross section for the leptoproduction of real photons
-from an unpolarised target can be written \red{as} \cite{Bel02b}
+The four-fold differential cross section for the leptoproduction of real photons
+from an unpolarised target can be written as \cite{Bel02b}
 \begin{center}
@@
 azimuthal angle between the scattering and production planes \cite{Tre04}.
-The {square of the} scattering amplitude $|\tau|^2$ can be written \red{as}
+The {square of the} scattering amplitude $|\tau|^2$ can be written as
 \begin{center}
@@
 ($\tau_{\textrm{DVCS}}$) and the interference term (I) \red{from both processes}. These
-contributions can be written \red{as}
+contributions can be written as
 \begin{equation}
@@
 of the BH process\red{,} $\lambda$ \red{is the}
-helicity of the lepton beam \red{and $e_\ell$ is the unit charge on
-  the lepton}.  The
+helicity of the lepton beam and $e_\ell$ is the unit charge on
+  the lepton.  The
 quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
@@
 explanation of the Fourier coefficients [$c_{n,\textrm{unp}}^V,s_{n,\textrm{unp}}^W$]
-($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be
-found in
-Ref.~\cite{Bel02b}.
+($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be found in ref.~\cite{Bel02b}.
 
-\red{T}wo sets of asymmetries measured at H{\sc
+Two sets of asymmetries measured at H{\sc
 ermes} with an unpolarised target and a polarised electron or positron
-beam \red{are considered here}:
-beam-helicity asymmetries and beam-charge asymmetries. \red{T}his paper, as Ref.~\cite{Air09}, presents results on the following asymmetries:
+beam are considered here:
+beam-helicity asymmetries and beam-charge asymmetries. This paper, \red{like} ref.~\cite{Air09}, presents results on the following asymmetries:
 \begin{align}
@@
 
-\red{Compared to the analysis in ref.~\cite{Air09}, t}he analysis presented here additionally includes a larger,
+Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger,
 independent data set taken during the years 2006 and 2007 after the
-experiment was upgraded in the target region. \red{The work covered
+experiment was upgraded in the target region. The work covered
   in this publication combines the data taken in 1996-2005 with this
-  new data set to produce a comprehensive set of asymmetry results.}
-The results in this paper make use \red{of} a missing-mass technique for event
-selection \red{and} represent the largest DVCS data set that will be published by H{\sc ermes}.
+  new data set to produce \red{the largest DVCS data set that will be published by H{\sc ermes}.}
+The results in this paper make use of \red{the same} missing-mass technique for event selection \red{as was used in ref.~\cite{Air09}.}

### 2011-07-22 experiment_and_data.tex
Fixed bugs in update

@@
 electron and positron beams incident upon an unpolarised hydrogen gas
-target internal to the H\sc{era} lepton storage ring at {D\sc{esy}. The integrated luminosities of the electron and positron data samples, respectively, are
+target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
 approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in ref.~\cite{Air09}.

### 2011-07-22 frame_dual.tex
Fixed bugs in update

@@
 compatible with each other. Combined results from these data sets are
-extracted and represent the most \red{statistically} precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
+extracted and represent the most statistically precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
 }

### 2011-07-22 results_dual.tex
Fixed bugs in update

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca0607}.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.

### 2011-07-22 theory.tex
Fixed bugs in update

@@
 longitudinal momentum fraction
-$x-\xi$. (b): \red{The Bethe-Hietler process, i.e. the} emission of a real photon from the scattering or
+$x-\xi$. (b): The Bethe-Hietler process, i.e. the emission of a real photon from the scattering or
 scattered lepton. It has the same initial and final states as DVCS.}
@@
 the DVCS process
-($\tau_{\textrm{DVCS}}$) and the interference term (I) \red{from both processes}. These
+($\tau_{\textrm{DVCS}}$) and the interference term (I) from both processes. These
 contributions can be written as
@@
 where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
-of the BH process\red{,} $\lambda$ \red{is the}
+of the BH process, $\lambda$ is the
 helicity of the lepton beam and $e_\ell$ is the unit charge on

### 2011-07-22 background_and_systematic_dual.tex
Reworded some of Andy's suggestions and finalised the paper for the next meeting.

@@
 arising from background in the data from neutral meson
-production is predominantly due to the failure to identify one photon from the decay of $\pi^0$ mesons. The procedure for estimating the corresponding
+production is \red{predominantly due to the failure to identify one photon from the decay of $\pi^0$ mesons}. The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
 
-The predominant contribution to the systematic uncertainty arises from detector
+The predominant contributio to the systematic uncertainty arises from detector
 effects, including the acceptance of the spectrometer, smearing
@@
 systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
-input from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
+\red{calculated} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
 $Q^{2}$ value for that bin.
@@
 which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty. The systematic uncertainty shown for each
-  amplitude measurement therefore does not include any uncertainty due to the
-  measurement of the beam polarisation.
+independent scale uncertainty \red{without consideration in the other presented uncertainties.}
 

### 2011-07-22 experiment_and_data.tex
Reworded some of Andy's suggestions and finalised the paper for the next meeting.

@@
  the $\mathcal{C}$-functions, the twist level and the suppression
- relative to the leading amplitudes at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
+ relative to the leading amplitudes at H{\sc ermes} kinematic conditions~\cite{Bel02b}.
+\red{Kinematic denotes a leading twist object that is kinematically supressed relative to the least-suppressed object in the set.}}
 \label{tab_amplitudes}

### 2011-07-22 results_dual.tex
Reworded some of Andy's suggestions and finalised the paper for the next meeting.

@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance to the 2006-2007 result is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit.
 
@@
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
-Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
+Monte Carlo events propogated through simulations of the two experimental \red{arrangements} are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
 4 were completed.
@@
 The ``Regge'' term \red{is extended to include} contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson Laboratory (to describe the skewness dependence).
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and \red{DVCS} data from Jefferson Laboratory (to describe the skewness dependence).
 The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude \red{reported here} well, but the projections in the other kinematic variables are not as well described.

### 2011-07-26 background_and_systematic_dual.tex
Update text

@@
   measured amplitudes \red{arises} from shift\red{s in}  the
-missing-mass distributions\red{.
-Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}.
-The missing-mass distribution is also adjusted for each calorimeter calibration period of data
-collected in 2007 to account for an observed time dependence. One
+missing-mass distributions\red{. Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}. One
 quarter of the difference between the asymmetries extracted using the standard
@@
 effects due to detector resolution and radiative processes during
-  detection, (e.g. of the photon in the calorimeter \cite{Bur10}), and
+  detection, and
 the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.

### 2011-07-26 experiment_and_data.tex
Update text

--- 2011-07-22 experiment_and_data.tex
@@
 The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in ref.~\cite{Air09}.
-This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.
+This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.
 
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&kinematic
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
 \\
@@
  the $\mathcal{C}$-functions, the twist level and the suppression
- relative to the leading amplitudes at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
+ relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
 \label{tab_amplitudes}

### 2011-07-26 results_dual.tex
Update text

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}.
-Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
-Monte Carlo events propogated through simulations of the two experimental \red{arrangements} are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
-4 were completed.
-The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.
+Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry} amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry \red{amplitude} are compatible with zero, and neither asymmetry \red{amplitude} shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations \red{as explained in section~4}.
+The missing-mass uncertainty for the combined data set \red{was} calculated \red{using} the procedure described in that section and the results \red{were} added in quadrature.
 
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated in a similar procedure as for those for the beam-helicity asymmetries.
+The systematic uncertainties are estimated in \red{the same} procedure as for those for the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
@@
 
-The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.
+The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the \red{average value} of the kinematic bins used for the data extractions.
 The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.

### 2011-07-26 theory.tex
Update text

@@
 be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
-desccription of the nucleon in terms of GPDs would allow the deduction
+description of the nucleon in terms of GPDs would allow the deduction
 of the total angular momentum of partons in the nucleon\red{,} and the
@@
 longitudinal momentum fraction
-$x-\xi$. (b): The Bethe-Hietler process, i.e. the emission of a real photon from the scattering or
+$x-\xi$. (b): The Bethe-H\red{ei}tler process, i.e. the emission of a real photon from the scattering or
 scattered lepton. It has the same initial and final states as DVCS.}

### 2011-07-28 bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual.C
added root macros

@@ -1,0 +1,2384 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Jul 27 13:30:20 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",-0,0,1200,1000);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetFillStyle(4000);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.35);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.425);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.125);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0225095);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.825,0.25,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2,-0.15,2,0.15);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(2);
+   pad1_1->SetLeftMargin(0.5);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
[…]

### 2011-07-28 bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C

@@ -1,0 +1,2193 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Jul  6 10:40:22 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",0,0,1200,1000);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetFillStyle(4000);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.35);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.425);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.125);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0225095);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.825,0.25,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2,-0.15,2,0.15);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(2);
+   pad1_1->SetLeftMargin(0.5);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
[…]

### 2011-07-28 bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_dual.C

@@ -1,0 +1,1524 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Jul  6 14:13:57 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",-0,0,1400,1000);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.25);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.25);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.0555556);
+   pad1->SetRightMargin(0.0167598);
+   pad1->SetTopMargin(0.026009);
+   pad1->SetBottomMargin(0.0650226);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.746749,0.364784,0.973991);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2.43553,-0.35,-0.09691,0.25);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(0);
+   pad1_1->SetLogx();
+   pad1_1->SetLeftMargin(0.166667);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
[…]

### 2011-07-28 bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual.C

@@ -1,0 +1,1720 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Jul  6 10:30:27 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",0,0,1200,800);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.35);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.45);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.125);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0281369);
+   pad1->SetBottomMargin(0.126616);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.7,0.25,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2,-0.65,2,0.25);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(2);
+   pad1_1->SetLeftMargin(0.5);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
+   TH1 *hframe = new TH1F("hframe","",3,0,2);
[…]

### 2011-07-28 bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual.C

@@ -1,0 +1,1767 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Jul 27 13:18:47 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",-0,0,1200,800);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.35);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.45);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.125);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0281369);
+   pad1->SetBottomMargin(0.126616);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.7,0.25,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2,-0.65,2,0.25);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(2);
+   pad1_1->SetLeftMargin(0.5);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
[…]

### 2011-07-28 bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual.C

@@ -1,0 +1,1125 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Tue Jul  5 12:47:19 2011) by ROOT version5.14/00
+   TCanvas *combined = new TCanvas("combined", "",-0,0,1300,900);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.2);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.25);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.0784314);
+   pad1->SetRightMargin(0.0171544);
+   pad1->SetTopMargin(0.0355092);
+   pad1->SetBottomMargin(0.0887731);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.672585,0.379903,0.964491);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2.6454,-0.45,-0.09691,0.3);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(0);
+   pad1_1->SetLogx();
+   pad1_1->SetLeftMargin(0.235294);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
[…]

### 2011-08-08 background_and_systematic_dual.tex
Added comment updates from Caro, Delia and WDN.
Chnaged the plotting amcro to equalize sizes between legend texts
Changed the first picture

@@
 arising from background in the data from neutral meson
-production is \red{predominantly due to the failure to identify one photon from the decay of $\pi^0$ mesons}. The procedure for estimating the corresponding
+production is \red{predominantly due to the failure to identify one of
+  the two photons from the decay of produeced neutral mesons}. The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
   $Q^{2}$ projections has this uncertainty estimated at the
-  centre of the relevant kinematic bin \red{and} included as part of the
+  centre of the relevant kinematic bin and included as part of the
   total systematic uncertainty.
 
-\red{A} contribution to the systematic uncertainties of the
-  measured amplitudes \red{arises} from shift\red{s in}  the
-missing-mass distributions\red{. Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}. One
+A contribution to the systematic uncertainties of the
+  measured amplitudes arises from shifts in  the
+missing-mass distributions. Such shifts appear in a comparison of electron and positron data~\cite{Zei09,Bur10}. One
 quarter of the difference between the asymmetries extracted using the standard
@@
 
-The predominant contributio to the systematic uncertainty arises from detector
+The predominant contribution to the systematic uncertainty arises from detector
 effects, including the acceptance of the spectrometer, smearing
@@
 generator based on the GPD model described in ref.~\cite{Van99,Goe01} was
-used for the simulation because it describes the data well and \red{was employed in r}ef.~\cite{Air09}. Asymmetry amplitudes were extracted
+used for the simulation because it describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
 from these simulated events using the same analysis procedure used to
@@
 systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
-\red{calculated} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
+calculated from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
 $Q^{2}$ value for that bin.
@@
   surveying measurements~\cite{Bur10}. The contribution from
-each uncertainty to each amplitude extracted in a single kinematic bin
+each uncertainty to each amplitude extracted in a single\red{, overall} kinematic bin
 from the 2006-2007 data  is summarised in Table
@@
 which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty \red{without consideration in the other presented uncertainties.}
+independent scale uncertainty without consideration in the other presented uncertainties.
 
@@
 resonant state (``associated production''). The recoiling proton is not detected and
-  the calorimeter resolution does not allow separation of the latter events from \red{the} rest of the data sample.
+  the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
@@
 }
-  \caption{The contributions to the systematic uncertainty due to the
+  \caption{The contributions to the \red{overall systematic 
+uncertainties of the extracted asymmetry amplitudes} due to the
 background correction, the time-dependent shifts of the missing-mass
-distributions and detector effects for the 2006-2007 data to the total
-systematic uncertainty. The total systematic uncertainties, shown in the
+distributions and detector effects for the 2006-2007 data. The total
+systematic uncertainties \red{of the amplitudes}, shown in the
 right-most column, are the individual contributions added in quadrature.}

### 2011-08-08 experiment_and_data.tex
Added comment updates from Caro, Delia and WDN.
Chnaged the plotting amcro to equalize sizes between legend texts
Changed the first picture

@@
 \section{Experiment and Data Selection}
-The new data presented in this work were collected in 2006 and 2007\red{. As in ref.~\cite{Air09}, the data were collected} with the H{\sc ermes}
+The new data presented in this work were collected in 2006 and 2007. As in ref.~\cite{Air09}, the data were collected with the H{\sc ermes}
 spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
@@
 Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
-$0.0$\,GeV$^2 < -t < 0.7$\,GeV$^2$, $W^{2}$ $>$
+$-t < 0.7$\,GeV$^2$, $W^{2}$ $>$
 9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
@@
 corresponded to the square of the proton mass within the limits of the
-energy resolution of the H{\sc ermes} calorimeter.
-Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon.
-The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in ref.~\cite{Air09}.
-This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.
+energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the
+four-momentum of the virtual photon, $p$ is the initial four-momentum
+of the target proton and $q'$ is the four-momentum of the produced
+photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
+M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
+ref.~\cite{Air09}. This exclusive region was shifted by up to
+0.17\,GeV$^{2}$ \red{for certain subsets of the data in order }to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.
 
@@
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
-combination of complex Compton Form Factors (CFF).
+combination of complex Compton Form Factors (CFF\red{s}).
 A CFF is a convolution of a GPD with a hard scattering kernel.
@@
 Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
-\begin{center}
-\begin{equation}
- s_{1,\textrm{unp}}^{\textrm{I}} \approx 8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
-\label{eq:s1}
-\end{equation}
-\end{center}
-\begin{center}
-\begin{equation}
- c_{1,\textrm{unp}}^{\textrm{I}} \approx 8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}},
-\label{eq:c1}
-\end{equation}
-\end{center}
+\begin{eqnarray}
+s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\red{\textrm{and}}&\label{eq:s1}
+\\
+ c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
+\end{eqnarray}
 where the definition of the kinematic factor $k$ is found
@@
 upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes \red{are} higher
-twist \red{quantities} (see Table~\ref{tab_amplitudes}).
+However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher\red{-}twist quantities (see Table~\ref{tab_amplitudes}).
 
 The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
-contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ function,
+contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$\red{-}fnction,
 which is bilinear in CFFs.
@@
 is more difficult to constrain GPDs
-\red{via} the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
+via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
 kinematically-unsuppressed leading-twist amplitudes.
@@
 $c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
-$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. Although the CFFs
+$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$\red{-}ffunction. Although the CFFs
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
@@
 \caption{Asymmetry amplitudes that can
-be extracted from the available data set, the related Fourier coefficients,
- the $\mathcal{C}$-functions, the twist level and the suppression
- relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
+be extracted from the available data set, the related Fourier
+coefficients, dominant $\mathcal{C}$-function, twist-level and level of
+suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
 \label{tab_amplitudes}

### 2011-08-08 results.tex
Added comment updates from Caro, Delia and WDN.
Chnaged the plotting amcro to equalize sizes between legend texts
Changed the first picture

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from \red{the} previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from the previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.
 \ref{release_bsa_0607} and \ref{release_bca_0607}.
@@
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
+2006-2007 data respectively is present in the amplitudes due to the uncertainty of
 the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets.
-Only the statistical uncertainties were employed in this test \red{as the largest contributions to the systematic uncertainties are largely correlated}.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated.
 This test revealed no significant evidence for incompatibility between the data sets.
@@
 The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
-The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result.
-This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 \red{than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit}.
+The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
+This resemblance to the 2006-2007 result is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
 
@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
-The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest \red{magnitude} of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude \red{shows} no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must \red{approach zero as $-t$ approaches zero} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
+The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry is} shown in the second row of Fig.~\ref{bsa_xbjrange}.
-\red{Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows} any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}.
+Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.
-\red{Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
+Monte Carlo events propogated through simulations of the two experimental setups are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec.
 4 were completed.
-The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.}
+The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.
 
@@
 Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.
-\red{The systematic uncertainties are extimated in a similar procedure as for those for the beam-helicity asymmetries.}
+The systematic uncertainties are estimated in a similar procedure as for those for the beam-helicity asymmetries.
 
-\red{The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.} The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from \red{H{\sc ermes} and Jefferson Laboratory,} and the collider \red{experiments} at H{\sc era}.
+The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.
+The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
-In th\red{is} model, the $t$ dependence is approximated by a physically motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A \red{of} Jefferson Laboratory; the model fit represented by the dashed curves includes \red{these} data.
+In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
+The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.
-The model incorporates only twist-2 GPDs and so can provide \red{results} only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
+The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
 All of the amplitudes are well described by the model.
 
-The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{based on} a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic \red{scattering} data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson \red{Laboratory} (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well \red{in the H{\sc ermes} kinematic region}, but the projections in the other kinematic variables are not as well described.
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson Laboratory (to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well in the H{\sc ermes} kinematic region, but the projections in the other kinematic variables are not as well described.
 
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-There is no observed $-t$ dependence o\red{f} any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in \red{any} of the distinct ranges of $x_{\textrm{B}}$.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner.
+There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.
 No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-08-08 results_dual.tex
Added comment updates from Caro, Delia and WDN.
Chnaged the plotting amcro to equalize sizes between legend texts
Changed the first picture

@@
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the \red{imprecision} of
+2006-2007 data respectively is present in the amplitudes due to the imprecision of
 the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 
-A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from \red{the two} data sets.
+A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
 Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual}
+ \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual_update_1.pdf}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006 and 2007 data a lower weighting in the combined fit.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
 
@@
 The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}.
-Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry} amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry \red{amplitude} are compatible with zero, and neither asymmetry \red{amplitude} shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations \red{as explained in section~4}.
-The missing-mass uncertainty for the combined data set \red{was} calculated \red{using} the procedure described in that section and the results \red{were} added in quadrature.
+Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
+The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated in \red{the same} procedure as for those for the beam-helicity asymmetries.
+The systematic uncertainties are estimated in the same procedure as \red{used to estimate the systematic uncertainties of} the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is a\red{n expected} relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
-These amplitudes \red{are found to} diverge with opposite sign from zero at increasing values of $-t$ but they
+There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
+These amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they
 have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the \red{average value} of the kinematic bins used for the data extractions.
+The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions.
 The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.
@@
 The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
-All of the \red{relevant} amplitudes \red{reported here} are well described by the model.
+All of the relevant amplitudes reported here are well described by the model.
 
-The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{from a fit} based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
-The ``Regge'' term \red{is extended to include} contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and \red{DVCS} data from Jefferson Laboratory (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude \red{reported here} well, but the projections in the other kinematic variables are not as well described.
+The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Laboratory (to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
 
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+\red{These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections}.
 There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.

### 2011-08-08 theory.tex
Added comment updates from Caro, Delia and WDN.
Chnaged the plotting amcro to equalize sizes between legend texts
Changed the first picture

--- 2011-07-22 theory.tex
@@
 be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
-desccription of the nucleon in terms of GPDs would allow the deduction
-of the total angular momentum of partons in the nucleon\red{,} and the
-construction of a longitudinal-momentum\red{-}dissected transverse spatial map of parton positions.
+description of the nucleon in terms of GPDs would allow the deduction
+of the total angular momentum of partons in the nucleon, and the
+construction of a longitudinal-momentum-dissected transverse spatial map of parton positions.
 
@@
 as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
-
 \begin{figure}
 \begin{center}
-\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
-\hspace{3cm}
-\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
+\subfigure[DVCS]{\includegraphics[width=0.45\textwidth]{dvcs_both}}
+\subfigure[Bethe Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
 \caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
@@
 longitudinal momentum fraction
-$x-\xi$. (b): The Bethe-Hietler process, i.e. the emission of a real photon from the scattering or
+$x-\xi$. (b): The Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
 scattered lepton. It has the same initial and final states as DVCS.}
@@
 \end{figure}
-
 Exclusive leptoproduction of real photons
@@
 Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by \red{the struck} quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
 emission of a Bremsstrahlung photon by the lepton. 
@@
 the DVCS process
-($\tau_{\textrm{DVCS}}$) and the interference term (I) from both processes. These
+($\tau_{\textrm{DVCS}}$) and the\red{ir} interference term (I). These
 contributions can be written as
-\begin{equation}
- |\tau_{\textrm{BH}}|^{2} =
-\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
-\left(c_{0,\textrm{unp}}^{
-\textrm{BH}} + \sum_{n=1}^2 c_{n,\textrm{unp}}^{\textrm{BH}}\cos(n\phi)\right),
-\label{e:tbh}
-\end{equation}
-\begin{equation}
- \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
+\begin{eqnarray}
+ |\tau_{\textrm{BH}}|^{2} &=&
+ \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
+  c_{n,\textrm{unp}}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
+|\tau_{\textrm{DVCS}}|^{2} &=&
 K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
@@
 c_{n,\textrm{unp}}^{\textrm{DVCS}}\cos(n\phi) + \lambda
-s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right),
-\label{e:tdvcs}
-\end{equation}
-\begin{equation}
-\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
+s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\red{\textrm{and}}
+\label{e:tdvcs}\\
+ \textrm{I} &=& \frac{- e_\ell
 K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
-I}}
-+
+I}}+
 \sum_{n=1}^3 c_{n,\textrm{unp}}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
-s_{n,\textrm{unp}}^{\textrm{I}}\sin(n\phi)\right),
-\label{e:ti}
-\end{equation}
+s_{n,\textrm{unp}}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
+\end{eqnarray}
 where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
 of the BH process, $\lambda$ is the
-helicity of the lepton beam and $e_\ell$ is the unit charge on
+helicity of the lepton beam and $e_\ell$ is the unit charge o\red{f}
   the lepton.  The
@@
 beam are considered here:
-beam-helicity asymmetries and beam-charge asymmetries. This paper, \red{like} ref.~\cite{Air09}, presents results on the following asymmetries:
+beam-helicity asymmetries and beam-charge asymmetries. This paper, like ref.~\cite{Air09}, presents results on the following asymmetries:
 \begin{align}
@@
 (\textrm{d}\sigma(\phi)^{+\leftarrow}
-+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
-&=\dfrac{K_{\textrm{DVCS}}
-s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
++ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
+%\\ \nonumber
+&=\dfrac{ K_{\textrm{DVCS}} s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
 (\phi)\mathcal{P}_{2}(\phi)}
@@
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\,\,\red{,}and}&
+c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{,\, and}&
 \label{e:aludvcs}
@@
   in this publication combines the data taken in 1996-2005 with this
-  new data set to produce \red{the largest DVCS data set that will be published by H{\sc ermes}.}
-The results in this paper make use of \red{the same} missing-mass technique for event selection \red{as was used in ref.~\cite{Air09}.}
+  new data set to produce the largest DVCS data set that will be published by H{\sc ermes}.
+The results in this paper make use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.

### 2011-08-08 bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual.C

@@ -521,7 +521,7 @@
    leg->SetLineWidth(1);
    leg->SetFillColor(0);
    leg->SetFillStyle(0);
-   TLegendEntry *entry=leg->AddEntry("l1","Kumericki + Mueller (a)","l");
+   TLegendEntry *entry=leg->AddEntry("l1","KM10 (a)","l");
    entry->SetLineColor(4);
    entry->SetLineStyle(1);
    entry->SetLineWidth(1);
@@ -530,7 +530,7 @@
    entry->SetMarkerSize(1);
    entry->SetTextAlign(12);
    entry->SetTextColor(1);
-   entry=leg->AddEntry("ll1","Kumericki + Mueller (b)","l");
+   entry=leg->AddEntry("ll1","KM11 (b)","l");
    entry->SetLineColor(6);
    entry->SetLineStyle(2);
    entry->SetLineWidth(1);
@@ -1006,7 +1006,7 @@
    leg->SetLineWidth(1);
    leg->SetFillColor(0);
    leg->SetFillStyle(0);
-   entry=leg->AddEntry("lll1","Liuti + Goldstein","l");
+   entry=leg->AddEntry("lll1","GHL11","l");
    entry->SetLineColor(8);
    entry->SetLineStyle(4);
    entry->SetLineWidth(1);

### 2011-08-31 results_dual.tex
Cosmetic changes, ready for second circulation

@@
 This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
+\red{The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
+The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.}
 
@@
 Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
-The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 

### 2011-08-31 summary.tex
Fixed bugs in update
Cosmetic changes, ready for second circulation

@@
 All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
-No additional features are observed in any particular $\red{x_{\textrm{B}}}$-bin.
+No additional features are observed in any particular $x_{\textrm{B}}$-bin.
 
@@
 the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
+the Basque Foundation for Science (IKERBASQUE);
 and the European Community Research Infrastructure Integrating Activity

### 2011-09-06 experiment_and_data.tex

@@
 The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
-contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$\red{-}fnction,
+contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$\red{-}function,
 which is bilinear in CFFs.
@@
 $c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
-$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$\red{-}ffunction. Although the CFFs
+$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$\red{-}function. Although the CFFs
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,

### 2011-09-06 macros/bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual.C
added Luiti BCA curves

@@ -557,7 +557,7 @@
    line->SetLineStyle(2);
    line->Draw();
    
-   gre = new TGraphErrors(7);
+   gre = new TGraphErrors(6);
    gre->SetName("Graph");
    gre->SetTitle("Graph");
    gre->SetFillColor(1);
@@ -565,20 +565,18 @@
    gre->SetMarkerColor(2);
    gre->SetMarkerStyle(21);
    gre->SetMarkerSize(0.85);
-   gre->SetPoint(0,-99,-0.0210962);
-   gre->SetPointError(0,0,0.00325248);
-   gre->SetPoint(1,0.018761,-0.0169322);
-   gre->SetPointError(1,0,0.00718519);
-   gre->SetPoint(2,0.04394,-0.0048622);
-   gre->SetPointError(2,0,0.00727148);
-   gre->SetPoint(3,0.078792,-0.0124538);
-   gre->SetPointError(3,0,0.00781673);
-   gre->SetPoint(4,0.142805,-0.0162538);
-   gre->SetPointError(4,0,0.00675921);
-   gre->SetPoint(5,0.260879,-0.0399285);
-   gre->SetPointError(5,0,0.00912486);
-   gre->SetPoint(6,0.466061,-0.0719502);
-   gre->SetPointError(6,0,0.013896);
+   gre->SetPoint(0,0.018761,-0.0169322);
+   gre->SetPointError(0,0,0.00718519);
+   gre->SetPoint(1,0.04394,-0.0048622);
+   gre->SetPointError(1,0,0.00727148);
+   gre->SetPoint(2,0.078792,-0.0124538);
+   gre->SetPointError(2,0,0.00781673);
+   gre->SetPoint(3,0.142805,-0.0162538);
+   gre->SetPointError(3,0,0.00675921);
+   gre->SetPoint(4,0.260879,-0.0399285);
+   gre->SetPointError(4,0,0.00912486);
+   gre->SetPoint(5,0.466061,-0.0719502);
+   gre->SetPointError(5,0,0.013896);
    
    TH1F *Graph29 = new TH1F("Graph29","Graph",100,0.01041267,10.41267);
    Graph29->SetMinimum(-0.09467175);
@@ -663,7 +661,39 @@
    line->SetLineStyle(2);
    line->Draw();
    
-   gre = new TGraphErrors(7);
+   line = new TLine(0.019,0.00927,0.044,0.0115);
+
[…]

### 2011-09-07 background_and_systematic_dual.tex
Implemented Delia's and WDN's final comments and removed red text.

@@
 arising from background in the data from neutral meson
-production is \red{predominantly due to the failure to identify one of
-  the two photons from the decay of produeced neutral mesons}. The procedure for estimating the corresponding
+production is predominantly due to the failure to identify one of
+  the two photons from the decay of produced neutral mesons. The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
   surveying measurements~\cite{Bur10}. The contribution from
-each uncertainty to each amplitude extracted in a single\red{, overall} kinematic bin
+each uncertainty to each amplitude extracted in a single, overall kinematic bin
 from the 2006-2007 data  is summarised in Table
@@
   \hline
-  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.055 \\
+  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.022 \\
   \hline
@@
 }
-  \caption{The contributions to the \red{overall systematic 
-uncertainties of the extracted asymmetry amplitudes} due to the
+  \caption{The contributions to the overall systematic 
+uncertainties of the extracted asymmetry amplitudes due to the
 background correction, the time-dependent shifts of the missing-mass
 distributions and detector effects for the 2006-2007 data. The total
-systematic uncertainties \red{of the amplitudes}, shown in the
+systematic uncertainties of the amplitudes, shown in the
 right-most column, are the individual contributions added in quadrature.}

### 2011-09-07 experiment_and_data.tex
Implemented Delia's and WDN's final comments and removed red text.

@@
 ref.~\cite{Air09}. This exclusive region was shifted by up to
-0.17\,GeV$^{2}$ \red{for certain subsets of the data in order }to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.
+0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.
 
@@
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
-combination of complex Compton Form Factors (CFF\red{s}).
-A CFF is a convolution of a GPD with a hard scattering kernel.
-Contributions of GPDs to the cross section may be relatively suppressed by powers of $1/Q$, the origin of which may be kinematic in nature or due to the twist level of the GPD.
-Leading twist is twist-2.
-Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is suppressed by $\mathcal{O}(1/Q^{n-2})$.
-Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
+combination of complex Compton Form Factors (CFFs). A CFF is a
+convolution of a GPD with a hard scattering kernel. Contributions of
+GPDs to the cross section may be relatively suppressed by powers of
+$1/Q$, the origin of which may be kinematic in nature or due to the
+twist level of the GPD. Leading twist is twist-2. Typically, the
+contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
+suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes}
+presents the asymmetry amplitudes extracted in this analysis and the
+related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
 
@@
 \begin{eqnarray}
-s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\red{\textrm{and}}&\label{eq:s1}
+s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
 \\
@@
 upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher\red{-}twist quantities (see Table~\ref{tab_amplitudes}).
+However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher-twist quantities (see Table~\ref{tab_amplitudes}).
 
 The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
-contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$\red{-}function,
+contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
 which is bilinear in CFFs.
@@
 $c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
-$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$\red{-}function. Although the CFFs
+$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
@@
 \hline
-Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
+Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level & Relative Suppression   \\ 
 \hline

### 2011-09-07 results_dual.tex
Implemented Delia's and WDN's final comments and removed red text.

--- 2011-08-08 results_dual.tex
@@
 This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
+The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
+The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 
@@
 Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
-The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated in the same procedure as \red{used to estimate the systematic uncertainties of} the beam-helicity asymmetries.
+The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
@@
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-\red{These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections}.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections.
 There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.

### 2011-09-07 summary.tex
Implemented Delia's and WDN's final comments and removed red text.

@@
 A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-\red{The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}.
-There is} a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
+The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}.
+There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
 There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.

### 2011-09-07 theory.tex
Implemented Delia's and WDN's final comments and removed red text.

@@
 which an electron/positron ($e$) interacts with a quark in the nucleon
-($p$) via a virtual photon ($\gamma^\ast$). The quark is found in the
+($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
 nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
@@
 \end{figure}
+
 Exclusive leptoproduction of real photons
@@
 the DVCS process
-($\tau_{\textrm{DVCS}}$) and the\red{ir} interference term (I). These
+($\tau_{\textrm{DVCS}}$) and their interference term (I). These
 contributions can be written as
@@
 c_{n,\textrm{unp}}^{\textrm{DVCS}}\cos(n\phi) + \lambda
-s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\red{\textrm{and}}
+s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
 \label{e:tdvcs}\\
@@
 of the BH process, $\lambda$ is the
-helicity of the lepton beam and $e_\ell$ is the unit charge o\red{f}
+helicity of the lepton beam and $e_\ell$ is the unit charge of
   the lepton.  The
@@
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{,\, and}&
+c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
 \label{e:aludvcs}

### 2011-09-07 background_and_systematic_dual.tex
Small changes

--- 2011-08-08 background_and_systematic_dual.tex
@@
 each uncertainty to each amplitude extracted in a single\red{, overall} kinematic bin
-from the 2006-2007 data  is summarised in Table
+from the 2006-2007 data  is summarised in table
 \ref{table_systematic_contributions_0607}.
@@
 calculation based on the parameterisation from ref.~\cite{Bra76} is
-used to estimate the contribution to the event sample from resonant
+used to estimate the \red{fractional} contribution to the event sample from resonant
 production in each kinematic bin.
 The results, called the associated fractions and labelled ``Assoc.
-fraction'', are shown in the last row of each figure in the results section.
+fraction'', are shown in the last row of figure\red{s} in the results section.
 The method used to perform this estimation is described in detail in

### 2011-09-07 experiment_and_data.tex
Small changes

--- 2011-09-06 experiment_and_data.tex
@@
 target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of 30.3\,\% and 39.2\% \cite{Ben01}. The procedure used to select events is similar to that used in ref.~\cite{Air09}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$~\cite{Ben01}, with average beam polarisations of 30.3\,\% and 39.2\% \cite{tpol,lpol}.
+The procedure used to select events is similar to that used in ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult
@@
 coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
-DVCS terms in Eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
 may also be affected by the lepton propagators and the other
 $\phi$-dependent terms in the denominators in
-Eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
+eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
@@
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in Eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
+neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
 are kinematically suppressed by an order of magnitude or more.
@@
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
 As a result of

### 2011-09-07 results_dual.tex
Small changes

--- 2011-08-08 results_dual.tex
@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
+The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in figures~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
 The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
@@
 This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
+\red{The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.}
 
 The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
-sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}.
+sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
@@
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
-The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of figure~\ref{bsa_xbjrange}.
 Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
-The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 
-The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}.
+The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}.
 The systematic uncertainties are estimated in the same procedure as \red{used to estimate the systematic uncertainties of} the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}.
-These amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they
-have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
+There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they \red{depend on the same $\mathcal{C}$-function.
+The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}.
+The measured} amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions.
+The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions.
 The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.
@@
 
-The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in figure~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.
@@
 
-In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
 \red{These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections}.

### 2011-09-07 summary.tex
Small changes

--- 2011-08-31 summary.tex
@@
 These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
-Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}.
+Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
 A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.

### 2011-09-07 theory.tex
Small changes

--- 2011-08-08 theory.tex
@@
 Generalised Parton Distributions (GPDs)
-\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
-distribution functions (PDFs) and nucleon form factors to provide a
+\cite{Mue94,Ji97a,Rad97} encompass the familiar Parton
+Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
 comprehensive description of the structure of the nucleon.
@@
 two experimentally indistinguishable processes shown in
-Fig.~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
+figure~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
 which is the emission of a real photon by the struck quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the

### 2011-09-07 background_and_systematic_dual.tex

--- 2011-09-07 background_and_systematic_dual.tex
@@
 each uncertainty to each amplitude extracted in a single, overall kinematic bin
-from the 2006-2007 data  is summarised in Table
-\ref{table_systematic_contributions_0607}.
+from the 2006-2007 data  is summarised in Table~\ref{table_systematic_contributions_0607}.
 

### 2011-09-07 experiment_and_data.tex

--- 2011-09-07 experiment_and_data.tex
@@
 However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
-As a result of
-the more complicated dependence on the CFFs and this suppression, it
+As a result of the more complicated dependence on the CFFs and this suppression, it
 is more difficult to constrain GPDs

### 2011-09-07 results_dual.tex

@@
 
-The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in figures~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
+The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
 The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006\red{-}2007 data a lower weighting in the combined fit.
-\red{The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.}
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006-2007 data a lower weighting in the combined fit.
+The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
+The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
 
@@
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
-There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they \red{depend on the same $\mathcal{C}$-function.
+There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
 The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}.
-The measured} amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
+The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-\red{These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections}.
+In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections.
 There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.

### 2011-09-13 background_and_systematic_dual.tex
Made Delias and wdns changes

@@
 calculation based on the parameterisation from ref.~\cite{Bra76} is
-used to estimate the \red{fractional} contribution to the event sample from resonant
+used to estimate the fractional contribution to the event sample from resonant
 production in each kinematic bin.
 The results, called the associated fractions and labelled ``Assoc.
-fraction'', are shown in the last row of figure\red{s} in the results section.
+fraction'', are shown in the last row of figures in the results section.
 The method used to perform this estimation is described in detail in

### 2011-09-13 experiment_and_data.tex
Made Delias and wdns changes

@@
 $1/Q$, the origin of which may be kinematic in nature or due to the
-twist level of the GPD. Leading twist is twist-2. Typically, the
+twist-level of the GPD. Leading twist is twist-2. Typically, the
 contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
@@
 
-At H{\sc ermes} kinematic conditions, the leading-twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
+At H{\sc ermes} kinematic conditions, the leading twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
 These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
@@
 $A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
-upon this $\mathcal{C}$-function.
-However, the $A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ amplitudes are higher-twist quantities (see Table~\ref{tab_amplitudes}).
+upon this $\mathcal{C}$-function. However, the
+$A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed
+compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$
+amplitudes are higher twist quantities (see Table~\ref{tab_amplitudes}).
 
@@
 via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
-kinematically-unsuppressed leading-twist amplitudes.
+kinematically-unsuppressed leading twist amplitudes.
 

### 2011-09-13 results_dual.tex
Made Delias and wdns changes

@@
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated in the same procedure as \red{used to estimate the systematic uncertainties of} the beam-helicity asymmetries.
+The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries.
 The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.

### 2011-11-21 rec-dvcsP0607.tex

% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear

\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4}
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4}

% Enable use of graphics

\usepackage{graphicx}

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.

%\bibliographystyle{apsrev}

% ===========================================================================

\begin{document}

\title{
  Beam Helicity and Charge Asymmetries in the Bethe-Heitler and Deeply-Virtual Compton Scattering Processes on an Unpol Proton Target \\
  \underline{Paper Tag: dvcsP0607}
  \hspace*{1cm}\underline{Drafting Committee: 90}
}

% List of Institute Addresses

\def\groupargonne{\affiliation{Physics Division, Argonne National Laboratory, Argonne, Illinois 60439-4843, USA}}
\def\groupbari{\affiliation{Istituto Nazionale di Fisica Nucleare, Sezione di Bari, 70124 Bari, Italy}}
\def\groupbeijing{\affiliation{School of Physics, Peking University, Beijing 100871, China}}
\def\groupcolorado{\affiliation{Nuclear Physics Laboratory, University of Colorado, Boulder, Colorado 80309-0390, USA}}
\def\groupdesy{\affiliation{DESY, 22603 Hamburg, Germany}}
\def\groupzeuthen{\affiliation{DESY, 15738 Zeuthen, Germany}}
\def\groupdubna{\affiliation{Joint Institute for Nuclear Research, 141980 Dubna, Russia}}
\def\grouperlangen{\affiliation{Physikalisches Institut, Universit\"at Erlangen-N\"urnberg, 91058 Erlangen, Germany}}
\def\groupferrara{\affiliation{Istituto Nazionale di Fisica Nucleare, Sezione di Ferrara and Dipartimento di Fisica, Universit\`a di Ferrara, 44100 Ferrara, Italy}}
\def\groupfrascati{\affiliation{Istituto Nazionale di Fisica Nucleare, Laboratori Nazionali di Frascati, 00044 Frascati, Italy}}
\def\groupgent{\affiliation{Department of Subatomic and Radiation Physics, University of Gent, 9000 Gent, Belgium}}
\def\groupgiessen{\affiliation{Physikalisches Institut, Universit\"at Gie{\ss}en, 35392 Gie{\ss}en, Germany}}
\def\groupglasgow{\affiliation{SUPA, School of Physics and Astronomy, University of Glasgow, Glasgow G12 8QQ, United Kingdom}}
\def\groupillinois{\affiliation{Department of Physics, University of Illinois, Urbana, Illinois 61801-3080, USA}}
\def\groupmichigan{\affiliation{Randall Laboratory of Physics, University of Michigan, Ann Arbor, Michigan 48109-1040, USA }}
\def\groupmoscow{\affiliation{Lebedev Physical Institute, 117924 Moscow, Russia}}
\def\groupnikhef{\affiliation{National Institute for Subatomic Physics (Nikhef), 1009 DB Amsterdam, The Netherlands}}
\def\groupstpetersburg{\affiliation{Petersburg Nuclear Physics Institute, Gatchina, Leningrad region, 188300 Russia}}
\def\groupprotvino{\affiliation{Institute for High Energy Physics, Protvino, Moscow region, 142281 Russia}}
\def\groupregensburg{\affiliation{Institut f\"ur Theoretische Physik, Universit\"at Regensburg, 93040 Regensburg, Germany}}
\def\grouprome{\affiliation{Istituto Nazionale di Fisica Nucleare, Sezione Roma 1, Gruppo Sanit\`a and Physics Laboratory, Istituto Superiore di Sanit\`a, 00161 Roma, Italy}}
\def\grouptriumf{\affiliation{TRIUMF, Vancouver, British Columbia V6T 2A3, Canada}}
\def\grouptokyo{\affiliation{Department of Physics, Tokyo Institute of Technology, Tokyo 152, Japan}}
\def\groupamsterdam{\affiliation{Department of Physics and Astronomy, Vrije Universiteit, 1081 HV Amsterdam, The Netherlands}}
\def\groupwarsaw{\affiliation{Andrzej Soltan Institute for Nuclear Studies, 00-689 Warsaw, Poland}}
\def\groupyerevan{\affiliation{Yerevan Physics Institute, 375036 Yerevan, Armenia}}
\def\groupnone{\noaffiliation}

% Set Institute Order

\groupargonne
\groupbari
\groupbeijing
\groupcolorado
\groupdesy
\groupzeuthen
\groupdubna
\grouperlangen
\groupferrara
\groupfrascati
\groupgent
\groupgiessen
\groupglasgow
\groupillinois
\groupmichigan
\groupmoscow
\groupnikhef
\groupstpetersburg
\groupprotvino
\groupregensburg
\grouprome
\grouptriumf
\grouptokyo
\groupamsterdam
\groupwarsaw
\groupyerevan

% List of Authors

\author{A.~Airapetian}  \groupgiessen
\author{N.~Akopov}  \groupyerevan
\author{Z.~Akopov}  \groupdesy
\author{E.C.~Aschenauer}  \groupzeuthen
\author{W.~Augustyniak}  \groupwarsaw
\author{R.~Avakian}  \groupyerevan
\author{A.~Avetissian}  \groupyerevan
\author{E.~Avetisyan}  \groupdesy
\author{B.~Ball}  \groupmichigan
\author{S.~Belostotski}  \groupstpetersburg
\author{N.~Bianchi}  \groupfrascati
\author{H.P.~Blok}  \groupnikhef \groupamsterdam
\author{H.~B\"ottcher}  \groupzeuthen
\author{A.~Borissov}  \groupdesy
\author{J.~Bowles}  \groupglasgow
\author{I.~Brodski}  \groupgiessen
\author{V.~Bryzgalov}  \groupprotvino
\author{J.~Burns}  \groupglasgow
\author{M.~Capiluppi}  \groupferrara
\author{G.P.~Capitani}  \groupfrascati
\author{E.~Cisbani}  \grouprome
\author{G.~Ciullo}  \groupferrara
\author{M.~Contalbrigo}  \groupferrara
\author{P.F.~Dalpiaz}  \groupferrara
\author{W.~Deconinck}  \groupdesy
\author{R.~De~Leo}  \groupbari
\author{L.~De~Nardo}  \groupdesy \grouptriumf
\author{E.~De~Sanctis}  \groupfrascati
\author{M.~Diefenthaler}  \grouperlangen
\author{P.~Di~Nezza}  \groupfrascati
\author{J.~Dreschler}  \groupnikhef
\author{M.~D\"uren}  \groupgiessen
\author{M.~Ehrenfried}  \groupgiessen
\author{G.~Elbakian}  \groupyerevan
\author{F.~Ellinghaus}  \groupcolorado
\author{R.~Fabbri}  \groupzeuthen
\author{A.~Fantoni}  \groupfrascati
\author{L.~Felawka}  \grouptriumf
\author{S.~Frullani}  \grouprome
\author{D.~Gabbert}  \groupzeuthen
\author{G.~Gapienko}  \groupprotvino
\author{V.~Gapienko}  \groupprotvino
\author{F.~Garibaldi}  \grouprome
\author{G.~Gavrilov}  \groupdesy \groupstpetersburg \grouptriumf
\author{V.~Gharibyan}  \groupyerevan
\author{F.~Giordano}  \groupferrara
\author{S.~Gliske}  \groupmichigan
\author{M.~Golembiovskaya}  \groupdesy
\author{C.~Hadjidakis}  \groupfrascati
\author{M.~Hartig}  \groupdesy
\author{D.~Hasch}  \groupfrascati
\author{T.~Hasegawa}  \grouptokyo
\author{G.~Hill}  \groupglasgow
\author{A.~Hillenbrand}  \groupzeuthen
\author{M.~Hoek}  \groupglasgow
\author{Y.~Holler}  \groupdesy
\author{I.~Hristova}  \groupzeuthen
\author{Y.~Imazu}  \grouptokyo
\author{A.~Ivanilov}  \groupprotvino
\author{A.~Izotov}  \groupstpetersburg
\author{H.E.~Jackson}  \groupargonne
\author{A.~Jgoun}  \groupstpetersburg
\author{H.S.~Jo}  \groupgent
\author{S.~Joosten}  \groupillinois
\author{R.~Kaiser}  \groupglasgow
\author{G.~Karyan}  \groupyerevan
\author{T.~Keri}  \groupgiessen
\author{E.~Kinney}  \groupcolorado
\author{A.~Kisselev}  \groupstpetersburg
\author{N.~Kobayashi}  \grouptokyo
\author{V.~Korotkov}  \groupprotvino
\author{V.~Kozlov}  \groupmoscow
\author{P.~Kravchenko}  \groupstpetersburg
\author{V.G.~Krivokhijine}  \groupdubna
\author{L.~Lagamba}  \groupbari
\author{R.~Lamb}  \groupillinois
\author{L.~Lapik\'as}  \groupnikhef
\author{I.~Lehmann}  \groupglasgow
\author{P.~Lenisa}  \groupferrara
\author{L.A.~Linden-Levy}  \groupillinois
\author{A.~L\'opez~Ruiz}  \groupgent
\author{W.~Lorenzon}  \groupmichigan
\author{X.-G.~Lu}  \groupdesy
\author{B.-Q.~Ma}  \groupbeijing
\author{D.~Mahon}  \groupglasgow
\author{N.C.R.~Makins}  \groupillinois
\author{S.I.~Manaenkov}  \groupstpetersburg
\author{L.~Manfr\'e}  \grouprome
\author{Y.~Mao}  \groupbeijing
\author{B.~Marianski}  \groupwarsaw
\author{A.~Martinez de la Ossa}  \groupcolorado
\author{H.~Marukyan}  \groupyerevan
\author{C.A.~Miller}  \grouptriumf
\author{Y.~Miyachi}  \grouptokyo
\author{A.~Movsisyan}  \groupyerevan
\author{V.~Muccifora}  \groupfrascati
\author{M.~Murray}  \groupglasgow
\author{A.~Mussgiller}  \grouperlangen
\author{E.~Nappi}  \groupbari
\author{Y.~Naryshkin}  \groupstpetersburg
\author{A.~Nass}  \grouperlangen
\author{M.~Negodaev}  \groupzeuthen
\author{W.-D.~Nowak}  \groupzeuthen
\author{L.L.~Pappalardo}  \groupferrara
\author{R.~Perez-Benito}  \groupgiessen
\author{N.~Pickert}  \grouperlangen
\author{M.~Raithel}  \grouperlangen
\author{P.E.~Reimer}  \groupargonne
\author{A.R.~Reolon}  \groupfrascati
\author{C.~Riedl}  \groupzeuthen
\author{K.~Rith}  \grouperlangen
\author{G.~Rosner}  \groupglasgow
\author{A.~Rostomyan}  \groupdesy
\author{J.~Rubin}  \groupargonne
\author{D.~Ryckbosch}  \groupgent
\author{Y.~Salomatin}  \groupprotvino
\author{F.~Sanftl}  \groupregensburg
\author{A.~Sch\"afer}  \groupregensburg
\author{G.~Schnell}  \groupgent
\author{K.P.~Sch\"uler}  \groupdesy
\author{B.~Seitz}  \groupglasgow
\author{T.-A.~Shibata}  \grouptokyo
\author{V.~Shutov}  \groupdubna
\author{M.~Stancari}  \groupferrara
\author{M.~Statera}  \groupferrara
\author{E.~Steffens}  \grouperlangen
\author{J.J.M.~Steijger}  \groupnikhef
\author{H.~Stenzel}  \groupgiessen
\author{J.~Stewart}  \groupzeuthen
\author{F.~Stinzing}  \grouperlangen
\author{S.~Taroian}  \groupyerevan
\author{A.~Terkulov}  \groupmoscow
\author{A.~Trzcinski}  \groupwarsaw
\author{M.~Tytgat}  \groupgent
\author{A.~Vandenbroucke}  \groupgent
\author{P.B.~van~der~Nat}  \groupnikhef
\author{Y.~Van~Haarlem}  \groupgent
\author{C.~Van~Hulse}  \groupgent
\author{M.~Varanda}  \groupdesy
\author{D.~Veretennikov}  \groupstpetersburg
\author{V.~Vikhrov}  \groupstpetersburg
\author{I.~Vilardi}  \groupbari
\author{C.~Vogel}  \grouperlangen
\author{S.~Wang}  \groupbeijing
\author{S.~Yaschenko}  \grouperlangen
\author{H.~Ye}  \groupbeijing
\author{Z.~Ye}  \groupdesy
\author{S.~Yen}  \grouptriumf
\author{W.~Yu}  \groupgiessen
\author{V.~Zagrebelnyy}  \groupdesy \groupgiessen
\author{D.~Zeiler}  \grouperlangen
\author{B.~Zihlmann}  \groupdesy
\author{P.~Zupranski}  \groupwarsaw

\collaboration{The HERMES Collaboration} \noaffiliation

\date{\today}

\begin{abstract}
% insert abstract here
\end{abstract}

% insert suggested PACS numbers in braces
\pacs{}

% maketitle must be placed here
\maketitle

\end{document}

### 2011-11-21 results_dual.tex

@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
-The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+The leading twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
 This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
@@
 The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries.
-The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
+The leading twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
 There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
@@
 The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
-Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.
+Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.
 
@@
 The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
+The model describes the trends of the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes well.
 

### 2011-11-21 macros/bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual.C
Cleaned up this branch to only include the html file.

@@ -1,2800 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 16:36:03 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",2,22,1200,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetFillStyle(4000);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.35);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.425);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.125);
-   pad1->SetRightMargin(0.0135135);
-   pad1->SetTopMargin(0.0225095);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.825,0.25,1);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2,-0.15,2,0.15);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(2);
-   pad1_1->SetLeftMargin(0.5);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   
[…]

### 2011-11-21 macros/bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C

@@ -1,2637 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 15:04:47 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",0,22,1200,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetFillStyle(4000);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.35);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.425);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.125);
-   pad1->SetRightMargin(0.0135135);
-   pad1->SetTopMargin(0.0225095);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.825,0.25,1);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2,-0.15,2,0.15);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(2);
-   pad1_1->SetLeftMargin(0.5);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   
[…]

### 2011-11-21 macros/bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_dual.C

@@ -1,1689 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 17:24:30 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",1,22,1280,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.25);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.25);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.0555556);
-   pad1->SetRightMargin(0.0167598);
-   pad1->SetTopMargin(0.026009);
-   pad1->SetBottomMargin(0.0650226);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.746749,0.364784,0.973991);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2.435528,-0.35,-0.09691001,0.25);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(0);
-   pad1_1->SetLogx();
-   pad1_1->SetLeftMargin(0.166667);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
[…]

### 2011-11-21 macros/bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual.C

@@ -1,2059 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 14:43:44 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",14,32,1200,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.35);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.45);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.125);
-   pad1->SetRightMargin(0.0135135);
-   pad1->SetTopMargin(0.0281369);
-   pad1->SetBottomMargin(0.126616);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.7,0.25,1);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2,-0.65,2,0.25);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(2);
-   pad1_1->SetLeftMargin(0.5);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   
[…]

### 2011-11-21 macros/bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual.C

@@ -1,1968 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 15:24:37 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",-7,22,1200,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.35);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.45);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.125);
-   pad1->SetRightMargin(0.0135135);
-   pad1->SetTopMargin(0.0281369);
-   pad1->SetBottomMargin(0.126616);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.7,0.25,1);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2,-0.65,2,0.25);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(2);
-   pad1_1->SetLeftMargin(0.5);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
-   
[…]

### 2011-11-21 macros/bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual.C

@@ -1,1242 +1,0 @@
-{
-//=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 16:44:00 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",0,22,1280,756);
-   gStyle->SetOptStat(0);
-   combined->SetHighLightColor(2);
-   combined->Range(0,0,1,1);
-   combined->SetFillColor(0);
-   combined->SetBorderMode(0);
-   combined->SetBorderSize(2);
-   combined->SetLeftMargin(0.2);
-   combined->SetRightMargin(0.05);
-   combined->SetBottomMargin(0.25);
-   combined->SetFrameFillStyle(0);
-   combined->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1
-   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
-   pad1->Draw();
-   pad1->cd();
-   pad1->Range(0,0,1,1);
-   pad1->SetFillColor(0);
-   pad1->SetBorderMode(0);
-   pad1->SetBorderSize(2);
-   pad1->SetLeftMargin(0.0784314);
-   pad1->SetRightMargin(0.0171544);
-   pad1->SetTopMargin(0.0355092);
-   pad1->SetBottomMargin(0.0887731);
-   pad1->SetFrameFillStyle(0);
-   pad1->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.672585,0.379903,0.964491);
-   pad1_1->Draw();
-   pad1_1->cd();
-   pad1_1->Range(-2.645402,-0.45,-0.09691001,0.3);
-   pad1_1->SetFillStyle(4000);
-   pad1_1->SetBorderMode(0);
-   pad1_1->SetBorderSize(0);
-   pad1_1->SetLogx();
-   pad1_1->SetLeftMargin(0.235294);
-   pad1_1->SetRightMargin(0);
-   pad1_1->SetTopMargin(0);
-   pad1_1->SetBottomMargin(0);
-   pad1_1->SetFrameFillColor(0);
-   pad1_1->SetFrameFillStyle(0);
-   pad1_1->SetFrameBorderMode(0);
[…]

### 2011-12-07 experiment_and_data.tex
Added Marcos comments.

@@
 $\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
-$\mathcal{A}_{\textrm{C}}$ asymmetry are physically motivated. The other terms
+$\mathcal{A}_{\textrm{C}}$ asymmetry are \red{motivated by the
+  physical processes under investigation}. The other terms
 are included as both a consistency check for any off-phase

### 2011-12-07 summary.tex
Added Marcos comments.

@@
 A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The asymmetry amplitudes extracted from the combined data set are the statistically most precise DVCS measurements presented by H{\sc ermes}.
+The asymmetry amplitudes extracted from the combined data set are the \red{most} statistically precise DVCS measurements presented by H{\sc ermes}.
 There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
@@
 No additional features are observed in any particular $x_{\textrm{B}}$-bin.
+\red{The results from this paper will be made available in 4 bins in the Durham Database.}
 

### 2011-12-12 frame_dual.tex
Small changes
added desrciption of simonettas model and updated references
Made Delias and wdns changes
new tables and format
started going through the paper and changing to collaboration wishes

@@
 \usepackage{subfigure}
+\usepackage{multirow}
+\usepackage{rotating}
 \usepackage{appendix}
@@
 \title{Beam-Helicity and Beam-Charge Asymmetries \\
-        in the Bethe-Heitler and DVCS processes on \\
+        in the Bethe--Heitler and DVCS processes on \\
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v1.2)}
+  	\underline{Paper Tag: PDVCS0607 (v2.0)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 % List of Institute Addresses 
-\collaboration{The HERMES Collaboration}
-\collaborationImg{\includegraphics{hermeslogo.pdf}}
+\collaboration{The {\sc Hermes} Collaboration}
+%\collaborationImg{\includegraphics{hermeslogo.pdf}}
 
@@
 \author[2]{R.~De~Leo}
-\author[5,22]{L.~De~Nardo}
+\author[5,22,11]{L.~De~Nardo}
 \author[10]{E.~De~Sanctis}
@@
 \affiliation[24]{Department of Physics and Astronomy, Vrije Universiteit, 1081 HV Amsterdam, The Netherlands}
-\affiliation[25]{Andrzej Soltan Institute for Nuclear Studies, 00-689 Warsaw, Poland}
+\affiliation[25]{National Center for Nuclear Research, 00-689 Warsaw, Poland}
 \affiliation[26]{Yerevan Physics Institute, 375036 Yerevan, Armenia}
@@
 precise than those extracted from the earlier data
-set of 1996-2005 previously analysed in the same manner by the
-collaboration. Results from the two data sets are found to be
+set of 1996-2005 previously analysed in the same manner by \red{\sc{Hermes}}. Results from the two data sets are found to be
 compatible with each other. Combined results from these data sets are

### 2011-12-12 theory.tex
added desrciption of simonettas model and updated references
started going through the paper and changing to collaboration wishes

@@
 comprehensive description of the structure of the nucleon.
-Although GPDs are difficult to access experimentally, the H{\sc ermes}
-collaboration has previously published results
+Although GPDs are difficult to access experimentally, the {\sc Hermes}
+\red{C}ollaboration has previously published results
 \cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
-the leptoproduction of real photons from a nucleon or nucleus that can
+the \red{exclusive} leptoproduction of real photons from a nucleon or nucleus that can
 be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
@@
 \subfigure[DVCS]{\includegraphics[width=0.45\textwidth]{dvcs_both}}
-\subfigure[Bethe Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
+\subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
 \caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
@@
 figure~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by the struck quark from the nucleon, and the Bethe-Heitler (BH) process, which is elastic lepton-proton scattering with the
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-proton scattering with the
 emission of a Bremsstrahlung photon by the lepton. 
@@
 
-The four-fold differential cross section for the leptoproduction of real photons
+The four-fold differential cross section for the \red{exclusive} leptoproduction of real photons
 from an unpolarised target can be written as \cite{Bel02b}
@@
 beam are considered here:
-beam-helicity asymmetries and beam-charge asymmetries. This paper, like ref.~\cite{Air09}, presents results on the following asymmetries:
+beam-helicity asymmetries and beam-charge asymmetries. This paper,
+like ref.~\cite{Air09}, presents results \red{related to} the following asymmetries:
 \begin{align}

### 2011-12-19 background_and_systematic_dual.tex
Updated by doing the changes of Gunar without touching references

@@
 The predominant contribution to the systematic uncertainty arises from detector
-effects, including the acceptance of the spectrometer, smearing
-effects due to detector resolution and radiative processes during
-  detection, and
-the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+effects. \red{These include} the acceptance of the spectrometer, smearing
+effects due to detector resolution \red{(e.g.
+the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter)}, radiative processes during detection \red{(e.g.
+e.m.
+showers in the calorimeter being incorrectly reconstructed)}, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
-An event
-generator based on the GPD model described in ref.~\cite{Van99,Goe01} was
+An event generator based on the GPD model described in ref\red{s}.~\cite{Van99,Goe01} was
 used for the simulation because it describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
@@
   missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
-systematic uncertainty from misalignment of the
-spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
-  surveying measurements~\cite{Bur10}. The contribution from
-each uncertainty to each amplitude extracted in a single, overall kinematic bin
-from the 2006-2007 data  is summarised in Table~\ref{table_systematic_contributions_0607}.
+systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
+  surveying measurements.
+\red{However, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
+The systematic uncertainty contribution due to potential from misalignment is so small as to be negligible, so this information is given purely for completeness.}
+
+The contribution from each uncertainty to each amplitude extracted in a single, overall kinematic bin from the 2006-2007 data  is summarised in Table~\ref{table_systematic_contributions_0607}.
 
@@
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state (``associated production''). The recoiling proton is not detected and
-  the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
+resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
@@
 The results, called the associated fractions and labelled ``Assoc.
-fraction'', are shown in the last row of figures in the results section.
+fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section.
 The method used to perform this estimation is described in detail in

### 2011-12-19 experiment_and_data.tex
Updated by doing the changes of Gunar without touching references

@@
 corresponded to the square of the proton mass within the limits of the
-energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the
+energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
 four-momentum of the virtual photon, $p$ is the initial four-momentum
@@
 $\phi$-dependent terms in the denominators in
-eqs.~\ref{e:alui}-\ref{e:ac}. The  $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{V}$ Fourier
-coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
-combination of complex Compton Form Factors (CFFs). A CFF is a
-convolution of a GPD with a hard scattering kernel. Contributions of
-GPDs to the cross section may be relatively suppressed by powers of
-$1/Q$, the origin of which may be kinematic in nature or due to the
-twist-level of the GPD. Leading twist is twist-2. Typically, the
-contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
-suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes}
-presents the asymmetry amplitudes extracted in this analysis and the
-related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
-
-At H{\sc ermes} kinematic conditions, the leading twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
-These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
-Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
-\begin{eqnarray}
-s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
-\\
- c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
-\end{eqnarray}
-where the definition of the kinematic factor $k$ is found
-  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
-written
-\cite{Bel02b} 
-\begin{equation}
- \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
-\label{Eq_cunp}
-\end{equation}
-where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
-factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
-$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
-$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
-conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
-contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
-are kinematically suppressed by an order of magnitude or more.
-Hence, the behaviour of
-$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
-and therefore GPD $H$ can be constrained through
-measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.
+eqs.~\ref{e:alui}-\ref{e:ac}. 
 The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,

### 2011-12-19 frame_dual.tex
Updated by doing the changes of Gunar without touching references

@@
 
-\def\desy{{\sc desy}}
+\def\desy{{\sc Desy}}
 
@@
 compatible with each other. Combined results from these data sets are
-extracted and represent the most statistically precise asymmetry amplitude measurements available in the H{\sc ermes} kinematic region.
+extracted and represent the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
 }

### 2011-12-19 results_dual.tex
Updated by doing the changes of Gunar without touching references

@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
-The leading twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+The leading\red{-}twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
 This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
@@
 The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}.
-The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ but they have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$.
+The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ \red{and they indicate a weak increase with} $x_{\textrm{B}}$ and $Q^{2}$.
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions.
-The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}.
+The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab\red{.}, and the collider experiments at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.

### 2011-12-19 theory.tex
Updated by doing the changes of Gunar without touching references

@@
 
+\red{The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{I}}$ Fourier
+coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
+combination of complex Compton Form Factors (CFFs). A CFF is a
+convolution of a GPD with a hard scattering kernel. Contributions of
+GPDs to the cross section may be relatively suppressed by powers of
+$1/Q$, the origin of which may be kinematic in nature or due to the
+twist-level of the GPD. Leading twist is twist-2. Typically, the
+contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
+suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes}
+presents the asymmetry amplitudes extracted in this analysis and the
+related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
+
+At H{\sc ermes} kinematic conditions, the leading twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
+These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
+\begin{eqnarray}
+s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
+\\
+ c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
+\end{eqnarray}
+where the definition of the kinematic factor $k$ is found
+  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
+written
+\cite{Bel02b} 
+\begin{equation}
+ \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
+\label{Eq_cunp}
+\end{equation}
+where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
+factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
+$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
+$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
+conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
+contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
+neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
+are kinematically suppressed by an order of magnitude or more.
+Hence, the behaviour of
+$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
+and therefore GPD $H$ can be constrained through
+measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.}
+
 Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger,

### 2011-12-20 background_and_systematic_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

@@
-\section{Background Corrections and Systematic Uncertainties for the
+1\section{Background Corrections and Systematic Uncertainties for the
   2006-2007 Data}
@@
 
-The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
-which is present in the beam-helicity amplitudes and is quoted as an
-independent scale uncertainty without consideration in the other presented uncertainties.
+The beam polarisation measurement has total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period.
+\red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without consideration in the other presented uncertainties.
 
-The data sample in the exclusive region contains events involving both
-production of real photons in which the proton remains intact and
+The data sample in the exclusive region contains events involving production of real photons in which the proton remains intact and
 events involving the excitation of the target proton to a $\Delta^+$

### 2011-12-20 experiment_and_data.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

@@
 rest frame. The polar angle between the virtual and real photons was required to
-be within the limits 5 mrad $<$
-$\theta_{\gamma^{*}\gamma}$ $<$ 45 mrad.
+be within the limits 5~mrad $<$
+$\theta_{\gamma^{*}\gamma}$ $<$ 45~mrad.
 
 An event sample was selected using a missing-mass technique requiring
-that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
+that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{P}-q')^{2}$
 of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
@@
 energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
-four-momentum of the virtual photon, $p$ is the initial four-momentum
-of the target proton and $q'$ is the four-momentum of the produced
+four-momentum of the virtual photon, $M_{P}$ is the initial four-momentum
+of the target proton\red{, i.e. the mass of the proton,} and $q'$ is the four-momentum of the produced
 photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
@@
   physical processes under investigation}. The other terms
-are included as both a consistency check for any off-phase
+are included both \red{as} a consistency check for any off-phase
 extraneous harmonics in the data and as a test of the
@@
 $A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
-coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and
-DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
 may also be affected by the lepton propagators and the other
@@
 As a result of the more complicated dependence on the CFFs and this suppression, it
-is more difficult to constrain GPDs
-via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the
-kinematically-unsuppressed leading twist amplitudes.
+is more difficult to constrain GPDs via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the kinematically-unsuppressed leading twist amplitudes.
 
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-where $\alpha_{\textrm{S}}$ is the strong coupling constant.
+where $\alpha_{\textrm{S}}$ is the strong coupling constant. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
+related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
 \begin{table}

### 2011-12-20 frame_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

@@
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v2.0)}
+  	\underline{Paper Tag: PDVCS0607 (v2.1)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 are extracted from the H{\sc ermes} data set of 2006-2007 using a
-missing-mass event selection technique. The beam-charge asymmetry
+missing-mass event selection technique. The asymmetry
 amplitudes extracted from the new data set are more

### 2011-12-20 results_dual.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+Results for the beam-helicity and beam-charge asymmetry amplitudes extracted 
+\red{in Ref.~\cite{fd} from the previously published 1996-2005 data set} and \red{the results extracted from the 2006-2007 hydrogen data sets in this work} are \red{compared} in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
-Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated.
+A statistical test \red{(Student's test)} was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated\red{, i.e.
+effects from detector resolution, acceptance and smearing}.
 This test revealed no significant evidence for incompatibility between the data sets.
-The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
+The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the \red{entire} hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
 \begin{figure}
@@
 from 1996 until 2007. The error bars (bands) represent the statistical
-(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
+(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of
 the beam polarisation measurement.
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of the beam polarisation measurement.}
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
   \label{bsa_xbjrange2}

### 2011-12-20 theory.tex
Updated paper with the replies to the comments as discussed in the alst drafting meeting. In p[articular, restructured much of chapter 2 into chapter 1.

@@
 transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
-representing the initial (final) four-momentum of the proton; the average
+representing the initial (final) four-momentum of the \red{nucleon}; the average
 fraction $x$ of the nucleon's longitudinal momentum carried by the active
@@
 the skewness $\xi$; and the square $-Q^2=q^2$ of the four-momentum of
-the virtual photon that mediates the lepton-proton scattering
+the virtual photon that mediates the lepton-\red{nucleon} scattering
 process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
@@
 \subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
-\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
-which an electron/positron ($e$) interacts with a quark in the nucleon
+\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The \red{leading} DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
 ($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
@@
 photon ($\gamma$). The quark is absorbed by the nucleon with
-longitudinal momentum fraction
-$x-\xi$. (b): The Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
+longitudinal momentum fraction $x-\xi$. (b): The \red{leading} Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
 scattered lepton. It has the same initial and final states as DVCS.}
@@
 Exclusive leptoproduction of real photons
-($e\,p\,\rightarrow\,e'\,p'\,\gamma$) arises from
-two experimentally indistinguishable processes shown in
-figure~\ref{spin}: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-proton scattering with the
-emission of a Bremsstrahlung photon by the lepton. 
+($e\,N\,\rightarrow\,e'\,N'\,\gamma$) arises from
+two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-\red{nucleon} scattering with the
+emission of a Bremsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
 The BH process is calculable in the QED framework; this process is
@@
 charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
-the nucleon mass, and $\phi$ is the
+the \red{target} mass, and $\phi$ is the
 azimuthal angle between the scattering and production planes \cite{Tre04}.
@@
 Two sets of asymmetries measured at H{\sc
-ermes} with an unpolarised target and a polarised electron or positron
+ermes} with an unpolarised \red{Hydrogen} target and a polarised electron or positron
 beam are considered here:
@@
 cross sections with positive (negative) beam charge and
-$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
+$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
 to cross sections taken with beam spin parallel (anti-parallel) to the
@@
 contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
-suppressed by $\mathcal{O}(1/Q^{n-2})$. Table~\ref{tab_amplitudes}
-presents the asymmetry amplitudes extracted in this analysis and the
-related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
+suppressed by $\mathcal{O}(1/Q^{n-2})$.
 
-At H{\sc ermes} kinematic conditions, the leading twist beam-helicity asymmetry amplitude is $A_{\textrm{LU,I}}^{\sin\phi}$ and the leading beam-charge asymmetry amplitude is $A^{\cos\phi}_{\textrm{C}}$.
-These asymmetry amplitudes, for an unpolarised target, are sensitive respectively to Fourier coefficients $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+\red{T}he leading-twist Fourier coefficients are $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
 Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
@@
 and therefore GPD $H$ can be constrained through
-measurements of $A_{\textrm{LU,I}}^{\sin\phi}$ and $A^{\cos\phi}_{\textrm{C}}$.}
+measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.}
 

### 2011-12-21 macros/bsadvcsplots_tc_xbjrange_withfracs.C
assoc fractions added to figure 6 plot and macro added

@@ -1,0 +1,1420 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Dec 21 11:30:00 2011) by ROOT version5.28/00b
+   TCanvas *combined = new TCanvas("combined", "",3,22,1280,756);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.45);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.425);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.5);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0225095);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.75,0.379903,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2.695373,-0.45,-0.09691001,0.3);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(0);
+   pad1_1->SetLogx();
+   pad1_1->SetLeftMargin(0.25);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
[…]

### 2011-12-21 macros/bcaplots_tc_xbjrange_withfracs.C
added frac panel to fig 7

@@ -1,0 +1,1882 @@
+{
+//=========Macro generated from canvas: combined/
+//=========  (Wed Dec 21 12:41:45 2011) by ROOT version5.28/00b
+   TCanvas *combined = new TCanvas("combined", "",9,44,1007,729);
+   gStyle->SetOptStat(0);
+   combined->SetHighLightColor(2);
+   combined->Range(0,0,1,1);
+   combined->SetFillColor(0);
+   combined->SetBorderMode(0);
+   combined->SetBorderSize(2);
+   combined->SetLeftMargin(0.45);
+   combined->SetRightMargin(0.05);
+   combined->SetBottomMargin(0.425);
+   combined->SetFrameFillStyle(0);
+   combined->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1
+   TPad *pad1 = new TPad("pad1", "pad1",0,0,0.99,0.99);
+   pad1->Draw();
+   pad1->cd();
+   pad1->Range(0,0,1,1);
+   pad1->SetFillColor(0);
+   pad1->SetBorderMode(0);
+   pad1->SetBorderSize(2);
+   pad1->SetLeftMargin(0.5);
+   pad1->SetRightMargin(0.0135135);
+   pad1->SetTopMargin(0.0225095);
+   pad1->SetFrameFillStyle(0);
+   pad1->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: pad1_1
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.8,0.379903,1);
+   pad1_1->Draw();
+   pad1_1->cd();
+   pad1_1->Range(-2.695373,-0.35,-0.09691001,0.25);
+   pad1_1->SetFillStyle(4000);
+   pad1_1->SetBorderMode(0);
+   pad1_1->SetBorderSize(0);
+   pad1_1->SetLogx();
+   pad1_1->SetLeftMargin(0.25);
+   pad1_1->SetRightMargin(0);
+   pad1_1->SetTopMargin(0);
+   pad1_1->SetBottomMargin(0);
+   pad1_1->SetFrameFillColor(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   pad1_1->SetFrameFillStyle(0);
+   pad1_1->SetFrameBorderMode(0);
+   
[…]

### 2012-01-10 macros/bsadvcsplots_tc_xbjrange_withfracs.C
2-d plots edited as required

@@ -1,7 +1,7 @@
 {
 //=========Macro generated from canvas: combined/
 //=========  (Wed Dec 21 11:30:00 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",3,22,1280,756);
+   TCanvas *combined = new TCanvas("combined", "",3,22,1280,900);
    gStyle->SetOptStat(0);
    combined->SetHighLightColor(2);
    combined->Range(0,0,1,1);
@@ -29,7 +29,7 @@
    pad1->SetFrameBorderMode(0);
   
 // ------------>Primitives in pad: pad1_1
-   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.75,0.379903,1);
+   pad1_1 = new TPad("pad1_1", "pad1_1",0,0.75,0.4,1);
    pad1_1->Draw();
    pad1_1->cd();
    pad1_1->Range(-2.695373,-0.45,-0.09691001,0.3);
@@ -37,7 +37,7 @@
    pad1_1->SetBorderMode(0);
    pad1_1->SetBorderSize(0);
    pad1_1->SetLogx();
-   pad1_1->SetLeftMargin(0.25);
+   pad1_1->SetLeftMargin(0.3);
    pad1_1->SetRightMargin(0);
    pad1_1->SetTopMargin(0);
    pad1_1->SetBottomMargin(0);
@@ -56,7 +56,7 @@
    hframe__1__1__1->GetXaxis()->SetNdivisions(505);
    hframe__1__1__1->GetXaxis()->SetLabelSize(0.1);
    hframe__1__1__1->GetXaxis()->SetTitleSize(0.1);
-   hframe__1__1__1->GetXaxis()->SetTitleOffset(1.01);
+   hframe__1__1__1->GetXaxis()->SetTitleOffset(1.1);
    hframe__1__1__1->GetYaxis()->SetTitle("A_{LU,I}^{sin #phi}");
    hframe__1__1__1->GetYaxis()->CenterTitle(true);
    hframe__1__1__1->GetYaxis()->SetNdivisions(205);
@@ -64,7 +64,7 @@
    hframe__1__1__1->GetYaxis()->SetLabelOffset(0.02);
    hframe__1__1__1->GetYaxis()->SetLabelSize(25);
    hframe__1__1__1->GetYaxis()->SetTitleSize(35);
[…]

### 2012-01-10 background_and_systematic_dual.tex
Updated with commetns from the DC before christmas

@@
 effects due to detector resolution \red{(e.g.
-the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter)}, radiative processes during detection \red{(e.g.
-e.m.
-showers in the calorimeter being incorrectly reconstructed)}, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter)}, \red{external radiation in detector material}, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
@@
   surveying measurements.
-\red{However, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
-The systematic uncertainty contribution due to potential from misalignment is so small as to be negligible, so this information is given purely for completeness.}
+\red{Therefore, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
+This overestimate is very slight, because the systematic uncertainty contribution from potential misalignment is very small.}
 
@@
 The beam polarisation measurement has total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period.
-\red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without consideration in the other presented uncertainties.
+\red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without \red{inclusion} in the other presented uncertainties.
 
-The data sample in the exclusive region contains events involving production of real photons in which the proton remains intact and
+The data sample in the exclusive region contains events \red{not only} involving production of real photons in which the proton remains intact, \red{but also}
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of the latter events from the rest of the data sample.
+resonant state (``associated production'').
+The recoiling proton is not detected and the calorimeter resolution does not allow separation of \red{all of} the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these

### 2012-01-10 experiment_and_data.tex
Updated with commetns from the DC before christmas

@@
 target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$~\cite{Ben01}, with average beam polarisations of 30.3\,\% and 39.2\% \cite{tpol,lpol}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$~\cite{Ben01}, with average beam polarisations of \red{$0.303$ and $0.392$.} \cite{tpol,lpol}.
 The procedure used to select events is similar to that used in ref.~\cite{Air09}.
@@
 $\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
-rest frame. The polar angle between the virtual and real photons was required to
+rest frame. The polar angle between the \red{directions of the} virtual and real photons was required to
 be within the limits 5~mrad $<$
@@
 
-An event sample was selected using a missing-mass technique requiring
+An event sample was selected requiring
 that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{P}-q')^{2}$
@@
 energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
-four-momentum of the virtual photon, $M_{P}$ is the initial four-momentum
-of the target proton\red{, i.e. the mass of the proton,} and $q'$ is the four-momentum of the produced
+four-momentum of the virtual photon, $p$ is the initial four-momentum
+of the target proton and $q'$ is the four-momentum of the produced
 photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
@@
  \langle N(e_{\ell},P_{\ell},\phi)\rangle =
-\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\textrm{d}\sigma_{\textrm{UU}}
+\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\sigma_{\textrm{UU}}
 (\phi)\times
@@
 efficiency and d$\sigma_{\textrm{UU}}$ denotes the
-cross section for an unpolarised target integrated over both beam charges and
+cross section for an unpolarised target \red{summed} over both beam charges and
 beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
@@
 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$
-amplitudes are higher twist quantities (see Table~\ref{tab_amplitudes}).
+amplitudes \red{depend upon} higher twist quantities (see Table~\ref{tab_amplitudes}).
 
-The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ has a
+The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ \red{receives} a
 contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small at HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small \red{in} HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^3K}{(1-y)(2-2y+y^2)}$
 \\

### 2012-01-10 frame_dual.tex
Updated with commetns from the DC before christmas

@@
 set of 1996-2005 previously analysed in the same manner by \red{\sc{Hermes}}. Results from the two data sets are found to be
-compatible with each other. Combined results from these data sets are
-extracted and represent the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
+compatible with each other. \red{Results from these combined} data sets are
+extracted and \red{are} the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
 }

### 2012-01-10 results_dual.tex
2-d plots edited as required
Updated with commetns from the DC before christmas

@@
 \section{Results}
-Results for the beam-helicity and beam-charge asymmetry amplitudes extracted 
-\red{in Ref.~\cite{fd} from the previously published 1996-2005 data set} and \red{the results extracted from the 2006-2007 hydrogen data sets in this work} are \red{compared} in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{fd} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc.
-fraction''), which is shown in the bottom row of each figure.
 The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.

### 2012-01-10 theory.tex
Updated with commetns from the DC before christmas

@@
 Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
-comprehensive description of the structure of the nucleon.
-Although GPDs are difficult to access experimentally, the {\sc Hermes}
-\red{C}ollaboration has previously published results
-\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
-the \red{exclusive} leptoproduction of real photons from a nucleon or nucleus that can
-be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
+comprehensive description of the structure of the nucleon. A thorough
 description of the nucleon in terms of GPDs would allow the deduction
@@
 construction of a longitudinal-momentum-dissected transverse spatial map of parton positions.
+\red{There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{air09}).
+In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus is the simplest to describe mathematically and is the most widely-used reaction channel for such work.}
 
@@
 which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-\red{nucleon} scattering with the
-emission of a Bremsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
+emission of a \red{b}remsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
 The BH process is calculable in the QED framework; this process is
@@
 scattering amplitudes of the two processes interfere and the large BH amplitude
-amplifies the contribution of the DVCS amplitude to the interference term. 
-It is through the study of this interference term at H{\sc ermes} that
-useful information for the constraint of certain GPDs can be obtained \cite{Bel02b}.
+amplifies \red{the interference term, which is proporional to the DVCS amplitude.
+At H{\sc ermes} kinematic conditions, it is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained~\cite{Bel02b}, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs}.
 
@@
 Two sets of asymmetries measured at H{\sc
-ermes} with an unpolarised \red{Hydrogen} target and a polarised electron or positron
+ermes} with an unpolarised \red{hydrogen} target and a polarised electron or positron
 beam are considered here:
@@
 \displaystyle\sum_{n=1}^2
-s_{n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
 (\phi)\mathcal{P}_{
@@
 \displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{BH}}\cos(n\phi) + 
-K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},& 
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)},& 
 \label{e:alui}
@@
 %\\ \nonumber
-&=\dfrac{ K_{\textrm{DVCS}} s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+&=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
 (\phi)\mathcal{P}_{2}(\phi)}
 \displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{BH}}\cos(n\phi) + 
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
 \label{e:aludvcs}
@@
 \displaystyle\sum_{n=0}^3
-c_{n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
 (\phi)\mathcal{P}_
@@
 \displaystyle\sum_{n=0}^2
-c_{n}^{\textrm{BH}}\cos(n\phi) + 
-K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)} ,&
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} ,&
 \label{e:ac}
@@
 where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
-cross sections with positive (negative) beam charge and
+\red{the differential} cross section with positive (negative) beam charge and
 $\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
-to cross sections taken with beam spin parallel (anti-parallel) to the
+to \red{differential} cross section taken with beam spin parallel (anti-parallel) to the
 beam momentum.
 
-\red{The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{I}}$ Fourier
-coefficients depend on ``$\mathcal{C}$-functions'' \cite{{Bel02b}}, each of which is a
-combination of complex Compton Form Factors (CFFs). A CFF is a
-convolution of a GPD with a hard scattering kernel. Contributions of
-GPDs to the cross section may be relatively suppressed by powers of
+The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{\red{W}}}$ Fourier
+coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
+combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
+\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}. Contributions to the cross section may be relatively suppressed by powers of
 $1/Q$, the origin of which may be kinematic in nature or due to the
-twist-level of the GPD. Leading twist is twist-2. Typically, the
-contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
+twist-level of the GPD\red{s appearing in that contribution}. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
 suppressed by $\mathcal{O}(1/Q^{n-2})$.
 
-\red{T}he leading-twist Fourier coefficients are $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
-Both of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
+\red{The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+All} of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
 \begin{eqnarray}
-s_{1,\textrm{unp}}^{\textrm{I}} \approx&\,\,\,\,8\lambda ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}&\label{eq:s1}
+c_{0,\textrm{unp}}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
 \\
- c_{1,\textrm{unp}}^{\textrm{I}} \approx&8k(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,&\label{eq:c1}
+s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}\label{eq:s1}
+\\
+c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,.\label{eq:c1}
 \end{eqnarray}
-where the definition of the kinematic factor $k$ is found
-  in ref.\cite{Bel02b}. The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
+\red{The definition of the kinematic factor \red{$K$ is~\cite{Bel02b}}
+\begin{equation}
+K=\sqrt{\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
+\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace}
+\end{equation} 
+where $y$ is the fractional energy transfer from the beam lepton the virtual photon.
+The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that these amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.}
+The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
 written
@@
 $\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
-$\widetilde{H}$ and $E$.  At H{\sc ermes} kinematic
+$\widetilde{H}$ and $E$.  In H{\sc ermes} kinematic
 conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
@@
 and therefore GPD $H$ can be constrained through
-measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.}
+measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.
 
-Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger,
-independent data set taken during the years 2006 and 2007 after the
-experiment was upgraded in the target region. The work covered
+Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the
+experiment was \red{augmented} in the target region. The work covered
   in this publication combines the data taken in 1996-2005 with this

### 2012-01-10 experiment_and_data.tex
finishing comments

@@
 0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
+\red{The data sample in the exclusive region contains events \red{not only} involving production of real photons in which the proton remains intact, \red{but also}
+events involving the excitation of the target proton to a $\Delta^+$
+resonant state (``associated production'').
+The recoiling proton is not detected and the calorimeter resolution does not allow separation of \red{all of} the latter events from the rest of the data sample.
+No systematic uncertainty is assigned for the contribution from these
+events; they are treated as part of the signal. A Monte Carlo
+calculation based on the parameterisation from ref.~\cite{Bra76} is
+used to estimate the fractional contribution to the event sample from resonant
+production in each kinematic bin.
+The results, called the associated fractions and labelled ``Assoc.
+fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section.
+The method used to perform this estimation is described in detail in
+ref.~\cite{Air08}.}
 
@@
 cross section for an unpolarised target \red{summed} over both beam charges and
-beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$,
-$\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$ and
+beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$, $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$ and
 $\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
 $\phi$ as
+\begin{equation}
+ \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
+A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
++ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
+\label{aludvcs_asym}
+\end{equation}
 \begin{equation}
@@
 \label{alui_asym}
-\end{equation}
-\begin{equation}
- \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
-A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
-+ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
-\label{aludvcs_asym}
 \end{equation}
@@
 eqs.~\ref{e:alui}-\ref{e:ac}.
-The asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$,
-$A^{\cos(0\phi)}_{\textrm{C}}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ also depend
-upon this $\mathcal{C}$-function. However, the
-$A^{\cos(0\phi)}_{\textrm{C}}$ amplitude is kinematically suppressed
-compared to the $A^{\cos\phi}_{\textrm{C}}$ amplitude, and the
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$
-amplitudes \red{depend upon} higher twist quantities (see Table~\ref{tab_amplitudes}).
 
@@
 
+\red{The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}.
+Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{0,\textrm{unp}}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{1,\textrm{unp}}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
+
+Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation.
+Neglecting antiquark-gluon-quark contributions, these higher-twist dependent amplitudes can be considered as being kinematically suppressed compared to the leading-twist amplitudes.}
+
 The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
@@
 $\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
-in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
-where $\alpha_{\textrm{S}}$ is the strong coupling constant. Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
-related Fourier coefficients, dominant $\mathcal{C}$-function, twist-level and level of suppression.
+in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
+related Fourier coefficients, dominant $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
 \begin{table}
@@
 \hline
-Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level & Relative Suppression   \\ 
+Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level   \\ 
 \hline
@@
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
-&  2 & --\\
+&  2 \\
 \hline
@@
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
-&  3 & $1/Q$\\
+&  3 \\
 \hline
@@
 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
-$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
+$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 \\
 \hline
@@
 $A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^3K}{(1-y)(2-2y+y^2)}$
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
 \\
@@
 $A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
 \\
@@
 $A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
-$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 \\
 \hline
 $A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
-$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
+$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 \\
 \hline

### 2012-01-11 macros/bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C
added error bands to bca plot

@@ -48,7 +48,7 @@
    pad1_1->SetFrameBorderMode(0);
    
    TH1F *hframe__1 = new TH1F("hframe__1","",3,0,2);
-   hframe__1->SetMinimum(-0.15);
+   hframe__1->SetMinimum(-0.225);
    hframe__1->SetMaximum(0.15);
    hframe__1->SetDirectory(0);
    hframe__1->SetStats(0);
@@ -89,6 +89,29 @@
    gre->SetHistogram(Graph1);
    
    gre->Draw("p");
+	
+	float overall_s = 0.5;
+	float overall_e = 1.5;
+	
+	float c0_o_s = -0.15;
+	float c0_o_y = 0.011;
+	float c0_o_e;
+	c0_o_e = c0_o_s + c0_o_y;
+	
+	float c0_o_s2 = -0.2;
+	float c0_o_y2 = 0.008;
+	float c0_o_e2;
+	c0_o_e2 = c0_o_s2 + c0_o_y2;
+	
+	
+	Double_t *dum = 0;
+	pline = new TPolyLine(4,dum,dum,"");
+	pline->SetFillColor(2);
+	pline->SetPoint(0,overall_s,c0_o_s);
+	pline->SetPoint(1,overall_s,c0_o_e);
+	pline->SetPoint(2,overall_e,c0_o_e);
+	pline->SetPoint(3,overall_e,c0_o_s);
+	pline->Draw("fsame");
    
    gre = new TGraphErrors(1);
    gre->SetName("Graph");
@@ -128,23 +151,16 @@
    
    gre->Draw("p");
    
-   gre = new TGraphErrors(1);
-   gre->SetName("Graph");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-   gre->SetLineColor(4);
-   gre->SetMarkerColor(4);
-   gre->SetMarkerStyle(26);
-   gre->SetPoint(0,1.2,-0.02);
-   gre->SetPointError(0,0,0.01);
-   
-   TH1F *Graph4 = new TH1F("Graph4","Graph",100,1.1,2.3);
-   Graph4->SetMinimum(-0.032);
-   Graph4->SetMaximum(-0.008);
-   Graph4->SetDirectory(0);
-   Graph4->SetStats(0);
-   gre->SetHistogram(Graph4);
-   
+	Double_t *dum = 0;
+	pline = new TPolyLine(4,dum,dum,"");
+	pline->SetFillColor(4);
[…]

### 2012-01-11 background_and_systematic_dual.tex

@@
 
-The data sample in the exclusive region contains events \red{not only} involving production of real photons in which the proton remains intact, \red{but also}
-events involving the excitation of the target proton to a $\Delta^+$
-resonant state (``associated production'').
-The recoiling proton is not detected and the calorimeter resolution does not allow separation of \red{all of} the latter events from the rest of the data sample.
-No systematic uncertainty is assigned for the contribution from these
-events; they are treated as part of the signal. A Monte Carlo
-calculation based on the parameterisation from ref.~\cite{Bra76} is
-used to estimate the fractional contribution to the event sample from resonant
-production in each kinematic bin.
-The results, called the associated fractions and labelled ``Assoc.
-fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section.
-The method used to perform this estimation is described in detail in
-ref.~\cite{Air08}.
-
 \begin{table}

### 2012-01-11 macros/bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C
bca error bands added

@@ -1,7 +1,7 @@
 {
 //=========Macro generated from canvas: combined/
-//=========  (Thu Oct  6 15:04:47 2011) by ROOT version5.28/00b
-   TCanvas *combined = new TCanvas("combined", "",0,22,1200,756);
+//=========  (Wed Jan 11 18:10:10 2012) by ROOT version5.28/00b
+   TCanvas *combined = new TCanvas("combined", "",0,44,1200,756);
    gStyle->SetOptStat(0);
    combined->SetHighLightColor(2);
    combined->Range(0,0,1,1);
@@ -33,7 +33,7 @@
    pad1_1 = new TPad("pad1_1", "pad1_1",0,0.825,0.25,1);
    pad1_1->Draw();
    pad1_1->cd();
-   pad1_1->Range(-2,-0.15,2,0.15);
+   pad1_1->Range(-2,-0.225,2,0.15);
    pad1_1->SetFillStyle(4000);
    pad1_1->SetBorderMode(0);
    pad1_1->SetBorderSize(2);
@@ -47,26 +47,26 @@
    pad1_1->SetFrameFillStyle(0);
    pad1_1->SetFrameBorderMode(0);
    
-   TH1F *hframe__1 = new TH1F("hframe__1","",3,0,2);
-   hframe__1->SetMinimum(-0.225);
-   hframe__1->SetMaximum(0.15);
-   hframe__1->SetDirectory(0);
-   hframe__1->SetStats(0);
-   hframe__1->GetXaxis()->SetBinLabel(2,"Integrated Overall");
-   hframe__1->GetXaxis()->SetBit(TAxis::kLabelsHori);
-   hframe__1->GetXaxis()->SetLabelOffset(0.015);
-   hframe__1->GetXaxis()->SetLabelSize(0.01);
-   hframe__1->GetXaxis()->SetTickLength(0);
-   hframe__1->GetYaxis()->SetTitle("A_{C}^{cos (0#phi)}");
-   hframe__1->GetYaxis()->CenterTitle(true);
-   hframe__1->GetYaxis()->SetNdivisions(205);
-   hframe__1->GetYaxis()->SetLabelFont(63);
-   hframe__1->GetYaxis()->SetLabelOffset(0.05);
-   hframe__1->GetYaxis()->SetLabelSize(25);
-   hframe__1->GetYaxis()->SetTitleSize(35);
[…]

### 2012-01-11 macros/bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual.C
bsa error bands added

@@ -48,7 +48,7 @@
    pad1_1->SetFrameBorderMode(0);
    
    TH1F *hframe__1__1 = new TH1F("hframe__1__1","",3,0,2);
-   hframe__1__1->SetMinimum(-0.65);
+   hframe__1__1->SetMinimum(-0.69);
    hframe__1__1->SetMaximum(0.25);
    hframe__1__1->SetDirectory(0);
    hframe__1__1->SetStats(0);
@@ -89,25 +89,34 @@
    Graph11->SetStats(0);
    gre->SetHistogram(Graph11);
    
-   gre->Draw("p");
-   
-   gre = new TGraphErrors(1);
-   gre->SetName("Graph");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-   gre->SetLineColor(2);
-   gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,1,-0.222422);
-   gre->SetPointError(0,0,0.0325037);
-   
-   TH1F *Graph22 = new TH1F("Graph22","Graph",100,0.9,2.1);
-   Graph22->SetMinimum(-0.2614264);
-   Graph22->SetMaximum(-0.1834176);
-   Graph22->SetDirectory(0);
-   Graph22->SetStats(0);
-   gre->SetHistogram(Graph22);
-   
+	float s1i_o_s =-0.6
+	float s1i_o_e;
+	s1i_o_e=-0.6+0.022;
+	
+	float s1i_o_s2=-0.67
+	float s1i_o_e2;
+	s1i_o_e2=-0.67+0.020;
+	
+	Double_t *dum = 0;
+	TPolyLine *pline = new TPolyLine(4,dum,dum,"");
+	pline->SetFillColor(2);
+	pline->SetPoint(0,0.5,s1i_o_s);
+	pline->SetPoint(1,0.5,s1i_o_e);
+	pline->SetPoint(2,1.5,s1i_o_e);
+	pline->SetPoint(3,1.5,s1i_o_s);
+	pline->Draw("fsame");
+	
+	Double_t *dum = 0;
+	TPolyLine *pline = new TPolyLine(4,dum,dum,"");
+	pline->SetFillColor(4);
+	pline->SetFillStyle(0);
+	pline->SetPoint(0,0.5,s1i_o_s2);
+	pline->SetPoint(1,0.5,s1i_o_e2);
+	pline->SetPoint(2,1.5,s1i_o_e2);
[…]

### 2012-01-12 background_and_systematic_dual.tex
Slight changes to text, halfway through fixing the bibliography

@@
-1\section{Background Corrections and Systematic Uncertainties for the
+\section{Background Corrections and Systematic Uncertainties for the
   2006-2007 Data}
@@
 
-The contribution from each uncertainty to each amplitude extracted in a single, overall kinematic bin from the 2006-2007 data  is summarised in Table~\ref{table_systematic_contributions_0607}.
+The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data \red{(in a single, overall kinematic bin)} is summarised in Table~\ref{table_systematic_contributions_0607}.
 
-The beam polarisation measurement has total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period.
+The beam polarisation measurement\red{s} ha\red{ve} total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period.
 \red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without \red{inclusion} in the other presented uncertainties.

### 2012-01-12 results_dual.tex
Slight changes to text, halfway through fixing the bibliography

@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_dual}
+    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_withfrac.pdf}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance is not so evident for the beam-helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007 than in 1996-2005, giving the 2006-2007 data a lower weighting in the combined fit.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes \red{as it is for the beam-charge asymettry amplitudes,} because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 \red{and thus the 2006-2007 data has} a lower weighting in the combined fit.
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
@@
 The leading\red{-}twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $K$ from \red{e}q.~\ref{eq:K}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.

### 2012-01-12 theory.tex
Slight changes to text, halfway through fixing the bibliography

@@
 Generalised Parton Distributions (GPDs)
-\cite{Mue94,Ji97a,Rad97} encompass the familiar Parton
+\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
 Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
@@
 of the total angular momentum of partons in the nucleon, and the
-construction of a longitudinal-momentum-dissected transverse spatial map of parton positions.
-\red{There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{air09}).
+construction of a longitudinal-momentum-dissected transverse spatial map of parton positions~\cite{Bur00}.
+\red{There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).
 In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus is the simplest to describe mathematically and is the most widely-used reaction channel for such work.}
@@
 by the active quark at the start and end of the process, written as
-the skewness $\xi$; and the square $-Q^2=q^2$ of the four-momentum of
+the skewness $\xi$; and \red{$Q^2=-(q^2)$, i.e. }the negative square of the four-momentum of
 the virtual photon that mediates the lepton-\red{nucleon} scattering
@@
 $\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
-to \red{differential} cross section taken with beam spin parallel (anti-parallel) to the
+to \red{the differential} cross section taken with beam spin parallel (anti-parallel) to the
 beam momentum.
@@
 combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
-\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}. Contributions to the cross section may be relatively suppressed by powers of
-$1/Q$, the origin of which may be kinematic in nature or due to the
-twist-level of the GPD\red{s appearing in that contribution}. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
+\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}.
+Contributions to the cross section \red{are} relatively suppressed by \red{factors that} may be kinematic in nature or due to the twist-level of the GPD\red{s appearing in that contribution}.
+Leading twist is twist-2.
+Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
 suppressed by $\mathcal{O}(1/Q^{n-2})$.
@@
 K=\sqrt{\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
-\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace}
+\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace}\label{eq:K}
 \end{equation} 
 where $y$ is the fractional energy transfer from the beam lepton the virtual photon.
-The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that these amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.}
+The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.}
 The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
@@
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in eq.~\ref{Eq_cunp} (in first approximation) with respect to $\mathcal{H}$ since they
+neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ \red{(in first approximation)} since they
 are kinematically suppressed by an order of magnitude or more.

### 2012-01-13 results_dual.tex
Fixed label sizes on the plots

--- 2012-01-10 results_dual.tex
@@
 \begin{center}
-\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
+\includegraphics[width=15cm,keepaspectratio]{macros/bsa_both_morgan}
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
@@
 \begin{center}
- \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual}
+ \includegraphics[width=15cm,keepaspectratio]{macros/bca_both_morgan}
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual_update_1.pdf}
+ \includegraphics[width=15cm]{macros/morgan_change}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual}
+    \includegraphics[width=15cm]{macros/morgan_change2}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
@@
  \begin{center}
- \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual}
+ \includegraphics[width=15cm]{macros/bsa_2d_morgan}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic_dual}
+    \includegraphics[width=15cm]{macros/bca_2d_morgan}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.

### 2012-01-13 macros/bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C

@@ -749,7 +749,8 @@
    TLegend *leg = new TLegend(0.07,0.63,0.83,0.99,NULL,"b1NDC");
    leg->SetBorderSize(0);
    leg->SetTextColor(4);
-   leg->SetTextFont(62);
+   leg->SetTextFont(13);
+   leg->SetTextSize(18);
    leg->SetLineColor(0);
    leg->SetLineStyle(1);
    leg->SetLineWidth(1);

### 2012-01-13 macros/bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_dual.C

@@ -140,12 +140,17 @@
    gre->SetHistogram(Graph1);
    
    gre->Draw("p");
-   TLatex *   tex = new TLatex(0.022,0.15,"0.03 < x_{B} < 0.08");
-   tex->SetTextSize(0.12);
+   TLatex *   tex = new TLatex(0.04,0.15,"0.03 < x_{B} < 0.08");
+
+   // Alterations from stock
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
- tex = new TLatex(0.02,0.06,"<Q^{2}> 1.56 GeV^{2}");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.06,"<Q^{2}> 1.56 GeV^{2}");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
+   // end alterations from stock
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_1->Modified();
@@ -550,12 +555,14 @@
    gre->SetHistogram(Graph6);
    
    gre->Draw("p");
-      tex = new TLatex(0.02,0.16,"0.08 < x_{B} < 0.12");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.16,"0.08 < x_{B} < 0.12");
+   tex->SetTextFont(43);   
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
- tex = new TLatex(0.02,0.06,"<Q^{2}> 2.52 GeV^{2}");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.06,"<Q^{2}> 2.52 GeV^{2}");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_2->Modified();
@@ -952,12 +959,14 @@
    gre->SetHistogram(Graph11);
    
    gre->Draw("p");
-      tex = new TLatex(0.022,0.16,"0.12 < x_{B} < 0.35");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.16,"0.12 < x_{B} < 0.35");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
[…]

### 2012-01-13 experiment_and_data.tex
Added covmat plot

@@
 target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$~\cite{Ben01}, with average beam polarisations of \red{$0.303$ and $0.392$.} \cite{tpol,lpol}.
-The procedure used to select events is similar to that used in ref.~\cite{Air09}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of \red{$0.303$ and $0.392$.} The procedure used to select events is similar to that used in ref.~\cite{Air09}.
 A brief summary of this procedure is outlined in the following; consult

### 2012-01-13 results_dual.tex
Added covmat plot

--- 2012-01-12 results_dual.tex
@@
 In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.

### 2012-01-13 results_dual.tex

@@
   \begin{center}
-    \includegraphics[width=15cm]{bcaplots_tc_xbjrange_withfrac.pdf}
+    \includegraphics[width=15cm]{macros/bca_2d_morgan}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.

### 2012-01-17 background_and_systematic_dual.tex
version 2.2

@@
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
-An event generator based on the GPD model described in ref\red{s}.~\cite{Van99,Goe01} was
+An event generator based on the GPD model described in ref.~\cite{Guz06} was
 used for the simulation because it describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted

### 2012-01-17 experiment_and_data.tex
version 2.2

@@
 used to estimate the fractional contribution to the event sample from resonant
-production in each kinematic bin.
-The results, called the associated fractions and labelled ``Assoc.
+production in each kinematic bin --- the uncertainty on this estimate
+cannot be adequately quantified because no measurements have been made
+in the H{\sc ermes} kinematic region.
+The results of the estimate, called the associated fractions and labelled ``Assoc.
 fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section.
@@
 $A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
-coefficients $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{I}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+coefficients $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{I}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
 may also be affected by the lepton propagators and the other
@@
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small \red{in} HERMES kinematic conditions due to the size of the $s_{1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small \red{in} HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it
@@
 \red{The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}.
-Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{0,\textrm{unp}}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{1,\textrm{unp}}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
+Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
 
@@
 The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
-$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
+$c_{\textrm{unp},3}^{\textrm{I}}$ Fourier coefficient and hence the
 $\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
@@
 be extracted from the available data set, the related Fourier
-coefficients, dominant $\mathcal{C}$-function, twist-level and level of
-suppression relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
+coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in ref.~\ref{eq:K}}.}
 \label{tab_amplitudes}

### 2012-01-17 results_dual.tex
version 2.2

@@
 \section{Results}
-\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{fd} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{Air09} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 the 1996-2005 (open triangles) and 2006-2007 (filled squares)
-hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
+hydrogen data. \red{The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.}  
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
@@
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
-The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature.
-The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+\red{The error bars represent the statistical uncertainties.
+The error bands represent the systematic uncertainties.} The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{release_bca_0607}
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.
+\red{The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row}}
   \label{bsa_xbjrange2}
@@
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
-The error bars (bands) represent the statistical (systematic) uncertainties.}
+The error bars (bands) represent the statistical (systematic) uncertainties.
+\red{The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row}}
   \label{bca_xbjrange2}
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance is not so evident for the beam-helicity asymmetry amplitudes \red{as it is for the beam-charge asymettry amplitudes,} because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 \red{and thus the 2006-2007 data has} a lower weighting in the combined fit.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes \red{as it is for the beam-charge asymmetry amplitudes,} because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 \red{and thus the 2006-2007 data has} a lower weighting in the combined fit.
 The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
@@
 In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab\red{.}; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.
@@
 No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.
+\red{The results from this paper will be made available in the Durham Database in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.}

### 2012-01-17 summary.tex
version 2.2

@@
 No additional features are observed in any particular $x_{\textrm{B}}$-bin.
-\red{The results from this paper will be made available in 4 bins in the Durham Database.}
 
 \acknowledgments
+
 We gratefully acknowledge the \desy\ management for its support and the staff

### 2012-01-17 theory.tex
version 2.2

@@
  \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
-  c_{n,\textrm{unp}}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
+  c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
 |\tau_{\textrm{DVCS}}|^{2} &=&
@@
 \sum_{n=1}^2
-c_{n,\textrm{unp}}^{\textrm{DVCS}}\cos(n\phi) + \lambda
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
 s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
@@
 I}}+
-\sum_{n=1}^3 c_{n,\textrm{unp}}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
-s_{n,\textrm{unp}}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
+\sum_{n=1}^3 c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
+s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
 \end{eqnarray}
@@
 the target rest frame. A full
-explanation of the Fourier coefficients [$c_{n,\textrm{unp}}^V,s_{n,\textrm{unp}}^W$]
+explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]
 ($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be found in ref.~\cite{Bel02b}.
@@
 
-The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{\red{W}}}$ Fourier
+The $s_{\textrm{unp}\red{,n}}^{W}$ and $c_{\textrm{unp}\red{,n}}^{\textrm{\red{W}}}$ Fourier
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a

### 2012-01-17 macros/bsadvcsplots_tc_xbjrange_withfracs.C

@@ -138,12 +138,14 @@
    gre->SetHistogram(Graph111);
    
    gre->Draw("p");
-   TLatex *   tex = new TLatex(0.022,0.15,"0.03 < x_{B} < 0.08");
-   tex->SetTextSize(0.12);
+   TLatex *   tex = new TLatex(0.04,0.15,"0.03 < x_{B} < 0.08");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.02155416,0.05141525,"<Q^{2}> = 1.56 GeV^{2}");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.05141525,"<Q^{2}> = 1.56 GeV^{2}");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_1->Modified();
@@ -613,12 +615,14 @@
    gre->SetHistogram(Graph666);
    
    gre->Draw("p");
-      tex = new TLatex(0.02,0.16,"0.08 < x_{B} < 0.12");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.16,"0.08 < x_{B} < 0.12");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.02,0.06,"<Q^{2}> = 2.52 GeV^{2}");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.06,"<Q^{2}> = 2.52 GeV^{2}");
+   tex->SetTextFont(43);
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_2->Modified();
@@ -1072,12 +1076,14 @@
    gre->SetHistogram(Graph111111);
    
    gre->Draw("p");
-      tex = new TLatex(0.022,0.16,"0.12 < x_{B} < 0.35");
-   tex->SetTextSize(0.12);
+   tex = new TLatex(0.04,0.16,"0.12 < x_{B} < 0.35");
+   tex->SetTextFont(43);  
+   tex->SetTextSize(18);
    tex->SetLineWidth(2);
    tex->Draw();
[…]

### 2012-01-17 background_and_systematic_dual.tex
Started work on version 2.3 prior to meeting tomorrow

@@
 production is predominantly due to the failure to identify one of
-  the two photons from the decay of produced neutral mesons. The procedure for estimating the corresponding
+  the two photons from the decay of \red{these} neutral mesons. The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
 The predominant contribution to the systematic uncertainty arises from detector
-effects. \red{These include} the acceptance of the spectrometer, smearing
-effects due to detector resolution \red{(e.g.
-the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter)}, \red{external radiation in detector material}, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+effects. These include the acceptance of the spectrometer, smearing
+effects due to detector resolution (e.g.
+the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
 An event generator based on the GPD model described in ref.~\cite{Guz06} was
-used for the simulation because it describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
+used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
 from these simulated events using the same analysis procedure used to
@@
   surveying measurements.
-\red{Therefore, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
-This overestimate is very slight, because the systematic uncertainty contribution from potential misalignment is very small.}
+Therefore, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
+This overestimate is very slight, because the systematic uncertainty contribution from potential misalignment is very small.
 
-The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data \red{(in a single, overall kinematic bin)} is summarised in Table~\ref{table_systematic_contributions_0607}.
+The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in Table~\ref{table_systematic_contributions_0607}.
 
-The beam polarisation measurement\red{s} ha\red{ve} total uncertaint\red{ies} of 2.8\% \red{for the 1996-2005 data-taking period} and 3.4\% for the 2006-2007 data taking period.
-\red{These uncertainties are present} in the beam-helicity amplitudes and \red{are} quoted as independent scale uncertaint\red{ies} without \red{inclusion} in the other presented uncertainties.
+The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
+These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
 

### 2012-01-17 experiment_and_data.tex
Started work on version 2.3 prior to meeting tomorrow

@@
 electron and positron beams incident upon an unpolarised hydrogen gas
-target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of \red{$0.303$ and $0.392$.} The procedure used to select events is similar to that used in ref.~\cite{Air09}.
-A brief summary of this procedure is outlined in the following; consult
-refs.~\cite{Zei09,Bur10} for more details.
+target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples are
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of $0.303$ and $0.392$ \red{respectively}.
+The procedure used to select events is similar to that used in ref.~\cite{Air09}.
+A brief summary of this procedure is outlined in the following; \red{more details are given in refs.~\cite{Zei09,Bur10}.}
 
-An event
-was selected as having exactly one photon and one lepton
+\red{Events were selected if} having exactly one photon and one lepton
 track detected within the acceptance of the spectrometer.
@@
 $\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
-rest frame. The polar angle between the \red{directions of the} virtual and real photons was required to
+rest frame. The polar angle between the directions of the virtual and real photons was required to
 be within the limits 5~mrad $<$
@@
 corresponded to the square of the proton mass within the limits of the
-energy resolution of the H{\sc ermes} \red{spectrometer (mainly the calorimeter)}. Here, $q$ is the
+energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). Here, $q$ is the
 four-momentum of the virtual photon, $p$ is the initial four-momentum
@@
 0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
-\red{The data sample in the exclusive region contains events \red{not only} involving production of real photons in which the proton remains intact, \red{but also}
+The data sample in the exclusive region contains events not only involving production of real photons in which the proton remains intact, but also
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state (``associated production'').
-The recoiling proton is not detected and the calorimeter resolution does not allow separation of \red{all of} the latter events from the rest of the data sample.
+resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
@@
 The method used to perform this estimation is described in detail in
-ref.~\cite{Air08}.}
+ref.~\cite{Air08}.
 
@@
 efficiency and d$\sigma_{\textrm{UU}}$ denotes the
-cross section for an unpolarised target \red{summed} over both beam charges and
+cross section for an unpolarised target summed over both beam charges and
 beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$, $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$ and
@@
 where the approximation is due to the truncation of the infinite
-Fourier series that would describe the fitted distribution
-  perfectly. Only the $\sin(n\phi)$ terms of the
+Fourier series that would describe \red{exactly} the fitted distribution. Only the $\sin(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
-$\mathcal{A}_{\textrm{C}}$ asymmetry are \red{motivated by the
-  physical processes under investigation}. The other terms
-are included both \red{as} a consistency check for any off-phase
+$\mathcal{A}_{\textrm{C}}$ asymmetry are motivated by the
+  physical processes under investigation. The other terms
+are included both as a consistency check for any off-phase
 extraneous harmonics in the data and as a test of the
@@
 
-The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ \red{receives} a
+The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ receives a
 contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small \red{in} HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it
@@
 
-\red{The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}.
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}.
 Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
 
-Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation.
-Neglecting antiquark-gluon-quark contributions, these higher-twist dependent amplitudes can be considered as being kinematically suppressed compared to the leading-twist amplitudes.}
+Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}.
+Neglecting antiquark-gluon-quark contributions, these higher-twist dependent amplitudes can be considered as being kinematically suppressed compared to the leading-twist amplitudes.
 

### 2012-01-17 frame_dual.tex
version 2.2
Started work on version 2.3 prior to meeting tomorrow

--- 2011-12-20 frame_dual.tex
@@
 \usepackage{appendix}
+%\usepackage[section]{placeins}
 
@@
 \title{Beam-Helicity and Beam-Charge Asymmetries \\
-        in the Bethe--Heitler and DVCS processes on \\
+        in the \red{DVCS and Bethe--Heitler processes} on \\
         an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v2.1)}
+  	\underline{Paper Tag: PDVCS0607 (v2.3)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 precise than those extracted from the earlier data
-set of 1996-2005 previously analysed in the same manner by \red{\sc{Hermes}}. Results from the two data sets are found to be
-compatible with each other. Combined results from these data sets are
-extracted and represent the most \red{precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.}
+set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. Results from the two data sets are 
+compatible with each other. Results from these combined data sets are
+extracted and are the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
 }

### 2012-01-17 results_dual.tex
Started work on version 2.3 prior to meeting tomorrow

--- 2012-01-13 results_dual.tex
@@
 \section{Results}
-\red{The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{fd} from the previously published 1996-2005 data set} are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{Air09} from the previously published 1996-2005 data set are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
-the 1996-2005 (open triangles) and 2006-2007 (filled squares)
-hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
+the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
+hydrogen data. The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.
 An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
-2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
+2006-2007 data respectively is present in the amplitudes due to the uncertainty of
 the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 
-A statistical test \red{(Student's test)} was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
-Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated\red{, i.e.
-effects from detector resolution, acceptance and smearing}.
+A statistical test (Student's test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated, i.e.
+effects from detector resolution, acceptance and smearing.
 This test revealed no significant evidence for incompatibility between the data sets.
-The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the \red{entire} hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
+The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the entire hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
 \begin{figure}
@@
  \includegraphics[width=15cm,keepaspectratio]{macros/bca_both_morgan}
-  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
-The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature.
+  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares) hydrogen data.
+The error bars represent the statistical uncertainties.
+The error bands represent the systematic uncertainties.
 The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
@@
 from 1996 until 2007. The error bars (bands) represent the statistical
-(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of
+(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of
 the beam polarisation measurement.
@@
 The error bars (bands) represent the statistical (systematic) uncertainties.
-An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the \red{uncertainty} of the beam polarisation measurement.}
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
   \label{bsa_xbjrange2}
@@
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
-The error bars (bands) represent the statistical (systematic) uncertainties.}
+The error bars (bands) represent the statistical (systematic) uncertainties.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
   \label{bca_xbjrange2}
@@
 The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
-This resemblance is not so evident for the beam-helicity asymmetry amplitudes \red{as it is for the beam-charge asymettry amplitudes,} because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 \red{and thus the 2006-2007 data has} a lower weighting in the combined fit.
-The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4.
-The missing-mass uncertainty for the combined data set was calculated using the procedure described in that section and the results were added in quadrature.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes as it is for the beam-charge asymmetry amplitudes, because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 and thus the 2006-2007 data has a lower weighting in the combined fit.
+The \red{major contributions to the} systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4\red{, i.e.
+contributions from acceptance, smearing, finite bin widths and misalignment.
+\red{The background in the data sample is estimated using the method from refs.~\cite{Zei09, Bur10}.} The missing-mass uncertainty for the combined data \red{sets were} calculated using the procedure described in that section~4 and the results were \red{averaged}.
+The total systematic uncertainties for the combined results are the result of these three independent contributions added in quadrature.}
 
@@
 sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
-The leading\red{-}twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $K$ from \red{e}q.~\ref{eq:K}.
+The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches \red{its minimum value because of} the dependence of the amplitude on the factor $K$ \red{defined in} eq.~\ref{eq:K}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
@@
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated in the same procedure as used to estimate the systematic uncertainties of the beam-helicity asymmetries.
+The systematic uncertainties are estimated \red{using} the same procedure as \red{was} used to estimate th\red{ose for} the beam-helicity asymmetries.
 The leading twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
 There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
-The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ can be found in table~\ref{tab_amplitudes}.
-The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ \red{and they indicate a weak increase with} $x_{\textrm{B}}$ and $Q^{2}$.
-The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ \red{is approximately fulfilled}.
+The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ and they indicate a weak increase with $x_{\textrm{B}}$ and $Q^{2}$.
+The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero over the \red{whole} range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
 The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
@@
 
-The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions.
-The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab\red{.}, and the collider experiments at H{\sc era}.
+The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data \red{analysis}.
+The solid and dashed curves show \red{results of} calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
 In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
-The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.
@@
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections.
-There is no observed $-t$ dependence of any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in any of the distinct ranges of $x_{\textrm{B}}$.
-No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}.
+The results from this paper will be made available in the Durham Database in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.

### 2012-01-17 summary.tex
Started work on version 2.3 prior to meeting tomorrow

@@
 Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
-These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
+These asymmetries were extracted from a\red{n} unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
 Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
 A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The asymmetry amplitudes extracted from the combined data set are the \red{most} statistically precise DVCS measurements presented by H{\sc ermes}.
+The asymmetry amplitudes extracted from the combined data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
 There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.

### 2012-01-17 theory.tex
Started work on version 2.3 prior to meeting tomorrow

@@
 of the total angular momentum of partons in the nucleon, and the
-construction of a longitudinal-momentum-dissected transverse spatial map of parton positions~\cite{Bur00}.
-\red{There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).
-In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus is the simplest to describe mathematically and is the most widely-used reaction channel for such work.}
+construction of a longitudinal-momentum-dissected transverse spatial map of parton \red{densitie}s~\cite{Bur00}.
+There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).
+In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus \red{(see fig.~\ref{spin})} is the simplest to describe mathematically and is the most widely-used reaction channel for such work.
 
@@
 Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
-transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
-representing the initial (final) four-momentum of the \red{nucleon}; the average
+transfer to the target nucleon in the \red{exclusive} scattering process with $p$ ($p^{\prime}$)
+representing the initial (final) four-momentum of the nucleon; the average
 fraction $x$ of the nucleon's longitudinal momentum carried by the active
@@
 by the active quark at the start and end of the process, written as
-the skewness $\xi$; and \red{$Q^2=-(q^2)$, i.e. }the negative square of the four-momentum of
-the virtual photon that mediates the lepton-\red{nucleon} scattering
+the skewness $\xi$; and $Q^2=-(q^2)$, i.e. the negative square of the four-momentum of
+the virtual photon that mediates the lepton-nucleon scattering
 process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
@@
 \subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
-\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The \red{leading} DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
+\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
 ($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
@@
 photon ($\gamma$). The quark is absorbed by the nucleon with
-longitudinal momentum fraction $x-\xi$. (b): The \red{leading} Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
+longitudinal momentum fraction $x-\xi$. (b): The leading Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
 scattered lepton. It has the same initial and final states as DVCS.}
@@
 two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-\red{nucleon} scattering with the
-emission of a \red{b}remsstrahlung photon by the lepton. \red{The leading terms in these processes are shown in figure~\ref{spin}.}
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the
+emission of a bremsstrahlung photon by the lepton. The leading terms in these processes are shown in figure~\ref{spin}.
 The BH process is calculable in the QED framework; this process is
@@
 scattering amplitudes of the two processes interfere and the large BH amplitude
-amplifies \red{the interference term, which is proporional to the DVCS amplitude.
-At H{\sc ermes} kinematic conditions, it is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained~\cite{Bel02b}, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs}.
+amplifies the interference term, which is proporional to the DVCS amplitude.
+At H{\sc ermes} kinematic conditions, it is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained~\cite{Bel02b}, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs.
 
-The four-fold differential cross section for the \red{exclusive} leptoproduction of real photons
-from an unpolarised target can be written as \cite{Bel02b}
+The four-fold differential cross section for the exclusive leptoproduction of real photons
+from an unpolarised \red{hydrogen} target can be written as \cite{Bel02b}
 \begin{center}
@@
 charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
-the \red{target} mass, and $\phi$ is the
+the target mass, and $\phi$ is the
 azimuthal angle between the scattering and production planes \cite{Tre04}.
@@
 of the BH process, $\lambda$ is the
-helicity of the lepton beam and $e_\ell$ is the unit charge of
-  the lepton.  The
+helicity of the lepton beam and $e_\ell$ is the charge of
+ the \red{beam} lepton.  The
 quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
@@
 $y$ is the fraction of the beam energy carried by the virtual photon in
-the target rest frame. A full
-explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]
-($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be found in ref.~\cite{Bel02b}.
+the target rest frame.
+A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]\red{, where V (W) denotes BH, DVCS or I (DVCS or I),} can be found in ref.~\cite{Bel02b}.
 
 Two sets of asymmetries measured at H{\sc
-ermes} with an unpolarised \red{hydrogen} target and a polarised electron or positron
+ermes} with an unpolarised hydrogen target and a polarised electron or positron
 beam are considered here:
 beam-helicity asymmetries and beam-charge asymmetries. This paper,
-like ref.~\cite{Air09}, presents results \red{related to} the following asymmetries:
+like ref.~\cite{Air09}, presents results related to the following asymmetries:
 \begin{align}
@@
 K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
-c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} \textrm{\, and}&
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)}\, , &
 \label{e:aludvcs}
@@
 where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
-\red{the differential} cross section with positive (negative) beam charge and
-$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer\red{s}
-to \red{the differential} cross section taken with beam spin parallel (anti-parallel) to the
+the differential cross section with positive (negative) beam charge and
+$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refers
+to the differential cross section taken with beam spin parallel (anti-parallel) to the
 beam momentum.
 
-The $s_{\textrm{unp}\red{,n}}^{W}$ and $c_{\textrm{unp}\red{,n}}^{\textrm{\red{W}}}$ Fourier
+The $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{\textrm{W}}$ Fourier
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
-combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
-\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}.
-Contributions to the cross section \red{are} relatively suppressed by \red{factors that} may be kinematic in nature or due to the twist-level of the GPD\red{s appearing in that contribution}.
+combination of complex-valued Compton Form Factors (CFFs). A CFF is a
+flavour-sum of convolutions of GPDs with hard scattering kernels.
+Contributions to the cross section are relatively suppressed by factors that may be kinematic in nature or due to the twist-level of the GPDs appearing in that contribution.
 Leading twist is twist-2.
@@
 
-\red{The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
-All} of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
+The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
 \begin{eqnarray}
@@
 \\
-s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\textrm{and}\label{eq:s1}
+s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\, ,\label{eq:s1}
 \\
@@
 \end{eqnarray}
-\red{The definition of the kinematic factor \red{$K$ is~\cite{Bel02b}}
+The definition of the kinematic factor $K$ is~\cite{Bel02b}
 \begin{equation}
@@
 where $y$ is the fractional energy transfer from the beam lepton the virtual photon.
-The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.}
+The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.
 The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
@@
 contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
-neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ \red{(in first approximation)} since they
+neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ (in first approximation) since they
 are kinematically suppressed by an order of magnitude or more.
@@
 Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the
-experiment was \red{augmented} in the target region. The work covered
+experiment was augmented in the target region. The work covered
   in this publication combines the data taken in 1996-2005 with this

### 2012-01-18 background_and_systematic_dual.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
   2006-2007 Data}
-The extracted asymmetry amplitudes are subject to systematic uncertainties that
-result from a combination of background processes, 
-shifts in the missing-mass distributions and various detector and binning
-effects determined in the same manner as in refs.~\cite{Air08,Air09}.
+The extracted asymmetry amplitudes are subject to systematic uncertainties \red{contributions} that result from a combination of background processes, shifts in the missing-mass distributions\red{,} and various detector and binning effects determined in the same manner as \red{used} in refs.~\cite{Air08,Air09} \red{in orer to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets}.
 
@@
 effects due to detector resolution (e.g.
-the opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+the \red{minimum} opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, \red{potential misalignment} and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
-An event generator based on the GPD model described in ref.~\cite{Guz06} was
-used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}. Asymmetry amplitudes were extracted
-from these simulated events using the same analysis procedure used to
+An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}.
+Asymmetry amplitudes were extracted from these simulated events using the same analysis procedure used to
 extract amplitudes from experimental data. In each kinematic bin, the
@@
   uncertainties arising from the background correction, the
-  missing-mass shifts, and the detector effects.  The 1996-2005 sample also has a
-systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
+  missing-mass shifts, and the detector effects.
+The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
   surveying measurements.
-Therefore, because the systematic uncertainty calculation for the 2006-07 data is identical to that for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated.
-This overestimate is very slight, because the systematic uncertainty contribution from potential misalignment is very small.
+\red{However}, because the systematic uncertainty calculation for the 2006-07 data \red{uses the same Monte Carlo generator and reconstruction technique as was used} for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated\red{; t}his overestimate is very slight, because the systematic uncertainty contribution from potential misalignment \red{affecting the 1996-2005 data set} is very small.
 
@@
 \resizebox{\textwidth}{!} {
- \begin{tabular}{|c|c|c|c|c|c|c|}
+ \begin{tabular}{|c|c||c|c|c|c|c|}
   \hline
- & $A$ $\pm$ $\delta_{stat.}$ $\pm$ $\delta_{syst.}$ & Background & Missing-Mass Shift  & Detector Effects & & Total \\
+ & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
   \hline
   \hline
-  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  $\pm$   0.022 & 0.002 & 0.001 & 0.022 & & 0.022 \\
+  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
   \hline
-  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  $\pm$  0.003 & 0.002 & 0.002 & 0.001 & & 0.003 \\
+  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
   \hline
-  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  $\pm$   0.003 & 0.003 & 0.001 & 0.001 & & 0.003 \\
+  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
   \hline
   \hline
-  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 $\pm$  0.011 & 0.001 & 0.003 & 0.010 & & 0.011 \\
+  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
   \hline
-  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 $\pm$   0.002 & 0.002 & 0.001 & 0.001 & & 0.002 \\
+  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
   \hline
-  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005  $\pm$   0.014 & 0.001 & 0.000 & 0.014 & & 0.014 \\
+  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
   \hline
-  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005   $\pm$   0.004 & 0.000 & 0.001 & 0.003 & & 0.004 \\
+  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
   \hline
@@
 }
-  \caption{The contributions to the overall systematic 
-uncertainties of the extracted asymmetry amplitudes due to the
-background correction, the time-dependent shifts of the missing-mass
-distributions and detector effects for the 2006-2007 data. The total
-systematic uncertainties of the amplitudes, shown in the
-right-most column, are the individual contributions added in quadrature.}
+  \caption{\red{The values of the asymmetries extracted in a single bin over the entire kinematic range with their statistical uncertainties are presented in the second column of this table.
+The third, fourth and fifth columns show t}he contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data.
+The total
+systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
   \label{table_systematic_contributions_0607}

### 2012-01-18 experiment_and_data.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
 An event sample was selected requiring
-that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{P}-q')^{2}$
+that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{p}-q')^{2}$
 of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
-corresponded to the square of the proton mass within the limits of the
-energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). Here, $q$ is the
+corresponded to the square of the proton mass\red{, $M_{p}$,} within the limits of the
+energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). \red{Recall that} $q$ is the
 four-momentum of the virtual photon, $p$ is the initial four-momentum
@@
 0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
-The data sample in the exclusive region contains events not only involving production of real photons in which the proton remains intact, but also
+The data sample in the exclusive region contains events not only involving \red{the} production of real photons in which the proton remains intact, but also
 events involving the excitation of the target proton to a $\Delta^+$
-resonant state (``associated production''). The recoiling proton is not detected and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
+resonant state (``associated production'').
+The recoiling proton is not \red{considered} and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
@@
 used to estimate the fractional contribution to the event sample from resonant
-production in each kinematic bin --- the uncertainty on this estimate
+production in each kinematic bin\red{;} the uncertainty on this estimate
 cannot be adequately quantified because no measurements have been made
@@
 \mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\sigma_{\textrm{UU}}
-(\phi)\times
+(\phi)
 [1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
@@
 
-The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the fourier coefficients defined in eqs.~\ref{eq:c0}---\ref{eq:c1}.
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients \red{$c_{0,\textrm{unp}}^{\textrm{I}}$, $c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$} defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
 Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
 
-Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}.
-Neglecting antiquark-gluon-quark contributions, these higher-twist dependent amplitudes can be considered as being kinematically suppressed compared to the leading-twist amplitudes.
+Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}\red{, i.e.
+n}eglecting antiquark-gluon-quark contributions\red{; these amplitudes that are dependent on higher-twist objects can therefore be considered as being functionally similar, but kinematically suppressed, when compared to the amplitudes that are dependent only on leading-twist objects.}
 
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant.
-Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and the
-related Fourier coefficients, dominant $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and\red{, for each of them,} the
+related \red{dominant} Fourier coefficient \red{and} $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
 \begin{table}
@@
 be extracted from the available data set, the related Fourier
-coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in ref.~\ref{eq:K}}.}
+coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in eq..~\ref{eq:K}}.}
 \label{tab_amplitudes}

### 2012-01-18 frame_dual.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
 missing-mass event selection technique. The asymmetry
-amplitudes extracted from the new data set are more
+amplitudes extracted from \red{this} data set are more
 precise than those extracted from the earlier data
-set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. Results from the two data sets are 
+set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. \red{The r}esults from the two data sets are 
 compatible with each other. Results from these combined data sets are
-extracted and are the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
+extracted and \red{constitute} the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
 }

### 2012-01-18 results_dual.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
 \section{Results}
-The results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work and results extracted in Ref.~\cite{Air09} from the previously published 1996-2005 data set are compared in figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}.
+\red{In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results} for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work \red{are compared with} results extracted in  from the 1996-2005 data set \red{published previously~\cite{Air09}}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-A statistical test (Student's test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
-Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties are largely correlated, i.e.
-effects from detector resolution, acceptance and smearing.
+A statistical test (Student's \red{t-}test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties\red{, i.e.
+effects from detector resolution, acceptance, misalignment and smearing, are largely correlated}.
 This test revealed no significant evidence for incompatibility between the data sets.
@@
 contributions from acceptance, smearing, finite bin widths and misalignment.
-\red{The background in the data sample is estimated using the method from refs.~\cite{Zei09, Bur10}.} The missing-mass uncertainty for the combined data \red{sets were} calculated using the procedure described in that section~4 and the results were \red{averaged}.
+\red{The background in the data sample is estimated using the method from refs.~\cite{Zei09, Bur10}.} The \red{uncertainty contributions due to the observed shifts in the missing-mass distributions} for the combined data \red{sets were} calculated using the procedure described in section~4 and the results were \red{averaged}.
 The total systematic uncertainties for the combined results are the result of these three independent contributions added in quadrature.}
@@
 There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
-The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regards to $A_{\textrm{C}}^{\cos\phi}$ \red{is approximately fulfilled}.
+The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regard to $A_{\textrm{C}}^{\cos\phi}$ \red{is approximately fulfilled}.
 The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ and they indicate a weak increase with $x_{\textrm{B}}$ and $Q^{2}$.
@@
 The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Laboratory (to describe the skewness dependence).
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Lab\red{.} (to describe the skewness dependence).
 The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
@@
 These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}.
-The results from this paper will be made available in the Durham Database in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.
+The results from this paper will be made available in the Durham Database\red{.
+The results will also be made} available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.

### 2012-01-18 summary.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
 Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
-A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample.
-The asymmetry amplitudes extracted from the combined data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
+A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 \red{data set}.
+The asymmetry amplitudes extracted from the com\red{plete} data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
 There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.

### 2012-01-18 theory.tex
Updated with all comments from DC meeting. Need to fix plots and order of subscripts.

@@
 construction of a longitudinal-momentum-dissected transverse spatial map of parton \red{densitie}s~\cite{Bur00}.
-There have been several exclusive experimental results that can be used to constrain GPDs, (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).
-In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus \red{(see fig.~\ref{spin})} is the simplest to describe mathematically and is the most widely-used reaction channel for such work.
+\red{The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels.
+Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive physics processes.
+In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see fig.~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}
 
@@
 as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
+Exclusive leptoproduction of real photons
+ arises from
+two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the emission of a bremsstrahlung photon by the lepton.
 \begin{figure}
@@
 photon ($\gamma$). The quark is absorbed by the nucleon with
-longitudinal momentum fraction $x-\xi$. (b): The leading Bethe-Heitler process, i.e. the emission of a real photon from the scattering or
-scattered lepton. It has the same initial and final states as DVCS.}
+longitudinal momentum fraction $x-\xi$.
+(b): The leading Bethe-Heitler process, i.e.
+the emission of a real photon from the \red{incoming or outgoing} lepton.
+\red{This process} has the same initial and final states as DVCS.}
 \label{spin}
@@
 \end{figure}
-Exclusive leptoproduction of real photons
-($e\,N\,\rightarrow\,e'\,N'\,\gamma$) arises from
-two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
-which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the
-emission of a bremsstrahlung photon by the lepton. The leading terms in these processes are shown in figure~\ref{spin}.
 The BH process is calculable in the QED framework; this process is
-dominant at the kinematic conditions of the H{\sc ermes} experiment, but the
+dominant at the kinematic conditions of the H{\sc ermes} experiment\red{. T}he
 scattering amplitudes of the two processes interfere and the large BH amplitude
-amplifies the interference term, which is proporional to the DVCS amplitude.
-At H{\sc ermes} kinematic conditions, it is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained~\cite{Bel02b}, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs.
+amplifies the interference term, which is proportional to the DVCS amplitude.
+\red{I}t is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.
 
@@
 \sum_{n=1}^2
-c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda\,
 s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
@@
 of the BH process, $\lambda$ is the
-helicity of the lepton beam and $e_\ell$ is the charge of
+helicity of the lepton beam and $e_\ell$ is the \red{sign of the} charge of
  the \red{beam} lepton.  The
@@
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
-combination of complex-valued Compton Form Factors (CFFs). A CFF is a
-flavour-sum of convolutions of GPDs with hard scattering kernels.
-Contributions to the cross section are relatively suppressed by factors that may be kinematic in nature or due to the twist-level of the GPDs appearing in that contribution.
+combination of CFFs.
+Contributions to the cross section are suppressed by factors that may be kinematic in nature or due to the twist-level of the GPDs appearing in that contribution.
 Leading twist is twist-2.
@@
 
-The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, $s_{1,\textrm{unp}}^{\textrm{I}}$ and $c_{1,\textrm{unp}}^{\textrm{I}}$.
+The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, \red{$c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$}.
 All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
@@
 \\
-s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\, ,\label{eq:s1}
+c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
 \\
-c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,.\label{eq:c1}
+s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
 \end{eqnarray}
-The definition of the kinematic factor $K$ is~\cite{Bel02b}
+The definition of the kinematic factor $K$ is~\cite{Bel02b}\red{:}
 \begin{equation}
-K=\sqrt{\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
-\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace}\label{eq:K}
+K^2=\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
+\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\red{\,.}\label{eq:K}
 \end{equation} 
-where $y$ is the fractional energy transfer from the beam lepton the virtual photon.
 The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.
@@
 
-Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the
-experiment was augmented in the target region. The work covered
-  in this publication combines the data taken in 1996-2005 with this
-  new data set to produce the largest DVCS data set that will be published by H{\sc ermes}.
-The results in this paper make use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.
+Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 \red{and makes use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.} The work covered in this publication \red{further} combines the data taken in 1996-2005 with this new\red{er} data set to produce the \red{statistically most precise DVCS measurements} that will be published by H{\sc ermes}.

### 2012-01-19 macros/covMat.C
Added covariance matrix macro

@@ -1,0 +1,145 @@
+
+c(){
+ 
+  int i,j;
+  TCanvas *c = new TCanvas("c","",5);
+  c->SetWindowSize(1000,1000);
+  
+  // Fill hist from here
+  Float_t aa[13][13];
+
+  // Cludgy. Make arrays
+  Float_t c0c[] = {1.000,  0.042, -0.009, -0.017, -0.005, -0.083, -0.041,  0.003, -0.003, -0.039,  0.004, -0.004,  0.006};
+
+  Float_t c1c[] = {0.042,  1.000, -0.001,  0.026, -0.011,  0.003, -0.002, -0.086, -0.030 -0.004,  0.004, -0.034,  0.005};
+
+  Float_t s1c[] = {-0.009, -0.001,  1.000,  0.015,  0.000, -0.040, -0.080, -0.001,  0.006,  0.004, -0.046,  0.003, -0.002};
+
+  Float_t c2c[] = {-0.017,  0.026,  0.015,  1.000,  0.026, -0.004,  0.028,  0.003,  0.002,  0.007,  0.001, -0.001, -0.002};
+
+  Float_t c3c[] = {-0.005, -0.011,  0.000,  0.026,  1.000, -0.001,  0.003, -0.002,  0.032, -0.000, -0.006,  0.007, -0.003};
+  
+  Float_t c0dvcs[] = {-0.083,  0.003, -0.040, -0.004, -0.001,  1.000,  0.033, -0.003,  0.013, -0.778, -0.034,  0.012, -0.014};
+
+  Float_t s1dvcs[] = {-0.041, -0.002, -0.080,  0.028,  0.003,  0.033,  1.000,  0.009,  0.001, -0.034, -0.775, -0.009,  0.007};
+
+  Float_t c1dvcs[] = {0.003, -0.086, -0.001,  0.003, -0.002, -0.003,  0.009,  1.000,  0.027,  0.013, -0.010, -0.780, -0.032};
+
+  Float_t s2dvcs[] = {-0.003, -0.030,  0.006,  0.002,  0.032,  0.013,  0.001,  0.027,  1.000, -0.013,  0.007, -0.030, -0.785};
+
[…]

### 2012-01-20 experiment_and_data.tex
Version 2.3

@@
 
-The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients \red{$c_{0,\textrm{unp}}^{\textrm{I}}$, $c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$} defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients \red{$c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$} defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
 Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
@@
 \hline
-$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
+$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{\textrm{unp},1}^{\textrm{I}}$  &
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
@@
 \hline
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{\textrm{unp},2}^{\textrm{I}}$ 
 &
@@
 \hline
-$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
+$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{\textrm{unp},1}^{\textrm{DVCS}}$ &
 $\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 \\
@@
 \hline
-$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
+$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{\textrm{unp},0}^{\textrm{I}}$  &
 $\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
@@
 \hline
-$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
+$A_{\textrm{C}}^{\cos\phi}$ & $c_{\textrm{unp},1}^{\textrm{I}}$  &
 $\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
@@
 \hline
-$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
+$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{\textrm{unp},2}^{\textrm{I}}$ &
 $\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 \\
 \hline
-$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
+$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{\textrm{unp},3}^{\textrm{I}}$ &
 $\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 \\

### 2012-01-20 results_dual.tex
Version 2.3

@@
 \begin{center}
-\includegraphics[width=15cm,keepaspectratio]{macros/bsa_both_morgan}
+\includegraphics[width=15cm,keepaspectratio]{bsa_sep}
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
@@
 \begin{center}
- \includegraphics[width=15cm,keepaspectratio]{macros/bca_both_morgan}
+ \includegraphics[width=15cm,keepaspectratio]{bca_sep}
   \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares) hydrogen data.
@@
  \begin{center}
- \includegraphics[width=15cm]{macros/morgan_change}
+ \includegraphics[width=15cm]{bsa_comb}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
 the beam polarisation measurement.
-Solid and dashed lines show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines.
+Solid and dashed lines \red{(KM10)} show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines \red{(GGL11)}.
 See text for details.
@@
   \begin{center}
-    \includegraphics[width=15cm]{macros/morgan_change2}
+    \includegraphics[width=15cm]{bca_comb}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
@@
 Theoretical calculations from the model described in Ref.
-\cite{Kum09} are shown as solid and dashed lines.
+\cite{Kum09} are shown as solid and dashed lines \red{(KM10); calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11)}.
 See text for details.
@@
  \begin{center}
- \includegraphics[width=15cm]{macros/bsa_2d_morgan}
+ \includegraphics[width=15cm]{bsa_2D}
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
@@
   \begin{center}
-    \includegraphics[width=15cm]{macros/bca_2d_morgan}
+    \includegraphics[width=15cm]{bca_2D}
     \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
@@
 The total systematic uncertainties for the combined results are the result of these three independent contributions added in quadrature.}
-
 The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
@@
 
-The dash-dotted curves in figure~\ref{bsa_xbjrange} shows the result of a calculation from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in figure\red{s~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}} show the result of calculations from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.

### 2012-01-20 theory.tex
Version 2.3

@@
  |\tau_{\textrm{BH}}|^{2} &=&
- \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
+ \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{\textrm{unp},0}^{\textrm{BH}} + \sum_{n=1}^2
   c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
 |\tau_{\textrm{DVCS}}|^{2} &=&
-K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
+K_{\textrm{DVCS}}\left(c_{\textrm{unp},0}^{\textrm{DVCS}} +
 \sum_{n=1}^2
 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda\,
-s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
+s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
 \label{e:tdvcs}\\
  \textrm{I} &=& \frac{- e_\ell
-K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
+K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{\textrm{unp},0}^{\textrm{
 I}}+
@@
 
-The Fourier coefficients that receive leading-twist contributions are $c_{0,\textrm{unp}}^{\textrm{I}}$, \red{$c_{1,\textrm{unp}}^{\textrm{I}}$ and $s_{1,\textrm{unp}}^{\textrm{I}}$}.
+The Fourier coefficients that receive leading-twist contributions are $c_{\textrm{unp},0}^{\textrm{I}}$, \red{$c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$}.
 All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
 \begin{eqnarray}
-c_{0,\textrm{unp}}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
+c_{\textrm{unp},0}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
 \\
-c_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
+c_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
 \\
-s_{1,\textrm{unp}}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
+s_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
 \end{eqnarray}
@@
 \end{equation} 
-The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these fourier coefficients vanish as $-t$ approaches its minimum value.
+The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these Fourier coefficients vanish as $-t$ approaches its minimum value.
 The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be

### 2012-01-20 macros/bcaplots_eml_par13_bin6_pic_cluster_0607_9605_withassoc_dual.C

@@ -745,36 +745,6 @@
    gre->SetHistogram(Graph1916);
    
    gre->Draw("p");
-   
-   TLegend *leg = new TLegend(0.07,0.63,0.83,0.99,NULL,"b1NDC");
-   leg->SetBorderSize(0);
-   leg->SetTextColor(4);
-   leg->SetTextFont(13);
-   leg->SetTextSize(18);
-   leg->SetLineColor(0);
-   leg->SetLineStyle(1);
-   leg->SetLineWidth(1);
-   leg->SetFillColor(0);
-   leg->SetFillStyle(0);
-   TLegendEntry *entry=leg->AddEntry("NULL","2006-2007","p");
-   entry->SetLineColor(1);
-   entry->SetLineStyle(1);
-   entry->SetLineWidth(1);
-   entry->SetMarkerColor(2);
-   entry->SetMarkerStyle(21);
-   entry->SetMarkerSize(1);
-   entry->SetTextAlign(12);
-   entry->SetTextColor(1);
-   entry=leg->AddEntry("NULL","JHEP11 (2009) 083","p");
-   entry->SetLineColor(1);
-   entry->SetLineStyle(1);
-   entry->SetLineWidth(1);
-   entry->SetMarkerColor(4);
-   entry->SetMarkerStyle(26);
-   entry->SetMarkerSize(1);
-   entry->SetTextAlign(12);
-   entry->SetTextColor(1);
-   leg->Draw();
    pad1_2->Modified();
    pad1->cd();
   
@@ -813,6 +783,7 @@
    line->SetLineStyle(2);
    line->Draw();
    
+   // Draw legend in this pad
    gre = new TGraphErrors(6);
    gre->SetName("Graph");
    gre->SetTitle("Graph");
@@ -937,6 +908,40 @@
    Graph231819->SetStats(0);
    gre->SetHistogram(Graph231819);
    
+   // Draw legend here
+
+
+   TLegend *leg = new TLegend(0.07,0.63,0.83,0.99,NULL,"b1NDC");
+   leg->SetBorderSize(0);
+   leg->SetTextColor(4);
+   leg->SetTextFont(13);
+   leg->SetTextSize(18);
+   leg->SetLineColor(0);
+   leg->SetLineStyle(1);
+   leg->SetLineWidth(1);
+   leg->SetFillColor(0);
+   leg->SetFillStyle(0);
[…]

### 2012-01-20 background_and_systematic_dual.tex
Version 2.3
Version 2.3 with correct abbrevs.

@@
 
-The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in Table~\ref{table_systematic_contributions_0607}.
-
+The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
 The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
 These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
-
 \begin{table}

### 2012-01-20 experiment_and_data.tex
Version 2.3 with correct abbrevs.

@@
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of Eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it

### 2012-01-20 results_dual.tex
Version 2.3 with correct abbrevs.

@@
 
-In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
 These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}.

### 2012-01-20 theory.tex
Version 2.3 with correct abbrevs.

@@
 Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive physics processes.
-In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see fig.~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}
+In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}
 

### 2012-01-24 background_and_systematic_dual.tex
Started on 2.4 by including all DC comments

@@
   2006-2007 Data}
-The extracted asymmetry amplitudes are subject to systematic uncertainties \red{contributions} that result from a combination of background processes, shifts in the missing-mass distributions\red{,} and various detector and binning effects determined in the same manner as \red{used} in refs.~\cite{Air08,Air09} \red{in orer to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets}.
+The extracted asymmetry amplitudes are subject to systematic uncertainties that result from a combination of background processes, shifts in the missing-mass distributions, and various detector and binning effects determined in the same manner as used in refs.~\cite{Air08,Air09} in or\red{d}er to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets.
 
@@
 production is predominantly due to the failure to identify one of
-  the two photons from the decay of \red{these} neutral mesons. The procedure for estimating the corresponding
+  the two photons from the decay of these neutral mesons. The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
 effects due to detector resolution (e.g.
-the \red{minimum} opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, \red{potential misalignment} and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+the minimum opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, potential misalignment and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
-An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because it\red{s output} describes the data well and was employed in ref.~\cite{Air09}.
+An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because its output describes the data well and \red{it} was employed in ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis procedure used to
@@
   surveying measurements.
-\red{However}, because the systematic uncertainty calculation for the 2006-07 data \red{uses the same Monte Carlo generator and reconstruction technique as was used} for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated\red{; t}his overestimate is very slight, because the systematic uncertainty contribution from potential misalignment \red{affecting the 1996-2005 data set} is very small.
+However, because the systematic uncertainty calculation for the 2006-\red{20}07 data uses the same Monte Carlo generator and reconstruction technique as was used for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated; this overestimate is very slight, because the systematic uncertainty contribution from potential misalignment affecting \red{the asymmetries extracted from} the 1996-2005 data set is very small~\cite{Bur10}.
 
-The contribution from each uncertainty to each amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
+The contribution from each uncertainty to each \red{physically-motivated} amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
 The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
@@
 }
-  \caption{\red{The values of the asymmetries extracted in a single bin over the entire kinematic range with their statistical uncertainties are presented in the second column of this table.
-The third, fourth and fifth columns show t}he contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data.
+  \caption{The values of the \red{physically-motivated} asymmetries extracted in a single bin over \red{all kinematic variables} with their statistical uncertainties are presented in the second column of this table.
+The third, fourth and fifth columns show the contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data.
 The total

### 2012-01-24 experiment_and_data.tex
Started on 2.4 by including all DC comments

@@
 target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples are
-approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of $0.303$ and $0.392$ \red{respectively}.
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of $0.303$ and $0.392$ respectively.
 The procedure used to select events is similar to that used in ref.~\cite{Air09}.
-A brief summary of this procedure is outlined in the following; \red{more details are given in refs.~\cite{Zei09,Bur10}.}
+A brief summary of this procedure is outlined in the following; more details are given in refs.~\cite{Zei09,Bur10}.
 
-\red{Events were selected if} having exactly one photon and one lepton
+Events were selected if having exactly one photon and one lepton
 track detected within the acceptance of the spectrometer.
@@
 of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
-corresponded to the square of the proton mass\red{, $M_{p}$,} within the limits of the
-energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). \red{Recall that} $q$ is the
+corresponded to the square of the proton mass, $M_{p}$, within the limits of the
+energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). Recall that $q$ is the
 four-momentum of the virtual photon, $p$ is the initial four-momentum
@@
 0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
-The data sample in the exclusive region contains events not only involving \red{the} production of real photons in which the proton remains intact, but also
+The data sample in the exclusive region contains events not only involving the production of real photons in which the proton remains intact, but also
 events involving the excitation of the target proton to a $\Delta^+$
 resonant state (``associated production'').
-The recoiling proton is not \red{considered} and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
+The recoiling proton is not considered and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
 No systematic uncertainty is assigned for the contribution from these
@@
 used to estimate the fractional contribution to the event sample from resonant
-production in each kinematic bin\red{;} the uncertainty on this estimate
+production in each kinematic bin; the uncertainty on this estimate
 cannot be adequately quantified because no measurements have been made
@@
 where the approximation is due to the truncation of the infinite
-Fourier series that would describe \red{exactly} the fitted distribution. Only the $\sin(n\phi)$ terms of the
+Fourier series that would describe exactly the fitted distribution. Only the $\sin(n\phi)$ terms of the
 $\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
@@
 
-The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients \red{$c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$} defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$ defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
 Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
 
-Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}\red{, i.e.
-n}eglecting antiquark-gluon-quark contributions\red{; these amplitudes that are dependent on higher-twist objects can therefore be considered as being functionally similar, but kinematically suppressed, when compared to the amplitudes that are dependent only on leading-twist objects.}
+Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}, i.e.
+neglecting antiquark-gluon-quark contributions; these amplitudes that are dependent on higher-twist objects can therefore be considered as being functionally similar, but kinematically suppressed, when compared to the amplitudes that are dependent only on leading-twist objects.
 
@@
 in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant.
-Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and\red{, for each of them,} the
-related \red{dominant} Fourier coefficient \red{and} $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and, for each of them, the
+related dominant Fourier coefficient and $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
 \begin{table}

### 2012-01-24 frame_dual.tex
Started on 2.4 by including all DC comments

@@
 \begin{document}
-\title{Beam-Helicity and Beam-Charge Asymmetries \\
-        in the \red{DVCS and Bethe--Heitler processes} on \\
-        an Unpolarised Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v2.3)}
+\title{Beam-Helicity and Beam-Charge Asymmetries\\
+        \red{Arising From} the DVCS and Bethe--Heitler \\
+        Processes \red{Using} a Proton Target
+  	\underline{Paper Tag: PDVCS0607 (v2.4)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 missing-mass event selection technique. The asymmetry
-amplitudes extracted from \red{this} data set are more
+amplitudes extracted from this data set are more
 precise than those extracted from the earlier data
@@
 compatible with each other. Results from these combined data sets are
-extracted and \red{constitute} the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
+extracted and constitute the most precise asymmetry amplitude measurements made in the H{\sc ermes} kinematic region using a missing-mass event selection technique.
 }

### 2012-01-24 results_dual.tex
Started on 2.4 by including all DC comments

@@
 \section{Results}
-\red{In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results} for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work \red{are compared with} results extracted in  from the 1996-2005 data set \red{published previously~\cite{Air09}}.
+In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted in  from the 1996-2005 data set published previously~\cite{Air09}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
 
-A statistical test (Student's \red{t-}test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
-Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties\red{, i.e.
-effects from detector resolution, acceptance, misalignment and smearing, are largely correlated}.
+A statistical test (Student's t-test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties, i.e.
+effects from detector resolution, acceptance, misalignment and smearing, are largely correlated.
 This test revealed no significant evidence for incompatibility between the data sets.
@@
 the beam polarisation measurement.
-Solid and dashed lines \red{(KM10)} show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines \red{(GGL11)}.
+Solid and dashed lines (KM10) show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
 See text for details.
@@
 Theoretical calculations from the model described in Ref.
-\cite{Kum09} are shown as solid and dashed lines \red{(KM10); calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11)}.
+\cite{Kum09} are shown as solid and dashed lines (KM10); calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
 See text for details.
@@
 This resemblance is not so evident for the beam-helicity asymmetry amplitudes as it is for the beam-charge asymmetry amplitudes, because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 and thus the 2006-2007 data has a lower weighting in the combined fit.
-The \red{major contributions to the} systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4\red{, i.e.
+The major contributions to the systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4, i.e.
 contributions from acceptance, smearing, finite bin widths and misalignment.
-\red{The background in the data sample is estimated using the method from refs.~\cite{Zei09, Bur10}.} The \red{uncertainty contributions due to the observed shifts in the missing-mass distributions} for the combined data \red{sets were} calculated using the procedure described in section~4 and the results were \red{averaged}.
-The total systematic uncertainties for the combined results are the result of these three independent contributions added in quadrature.}
+The background in the \red{combined} data sample is estimated using the method from refs.~\cite{Air08,Zei09, Bur10}.
+The uncertainty contributions due to the observed shifts in the missing-mass distributions for the combined data sets were calculated using the procedure described in section~4 and the results were averaged.
+The total systematic uncertainties for the combined results are \red{obtained by adding these} three independent contributions in quadrature.
 The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
@@
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
-This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches \red{its minimum value because of} the dependence of the amplitude on the factor $K$ \red{defined in} eq.~\ref{eq:K}.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches its minimum value because of the dependence of the amplitude on the factor $K$ defined in eq.~\ref{eq:K}.
 The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
@@
 The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}.
-The systematic uncertainties are estimated \red{using} the same procedure as \red{was} used to estimate th\red{ose for} the beam-helicity asymmetries.
+The systematic uncertainties are estimated using the same procedure as was used to estimate those for the beam-helicity asymmetries.
 The leading twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
 There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
-The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regard to $A_{\textrm{C}}^{\cos\phi}$ \red{is approximately fulfilled}.
+The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regard to $A_{\textrm{C}}^{\cos\phi}$ is approximately fulfilled.
 The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ and they indicate a weak increase with $x_{\textrm{B}}$ and $Q^{2}$.
-The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero over the \red{whole} range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero over the whole range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
 The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
@@
 
-The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data \red{analysis}.
-The solid and dashed curves show \red{results of} calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
+The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis.
+The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
 The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
@@
 
-The dash-dotted curves in figure\red{s~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}} show the result of calculations from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The dash-dotted curves in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the result of calculations from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
 The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.
-The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Lab\red{.} (to describe the skewness dependence).
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Lab.
+(to describe the skewness dependence).
 The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
@@
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one dimensional projections\red{: within experimental uncertainty, there is no evidence of a correlation between the $-t$ dependence  and the $x_{\textrm{B}}$ dependence for any of the amplitudes}.
-The results from this paper will be made available in the Durham Database\red{.
-The results will also be made} available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one\red{-}dimensional projections: within experimental uncertainty, there is no evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependence\red{s} for any of the amplitudes.
+The results from this paper will be made available in the Durham Database.
+The results will also be made available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.

### 2012-01-24 theory.tex
Started on 2.4 by including all DC comments

--- 2012-01-20 theory.tex
@@
 of the total angular momentum of partons in the nucleon, and the
-construction of a longitudinal-momentum-dissected transverse spatial map of parton \red{densitie}s~\cite{Bur00}.
-\red{The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels.
-Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive physics processes.
-In particular, the exclusive leptoproduction of real photons from a nucleon or nucleus ( $e\,N\,\rightarrow\,e'\,N'\,\gamma$; see fig.~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air00,Air00b,Air01,Air01a,Air02,Air03,Air04,Air06,Air08,Air08a,Air09,Air09a,Air09b,Air10,Air10a,Air10b,Air10c,Air11,Air11a,Air11b}).}
+construction of a longitudinal-momentum-dissected transverse spatial map of parton densities~\cite{Bur00}.
+The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels.
+Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes.
+In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a}).
 
@@
 Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
-transfer to the target nucleon in the \red{exclusive} scattering process with $p$ ($p^{\prime}$)
+transfer to the target nucleon in the exclusive scattering process with $p$ ($p^{\prime}$)
 representing the initial (final) four-momentum of the nucleon; the average
@@
 \begin{center}
-\subfigure[DVCS]{\includegraphics[width=0.45\textwidth]{dvcs_both}}
-\subfigure[Bethe-Heitler]{\includegraphics[width=0.45\textwidth]{bh_both}}
+\subfigure[DVCS]{\includegraphics[angle=90,width=0.45\textwidth]{dvcs_both_edited}}
+\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.45\textwidth]{bh_both_edited}}
 \caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
@@
 (b): The leading Bethe-Heitler process, i.e.
-the emission of a real photon from the \red{incoming or outgoing} lepton.
-\red{This process} has the same initial and final states as DVCS.}
+the emission of a real photon from the incoming or outgoing lepton.
+This process has the same initial and final states as DVCS.}
 \label{spin}
@@
 The BH process is calculable in the QED framework; this process is
-dominant at the kinematic conditions of the H{\sc ermes} experiment\red{. T}he
-scattering amplitudes of the two processes interfere and the large BH amplitude
+dominant at the kinematic conditions of the H{\sc ermes} experiment. The
+two processes interfere and the large BH amplitude
 amplifies the interference term, which is proportional to the DVCS amplitude.
-\red{I}t is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.
+It is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.
 
 The four-fold differential cross section for the exclusive leptoproduction of real photons
-from an unpolarised \red{hydrogen} target can be written as \cite{Bel02b}
+from an unpolarised hydrogen target can be written as \cite{Bel02b}
 \begin{center}
@@
 of the BH process, $\lambda$ is the
-helicity of the lepton beam and $e_\ell$ is the \red{sign of the} charge of
- the \red{beam} lepton.  The
+helicity of the lepton beam and $e_\ell$ is the sign of the charge of
+ the beam lepton.  The
 quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
@@
 $y$ is the fraction of the beam energy carried by the virtual photon in
-the target rest frame.
-A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]\red{, where V (W) denotes BH, DVCS or I (DVCS or I),} can be found in ref.~\cite{Bel02b}.
+the target rest frame. A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$], where V (W) denotes BH, DVCS or I (DVCS or I), can be found in ref.~\cite{Bel02b}.
 
@@
 
-The Fourier coefficients that receive leading-twist contributions are $c_{\textrm{unp},0}^{\textrm{I}}$, \red{$c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$}.
+The Fourier coefficients that receive leading-twist contributions are $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$.
 All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
@@
 \end{eqnarray}
-The definition of the kinematic factor $K$ is~\cite{Bel02b}\red{:}
+The definition of the kinematic factor $K$ is~\cite{Bel02b}:
 \begin{equation}
 K^2=\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
-\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\red{\,.}\label{eq:K}
+\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\,.\label{eq:K}
 \end{equation} 
@@
 
-Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 \red{and makes use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.} The work covered in this publication \red{further} combines the data taken in 1996-2005 with this new\red{er} data set to produce the \red{statistically most precise DVCS measurements} that will be published by H{\sc ermes}.
+Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 and makes use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.
+The work covered in this publication further combines the data taken in 1996-2005 with this newer data set to produce the statistically most precise DVCS measurements that will be published by H{\sc ermes}.

### 2012-01-24 results_dual.tex
Updated the paper with the comments received from Dieter re his model

@@
 The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
-The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences.
-In this model, the $t$ dependence is approximated by a physically motivated Regge dependence.
+The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}.
 The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data.

### 2012-01-25 results_dual.tex
Finished textual and figure changes

@@
 The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}.
-The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes 1these data.
 Both fits include the 1996-2005 H{\sc ermes} data.

### 2012-01-25 theory.tex
Finished textual and figure changes

@@
 Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes.
-In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a}).
+In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
 

### 2012-02-02 frame_dual.tex
fixed the axes on the second figure

@@
 \collaboration{The {\sc Hermes} Collaboration}
-%\collaborationImg{\includegraphics{hermeslogo.pdf}}
 
@@
 \maketitle
+\section{Introduction}
+Generalised Parton Distributions (GPDs)
+\cite{Mue94,Ji97,Rad97} encompass the familiar Parton
+Distribution Functions (PDFs) and nucleon Form Factors (FFs) to provide a
+comprehensive description of the structure of the nucleon. A thorough
+description of the nucleon in terms of GPDs would allow the deduction
+of the total angular momentum of partons in the nucleon, and the
+construction of a longitudinal-momentum-dissected transverse spatial map of parton densities~\cite{Bur00}.
+The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels.
+Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes.
+In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
 
-\include{theory}
-\include{experiment_and_data}
-\include{background_and_systematic_dual}
-\include{results_dual}
-\include{summary}
-\include{append_dual}
+Generalised parton distributions depend upon four kinematic variables: the
+Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
+transfer to the target nucleon in the exclusive scattering process with $p$ ($p^{\prime}$)
+representing the initial (final) four-momentum of the nucleon; the average
+fraction $x$ of the nucleon's longitudinal momentum carried by the active
+quark throughout the scattering process; half the difference of
+  the fractions of the nucleon's longitudinal momentum carried
+by the active quark at the start and end of the process, written as
+the skewness $\xi$; and $Q^2=-(q^2)$, i.e. the negative square of the four-momentum of
+the virtual photon that mediates the lepton-nucleon scattering
+process. In the Bjorken limit of $Q^2\rightarrow\infty$ with fixed
+$t$, the skewness $\xi$ is related to the Bjorken variable
+$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
+$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
+as a function of $x_{\textrm{B}}$ because there is no consensus on an experimentally observable representation of $\xi$. 
+Exclusive leptoproduction of real photons
+ arises from
+two experimentally indistinguishable processes: the Deeply Virtual Compton Scattering (DVCS) process,
+which is the emission of a real photon by the struck quark from the nucleon, and the Bethe--Heitler (BH) process, which is elastic lepton-nucleon scattering with the emission of a bremsstrahlung photon by the lepton.
+\begin{figure}
+\begin{center}
+\subfigure[DVCS]{\includegraphics[angle=90,width=0.45\textwidth]{dvcs_both_edited}}
+\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.45\textwidth]{bh_both_edited}}
+\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
+($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
+nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
+photon ($\gamma$). The quark is absorbed by the nucleon with
+longitudinal momentum fraction $x-\xi$.
+(b): The leading Bethe-Heitler process, i.e.
+the emission of a real photon from the incoming or outgoing lepton.
+This process has the same initial and final states as DVCS.}
+\label{spin}
+\end{center}
+\end{figure}
+The BH process is calculable in the QED framework; this process is
+dominant at the kinematic conditions of the H{\sc ermes} experiment. The
+two processes interfere and the large BH amplitude
+amplifies the interference term, which is proportional to the DVCS amplitude.
+It is through the study of this interference term that useful information for the constraint of certain GPDs can be obtained at H{\sc ermes} kinematic conditions, especially since the interference term is the only part of the squared scattering amplitude that is linear in CFFs~\cite{Bel02b}.
+
+The four-fold differential cross section for the exclusive leptoproduction of real photons
+from an unpolarised hydrogen target can be written as \cite{Bel02b}
+\begin{center}
+\begin{equation}
+\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
+|t|\textrm{d}\phi} =
+\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
+|\tau|^{2},
+\end{equation}
+\end{center}
+where $e$ is the elementary
+charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
+the target mass, and $\phi$ is the
+azimuthal angle between the scattering and production planes \cite{Tre04}.
+The {square of the} scattering amplitude $|\tau|^2$ can be written as
+\begin{center}
+\begin{equation}
+|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
+|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
+\end{equation}
+\end{center}
+with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
+the DVCS process
+($\tau_{\textrm{DVCS}}$) and their interference term (I). These
+contributions can be written as
+\begin{eqnarray}
+ |\tau_{\textrm{BH}}|^{2} &=&
+ \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{\textrm{unp},0}^{\textrm{BH}} + \sum_{n=1}^2
+  c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
+|\tau_{\textrm{DVCS}}|^{2} &=&
+K_{\textrm{DVCS}}\left(c_{\textrm{unp},0}^{\textrm{DVCS}} +
+\sum_{n=1}^2
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda\,
+s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
+\label{e:tdvcs}\\
+ \textrm{I} &=& \frac{- e_\ell
+K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{\textrm{unp},0}^{\textrm{
+I}}+
+\sum_{n=1}^3 c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
+s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
+\end{eqnarray}
+where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
+of the BH process, $\lambda$ is the
+helicity of the lepton beam and $e_\ell$ is the sign of the charge of
+ the beam lepton.  The
+quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
+$K_{\textrm{DVCS}}=1/Q^2$
+and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
+$y$ is the fraction of the beam energy carried by the virtual photon in
+the target rest frame. A full explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$], where V (W) denotes BH, DVCS or I (DVCS or I), can be found in ref.~\cite{Bel02b}.
+
+Two sets of asymmetries measured at H{\sc
+ermes} with an unpolarised hydrogen target and a polarised electron or positron
+beam are considered here:
+beam-helicity asymmetries and beam-charge asymmetries. This paper,
+like ref.~\cite{Air09}, presents results related to the following asymmetries:
+\begin{align}
+\hspace{0.5cm}\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi) &\equiv
+\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} -
+\textrm{d}\sigma(\phi)^{+\leftarrow}) -
+(\textrm{d}\sigma(\phi)^{-\rightarrow}
+- \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
++
+\textrm{d}\sigma(\phi)^{+\leftarrow}) +
+(\textrm{d}\sigma(\phi)^{-\rightarrow}
++ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
+&=\dfrac{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
+\displaystyle\sum_{n=1}^2
+s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+(\phi)\mathcal{P}_{
+2}(\phi)}
+\displaystyle\sum_{n=0}^2
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)},& 
+\label{e:alui}
+\end{align}
+
+\begin{align}
+\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
+\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
+\textrm{d}\sigma(\phi)^{-\rightarrow}) -
+(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
+\textrm{d}\sigma(\phi)^{-\leftarrow})}
+{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
+\textrm{d}\sigma(\phi)^{-\rightarrow}) +
+(\textrm{d}\sigma(\phi)^{+\leftarrow}
++ \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
+%\\ \nonumber
+&=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+(\phi)\mathcal{P}_{2}(\phi)}
+\displaystyle\sum_{n=0}^2
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
+c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)}\, , &
+\label{e:aludvcs}
+\end{align}
+
+\begin{align}
+\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
+\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
+\textrm{d}\sigma(\phi)^{+\leftarrow}) -
+(\textrm{d}\sigma(\phi)^{-\rightarrow}
++ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
++
+\textrm{d}\sigma(\phi)^{+\leftarrow}) +
+(\textrm{d}\sigma(\phi)^{-\rightarrow}
++ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
+&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
+\displaystyle\sum_{n=0}^3
+c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
+(\phi)\mathcal{P}_
+{2}(\phi)}
+\displaystyle\sum_{n=0}^2
+c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi) + 
+K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi)} ,&
+\label{e:ac}
+\end{align}
+where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
+the differential cross section with positive (negative) beam charge and
+$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refers
+to the differential cross section taken with beam spin parallel (anti-parallel) to the
+beam momentum.
+
+The $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{\textrm{W}}$ Fourier
+coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
+combination of CFFs.
+Contributions to the cross section are suppressed by factors that may be kinematic in nature or due to the twist-level of the GPDs appearing in that contribution.
+Leading twist is twist-2.
+Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
+suppressed by $\mathcal{O}(1/Q^{n-2})$.
+
+The Fourier coefficients that receive leading-twist contributions are $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$.
+All of these Fourier coefficients have a dominant contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function:
+\begin{eqnarray}
+c_{\textrm{unp},0}^{\textrm{I}} &\approx&-8(2-y)\frac{(2-y^2)}{(1-y)}K^2\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\label{eq:c0}
+\\
+c_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8K(2- 2y + y^{2})\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,,\label{eq:c1}
+\\
+s_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
+\end{eqnarray}
+The definition of the kinematic factor $K$ is~\cite{Bel02b}:
+\begin{equation}
+K^2=\frac{t}{Q^2}\Big(1-\frac{t_{\textrm{min}}}{t}\Big)\Big(1-x_{\textrm{B}}\Big)\Big(1-y-\frac{y^2\epsilon^2}{4}\Big)\Big\lbrace\sqrt{1+\epsilon^2}+\frac{4x_{\textrm{B}}(1-x_{\textrm{B}})+\epsilon^2}{4(1-x_{\textrm{B}})}
+\frac{t_{\textrm{min}}-t}{Q^2}\Big\rbrace\,.\label{eq:K}
+\end{equation} 
+The factor of $\Big(1-\frac{t_{\textrm{min}}}{t}\Big)$ implies that amplitudes proportional to these Fourier coefficients vanish as $-t$ approaches its minimum value.
+The $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$-function can be
+written
+\cite{Bel02b} 
+\begin{equation}
+ \mathcal{C}_{\textrm{unp}}^{\textrm{I}} = F_{1}\mathcal{H} + \frac{x_{\textrm{B}}}{2-x_{\textrm{B}}}(F_{1}+F_{2})\widetilde{\mathcal{H}} -\frac{t}{4M^{2}}F_{2}\mathcal{E},
+\label{Eq_cunp}
+\end{equation}
+where $F_{1}$ and $F_{2}$ are respectively the Dirac and Pauli form
+factors of the nucleon and $\mathcal{H}$, $\widetilde{\mathcal{H}}$ and
+$\mathcal{E}$ are CFFs that relate respectively to the GPDs $H$,
+$\widetilde{H}$ and $E$.  In H{\sc ermes} kinematic
+conditions (where $x_{\textrm{B}}$ and $\frac{-t}{4M^2}$ are of order 0.1), the
+contributions of CFFs $\widetilde{\mathcal{H}}$ and $\mathcal{E}$ can be
+neglected in eq.~\ref{Eq_cunp} with respect to $\mathcal{H}$ (in first approximation) since they
+are kinematically suppressed by an order of magnitude or more.
+Hence, the behaviour of
+$\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ is determined by CFF $\mathcal{H}$
+and therefore GPD $H$ can be constrained through
+measurements of the $\sin\phi$ and $\cos\phi$ terms of the $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}(\phi)$ and $\mathcal{A}_{\textrm{C}}(\phi)$ asymmetries respectively.
+
+Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 and makes use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.
+The work covered in this publication further combines the data taken in 1996-2005 with this newer data set to produce the statistically most precise DVCS measurements that will be published by H{\sc ermes}.
+\section{Experiment and Data Selection}
+The new data presented in this work were collected in 2006 and 2007. As in ref.~\cite{Air09}, the data were collected with the H{\sc ermes}
+spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
+electron and positron beams incident upon an unpolarised hydrogen gas
+target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples are
+approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of $0.303$ and $0.392$ respectively.
+The procedure used to select events is similar to that used in ref.~\cite{Air09}.
+A brief summary of this procedure is outlined in the following; more details are given in refs.~\cite{Zei09,Bur10}.
+
+Events were selected if having exactly one photon and one lepton
+track detected within the acceptance of the spectrometer.
+The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
+Q$^{2}$ $<$ 10\,GeV$^{2}$, 0.03 $<$ $x_{\textrm{B}}$ $<$ 0.35,
+$-t < 0.7$\,GeV$^2$, $W^{2}$ $>$
+9\,GeV$^{2}$ and $\nu$ $<$ 22\,GeV, where $W$ is the invariant mass of the
+$\gamma^{*}p$ system and $\nu$ is the energy of the virtual photon in the target
+rest frame. The polar angle between the directions of the virtual and real photons was required to
+be within the limits 5~mrad $<$
+$\theta_{\gamma^{*}\gamma}$ $<$ 45~mrad.
+
+An event sample was selected requiring
+that the squared missing-mass $M_{\textrm{X}}^{2}=(q+M_{p}-q')^{2}$
+of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
+corresponded to the square of the proton mass, $M_{p}$, within the limits of the
+energy resolution of the H{\sc ermes} spectrometer (mainly the calorimeter). Recall that $q$ is the
+four-momentum of the virtual photon, $p$ is the initial four-momentum
+of the target proton and $q'$ is the four-momentum of the produced
+photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} <
+M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in
+ref.~\cite{Air09}. This exclusive region was shifted by up to
+0.17\,GeV$^{2}$ for certain subsets of the data in order to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}. 
+The data sample in the exclusive region contains events not only involving the production of real photons in which the proton remains intact, but also
+events involving the excitation of the target proton to a $\Delta^+$
+resonant state (``associated production'').
+The recoiling proton is not considered and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
+No systematic uncertainty is assigned for the contribution from these
+events; they are treated as part of the signal. A Monte Carlo
+calculation based on the parameterisation from ref.~\cite{Bra76} is
+used to estimate the fractional contribution to the event sample from resonant
+production in each kinematic bin; the uncertainty on this estimate
+cannot be adequately quantified because no measurements have been made
+in the H{\sc ermes} kinematic region.
+The results of the estimate, called the associated fractions and labelled ``Assoc.
+fraction'', are shown in the last row of figures~\ref{bsa_xbjrange}--\ref{bca_xbjrange2} in the results section.
+The method used to perform this estimation is described in detail in
+ref.~\cite{Air08}.
+
+\section{Experimental Extraction of Asymmetry Amplitudes}
+
+The expectation value of the experimental yield $N$ is parameterised as
+\begin{equation}
+ \langle N(e_{\ell},P_{\ell},\phi)\rangle =
+\mathcal{L}(e_{\ell},P_{\ell})\eta(e_{\ell},\phi)\sigma_{\textrm{UU}}
+(\phi)
+[1+P_{\ell}\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)+e_{\ell}P_{\ell}
+\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)+e_{\ell}\mathcal{A}_{\textrm{C}}
+(\phi)],
+\end{equation}
+where $P_\ell$ is the beam polarisation, $\mathcal{L}$ is the integrated luminosity, $\eta$ is the detection
+efficiency and d$\sigma_{\textrm{UU}}$ denotes the
+cross section for an unpolarised target summed over both beam charges and
+beam helicities. The asymmetries $\mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi)$, $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi)$ and
+$\mathcal{A}_{\textrm{C}}(\phi)$ are expanded in
+$\phi$ as
+\begin{equation}
+ \mathcal{A}_{\textrm{LU}}^{\textrm{DVCS}}(\phi) \simeq 
+A_{\textrm{LU,DVCS}}^{\sin\phi}\sin\phi 
++ \sum^{1}_{n=0} A_{\textrm{LU,DVCS}}^{\cos(n\phi)}\cos(n\phi), 
+\label{aludvcs_asym}
+\end{equation}
+\begin{equation}
+\mathcal{A}_{\textrm{LU}}^{\textrm{I}}(\phi) \simeq \sum^{2}_{n=1}
+A_{\textrm{LU,I}}^{\sin(n\phi)}\sin(n\phi) 
++ \sum^{1}_{n=0} A_{\textrm{LU,I}}^{\cos(n\phi)}\cos(n\phi), 
+\label{alui_asym}
+\end{equation}
+\begin{equation}
+\mathcal{A}_{\textrm{C}}(\phi) \simeq \sum^{3}_{n=0}
+A_{\textrm{C}}^{\cos(n\phi)}\cos(n\phi) 
++ A_{\textrm{C}}^{\sin\phi}\sin\phi,
+\label{ac_asym}
+\end{equation}
+where the approximation is due to the truncation of the infinite
+Fourier series that would describe exactly the fitted distribution. Only the $\sin(n\phi)$ terms of the
+$\mathcal{A}_{\textrm{LU}}$ asymmetries and the $\cos(n\phi)$ terms of the
+$\mathcal{A}_{\textrm{C}}$ asymmetry are motivated by the
+  physical processes under investigation. The other terms
+are included both as a consistency check for any off-phase
+extraneous harmonics in the data and as a test of the
+normalisation of the fit. These terms are expected to be
+consistent with zero and are found to be so.
+
+A maximum-likelihood fitting technique \cite{Bar90} was used to
+extract the asymmetry amplitudes in each kinematic bin of $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+This method, described in ref.~\cite{Air08}, fits the expected
+azimuthal distribution function to the data without introducing binning effects in $\phi$.
+Event weights are introduced in the fitting procedure to account for
+luminosity imbalances with respect to the beam charge and polarisation.
+
+The asymmetry amplitudes $A_{\textrm{LU,I/DVCS}}^{\sin(n\phi)}$ and
+$A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
+coefficients $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{I}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+may also be affected by the lepton propagators and the other
+$\phi$-dependent terms in the denominators in
+eqs.~\ref{e:alui}-\ref{e:ac}.
+
+The DVCS asymmetry amplitude $A^{\sin\phi}_{\textrm{LU,DVCS}}$ receives a
+contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
+which is bilinear in CFFs.
+However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
+As a result of the more complicated dependence on the CFFs and this suppression, it
+is more difficult to constrain GPDs via the measurement of $A^{\sin\phi}_{\textrm{LU,DVCS}}$ than from the kinematically-unsuppressed leading twist amplitudes.
+
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$ defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
+Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
+
+Although strictly dependent on higher-twist quantities, the asymmetry amplitudes $A_{\textrm{LU},\textrm{I}}^{\sin(2\phi)}$ and $A^{\cos(2\phi)}_{\textrm{C}}$ can also be expressed as having a dependence on $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ using the Wandzura-Wilzcek approximation~\cite{Wan}, i.e.
+neglecting antiquark-gluon-quark contributions; these amplitudes that are dependent on higher-twist objects can therefore be considered as being functionally similar, but kinematically suppressed, when compared to the amplitudes that are dependent only on leading-twist objects.
+
+The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
+$c_{\textrm{unp},3}^{\textrm{I}}$ Fourier coefficient and hence the
+$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$-function. Although the CFFs
+in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$, where $\alpha_{\textrm{S}}$ is the strong coupling constant.
+Table~\ref{tab_amplitudes} presents the asymmetry amplitudes extracted in this analysis and, for each of them, the
+related dominant Fourier coefficient and $\mathcal{C}$-function, and the twist-level at which the contributing GPDs enter.
+\begin{table}
+\begin{center}
+\resizebox{\textwidth}{!} {
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist-Level   \\ 
+\hline
+\hline
+$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{\textrm{unp},1}^{\textrm{I}}$  &
+$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
+&  2 \\
+\hline
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{\textrm{unp},2}^{\textrm{I}}$ 
+&
+$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
+&  3 \\
+\hline
+\hline
+$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{\textrm{unp},1}^{\textrm{DVCS}}$ &
+$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 \\
+\hline
+\hline
+$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{\textrm{unp},0}^{\textrm{I}}$  &
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
+\\
+\hline
+$A_{\textrm{C}}^{\cos\phi}$ & $c_{\textrm{unp},1}^{\textrm{I}}$  &
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2
+\\
+\hline
+$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{\textrm{unp},2}^{\textrm{I}}$ &
+$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 \\
+\hline
+$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{\textrm{unp},3}^{\textrm{I}}$ &
+$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 \\
+\hline
+ \end{tabular}
+}
+\caption{Asymmetry amplitudes that can
+be extracted from the available data set, the related Fourier
+coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in eq.~\ref{eq:K}}.}
+\label{tab_amplitudes}
+\end{center}
+\end{table}
+
+\section{Background Corrections and Systematic Uncertainties for the
+  2006-2007 Data}
+The extracted asymmetry amplitudes are subject to systematic uncertainties that result from a combination of background processes, shifts in the missing-mass distributions, and various detector and binning effects determined in the same manner as used in refs.~\cite{Air08,Air09} in or\red{d}er to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets.
+
+The contribution to the uncertainties on the amplitude measurements
+arising from background in the data from neutral meson
+production is predominantly due to the failure to identify one of
+  the two photons from the decay of these neutral mesons. The procedure for estimating the corresponding
+uncertainty on the measured amplitude values is described in detail in
+refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
+  $Q^{2}$ projections has this uncertainty estimated at the
+  centre of the relevant kinematic bin and included as part of the
+  total systematic uncertainty.
+
+A contribution to the systematic uncertainties of the
+  measured amplitudes arises from shifts in  the
+missing-mass distributions. Such shifts appear in a comparison of electron and positron data~\cite{Zei09,Bur10}. One
+quarter of the difference between the asymmetries extracted using the standard
+and shifted missing-mass windows is taken as the corresponding systematic
+uncertainty.
+
+The predominant contribution to the systematic uncertainty arises from detector
+effects. These include the acceptance of the spectrometer, smearing
+effects due to detector resolution (e.g.
+the minimum opening angle between the scattered lepton and produced photon trajectories that can be resolved in the calorimeter), external radiation in detector material, potential misalignment and the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections.
+In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
+An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because its output describes the data well and \red{it} was employed in ref.~\cite{Air09}.
+Asymmetry amplitudes were extracted from these simulated events using the same analysis procedure used to
+extract amplitudes from experimental data. In each kinematic bin, the
+systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
+calculated from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
+$Q^{2}$ value for that bin.
+
+The total systematic uncertainty for the 2006-2007 data sample was
+determined for each kinematic bin by adding in quadrature the
+  uncertainties arising from the background correction, the
+  missing-mass shifts, and the detector effects.
+The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample due to improved
+  surveying measurements.
+However, because the systematic uncertainty calculation for the 2006-\red{20}07 data uses the same Monte Carlo generator and reconstruction technique as was used for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated; this overestimate is very slight, because the systematic uncertainty contribution from potential misalignment affecting \red{the asymmetries extracted from} the 1996-2005 data set is very small~\cite{Bur10}.
+
+The contribution from each uncertainty to each \red{physically-motivated} amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
+The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
+These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
+\begin{table}
+ \begin{center}
+\resizebox{\textwidth}{!} {
+ \begin{tabular}{|c|c||c|c|c|c|c|}
+  \hline
+ & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
+  \hline
+  \hline
+  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
+  \hline
+  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
+  \hline
+  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
+  \hline
+  \hline
+  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
+  \hline
+  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
+  \hline
+  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
+  \hline
+  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
+  \hline
+ \end{tabular}
+}
+  \caption{The values of the \red{physically-motivated} asymmetries extracted in a single bin over \red{all kinematic variables} with their statistical uncertainties are presented in the second column of this table.
+The third, fourth and fifth columns show the contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data.
+The total
+systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
+  \label{table_systematic_contributions_0607}
+\end{center}
+\end{table}
+\section{Results}
+In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted in  from the 1996-2005 data set published previously~\cite{Air09}.
+Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
+\begin{figure}
+\begin{center}
+\includegraphics[width=15cm,keepaspectratio]{bsa_sep}
+  \caption{Beam-helicity asymmetry amplitudes extracted separately from
+the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
+hydrogen data. The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.
+An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
+2006-2007 data respectively is present in the amplitudes due to the uncertainty of
+the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+ \label{release_bsa_0607}
+\end{center}
+ \end{figure}
+
+A statistical test (Student's t-test) was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from the two data sets.
+Only the statistical uncertainties were employed in this test as the largest contributions to the systematic uncertainties, i.e.
+effects from detector resolution, acceptance, misalignment and smearing, are largely correlated.
+This test revealed no significant evidence for incompatibility between the data sets.
+The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the entire hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
+\begin{figure}
+\begin{center}
+ \includegraphics[width=15cm,keepaspectratio]{bca_sep}
+  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares) hydrogen data.
+The error bars represent the statistical uncertainties.
+The error bands represent the systematic uncertainties.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+ \label{release_bca_0607}
+\end{center}
+ \end{figure}
+
+\begin{figure}
+ \begin{center}
+ \includegraphics[width=15cm]{bsa_comb}
+  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
+from 1996 until 2007. The error bars (bands) represent the statistical
+(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of
+the beam polarisation measurement.
+Solid and dashed lines (KM10) show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
+See text for details.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+  \label{bsa_xbjrange}
+ \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=15cm]{bca_comb}
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
+The error bars (bands) represent the statistical (systematic) uncertainties.
+Theoretical calculations from the model described in Ref.
+\cite{Kum09} are shown as solid and dashed lines (KM10); calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
+See text for details.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+  \label{bca_xbjrange}
+ \end{center}
+\end{figure}
+
+\begin{figure}
+ \begin{center}
+ \includegraphics[width=15cm]{bsa_2D}
+  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+The error bars (bands) represent the statistical (systematic) uncertainties.
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+  \label{bsa_xbjrange2}
+ \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=15cm]{bca_2D}
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+The error bars (bands) represent the statistical (systematic) uncertainties.
+The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
+  \label{bca_xbjrange2}
+ \end{center}
+\end{figure}
+
+The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in figures~\ref{bsa_xbjrange} and \ref{bca_xbjrange}.
+The number of analysable events available from the 2006-2007 data set (70352) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817).
+The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus resemble the 2006-2007 result.
+This resemblance is not so evident for the beam-helicity asymmetry amplitudes as it is for the beam-charge asymmetry amplitudes, because the beam polarisation was lower in 2006 and 2007 than in 1996-2005 and thus the 2006-2007 data has a lower weighting in the combined fit.
+The major contributions to the systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations as explained in section~4, i.e.
+contributions from acceptance, smearing, finite bin widths and misalignment.
+The background in the \red{combined} data sample is estimated using the method from refs.~\cite{Air08,Zei09, Bur10}.
+The uncertainty contributions due to the observed shifts in the missing-mass distributions for the combined data sets were calculated using the procedure described in section~4 and the results were averaged.
+The total systematic uncertainties for the combined results are \red{obtained by adding these} three independent contributions in quadrature.
+The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
+sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
+The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
+This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches its minimum value because of the dependence of the amplitude on the factor $K$ defined in eq.~\ref{eq:K}.
+The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$.
+The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of figure~\ref{bsa_xbjrange}.
+Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry amplitude are compatible with zero, and neither asymmetry amplitude shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$.
+
+The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in figure~\ref{bca_xbjrange}.
+The systematic uncertainties are estimated using the same procedure as was used to estimate those for the beam-helicity asymmetries.
+The leading twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero.
+There is an expected relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as they depend on the same $\mathcal{C}$-function.
+The kinematic suppression of $A_{\textrm{C}}^{\cos(0\phi)}$ with regard to $A_{\textrm{C}}^{\cos\phi}$ is approximately fulfilled.
+The measured amplitudes are found to diverge with opposite sign from zero at increasing values of $-t$ and they indicate a weak increase with $x_{\textrm{B}}$ and $Q^{2}$.
+The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero over the whole range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
+Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.
+
+The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis.
+The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
+The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes 1these data.
+Both fits include the 1996-2005 H{\sc ermes} data.
+The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes.
+All of the relevant amplitudes reported here are well described by the model.
+
+The dash-dotted curves in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the result of calculations from a fit based on a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}.
+The ``Regge'' term is extended to include contributions that determine the $t$-dependence of the corresponding GPD.
+The model incorporates fits to global deep-inelastic and elastic scattering data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and DVCS data from Jefferson Lab.
+(to describe the skewness dependence).
+The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
+The model describes the trends of the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes well.
+
+In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one\red{-}dimensional projections: within experimental uncertainty, there is no evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependence\red{s} for any of the amplitudes.
+The results from this paper will be made available in the Durham Database.
+The results will also be made available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.
+
+\section{Summary}
+Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
+These asymmetries were extracted from a\red{n} unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
+Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
+A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 \red{data set}.
+The asymmetry amplitudes extracted from the com\red{plete} data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
+There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
+There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
+Each of the higher order asymmetry amplitudes is consistent with zero.
+The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
+All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
+No additional features are observed in any particular $x_{\textrm{B}}$-bin.
+
+\acknowledgments
+We gratefully acknowledge the \desy\ management for its support and the staff
+at \desy\ and the collaborating institutions for their significant effort.
+This work was supported by 
+the Ministry of Economy and the Ministry of Education and Science of Armenia;
+the FWO-Flanders and IWT, Belgium;
+the Natural Sciences and Engineering Research Council of Canada;
+the National Natural Science Foundation of China;
+the Alexander von Humboldt Stiftung,
+the German Bundesministerium f\"ur Bildung und Forschung (BMBF), and
+the Deutsche Forschungsgemeinschaft (DFG);
+the Italian Istituto Nazionale di Fisica Nucleare (INFN);
+the MEXT, JSPS, and G-COE of Japan;
+the Dutch Foundation for Fundamenteel Onderzoek der Materie (FOM);
+the Russian Academy of Science and the Russian Federal Agency for 
+Science and Innovations;
+the U.K.~Engineering and Physical Sciences Research Council, 
+the Science and Technology Facilities Council,
+and the Scottish Universities Physics Alliance;
+the U.S.~Department of Energy (DOE) and the National Science Foundation (NSF);
+the Basque Foundation for Science (IKERBASQUE);
+and the European Community Research Infrastructure Integrating Activity
+under the FP7 "Study of strongly interacting matter (HadronPhysics2, Grant
+Agreement number 227431)".
+
+\appendix
+\appendixpage
+\addappheadtotoc
+\setcounter{equation}{0}
+
+\section{Tables of Results}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|c|c|c|c|c|r|r|r|} \hline
+\multicolumn{2}{|c|}{} & $\langle-t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin \phi} \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,DVCS}}^{\sin \phi} \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin (2\phi)} \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{2}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & &  &  \\
+\hline \hline
+\multicolumn{2}{|c|}{overall} &  0.117 & 0.097 &  2.52 &  -0.222  $\pm$  0.023  $\pm$   0.022 &
+ 0.005  $\pm$  0.023  $\pm$  0.003 & 0.005  $\pm$  0.023  $\pm$   0.003 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.217  $\pm$  0.051  $\pm$   0.010 &
+ 0.031  $\pm$  0.051   $\pm$  0.003 & -0.032  $\pm$  0.051  $\pm$   0.003\\
+& 0.03-0.06 &  0.043 & 0.088 &  2.26&  -0.222 $\pm$   0.052   $\pm$  0.014 &
+ -0.024 $\pm$   0.052  $\pm$   0.006 & 0.062  $\pm$  0.052  $\pm$   0.002\\
+& 0.06-0.10 &  0.078 & 0.099 &  2.51 & -0.163 $\pm$   0.057   $\pm$  0.012 &
+ -0.010  $\pm$  0.056  $\pm$   0.005 & 0.039  $\pm$  0.056   $\pm$  0.006 \\
+& 0.10-0.20 &  0.142 & 0.110 &  2.79 &  -0.246 $\pm$   0.049  $\pm$   0.011 &
+0.007  $\pm$  0.049  $\pm$   0.003 & 0.007  $\pm$  0.049  $\pm$  0.008\\
+& 0.20-0.35 &  0.260 & 0.121 &  3.27 &  -0.297 $\pm$   0.066  $\pm$   0.006 &
+0.086  $\pm$  0.066  $\pm$   0.003 & -0.035 $\pm$   0.066   $\pm$  0.008\\
+& 0.35-0.70 &  0.460 & 0.125 &  3.82 &  -0.189  $\pm$  0.095  $\pm$   0.015 & 
+-0.111  $\pm$  0.095   $\pm$  0.024 & -0.056 $\pm$   0.096  $\pm$   0.029\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$x_{\text{B}}$}}} & 0.03-0.06 &  0.095 & 0.049 &  1.34 &  -0.237  $\pm$  0.050  $\pm$   0.076 &
+0.002 $\pm$   0.050  $\pm$   0.005 & -0.064  $\pm$  0.051  $\pm$   0.010\\
+& 0.06-0.08 &  0.091 & 0.069 &  1.80 &  -0.235  $\pm$  0.050  $\pm$   0.047 &
+0.010 $\pm$  0.050  $\pm$   0.004 & 0.024 $\pm$   0.049  $\pm$   0.012\\
+& 0.08-0.10 &  0.104 & 0.089 &  2.30 &  -0.263 $\pm$  0.057  $\pm$   0.033 &
+0.069 $\pm$   0.056  $\pm$   0.004 & 0.028  $\pm$  0.056  $\pm$   0.007\\
+& 0.10-0.13 &  0.121 &  0.113 &  2.93 &  -0.223  $\pm$  0.059   $\pm$  0.030 & 
+-0.015  $\pm$  0.058  $\pm$   0.007 & -0.012  $\pm$  0.059  $\pm$   0.010\\
+& 0.13-0.20 &  0.159 & 0.157 &  4.06&  -0.216  $\pm$  0.063  $\pm$   0.013 &
+0.014  $\pm$  0.063  $\pm$   0.006 & 0.046  $\pm$  0.061  $\pm$   0.010 \\
+& 0.20-0.35 &  0.231 & 0.244 &  6.14 &  -0.113 $\pm$ 0.110  $\pm$   0.021 &
+-0.111  $\pm$  0.110 $\pm$    0.017 & 0.046  $\pm$  0.102  $\pm$  0.015\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$Q^2 [\text{GeV}^2]$}}} & 1.00-1.40 &  0.076 & 0.054  & 1.20 &  -0.193  $\pm$  0.051  $\pm$   0.061 &
+-0.001 $\pm$   0.051  $\pm$   0.002 & -0.020  $\pm$  0.051   $\pm$  0.010 \\
+& 1.40-1.80 &  0.089 & 0.069 &  1.59 &  -0.311 $\pm$  0.055  $\pm$   0.062 &
+0.047  $\pm$  0.055  $\pm$   0.011 & -0.021 $\pm$   0.054  $\pm$   0.005\\
+& 1.80-2.40 &  0.104 & 0.085 &  2.08 &  -0.224 $\pm$   0.051  $\pm$   0.042 &
+0.014 $\pm$   0.051  $\pm$   0.005 & 0.015  $\pm$  0.053  $\pm$   0.008\\
+& 2.40-3.20 &  0.126 & 0.105  & 2.77 &  -0.219 $\pm$   0.054  $\pm$   0.044 &
+0.010  $\pm$  0.054 $\pm$    0.007 & 0.028   $\pm$ 0.049  $\pm$   0.006\\
+& 3.20-4.50 &  0.151 & 0.134 &  3.76 &  -0.180 $\pm$   0.063  $\pm$   0.031 &
+-0.025  $\pm$  0.062 $\pm$    0.006 & -0.016 $\pm$   0.062  $\pm$   0.008\\
+& 4.50-10.0 &  0.218 & 0.200 &  5.82 &  -0.200  $\pm$  0.074 $\pm$    0.004 &
+-0.036  $\pm$  0.074  $\pm$   0.007 & 0.069 $\pm$  0.071$ \pm$  0.013\\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
+An additional 3.4\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.}
+\end{table}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|c|c|c|c|c|r|r|r|r|} \hline
+\multicolumn{2}{|c|}{} & $\langle t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (0\phi)}\pm \delta_{stat.} \pm \delta_{syst.}$ }} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos \phi } \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (2\phi) } \pm \delta_{stat.} \pm \delta_{syst.}$ }} &
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (3\phi) } \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{2}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & &  & &  \\
+\hline
+\hline
+\multicolumn{2}{|c|}{overall} &  0.117 & 0.097 &  2.52 &  -0.024 $\pm$  0.004 $\pm$  0.011 & 
+0.032  $\pm$  0.006 $\pm$   0.002 &  -0.004  $\pm$  0.005  $\pm$   0.014 &  0.001  $\pm$   0.005   $\pm$   0.004 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.014  $\pm$  0.009 $\pm$ 0.007 & 
+0.006  $\pm$  0.012  $\pm$   0.003 &  -0.038  $\pm$  0.012 $\pm$  0.001 &  -0.022   $\pm$  0.012   $\pm$   0.004\\
+& 0.03-0.06 &  0.043 & 0.088 &  2.26& -0.008  $\pm$  0.009  $\pm$   0.006 &
+0.016 $\pm$  0.012  $\pm$   0.014 &  -0.004  $\pm$  0.012  $\pm$  0.007 &  0.003   $\pm$  0.012   $\pm$   0.005\\
+& 0.06-0.10 &  0.078 & 0.099 &  2.51 & -0.025  $\pm$  0.009  $\pm$  0.007 & 
+0.030 $\pm$  0.013  $\pm$   0.013 & 0.011  $\pm$  0.012 $\pm$   0.013 &  -0.028   $\pm$  0.012  $\pm$    0.004\\
+& 0.10-0.20 &  0.142 & 0.110 &  2.79 &  -0.019  $\pm$  0.008   $\pm$  0.010 & 
+0.036 $\pm$  0.012  $\pm$   0.014 &  0.007  $\pm$  0.011  $\pm$  0.025 & 0.019   $\pm$  0.011    $\pm$  0.001\\
+& 0.20-0.35 &  0.260 & 0.121 &  3.27 &  -0.042 $\pm$   0.011  $\pm$  0.004 &
+0.078 $\pm$  0.016  $\pm$ 0.029 & -0.016 $\pm$   0.015  $\pm$  0.040 & 0.023  $\pm$   0.015   $\pm$   0.001\\
+& 0.35-0.70 &  0.460 & 0.125 &  3.82 &  -0.083  $\pm$  0.016  $\pm$   0.005 & 
+0.069 $\pm$  0.025  $\pm$   0.061 & 0.052 $\pm$   0.022  $\pm$  0.040 & 0.030   $\pm$  0.021   $\pm$ 0.017\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$x_{\text{B}}$}}} & 0.03-0.06 &  0.095 & 0.049 &  1.34 &  -0.038  $\pm$  0.009  $\pm$   0.013 & 
+ 0.007  $\pm$  0.013  $\pm$   0.013 & -0.026 $\pm$  0.012 $\pm$   0.013 &  -0.015   $\pm$  0.011  $\pm$    0.003\\
+& 0.06-0.08 &  0.091 & 0.069 &  1.80&   -0.046  $\pm$  0.008  $\pm$   0.012 &
+0.025  $\pm$  0.012  $\pm$   0.013 & -0.001  $\pm$ 0.011  $\pm$   0.009 & -0.003   $\pm$  0.011   $\pm$   0.005\\
+& 0.08-0.10 &  0.104 & 0.089 &  2.30 &  -0.004  $\pm$  0.010  $\pm$   0.016 & 
+0.033  $\pm$  0.014  $\pm$   0.019 & -0.013 $\pm$  0.013 $\pm$    0.017 & -0.013   $\pm$  0.013    $\pm$  0.002\\
+& 0.10-0.13 &  0.121 &  0.113 &  2.93 &  -0.025  $\pm$  0.010  $\pm$   0.015 & 
+0.035  $\pm$  0.014 $\pm$   0.002 & -0.015 $\pm$  0.013  $\pm$   0.006 & 0.001   $\pm$  0.013  $\pm$    0.009\\
+& 0.13-0.20 &  0.159 & 0.157 &  4.06&   -0.012   $\pm$ 0.011  $\pm$   0.007 & 
+0.029  $\pm$  0.015 $\pm$    0.031 & -0.003  $\pm$  0.014  $\pm$   0.001 & 0.016   $\pm$  0.014   $\pm$  0.005\\
+& 0.20-0.35 &  0.231 & 0.244 &  6.14 &  -0.009 $\pm$  0.018   $\pm$  0.026 & 
+0.060  $\pm$  0.026   $\pm$    0.018 & 0.069  $\pm$  0.024  $\pm$ 0.027 & 0.043  $\pm$   0.024  $\pm$   0.009\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$Q^2 [\text{GeV}^2]$}}} & 1.00-1.40 &  0.076 & 0.054  & 1.20 &  -0.046  $\pm$  0.008  $\pm$   0.023 & 
+0.021  $\pm$  0.012  $\pm$   0.028 &  -0.020 $\pm$  0.011  $\pm$  0.012 & -0.014  $\pm$  0.011   $\pm$   0.004\\
+& 1.40-1.80 &  0.089 & 0.069 &  1.59 &  -0.018  $\pm$  0.009  $\pm$   0.021 & 
+0.032  $\pm$  0.013  $\pm$   0.020 & -0.011  $\pm$  0.012  $\pm$  0.012 & 0.001  $\pm$  0.012   $\pm$  0.002\\
+& 1.80-2.40 &  0.104 & 0.085 &  2.08 &  -0.039  $\pm$  0.009  $\pm$   0.022 &
+0.016  $\pm$  0.012  $\pm$   0.017 & -0.008 $\pm$   0.012  $\pm$  0.013 & 0.018  $\pm$   0.012  $\pm$  0.004\\
+& 2.40-3.20 &  0.126 & 0.105  & 2.77 &  -0.016 $\pm$   0.010  $\pm$   0.019 &  
+0.068  $\pm$  0.014  $\pm$   0.020 & 0.006  $\pm$  0.013  $\pm$  0.013 & -0.022  $\pm$  0.013  $\pm$  0.009\\
+& 3.20-4.50 &  0.151 & 0.134 &  3.76 &  0.002  $\pm$  0.011   $\pm$  0.014 & 
+0.010 $\pm$   0.015  $\pm$   0.002 & -0.008  $\pm$  0.014 $\pm$ 0.015 & 0.014   $\pm$  0.014  $\pm$  0.002\\
+& 4.50-10.0 &  0.218 & 0.200 &  5.82 &  -0.003  $\pm$  0.013  $\pm$   0.014 & 
+0.037  $\pm$  0.018  $\pm$  0.038 & 0.042 $\pm$   0.017  $\pm$  0.003 & 0.010   $\pm$  0.017   $\pm$   0.005\\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
+\end{table}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|c|c|c|c|c|r|r|r|} \hline
+\multicolumn{2}{|c|}{} & $\langle t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin \phi} \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,DVCS}}^{\sin \phi} \pm \delta_{stat.} \pm \delta_{syst.}$ }} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin (2\phi)} \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{2}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & & &  \\
+\hline \hline
+\multicolumn{2}{|c|}{overall} &  0.118 & 0.097 &  2.51 &  -0.229  $\pm$  0.018  $\pm$   0.024 &
+ 0.017  $\pm$  0.018  $\pm$  0.001 & -0.010  $\pm$  0.018  $\pm$   0.001 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 &  1.72 &  -0.225  $\pm$  0.039 $\pm$   0.010 &
+ 0.048  $\pm$  0.039   $\pm$  0.003 & 0.003  $\pm$  0.039  $\pm$   0.003\\
+& 0.03-0.06 &  0.044 & 0.088 &  2.25 &  -0.242 $\pm$   0.039   $\pm$  0.014 &
+ 0.019 $\pm$   0.039  $\pm$   0.005 & 0.026  $\pm$  0.038  $\pm$   0.001\\
+& 0.06-0.10 &  0.079 & 0.099 &  2.49 & -0.177 $\pm$   0.043   $\pm$  0.012 &
+ -0.023  $\pm$  0.043  $\pm$   0.004 & -0.002  $\pm$  0.043   $\pm$  0.005 \\
+& 0.10-0.20 &  0.143 & 0.109 &  2.76 &  -0.253 $\pm$   0.037  $\pm$   0.010 &
+0.010  $\pm$  0.037  $\pm$   0.002 & -0.008  $\pm$  0.037  $\pm$  0.006\\
+& 0.20-0.35 &  0.261 & 0.119 &  3.23 &  -0.287 $\pm$   0.050  $\pm$   0.006 &
+0.105  $\pm$  0.051  $\pm$   0.002 & -0.047 $\pm$   0.051   $\pm$  0.005\\
+& 0.35-0.70 &  0.463 & 0.122 &  3.73 &  -0.173  $\pm$  0.072  $\pm$   0.016 & 
+-0.107  $\pm$  0.073   $\pm$  0.023 & -0.111 $\pm$   0.074  $\pm$   0.028\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$x_{\text{B}}$}}} & 0.03-0.06 &  0.099 & 0.049 & 1.34 & -0.249  $\pm$  0.038  $\pm$   0.079 &
+0.035 $\pm$   0.038  $\pm$   0.004 & -0.044  $\pm$  0.039  $\pm$  0.011 \\ 
+& 0.06-0.08 &  0.093 & 0.070 &  1.79 &  -0.228 $\pm$  0.037  $\pm$   0.049 &
+0.013  $\pm$  0.038  $\pm$   0.002 & 0.023 $\pm$   0.037  $\pm$   0.012\\
+& 0.08-0.10 &  0.106 & 0.089 &  2.30 &  -0.250 $\pm$   0.043  $\pm$   0.033 &
+0.047 $\pm$   0.043  $\pm$   0.004 & 0.032  $\pm$  0.043  $\pm$   0.007\\
+& 0.10-0.13 &  0.122 &  0.114 &  2.94 &  -0.237 $\pm$   0.045  $\pm$   0.030 &
+-0.003  $\pm$  0.045 $\pm$    0.006 & -0.027 $\pm$ 0.045  $\pm$   0.010\\
+& 0.13-0.20 &  0.160 & 0.157 &  4.06 &  -0.224 $\pm$   0.048  $\pm$   0.013 &
+0.033  $\pm$  0.048 $\pm$    0.006 & -0.050 $\pm$   0.047  $\pm$   0.006\\
+& 0.20-0.35 &  0.233 & 0.244 &  6.13 &  -0.077  $\pm$  0.085 $\pm$    0.022 &
+-0.141  $\pm$  0.085  $\pm$   0.012 & -0.023 $\pm$  0.080 $ \pm$  0.007\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$Q^2 [\text{GeV}^2]$}}} & 1.00-1.40 &  0.078 & 0.055  & 1.20  &  -0.218  $\pm$  0.038  $\pm$   0.063 &
+0.029 $\pm$   0.038  $\pm$   0.002 & -0.023  $\pm$  0.038  $\pm$   0.012\\
+& 1.40-1.80 &  0.092 & 0.069 &  1.59  &  -0.257  $\pm$  0.042  $\pm$   0.064 &
+0.040 $\pm$  0.042  $\pm$   0.006 & 0.011 $\pm$   0.042  $\pm$   0.004\\
+& 1.80-2.40 &  0.106 & 0.085 &  2.08  &  -0.233 $\pm$  0.041  $\pm$   0.042 &
+0.016 $\pm$   0.041  $\pm$   0.004 & -0.010  $\pm$  0.040  $\pm$   0.007\\
+& 2.40-3.20 &  0.127 & 0.105  & 2.77  &  -0.302  $\pm$  0.044   $\pm$  0.044 & 
+0.087  $\pm$  0.044  $\pm$   0.006 & 0.031  $\pm$  0.044  $\pm$   0.005\\
+& 3.20-4.50 &  0.152 & 0.134 &  3.77  &  -0.160  $\pm$  0.048  $\pm$   0.032 &
+-0.057  $\pm$  0.048  $\pm$   0.005 & -0.061  $\pm$  0.048  $\pm$   0.004 \\
+& 4.50-10.0 &  0.220 & 0.199 &  5.79  &  -0.169 $\pm$ 0.057  $\pm$   0.008 &
+-0.065  $\pm$  0.057 $\pm$ 0.005 & -0.017  $\pm$  0.056  $\pm$  0.013\\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.
+}
+\end{table}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|c|c|c|c|c|r|r|r|r|} \hline
+\multicolumn{2}{|c|}{} & $\langle t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (0\phi)} \pm \delta_{stat.} \pm \delta_{syst.}$ }} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos \phi } \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (2\phi) }\pm \delta_{stat.} \pm \delta_{syst.}$}} &
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (3\phi) } \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{2}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & &  &  &  \\
+\hline
+\hline
+\multicolumn{2}{|c|}{overall} &  0.119 & 0.097 &  2.51 &  -0.021 $\pm$  0.003 $\pm$  0.010 & 
+0.041  $\pm$  0.005 $\pm$   0.002 &  -0.003  $\pm$  0.005  $\pm$   0.014 &  -0.002  $\pm$   0.005   $\pm$   0.003 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 & 1.72  &  -0.017  $\pm$  0.007 $\pm$ 0.007 & 
+0.005  $\pm$  0.010  $\pm$   0.003 &  -0.023  $\pm$  0.010 $\pm$  0.001 &  -0.013   $\pm$  0.010   $\pm$   0.004\\
+& 0.03-0.06 &  0.044 & 0.088 & 2.25 & -0.005  $\pm$  0.007  $\pm$   0.006 &
+0.007 $\pm$  0.010  $\pm$   0.014 &  -0.003  $\pm$  0.010  $\pm$  0.007 &  0.005   $\pm$  0.010   $\pm$   0.004\\
+& 0.06-0.10 & 0.079  & 0.099 &  2.49 & -0.012  $\pm$  0.008  $\pm$  0.006 & 
+0.028 $\pm$  0.011  $\pm$   0.013 & 0.013  $\pm$  0.011 $\pm$   0.013 &  -0.023   $\pm$  0.011  $\pm$    0.003\\
+& 0.10-0.20 & 0.143  & 0.109 &  2.76 &  -0.016  $\pm$  0.007   $\pm$  0.009 & 
+0.052 $\pm$  0.009  $\pm$   0.015 &  -0.008  $\pm$  0.009  $\pm$  0.025 & 0.006   $\pm$  0.009    $\pm$  0.001\\
+& 0.20-0.35 &   0.261 & 0.119 &  3.23 &  -0.040 $\pm$   0.009  $\pm$  0.002 &
+0.108 $\pm$  0.013  $\pm$ 0.030 & -0.003 $\pm$   0.013  $\pm$  0.040 & 0.012  $\pm$   0.013   $\pm$   0.001\\
+& 0.35-0.70 &  0.462 & 0.122 &  3.73 &  -0.072  $\pm$  0.014  $\pm$   0.004 & 
+0.134 $\pm$  0.021  $\pm$   0.062 & 0.049 $\pm$   0.019  $\pm$  0.040 & 0.030   $\pm$  0.019   $\pm$ 0.017\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$x_{\text{B}}$}}} & 0.03-0.06 &  0.099 &  0.049 &   1.34 &  -0.045  $\pm$  0.007  $\pm$   0.014 & 
+0.016  $\pm$  0.011  $\pm$   0.014 & -0.017 $\pm$  0.010 $\pm$  0.013 &  0.004   $\pm$  0.009  $\pm$    0.003\\
+& 0.06-0.08 & 0.093  & 0.070 & 1.79  &   -0.035  $\pm$  0.007  $\pm$   0.013 &
+0.028  $\pm$  0.009  $\pm$   0.015 & -0.019  $\pm$ 0.009  $\pm$  0.009 & -0.012   $\pm$  0.009   $\pm$   0.005\\
+& 0.08-0.10 &  0.106 & 0.089 &  2.30 &  -0.017  $\pm$  0.008  $\pm$   0.017 & 
+0.044  $\pm$  0.011  $\pm$   0.019 & 0.005 $\pm$  0.011 $\pm$    0.016 & -0.009   $\pm$  0.011    $\pm$  0.002\\
+& 0.10-0.13 &  0.122 & 0.114  & 2.94  &  -0.007  $\pm$  0.008  $\pm$   0.015 & 
+0.030  $\pm$  0.012 $\pm$   0.002 & -0.001 $\pm$  0.012  $\pm$   0.006 & -0.009   $\pm$  0.011  $\pm$    0.009\\
+& 0.13-0.20 &  0.160 & 0.157 & 4.06 &   -0.006   $\pm$ 0.009  $\pm$   0.007 & 
+0.049  $\pm$  0.013 $\pm$    0.030 & -0.001  $\pm$  0.012  $\pm$   0.001 & 0.002   $\pm$  0.012   $\pm$  0.005\\
+& 0.20-0.35 & 0.233  & 0.244 &  6.13 &  0.019 $\pm$  0.016   $\pm$  0.027 & 
+0.050  $\pm$  0.022   $\pm$  0.018 & 0.051  $\pm$  0.022  $\pm$   0.027 & 0.006  $\pm$   0.021  $\pm$   0.008\\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$Q^2 [\text{GeV}^2]$}}} & 1.00-1.40 &  0.078 &  0.055 & 1.20 &  -0.048  $\pm$  0.007  $\pm$   0.024 & 
+0.029  $\pm$  0.010  $\pm$   0.030 &  -0.008 $\pm$  0.009  $\pm$  0.011 & 0.005  $\pm$  0.009   $\pm$   0.004\\
+& 1.40-1.80 & 0.092  & 0.069 &  1.59 &  -0.022  $\pm$  0.008  $\pm$   0.022 & 
+0.041  $\pm$  0.011  $\pm$   0.021 & -0.020  $\pm$  0.011  $\pm$  0.012 & -0.004  $\pm$  0.011   $\pm$  0.002\\
+& 1.80-2.40 &  0.106 & 0.085 &  2.08 &  -0.028  $\pm$  0.007  $\pm$   0.022 &
+ 0.031  $\pm$  0.010  $\pm$   0.018 & -0.012 $\pm$   0.010  $\pm$  0.013 & -0.000  $\pm$   0.010  $\pm$  0.004\\
+& 2.40-3.20 &  0.127 &  0.105 & 2.77 &  -0.017 $\pm$   0.008  $\pm$   0.019 &  
+0.059  $\pm$  0.012  $\pm$   0.019 & 0.014  $\pm$  0.011  $\pm$  0.013 & -0.010  $\pm$  0.011  $\pm$  0.009\\
+& 3.20-4.50 &   0.152 & 0.134 &  3.77 &  0.011  $\pm$  0.009   $\pm$  0.013 & 
+0.037 $\pm$   0.013  $\pm$   0.002 & -0.008  $\pm$  0.013 $\pm$ 0.015 & -0.012   $\pm$  0.012  $\pm$  0.001\\
+& 4.50-10.0 & 0.220  & 0.199 & 5.79  &  0.006  $\pm$  0.011  $\pm$   0.013 & 
+0.038  $\pm$  0.015  $\pm$  0.038 & 0.036 $\pm$   0.015  $\pm$  0.002 & 0.005   $\pm$  0.015   $\pm$   0.004\\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
+\end{table}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|cc|c|c|c|c|r|r|r|} \hline
+\multicolumn{3}{|c|}{} & $\langle t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin \phi} \pm \delta_{stat.} \pm \delta_{syst.}$ }} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,DVCS}}^{\sin \phi } \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{LU,I}}^{\sin (2\phi)} \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{3}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & & &  \\
+\hline \hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473  &  -0.253  $\pm$  0.046  $\pm$  0.019  &
+ 0.092  $\pm$   0.046  $\pm$ 0.008  &   -0.039 $\pm$  0.046  $\pm$  0.014 \\
+& & 0.03-0.06 & 0.043  &  0.060 &  1.558 &  -0.188 $\pm$  0.058    $\pm$  0.024 &
+ -0.021 $\pm$ 0.058  $\pm$  0.007 &  0.074 $\pm$  0.057  $\pm$  0.007 \\
+& & 0.06-0.10 &  0.078 & 0.060 &  1.567 & -0.241  $\pm$  0.069 $\pm$  0.018 &
+  -0.013 $\pm$  0.069  $\pm$  0.004  &  -0.034 $\pm$  0.068   $\pm$   0.012\\
+& & 0.10-0.20 &  0.142 & 0.060 & 1.576  &  -0.261 $\pm$  0.062   $\pm$  0.020  &
+ -0.015 $\pm$  0.062  $\pm$  0.006  &  0.025 $\pm$  0.062  $\pm$ 0.009 \\
+& & 0.20-0.35 &  0.259 & 0.057 & 1.701  & -0.284  $\pm$ 0.087   $\pm$  0.014 &
+ 0.145 $\pm$  0.088  $\pm$   0.006 &  -0.041 $\pm$ 0.091  $\pm$ 0.010 \\
+& & 0.35-0.70 & 0.465  &  0.054 &  1.819 &  -0.126  $\pm$  0.147 $\pm$ 0.008  & 
+ -0.120 $\pm$  0.147   $\pm$ 0.053  &  -0.115  $\pm$   0.159  $\pm$ 0.016 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.08 < x_{\text{B}} < 0.12$ }}} & 0.00-0.03 &  0.022  &0.095  & 2.311  &  -0.163  $\pm$   0.078 $\pm$   0.008 &
+ -0.063 $\pm$   0.079  $\pm$   0.003 &  0.096  $\pm$  0.079  $\pm$  0.016 \\
+& & 0.03-0.06 &  0.044 & 0.098 &  2.501 &  -0.302  $\pm$ 0.069   $\pm$  0.008  &
+ 0.053 $\pm$  0.070  $\pm$   0.007 & -0.024 $\pm$   0.068  $\pm$ 0.002  \\
+& & 0.06-0.10 & 0.079  & 0.098 & 2.462  &  -0.187 $\pm$  0.078  $\pm$  0.007  &
+ 0.003 $\pm$  0.078   $\pm$  0.007 &  -0.049 $\pm$  0.078  $\pm$  0.007  \\
+& & 0.10-0.20 & 0.142  &  0.098 & 2.484  &  -0.237  $\pm$   0.068  $\pm$ 0.005  & 
+ 0.009 $\pm$   0.068 $\pm$   0.010 &  -0.053 $\pm$  0.068  $\pm$  0.019 \\
+& & 0.20-0.35 &  0.258 & 0.099 & 2.736  &   -0.280 $\pm$  0.099  $\pm$  0.003  &
+ 0.077 $\pm$   0.100 $\pm$  0.005 &  -0.031  $\pm$  0.101  $\pm$  0.023  \\
+& & 0.35-0.70 &  0.459 & 0.099 & 3.211  &  -0.278 $\pm$ 0.151  $\pm$ 0.010   &
+ -0.025 $\pm$  0.152 $\pm$  0.014  &  0.150 $\pm$  0.163  $\pm$ 0.007 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.238  $\pm$  0.238 $\pm$ 0.066  &
+0.006 $\pm$  0.237  $\pm$  0.052 &  0.275 $\pm$  0.239 $\pm$ 0.041 \\
+& & 0.03-0.06 & 0.046  & 0.145 & 3.629  &  -0.235 $\pm$ 0.091   $\pm$  0.009  &
+ 0.037 $\pm$  0.092  $\pm$ 0.008  & 0.006 $\pm$  0.094 $\pm$ 0.009 \\
+& & 0.06-0.10 & 0.080  & 0.160 & 3.942  &  -0.086 $\pm$ 0.085  $\pm$  0.011 &
+-0.031 $\pm$   0.085 $\pm$  0.003  &  0.058 $\pm$ 0.083  $\pm$  0.007\\
+& & 0.10-0.20 & 0.145  &  0.174 & 4.309 &  -0.248  $\pm$  0.067  $\pm$ 0.004   &
+  0.029 $\pm$ 0.068  $\pm$  0.002  &  -0.004  $\pm$  0.066 $\pm$  0.007 \\
+& & 0.20-0.35 & 0.263  & 0.184 &  4.799 &  -0.283 $\pm$  0.085  $\pm$ 0.025  &
+ 0.133 $\pm$  0.085 $\pm$   0.010 &  -0.061  $\pm$  0.082   $\pm$  0.005\\
+& & 0.35-0.70 & 0.460  & 0.194 & 5.621  &  -0.117  $\pm$  0.117  $\pm$  0.046 &
+ -0.200 $\pm$  0.117  $\pm$  0.024  & -0.218 $\pm$ 0.110 $ \pm$ 0.048 \\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for $t$ bins with certain $x_{\textrm{B}}$ ranges.
+An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of
+the beam polarisation measurement.}
+\end{table}
+
+\begin{table}[width=15cm]
+ \begin{center}
+\resizebox{16cm}{!} {
+\begin{tabular}{|cc|c|c|c|c|r|r|r|r|} \hline
+\multicolumn{3}{|c|}{} & $\langle t\rangle$ & $\langle
+x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (0\phi)} \pm \delta_{stat.} \pm \delta_{syst.}$}} & 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos \phi } \pm \delta_{stat.} \pm \delta_{syst.}$}}& 
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (2\phi) } \pm \delta_{stat.} \pm \delta_{syst.}$}}&
+\multicolumn{1}{c|}{\multirow{2}{*}{$A_{\text{C}}^{\cos (3\phi) } \pm \delta_{stat.} \pm \delta_{syst.}$}} \\ 
+\multicolumn{3}{|c|}{} &  $[\text{GeV}^2]$ & & $[\text{GeV}^2]$ & & & & \\
+\hline
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473 &  -0.031  $\pm$  0.008 $\pm$ 0.006 &
+-0.013  $\pm$ 0.016  $\pm$ 0.002  &  -0.032 $\pm$  0.012 $\pm$ 0.004 &   -0.016  $\pm$   0.012 $\pm$ 0.003  \\
+& & 0.03-0.06 & 0.043  &  0.060 &  1.558 &  -0.007 $\pm$  0.015 $\pm$ 0.008  &
+0.019 $\pm$  0.015  $\pm$ 0.012  &  -0.019  $\pm$  0.015 $\pm$ 0.010 &   0.013 $\pm$  0.015  $\pm$  0.005 \\
+& & 0.06-0.10 &  0.078 & 0.060 &  1.567 & -0.025  $\pm$  0.012 $\pm$ 0.017  & 
+0.007 $\pm$ 0.017   $\pm$ 0.004  &  0.010 $\pm$ 0.017  $\pm$ 0.018  &  -0.014  $\pm$  0.017  $\pm$ 0.007 \\
+& & 0.10-0.20 &  0.142 & 0.060 & 1.576 &  -0.041 $\pm$   0.011 $\pm$ 0.019  & 
+ 0.036 $\pm$ 0.017  $\pm$   0.001 &  -0.009  $\pm$ 0.016  $\pm$ 0.026 & 0.008  $\pm$  0.015   $\pm$ 0.002 \\
+& & 0.20-0.35 &  0.259 & 0.057 & 1.701 &  -0.039 $\pm$  0.026  $\pm$ 0.023  &
+0.148 $\pm$  0.044 $\pm$  0.003 & 0.021 $\pm$   0.036 $\pm$ 0.038 & 0.061  $\pm$ 0.027   $\pm$  0.017 \\
+& & 0.35-0.70 & 0.465  &  0.054 &  1.819 &  -0.234  $\pm$  0.090  $\pm$  0.026  & 
+-0.054 $\pm$ 0.158 $\pm$ 0.062  &  -0.109 $\pm$  0.113 $\pm$  0.064 &  -0.084  $\pm$  0.061  $\pm$ 0.020 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.08 < x_{\text{B}} < 0.12$}}} & 0.00-0.03 &  0.022  &0.095  & 2.311 &  0.020  $\pm$ 0.015   $\pm$  0.014  &
+ 0.049 $\pm$  0.021 $\pm$ 0.017  & -0.002 $\pm$ 0.021  $\pm$  0.008 &  -0.014  $\pm$ 0.021   $\pm$ 0.005 \\
+& & 0.03-0.06 &  0.044 & 0.098 &  2.501  &  -0.013  $\pm$  0.013  $\pm$  0.014  &
+-0.002  $\pm$  0.018 $\pm$ 0.003 & 0.037  $\pm$  0.018 $\pm$ 0.011  & 0.000  $\pm$ 0.018   $\pm$  0.003\\
+& & 0.06-0.10 & 0.079  & 0.098 & 2.462 &  0.007  $\pm$  0.014  $\pm$  0.010  & 
+ 0.037 $\pm$ 0.020 $\pm$  0.002 & 0.012 $\pm$ 0.020 $\pm$ 0.010  &  -0.019 $\pm$  0.020  $\pm$ 0.010 \\
+& & 0.10-0.20 & 0.142  & 0.098 & 2.484  &  -0.020 $\pm$  0.013 $\pm$   0.026 & 
+0.038  $\pm$ 0.018 $\pm$ 0.018  & -0.024 $\pm$  0.017  $\pm$ 0.024 &  -0.005 $\pm$ 0.017  $\pm$ 0.007 \\
+& & 0.20-0.35 &  0.258 & 0.099 & 2.736 &   -0.064  $\pm$ 0.018  $\pm$   0.029 & 
+0.107  $\pm$ 0.025 $\pm$ 0.008 &  -0.011 $\pm$  0.024  $\pm$  0.042 &  -0.038 $\pm$ 0.024  $\pm$ 0.013 \\
+& & 0.35-0.70 &  0.459 & 0.099 & 3.211 &  -0.077 $\pm$   0.038 $\pm$ 0.023  & 
+0.023  $\pm$  0.063  $\pm$ 0.015 &  -0.046 $\pm$ 0.056  $\pm$  0.010 & 0.024 $\pm$ 0.048 $\pm$ 0.029 \\
+\hline
+\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.024 $\pm$  0.045  $\pm$   0.008 &
+ -0.007 $\pm$ 0.064  $\pm$ 0.001  & -0.013 $\pm$ 0.065 $\pm$ 0.023 & 0.026  $\pm$ 0.062 $\pm$ 0.011 \\
+& & 0.03-0.06 & 0.046  & 0.145 & 3.629 &  0.034  $\pm$   0.018 $\pm$   0.019 & 
+ -0.044 $\pm$ 0.027  $\pm$ 0.045  & -0.005  $\pm$ 0.025 $\pm$ 0.020 & -0.027 $\pm$ 0.025 $\pm$ 0.014 \\
+& & 0.06-0.10 & 0.080  & 0.160 & 3.942 &  -0.026 $\pm$   0.016 $\pm$  0.013  &
+ 0.044 $\pm$ 0.022  $\pm$ 0.038  & 0.012 $\pm$  0.022  $\pm$ 0.003  & -0.043 $\pm$ 0.021 $\pm$ 0.005 \\
+& & 0.10-0.20 & 0.145  &  0.174 & 4.309 &  0.013 $\pm$    0.012 $\pm$   0.010 &  
+ 0.059 $\pm$  0.017 $\pm$ 0.024  & 0.002  $\pm$ 0.017   $\pm$ 0.010  &  0.011 $\pm$  0.017  $\pm$ 0.003 \\
+& & 0.20-0.35 & 0.263  & 0.184 &  4.799 &  -0.000  $\pm$ 0.015   $\pm$  0.013 & 
+0.069  $\pm$ 0.022  $\pm$  0.034 &  0.017 $\pm$ 0.021  $\pm$  0.023 &  0.010  $\pm$  0.021 $\pm$ 0.005 \\
+& & 0.35-0.70 & 0.460  & 0.194 & 5.621  &   -0.023 $\pm$   0.021 $\pm$ 0.022  & 
+ 0.078 $\pm$  0.030 $\pm$  0.009 & 0.068 $\pm$   0.030  $\pm$ 0.020 &  0.061 $\pm$  0.029  $\pm$ 0.024 \\
+\hline
+  \end{tabular}
+}
+ \end{center}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during the 1996-2007 at H{\sc ermes} for $t$ bins with certain $x_{\textrm{B}}$ ranges.}
+\end{table}
+\clearpage
+\section{Covariance Matrix Results}
+Figure~\ref{pic:covmat} shows the covariance matrix for the 13 parameter fit for all amplitudes extracted in a single bin across the entire kinematic range.
+The covariance matrix for the fit in each of the kinematic bins presented in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2} will be made available in the Durham database.
+\begin{figure}[tbh]
+\centering
+\includegraphics[width=\textwidth]{CovMat.pdf}
+\caption{The covariance matrix results for the asymmetries extracted in a single bin across the whole kinematic range.}
+\label{pic:covmat}
+\end{figure}
+
 \bibliographystyle{natbib}
-\bibliography{jburnsref}
+\begin{thebibliography}{10}
+\bibitem{Mue94}
+D. M\"uller et al., \emph{Wave Functions, Evolution Equations and Evolution Kernels from Light-Ray Operators of QCD}
+\\Fortschr. Phys. {\bf 42} (1994) 101 [arxiv:hep-ph/9812448].
+
+\bibitem{Ji97}
+X.~Ji, \emph{Gauge-Invariant Decomposition of Nucleon Spin}
+\\Phys. Rev. Lett. {\bf 78} (1997) 610 [arxiv:hep-ph/9603249].\\
+
+X.~Ji, \emph{Deeply virtual Compton scattering}
+\\Phys. Rev. D \textbf{55} (1997) 7114 [arxiv:hep-ph/9609381].
+
+\bibitem{Rad97}
+A.~V. Radyushkin, \emph{Scaling Limit of Deeply Virtual Compton Scattering}
+\\Phys. Lett. B \textbf{380} (1996) 417 [arxiv:hep-ph/9604317].
+
+\bibitem{Bur00}
+M.~Burkardt, \emph{Impact Parameter Dependent Parton Distributions and Off-Forward Parton Distributions for $\zeta\to 0$}
+\\Phys. Rev. D \textbf{62} (2000) 071503 [ariv:hep-ph/0005108].
+\\Errarum-ibid Phys. Rev. D \textbf{66} (2002) 119903.
+
+\bibitem{Air01}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Measurement of the Beam-Spin Azimuthal Asymmetry associated with Deeply-Virtual Compton Scattering}
+\\Phys. Rev. Lett. \textbf{87} (2001) 182001 [arxiv:hep-ex/0106068].
+
+\bibitem{Air06}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{The Beam-Charge Azimuthal Asymmetry and Deeply Virtual Compton Scattering }
+\\Phys. Rev. D \textbf{75} (2007) 011103 [arxiv:hep-ex/0605108].
+
+\bibitem{Air08}
+H{\sc ermes} Collaboration, A.
+Airapetian et al., \emph{Measurement of Azimuthal Asymmetries With Respect To Both Beam Charge and Transverse Target Polarization in Exclusive Electroproduction of Real Photons}
+\\JHEP \textbf{06} (2008) 066 [arxiv:0802.2499].
+
+\bibitem{Air09}
+H{\sc ermes} Collaboration, A.
+Airapetian et al., \emph{Separation of contributions from deeply virtual Compton scattering and its interference with the Bethe--Heitler process in measurements on a hydrogen target}
+\\JHEP {\bf 11} (2009) 083 [arxiv:0909.3587].
+
+\bibitem{Air10}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Measurement of azimuthal asymmetries associated with deeply virtual Compton scattering on an unpolarized deuterium target}
+\\Nucl. Phys. B {\bf 829} (2010) 1 [arxiv:0911.0095].
+
+\bibitem{Air10a}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Nuclear-mass dependence of beam-helicity and beam-charge azimuthal asymmetries in DVCS}
+\\Phys. Rev. C {\bf 81} (2010) 035202 [arxiv:0911.0091].
+
+\bibitem{Air10b}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Exclusive Leptoproduction of Real Photons on a Longitudinally Polarised Hydrogen target}
+\\JHEP {\bf 06} (2010) 019 [arxiv:1004.0177].
+
+\bibitem{Air11}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Measurement of azimuthal asymmetries associated with deeply virtual Compton scattering on a longitudinally polarized deuterium target}
+\\Nucl. Phys. B {\bf 842} (2011) 265 [arxiv:1008.3996].
+
+\bibitem{Air11a}
+H{\sc ermes} Collaboration, A. Airapetian et al., \emph{Measurement of double-spin asymmetries associated with deeply virtual Compton scattering on a transversely polarized hydrogen target}
+\\Phys. Lett. B {\bf 704} (2011) 15 [arxiv:1106.2990].
+
+\bibitem{h101}
+H1 Collaboration, C. Adloff et al., \emph{Measurement of deeply virtual Compton scattering at HERA}
+\\Phys. Lett. B {\bf 517} (2001) 47 [arxiv:hep-ex/0107005].
+
+\bibitem{h105}
+H1 Collaboration, A. Aktas et al., \emph{Measurement of deeply virtual Compton scattering at HERA}
+\\Eur. Phys. J. C {\bf 44} (2005) 1 [arxiv:hep-ex/0505061].
+
+\bibitem{h107}
+H1 Collaboration, F. D. Aaron et al., \emph{Measurement of deeply virtual Compton scattering and its $t$-dependence at HERA}
+\\Phys. Lett. B {\bf 659} (2007) 769 [arxiv:0709.4114].
+
+\bibitem{h109}
+H1 Collaboration, F. D. Aaron et al., \emph{Deeply virtual Compton scattering and its Beam Charge Asymmetry in $e^{\pm}$ Collisions at HERA}
+Phys. Lett. B {\bf 681} (2009) 391 [arxiv:09075289].
+
+\bibitem{zeu03}
+Z{\sc eus} Collaboration, S. Chekanov et al., \emph{Measurement of deeply virtual Compton scattering at HERA}
+Phys. Lett. B {\bf 573} (2003) 46 [arxiv:hep-ex/0305028].
+
+\bibitem{zeu08}
+Z{\sc eus} Collaboration, S. Chekanov et al., \emph{A measurement of the $Q^2$, $W$ and $t$ dependences of deeply virtual Compton scattering at HERA}
+JHEP {\bf 05} (2009) 108 [arxiv:0812.2517].
+
+\bibitem{Maz07}
+JLab Hall A Collaboration, M. Mazouz et al., \emph{Deeply virtual Compton scattering off the neutron}
+\\Phys. Rev. Lett. {\bf 99} (2007) 242501 [arxiv:0709.0450].
+
+\bibitem{Cam06}
+JLab Hall A Collaboration,  C. Camacho et al., \emph{Scaling Tests of the Cross Section for Deeply Virtual Compton Scattering}
+\\Phys. Rev. Lett. \textbf{97} (2006) 262002 [arxiv:nucl-ex/0607029].
+
+\bibitem{Ste01}
+JLab C{\sc las} Collaboration, S. Stepanyan et al., \emph{Observation of exclusive DVCS in polarized electron beam asymmetry measurements}
+\\Phys. Rev. Lett. {\bf 87} (2001) 182002 [arxiv:hep-ex/0107043].
+
+\bibitem{Che06}
+JLab C{\sc las} Collaboration, S. Chen et al., \emph{Measurement of Deeply Virtual Compton Scattering with a Polarized Proton Target}
+\\Phys. Rev. Lett. {\bf 97} (2006) 072002 [arxiv:hep-ex/0605012].
+
+\bibitem{Gir08}
+JLab C{\sc las} Collaboration, F. X. Girod et al., \emph{Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries}
+\\Phys. Rev. Lett. \textbf{100} (2008) 162002 [arxiv:0711.0755].
+
+\bibitem{Gav09}
+JLab C{\sc las} Collaboration, G. Gavalian et al., \emph{Beam Spin Asymmetries in DVCS at CLAS with 4.8GeV}
+\\Phys. Rev. C {\bf 80} (2009) 035206 [arxiv:0812.2950].
+
+\bibitem{Com10}
+C{\sc ompass} Collaboration, \emph{C{\sc ompass} II proposal}
+\\C{\sc ern}/SPSC-2010-014, SPSC-P-340
+
+\bibitem{Bel02b}
+A.V. Belitsky, D. M\"uller and A. Kirchner, \emph{Theory of Deeply Virtual Compton Scattering on the nucleon}
+\\Nucl. Phys. B \textbf{629} (2002) 323 [arxiv:hep-ph/0112108].
+
+\bibitem{Tre04}
+A. Bacchetta, U D’Alesio, M Diehl and C. A. Miller, \emph{Single-spin asymmetries: The Trento conventions}
+\\Phys. Rev. D \textbf{70} (2004) 117504 [arxiv:hep-ph/0410050].
+
+\bibitem{Ack98}
+H{\sc ermes} Collaboration, K. Ackerstaff et al., \emph{The H{\sc ermes} Spectrometer}
+\\Nucl. Instrum. Meth. A {\bf 417} (1998)~230 [arxiv:hep-ex/9806008].
+
+\bibitem{Zei09}
+D.~Zeiler, \emph{Deeply Virtual Compton Scattering off an Unpolarized Hydrogen Target at the HERMES Experiment}
+\\Ph.D. thesis, Universit\"at Erlangen--N\"urnberg, Germany, October 2009, D{\sc esy}-THESIS-2009-041.
+
+\bibitem{Bur10}
+J. Burns, \emph{Deeply Virtual Compton Scattering off an Unpolarised Hydrogen Target at HERMES}
+\\Ph.D. thesis, University of Glasgow, United Kingdom, August 2010, D{\sc esy}-THESIS-2010-036.
+
+\bibitem{Bar90}
+R. Barlow, \emph{Extended maximum likelihood}
+\\Nucl. Instrum. Meth. A {\bf 297} (1990) 496.
+
+\bibitem{Wan}
+S.~Wandzura and F.~Wilczek, \emph{Sum rules for spin-dependent electroproduction-test of relativistic constituent quarks}
+\\Phys. Lett. B \textbf{72} (1977) 195.
+
+\bibitem{Bra76}
+F. W. Brasse et al., \emph{Parametrization of the $Q^2$ dependence of $\gamma_Vp$ total cross sections in the resonance region}
+\\Nucl. Phys. B {\bf 110} (1976) 413.
+
+\bibitem{Guz06}
+V.
+Guzey and T.
+Teckentrup, \emph{Dual parametrization of the proton generalized parton distribution functions H and E, and description of the deeply virtual Compton scattering cross sections and asymmetries}
+\\Phys. Rev. D {\bf 74} (2006) 054027 [arxiv:hep-ph/0607099].\\
+
+V. Guzey and T. Teckentrup, \emph{On the mistake in the implementation of the minimal model of the dual parametrization and resulting inability to describe the high-energy deeply virtual Compton data}
+\\Phys. Rev. D {\bf 79} (2009) 017501 [arxiv:0810.3899].
+
+\bibitem{Kum09}
+K. Kumericki and D. M\"uller, \emph{Deeply virtual Compton scattering at small $x_B$ and the access to the GPD H}
+\\Nucl. Phys. B {\bf 841} (2010) 1 [arxiv:0904.0458].
+
+\bibitem{Mue05}
+D. M\"uller and A. Sch\"afer, \emph{Complex conformal spin partial wave expansion of generalized parton distributions and distribution amplitudes}
+\\Nucl. Phys. B {\bf 739} (2006) 1 [arxiv:hep-ph/0509204].
+
+\bibitem{Kum07}
+K. Kumericki, D. M\"uller and K. Passek-Kumericki, \emph{Towards a fitting procedure for deeply virtual Compton scattering at next-to-leading order and beyond}
+\\Nucl. Phys. B \textbf{794} (2008) 244 [arxiv:hep-ph/0703179].
+
+\bibitem{Kum08}
+K. Kumericki, D. M\"uller and K. Passek-Kumericki, \emph{Sum rules and dualities for generalized parton distributions: is there a holographic principle?}
+\\Eur. Phys. J. C \textbf{58} (2008) 193 [arxiv:0805.0152].
+
+\bibitem{Liu11}
+G. Goldstein, J. Hernandez and S. Liuti, \emph{Flexible Parametrization of Generalized Parton Distributions from Deeply Virtual Compton Scattering Observables}
+\\Phys. Rev. D {\bf 84} 034007 (2011) [arxiv:1012.3776].
+
+\end{thebibliography}
 \end{document}

### 2012-02-03 paper.tex
Adding paper.tex

--- 2012-02-02 frame_dual.tex
@@
 \title{Beam-Helicity and Beam-Charge Asymmetries\\
-        \red{Arising From} the DVCS and Bethe--Heitler \\
-        Processes \red{Using} a Proton Target
-  	\underline{Paper Tag: PDVCS0607 (v2.4)}
+        Associated with Deeply Virtual Compton Scattering\\
+        on the Unpolarised Proton.
+  	\underline{Paper Tag: PDVCS0607 (v3.0)}
         \underline{Drafting Committee: DC90 (\today)}
@@
 \abstract{
-Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
+Beam-helicity and beam-charge asymmetries in the hard exclusive leptoproduction of real photons from an unpolarised hydrogen target by a 27.6\,GeV lepton beam 
 are extracted from the H{\sc ermes} data set of 2006-2007 using a
@@
 precise than those extracted from the earlier data
-set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. \red{The r}esults from the two data sets are 
+set of 1996-2005 previously analysed in the same manner by H{\sc ermes}. The results from the two data sets are 
 compatible with each other. Results from these combined data sets are
@@
 The GPDs appear in experimental measurements in the form of complex-valued Compton Form Factors (CFFs), which are flavour-sums of convolutions of GPDs with hard scattering kernels.
-Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive \red{leptoproduction} processes.
-In particular, the exclusive leptoproduction of \red{a single} real photon from a nucleon or nucleus \red{that remains intact} ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
+Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive leptoproduction processes.
+In particular, the exclusive leptoproduction of a single real photon from a nucleon or nucleus that remains intact ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
 
@@
 \end{center}
-with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
+with contributions from the \textrm{BH} process ($\tau_{\textrm{BH}}^2$),
 the DVCS process
-($\tau_{\textrm{DVCS}}$) and their interference term (I). These
+($\tau_{\textrm{DVCS}}^2$) and their interference term (I). These
 contributions can be written as
@@
 Compared to the analysis in ref.~\cite{Air09}, the analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 and makes use of the same missing-mass technique for event selection as was used in ref.~\cite{Air09}.
-The work covered in this publication further combines the data taken in 1996-2005 with this newer data set to produce the statistically most precise DVCS measurements that will be published by H{\sc ermes}.
+The work covered in this publication further combines the data taken in 1996-2005 with this newer data set to produce the statistically most precise DVCS measurements that will be presented by H{\sc ermes}.
 \section{Experiment and Data Selection}
@@
 The recoiling proton is not considered and the calorimeter resolution does not allow separation of all of the latter events from the rest of the data sample.
-No systematic uncertainty is assigned for the contribution from these
+No systematic uncertainty is assigned for the contributions from these
 events; they are treated as part of the signal. A Monte Carlo
@@
 which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contribution from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
+However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contributions from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it
@@
 be extracted from the available data set, the related Fourier
-coefficients, dominant $\mathcal{C}$-functions and twist-levels. {The constant K is defined in eq.~\ref{eq:K}}.}
+coefficients, dominant $\mathcal{C}$-functions and twist-levels.}
 \label{tab_amplitudes}
@@
   2006-2007 Data}
-The extracted asymmetry amplitudes are subject to systematic uncertainties that result from a combination of background processes, shifts in the missing-mass distributions, and various detector and binning effects determined in the same manner as used in refs.~\cite{Air08,Air09} in or\red{d}er to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets.
+The extracted asymmetry amplitudes are subject to systematic uncertainties that result from a combination of background processes, shifts in the missing-mass distributions, and various detector and binning effects determined in the same manner as used in refs.~\cite{Air08,Air09} in order to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets.
 
@@
 In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them.
-An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because its output describes the data well and \red{it} was employed in ref.~\cite{Air09}.
+An event generator based on the GPD model described in ref.~\cite{Guz06} was used for the simulation because its output describes the data well and it was employed in ref.~\cite{Air09}.
 Asymmetry amplitudes were extracted from these simulated events using the same analysis procedure used to
@@
   surveying measurements.
-However, because the systematic uncertainty calculation for the 2006-\red{20}07 data uses the same Monte Carlo generator and reconstruction technique as was used for the 1996-2005 data, the systematic uncertainty for 2006-07 is overestimated; this overestimate is very slight, because the systematic uncertainty contribution from potential misalignment affecting \red{the asymmetries extracted from} the 1996-2005 data set is very small~\cite{Bur10}.
-
-The contribution from each uncertainty to each \red{physically-motivated} amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
+However, because the systematic uncertainty calculation for the 2006-2007 data uses the same Monte Carlo generator and reconstruction technique as was used for the 1996-2005 data, the systematic uncertainty for 2006-2007 is overestimated; this overestimate is very slight, because the systematic uncertainty contribution from potential misalignment affecting the asymmetries extracted from the 1996-2005 data set is very small~\cite{Bur10}.
+
+The contribution from each uncertainty to each physically-motivated amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
 The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
@@
 }
-  \caption{The values of the \red{physically-motivated} asymmetries extracted in a single bin over \red{all kinematic variables} with their statistical uncertainties are presented in the second column of this table.
+  \caption{The values of the physically-motivated asymmetries extracted in a single bin over all kinematic variables with their statistical uncertainties are presented in the second column of this table.
 The third, fourth and fifth columns show the contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data.
@@
 \section{Results}
-In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted in  from the 1996-2005 data set published previously~\cite{Air09}.
+In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted in  from the 1996-2005\footnote{The hydrogen gas target for the data set of 1996-2005 was either unpolarised, transversely polarised or longitudinally polarised.
+However, the time-averaged polarisation of the polarised targets was negligible, while the rapid reversal time (60--180s) of the poalrisation direction minimised bias due to detector effects.} data set published previously~\cite{Air09}.
 Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
@@
   \caption{Beam-helicity asymmetry amplitudes extracted separately from
-the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
+the unpolarised 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
 hydrogen data. The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.
@@
  \includegraphics[width=15cm,keepaspectratio]{bca_sep}
-  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares) hydrogen data.
+  \caption{Beam-charge asymmetry amplitudes extracted separately from the unpolarised 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares) hydrogen data.
 The error bars represent the statistical uncertainties.
@@
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the unpolarised hydrogen data recorded at H{\sc ermes}
 from 1996 until 2007. The error bars (bands) represent the statistical
@@
 the beam polarisation measurement.
-Solid and dashed lines (KM10) show model calculations from~\cite{Kum09}; calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
+Solid and dashed lines (KM10) show model calculations from ref.~\cite{Kum09}; calculations from ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
 See text for details.
@@
     \includegraphics[width=15cm]{bca_comb}
-    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the unpolarised hydrogen data recorded at H{\sc ermes} from 1996 until 2007.
 The error bars (bands) represent the statistical (systematic) uncertainties.
-Theoretical calculations from the model described in Ref.
-\cite{Kum09} are shown as solid and dashed lines (KM10); calculations from Ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
+Theoretical calculations from the model described in ref.~\cite{Kum09} are shown as solid and dashed lines (KM10); calculations from ref.~\cite{Liu11} are shown as dashed-dotted lines (GGL11).
 See text for details.
@@
     \includegraphics[width=15cm]{bca_2D}
-    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+    \caption{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the unpolarised hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
 The error bars (bands) represent the statistical (systematic) uncertainties.
@@
 contributions from acceptance, smearing, finite bin widths and misalignment.
-The background in the \red{combined} data sample is estimated using the method from refs.~\cite{Air08,Zei09, Bur10}.
+The background in the combined data sample is estimated using the method from refs.~\cite{Air08,Zei09, Bur10}.
 The uncertainty contributions due to the observed shifts in the missing-mass distributions for the combined data sets were calculated using the procedure described in section~4 and the results were averaged.
-The total systematic uncertainties for the combined results are \red{obtained by adding these} three independent contributions in quadrature.
-The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
-sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
+The total systematic uncertainties for the combined results are obtained by adding these three independent contributions in quadrature.
+
+The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
@@
 The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}.
-The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}.
-The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes 1these data.
+The basic model~\cite{Mue05,Kum07,Kum08} is a flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewness and $t$ dependences.
+The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data.
 Both fits include the 1996-2005 H{\sc ermes} data.
@@
 (to describe the skewness dependence).
-The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
+It describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude reported here well, but the projections in the other kinematic variables are not as well described.
 The model describes the trends of the $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes well.
@@
 In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one\red{-}dimensional projections: within experimental uncertainty, there is no evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependence\red{s} for any of the amplitudes.
+These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one-dimensional projections: within experimental uncertainty, there is no evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependences for any of the amplitudes.
 The results from this paper will be made available in the Durham Database.
-The results will also be made available in the same 4 bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.
+The results will also be made available in the same 4-bin format as used in previous analyses at H{\sc ermes}~\cite{Air08,Air09,Air10b}.
 
@@
 Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
-These asymmetries were extracted from a\red{n} unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
+These asymmetries were extracted from an unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
 Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
-A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 \red{data set}.
-The asymmetry amplitudes extracted from the com\red{plete} data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
+A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 data set.
+The asymmetry amplitudes extracted from the complete data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
 There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
@@
 
+\newpage
 \appendix
@@
 H1 Collaboration, F. D. Aaron et al., \emph{Measurement of deeply virtual Compton scattering and its $t$-dependence at HERA}
-\\Phys. Lett. B {\bf 659} (2007) 769 [arxiv:0709.4114].
+\\Phys. Lett. B {\bf 659} (2007) 796 [arxiv:0709.4114].
 
@@
 H1 Collaboration, F. D. Aaron et al., \emph{Deeply virtual Compton scattering and its Beam Charge Asymmetry in $e^{\pm}$ Collisions at HERA}
-Phys. Lett. B {\bf 681} (2009) 391 [arxiv:09075289].
+Phys. Lett. B {\bf 681} (2009) 391 [arxiv:0907.5289].
 
@@
 JLab C{\sc las} Collaboration, F. X. Girod et al., \emph{Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries}
-\\Phys. Rev. Lett. \textbf{100} (2008) 162002 [arxiv:0711.0755].
+\\Phys. Rev. Lett. \textbf{100} (2008) 162002 [arxiv:0711.4805].
 
 \bibitem{Gav09}
-JLab C{\sc las} Collaboration, G. Gavalian et al., \emph{Beam Spin Asymmetries in DVCS at CLAS with 4.8GeV}
+JLab C{\sc las} Collaboration, G. Gavalian et al., \emph{Beam Spin Asymmetries in DVCS with CLAS with 4.8GeV}
 \\Phys. Rev. C {\bf 80} (2009) 035206 [arxiv:0812.2950].
@@
 \bibitem{Com10}
-C{\sc ompass} Collaboration, \emph{C{\sc ompass} II proposal}
+C{\sc ompass} Collaboration, \emph{Compass II proposal}
 \\C{\sc ern}/SPSC-2010-014, SPSC-P-340
@@
 \bibitem{Tre04}
-A. Bacchetta, U D’Alesio, M Diehl and C. A. Miller, \emph{Single-spin asymmetries: The Trento conventions}
+A. Bacchetta et al., \emph{Single-spin asymmetries: The Trento conventions}
 \\Phys. Rev. D \textbf{70} (2004) 117504 [arxiv:hep-ph/0410050].
@@
 \bibitem{Bra76}
-F. W. Brasse et al., \emph{Parametrization of the $Q^2$ dependence of $\gamma_Vp$ total cross sections in the resonance region}
+F. W. Brasse et al., \emph{Parametrization of the $Q^2$ dependence of $\gamma_V p$ total cross sections in the resonance region}
 \\Nucl. Phys. B {\bf 110} (1976) 413.

### 2012-02-04 paper.tex
final changes to v3.0

@@
         Associated with Deeply Virtual Compton Scattering\\
-        on the Unpolarised Proton.
+        on the Unpolarised Proton
   	\underline{Paper Tag: PDVCS0607 (v3.0)}
@@
 \end{center}
-with contributions from the \textrm{BH} process ($\tau_{\textrm{BH}}^2$),
+with contributions from the \textrm{BH} process ($\lvert\tau_{\textrm{BH}}\rvert^2$),
 the DVCS process
-($\tau_{\textrm{DVCS}}^2$) and their interference term (I). These
+($\lvert\tau_{\textrm{DVCS}}\rvert^2$) and their interference term (I). These
 contributions can be written as
@@
 
-The $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{\textrm{W}}$ Fourier
+The $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{W}$ Fourier
 coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
@@
 \\
-s_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\quad\,. \label{eq:s1}
+s_{\textrm{unp},1}^{\textrm{I}} &\approx&\,8Ky(2-y)\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}\,. \label{eq:s1}
 \end{eqnarray}
@@
 $A_{\textrm{C}}^{\cos(n\phi)}$ relate respectively to the Fourier
-coefficients $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{I}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
+coefficients $s_{\textrm{unp},n}^{W}$ and $c_{\textrm{unp},n}^{\textrm{I}}$ from the interference and DVCS terms in eqs.~\ref{e:alui}-\ref{e:ac}. The asymmetry amplitudes
 may also be affected by the lepton propagators and the other
@@
 contribution from the $\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$-function,
-which is bilinear in CFFs.
-However, this twist-3 amplitude is inherently small in HERMES kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contributions from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
+which is bilinear in CFFs. However, this twist-3 amplitude is
+inherently small in H{\sc ermes} kinematic conditions due to the size of the $s_{\textrm{unp},1}^{\textrm{DVCS}}$ Fourier coefficient compared to the contributions from the $c_{\textrm{unp},n}^{\textrm{BH}}$ coefficients in the denominator of eq.~\ref{e:aludvcs}.
 As a result of the more complicated dependence on the CFFs and this suppression, it
@@
 
-The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$ defined in eqs.~\ref{eq:c0}---\ref{eq:s1}.
+The leading-twist asymmetry amplitudes are $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$, which are proportional to the Fourier coefficients $c_{\textrm{unp},0}^{\textrm{I}}$, $c_{\textrm{unp},1}^{\textrm{I}}$ and $s_{\textrm{unp},1}^{\textrm{I}}$ defined in eqs.~\ref{eq:c0}--\ref{eq:s1}.
 Whilst all of these amplitudes receive contributions from $\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$, $c_{\textrm{unp},0}^{\textrm{I}}$ is kinematically suppressed in comparison to $c_{\textrm{unp},1}^{\textrm{I}}$, so $A_{\textrm{C}}^{\cos\phi}$ and $A_{\textrm{LU,I}}^{\sin\phi}$ are expected to have the largest magnitude in H{\sc ermes} kinematic conditions.
@@
 
-The contribution from each uncertainty to each physically-motivated amplitude extracted from the 2006-2007 data (in a single, overall kinematic bin) is summarised in table~\ref{table_systematic_contributions_0607}.
+Table~\ref{table_systematic_contributions_0607} shows, for each
+physically-motivated amplitude extracted from the 2006-2007 data (in a
+single, overall kinematic bin), the contribution of the various
+systematic uncertainties.
 The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
@@
 \section{Results}
-In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted in  from the 1996-2005\footnote{The hydrogen gas target for the data set of 1996-2005 was either unpolarised, transversely polarised or longitudinally polarised.
-However, the time-averaged polarisation of the polarised targets was negligible, while the rapid reversal time (60--180s) of the poalrisation direction minimised bias due to detector effects.} data set published previously~\cite{Air09}.
-Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
+In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted from the 1996-2005\footnote{The hydrogen gas target for the data set of 1996-2005 was either unpolarised, transversely polarised or longitudinally polarised.
+However, the time-averaged polarisation of the polarised targets was negligible, while the rapid reversal time (60--180s) of the polarisation direction minimised bias due to detector effects.} data set published previously~\cite{Air09}.
+Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``Overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
 The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
@@
   \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
-$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
+$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes
+extracted from all the unpolarised hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges.
 The error bars (bands) represent the statistical (systematic) uncertainties.
@@
 The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero over the whole range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$.
-The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
+The $A_{\textrm{C}}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs.
 Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading twist amplitudes.
@@
 \section{Summary}
-Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented.
-These asymmetries were extracted from an unpolarised hydrogen data set taken during the 2006 and 2007 operating periods of H{\sc ermes}.
-Analogous asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in ref.~\cite{Air09}.
-A comparison of the amplitudes extracted from these independent data sets has shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 data set.
-The asymmetry amplitudes extracted from the complete data set are the most statistically precise DVCS measurements presented by H{\sc ermes}.
-There is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry.
-There are non-zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry.
-Each of the higher order asymmetry amplitudes is consistent with zero.
-The combined results are compared to calculations from ongoing work to fit GPD models to experimental data.
-All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
+Beam-helicity and beam-charge asymmetries in the azimuthal
+distribution of real photons from leptoproduction on an unpolarised
+hydrogen target have been presented. These asymmetries were extracted
+from an unpolarised hydrogen data set taken during the 2006 and 2007
+operating periods of H{\sc ermes}. Analogous asymmetry amplitudes were
+extracted previously from hydrogen data obtained during the 1996-2005
+experimental period as described in ref.~\cite{Air09}. A comparison of
+the amplitudes extracted from these independent data sets has shown
+that they are compatible and the asymmetry amplitudes can therefore be
+extracted from the complete 1996-2007 data set. The asymmetry
+amplitudes extracted from the complete data set are the most
+statistically precise DVCS measurements presented by H{\sc
+  ermes}. There is a strong signal in the first harmonic of the
+interference contribution to the beam-helicity asymmetry. There are
+non-zero amplitudes in the zeroth and first harmonics of the
+beam-charge asymmetry. All asymmetry amplitudes related to higher
+harmonics are consistent with zero. The results from the complete data
+set are compared to calculations from ongoing work to fit GPD models to experimental data.
+All asymmetry amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$.
 No additional features are observed in any particular $x_{\textrm{B}}$-bin.
@@
 \begin{tabular}{|c|c|c|c|c|r|r|r|} \hline
-\multicolumn{2}{|c|}{} & $\langle-t\rangle$ & $\langle
+\multicolumn{2}{|c|}{} & $\langle -t\rangle$ & $\langle
 x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.217  $\pm$  0.051  $\pm$   0.010 &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.217  $\pm$  0.051  $\pm$   0.010 &
  0.031  $\pm$  0.051   $\pm$  0.003 & -0.032  $\pm$  0.051  $\pm$   0.003\\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and
+  $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with
+  statistical and systematic uncertainties and the average values of the kinematic variables from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $-t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
 An additional 3.4\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.}
@@
 \begin{tabular}{|c|c|c|c|c|r|r|r|r|} \hline
-\multicolumn{2}{|c|}{} & $\langle t\rangle$ & $\langle
+\multicolumn{2}{|c|}{} & $\langle -t\rangle$ & $\langle
 x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.014  $\pm$  0.009 $\pm$ 0.007 & 
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.018 & 0.068 &  1.72 &  -0.014  $\pm$  0.009 $\pm$ 0.007 & 
 0.006  $\pm$  0.012  $\pm$   0.003 &  -0.038  $\pm$  0.012 $\pm$  0.001 &  -0.022   $\pm$  0.012   $\pm$   0.004\\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry
+  amplitudes with statistical and systematic uncertainties and average
+  values of the kinematic variables from unpolarised hydrogen target data taken during 2006-2007 at H{\sc ermes} for each $-t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
 \end{table}
@@
 \begin{tabular}{|c|c|c|c|c|r|r|r|} \hline
-\multicolumn{2}{|c|}{} & $\langle t\rangle$ & $\langle
+\multicolumn{2}{|c|}{} & $\langle -t\rangle$ & $\langle
 x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 &  1.72 &  -0.225  $\pm$  0.039 $\pm$   0.010 &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 &  1.72 &  -0.225  $\pm$  0.039 $\pm$   0.010 &
  0.048  $\pm$  0.039   $\pm$  0.003 & 0.003  $\pm$  0.039  $\pm$   0.003\\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and
+  $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with
+  statistical and systematic uncertainties and the average values of
+  the kinematic variables from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $-t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.
 An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of the beam polarisation measurement.
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 & 1.72  &  -0.017  $\pm$  0.007 $\pm$ 0.007 & 
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & 0.00-0.03 &  0.019 & 0.069 & 1.72  &  -0.017  $\pm$  0.007 $\pm$ 0.007 & 
 0.005  $\pm$  0.010  $\pm$   0.003 &  -0.023  $\pm$  0.010 $\pm$  0.001 &  -0.013   $\pm$  0.010   $\pm$   0.004\\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry
+  amplitudes with statistical and systematic uncertainties and the
+  average values of the
+  kinematic variables from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for each $-t$, $x_{\textrm{B}}$ and $Q^{2}$ bin.}
 \end{table}
@@
 \begin{tabular}{|cc|c|c|c|c|r|r|r|} \hline
-\multicolumn{3}{|c|}{} & $\langle t\rangle$ & $\langle
+\multicolumn{3}{|c|}{} & $\langle -t\rangle$ & $\langle
 x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
@@
 \hline \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473  &  -0.253  $\pm$  0.046  $\pm$  0.019  &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473  &  -0.253  $\pm$  0.046  $\pm$  0.019  &
  0.092  $\pm$   0.046  $\pm$ 0.008  &   -0.039 $\pm$  0.046  $\pm$  0.014 \\
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.08 < x_{\text{B}} < 0.12$ }}} & 0.00-0.03 &  0.022  &0.095  & 2.311  &  -0.163  $\pm$   0.078 $\pm$   0.008 &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.08 < x_{\text{B}} < 0.12$ }}} & 0.00-0.03 &  0.022  &0.095  & 2.311  &  -0.163  $\pm$   0.078 $\pm$   0.008 &
  -0.063 $\pm$   0.079  $\pm$   0.003 &  0.096  $\pm$  0.079  $\pm$  0.016 \\
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.238  $\pm$  0.238 $\pm$ 0.066  &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$ 0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.238  $\pm$  0.238 $\pm$ 0.066  &
 0.006 $\pm$  0.237  $\pm$  0.052 &  0.275 $\pm$  0.239 $\pm$ 0.041 \\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for $t$ bins with certain $x_{\textrm{B}}$ ranges.
+\caption{Results of the $A_{\textrm{LU,I}}^{\sin(n\phi)}$ and
+  $A_{\textrm{LU,DVCS}}^{\sin \phi}$ asymmetry amplitudes with
+  statistical and systematic uncertainties and the average values of
+  the kinematic variables from unpolarised hydrogen target data taken during 1996-2007 at H{\sc ermes} for $-t$ bins with certain $x_{\textrm{B}}$ ranges.
 An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the uncertainty of
@@
 \begin{tabular}{|cc|c|c|c|c|r|r|r|r|} \hline
-\multicolumn{3}{|c|}{} & $\langle t\rangle$ & $\langle
+\multicolumn{3}{|c|}{} & $\langle -t\rangle$ & $\langle
 x_{\text{B}}\rangle$ & $\langle Q^2 \rangle $ & 
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473 &  -0.031  $\pm$  0.008 $\pm$ 0.006 &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.03 < x_{\text{B}} < 0.08$}}} & 0.00-0.03 &  0.018 & 0.058  & 1.473 &  -0.031  $\pm$  0.008 $\pm$ 0.006 &
 -0.013  $\pm$ 0.016  $\pm$ 0.002  &  -0.032 $\pm$  0.012 $\pm$ 0.004 &   -0.016  $\pm$   0.012 $\pm$ 0.003  \\
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.08 < x_{\text{B}} < 0.12$}}} & 0.00-0.03 &  0.022  &0.095  & 2.311 &  0.020  $\pm$ 0.015   $\pm$  0.014  &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.08 < x_{\text{B}} < 0.12$}}} & 0.00-0.03 &  0.022  &0.095  & 2.311 &  0.020  $\pm$ 0.015   $\pm$  0.014  &
  0.049 $\pm$  0.021 $\pm$ 0.017  & -0.002 $\pm$ 0.021  $\pm$  0.008 &  -0.014  $\pm$ 0.021   $\pm$ 0.005 \\
@@
 \hline
-\multirow{6}{*}{\rotatebox{90}{\mbox{$t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.024 $\pm$  0.045  $\pm$   0.008 &
+\multirow{6}{*}{\rotatebox{90}{\mbox{$-t [\text{GeV}^2]$}}} & \multirow{6}{*}{\rotatebox{90}{\mbox{$0.12 < x_{\text{B}} < 0.35$}}} & 0.00-0.03 & 0.026  & 0.130  & 2.954 &  -0.024 $\pm$  0.045  $\pm$   0.008 &
  -0.007 $\pm$ 0.064  $\pm$ 0.001  & -0.013 $\pm$ 0.065 $\pm$ 0.023 & 0.026  $\pm$ 0.062 $\pm$ 0.011 \\
@@
  \end{center}
-\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry amplitudes with statistical and systematic uncertainties and average kinematics from unpolarised hydrogen target data taken during the 1996-2007 at H{\sc ermes} for $t$ bins with certain $x_{\textrm{B}}$ ranges.}
+\caption{Results of the $A_{\textrm{C}}^{\cos(n\phi)}$ asymmetry
+  amplitudes with statistical and systematic uncertainties and the
+  average of the
+  kinematic variables from unpolarised hydrogen target data taken during the 1996-2007 at H{\sc ermes} for $-t$ bins with certain $x_{\textrm{B}}$ ranges.}
 \end{table}
@@
 \\Phys. Rev. D \textbf{62} (2000) 071503 [ariv:hep-ph/0005108].
-\\Errarum-ibid Phys. Rev. D \textbf{66} (2002) 119903.
+\\Erratum-ibid Phys. Rev. D \textbf{66} (2002) 119903.
 

### 2012-02-09 paper.tex
paper prepared for submission to g. schnell

@@
 \usepackage{lscape}
-\usepackage{vruler}
+%\usepackage{vruler}
 \usepackage{subfigure}
@@
 \usepackage{appendix}
-%\usepackage[section]{placeins}
 
@@
 
-% List of Institute Addresses 
 \collaboration{The {\sc Hermes} Collaboration}
@@
 \begin{center}
-\subfigure[DVCS]{\includegraphics[angle=90,width=0.45\textwidth]{dvcs_both_edited}}
-\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.45\textwidth]{bh_both_edited}}
+\subfigure[DVCS]{\includegraphics[angle=90,width=0.48\textwidth]{dvcs_both_edited}}
+\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.48\textwidth]{bh_both_edited}}
 \caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
@@
 + \textrm{d}\sigma(\phi)^{-\leftarrow})}& \nonumber \\[0.4cm]
-%\\ \nonumber
 &=\dfrac{ K_{\textrm{DVCS}} s_{\textrm{unp},1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}

### 2012-02-13 popSumm/popSumm_dc90.tex
Added the popular summary to the repo

\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{rotating}

\begin{document}
\title{Beam-Helicity and Beam-Charge Asymmetries Associated with Deeply Virtual Compton Scattering on an Unpolarised Proton}
\author{The {\sc Hermes } Collaboration}

\maketitle

The H{\sc ermes} experiment was located on the H{\sc era} storage ring at the D{\sc esy} research centre in Hamburg, Germany. It detected the products of the 27.6\,GeV H{\sc era} lepton beam scattering from a variety of gaseous targets to help determine the structure of the target nucleon or nucleus. In this work, the results of scattering fron a hydrogen target are presented. Although the hydrogen target was sometimes polarised (i.e., the spins of the target nucleons were oriented in a specific direction with relation to the beam direction), the integrated data set has vanishing polarisation, so we say that the results are presented for an unpolarised target. This work looks in particular at asymmetries in the distribution of photons created by the scattering process where the target nucleon remains intact ($ep\rightarrow ep\gamma$); this is referred to as \emph{exclusive leptoproduction of real photons}. The results of this work are of particular interest to scientists who want to learn about the spin structure of the nucleon; the size of the asymmetries presented here can help constrain models of the way that the properties of partons in the nucleon combine to produce the properties of the nucleon itself.

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[angle=90,width=0.48\textwidth]{dvcs_both_edited}}
\subfigure[Bethe-Heitler]{\includegraphics[angle=90,width=0.48\textwidth]{bh_both_edited}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The leading DVCS process in which an electron/positron ($e$) interacts with a quark in the nucleon
($N$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction $x-\xi$. (b): The leading Bethe-Heitler process, i.e. the emission of a real photon from the incoming or outgoing lepton. This process has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

The type of lepton used in H{\sc era} is either an electron ($e^-$) or a positron ($e^+$). By varying the beam properties, different asymmetries in the distribution of the photons can be constructed and their magnitude and sign can teach us about the partons that govern the production of the photons. In this work, the beam polarisation (i.e. the directions of the spin vectors of the beam leptons) and the beam charge were varied to produce beam-helicity and beam-charge asymmetries.

There are two physical processes that dominate the exclusive leptoproduction of real photons: Bethe-Heitler (BH) and Deeply Virtual Compton Scattering (DVCS) as shown in figure 1. In BH, the photon is produced by the beam lepton; BH contains little new information about nucleon structure within the precision available at H{\sc ermes}. In DVCS, the photon is produced by a parton in the target nucleon and these photons are the primary source of new information about nucleon structure. There are many more photons from the BH process than the DVCS process at H{\sc ermes} experimental conditions, but we can use the interference in the distributions to amplify the small contribution to the scattering amplitude from DVCS and thus gain useful information on nucleon structure by measuring asymmetries and distributions rather than absolute count rates.

\begin{figure}[ht]
\begin{center}
\includegraphics[angle=90,width=\textwidth]{dc90_data}
\caption{Top: The leading harmonic for the beam-helicity asymmetry as a function of three different kinematics variables for data taken throughout the lifetime of the H{\sc ermes} experiment. The amplitude seems flat across all the kinematic variables. Bottom: The leading harmonic for the beam-charge asymmetry as a function of three different kinematic variables. }
\end{center}
\end{figure}

The asymmetries in the photon distributions are measured around the azimuthal angle, which is to say that they are measured around the direction defined by the virtual photon that mediates the scattering process. The asymmetries that appear when mixing data sets of two different beam polarisations (parallel and anti-parallel to the beam direction) occur with a sinusoidal dependence. The asymmetries that appear when mixing data sets of two different beam charges (electrons and positrons) follow a co-sinusoidal dependence. We're primarily interested in the information in the leading harmonic of each term; the size of the $\sin\phi$ asymmetry amplitude and the size of the $\cos\phi$ asymmetry amplitude. In 2009, H{\sc ermes} presented results on these asymmetries from data taken in the period 1996--2005. This result builds on that previous publication and presents results on data taken over the entire lifetime of the H{\sc ermes} experiment, i.e. 1996--2007. The leading harmonics for each asymmetry are shown in figure 2. The results on this paper are the most statistically precise exclusive physics results that will be presented by H{\sc ermes} on Deeply Virtual Compton Scattering.

By comparing the sizes of these amplitudes to models that predict them, we can gain some insight to how well these models describe the structure of the nucleon. By Occam's razor, a model that predicts well many aspects of nucleon structure will likely resemble the physical truth underlying that structure. The models to which we compare the data are based on Generalised Parton Distributions (GPDs). The GPDs are multi-dimensional expansions on the familiar Parton Distribution Functions that were explored by the collider experiments at H{\sc era}. The models that are shown in figure 2 are postulated from a theoretical background and then fit to experimental data. There are two variants of the KM model that differ in the experimental data that they include. This model is postulated from first pinciples and is valid over a large kinematic range; it is fit to data from H{\sc ermes}, JLab and the colliders at H{\sc era}. The second model, GGL, is a variant of the popular phenomenological quark-diquark model that is trained to data from JLab only. The KM model fits the data better (but the data set to which it is fit includes part of the data published here).

\end{document}

### 2012-02-13 popSumm/popSumm_dc90.tex
Fixed WDN's comments on popsumm

@@
 It detected the products of the 27.6\,GeV H{\sc era} lepton beam scattering from a variety of gaseous targets to help determine the structure of the target nucleon or nucleus.
-In this work, the results of scattering fron a hydrogen target are presented.
+In this work, the results of scattering from a hydrogen target are presented.
 Although the hydrogen target was sometimes polarised (i.e., the spins of the target nucleons were oriented in a specific direction with relation to the beam direction), the integrated data set has vanishing polarisation, so we say that the results are presented for an unpolarised target.
@@
 In this work, the beam polarisation (i.e.
-the directions of the spin vectors of the beam leptons) and the beam charge were varied to produce beam-helicity and beam-charge asymmetries.
+the directions of the spin vectors of the beam leptons) and the charge of the beam leptons were varied to produce beam-helicity and beam-charge asymmetries.
 
@@
 In DVCS, the photon is produced by a parton in the target nucleon and these photons are the primary source of new information about nucleon structure.
-There are many more photons from the BH process than the DVCS process at H{\sc ermes} experimental conditions, but we can use the interference in the distributions to amplify the small contribution to the scattering amplitude from DVCS and thus gain useful information on nucleon structure by measuring asymmetries and distributions rather than absolute count rates.
+There are many more photons from the BH process than the DVCS process at H{\sc ermes} experimental conditions, but we can use the interference between the processes to gain useful information on nucleon structure by measuring asymmetries and distributions rather than absolute count rates.
 
@@
 The asymmetries in the photon distributions are measured around the azimuthal angle, which is to say that they are measured around the direction defined by the virtual photon that mediates the scattering process.
-The asymmetries that appear when mixing data sets of two different beam polarisations (parallel and anti-parallel to the beam direction) occur with a sinusoidal dependence.
-The asymmetries that appear when mixing data sets of two different beam charges (electrons and positrons) follow a co-sinusoidal dependence.
+The asymmetries that appear when comparing data sets of two different beam polarisations (parallel and anti-parallel to the beam direction) occur with a sinusoidal dependence.
+The asymmetries that appear when comparing data sets of two different beam charges (electrons and positrons) follow a co-sinusoidal dependence.
 We're primarily interested in the information in the leading harmonic of each term; the size of the $\sin\phi$ asymmetry amplitude and the size of the $\cos\phi$ asymmetry amplitude.
 In 2009, H{\sc ermes} presented results on these asymmetries from data taken in the period 1996--2005.
-This result builds on that previous publication and presents results on data taken over the entire lifetime of the H{\sc ermes} experiment, i.e.
+The result presented here builds on that previous publication and presents results on data taken over the entire lifetime of the H{\sc ermes} experiment, i.e.
 1996--2007.
@@
 The models that are shown in figure 2 are postulated from a theoretical background and then fit to experimental data.
-There are two variants of the KM model that differ in the experimental data that they include.
-This model is postulated from first pinciples and is valid over a large kinematic range; it is fit to data from H{\sc ermes}, JLab and the colliders at H{\sc era}.
-The second model, GGL, is a variant of the popular phenomenological quark-diquark model that is trained to data from JLab only.
+There are two variants of the Kumericki-Mueller (KM) model that differ in the experimental data that they include.
+This model is postulated from first principles and is valid over a large kinematic range; it is fit to data from H{\sc ermes}, JLab and the colliders at H{\sc era}.
+The second model, by Goldstein, Gonzales and Liuti (GGL), is a variant of the popular phenomenological quark-diquark model that is trained to data from JLab only.
 The KM model fits the data better (but the data set to which it is fit includes part of the data published here).

### 2012-03-08 paper.tex
Bibliography ordering was wrong...
Added gunars trivial changes. Also added one of the macros that have been left out of the repo...

@@
 
-\setvruler[15pt][1][1][3][1][30pt][30pt][-42pt]
 \maketitle
@@
 Constraints on these CFFs, and thus GPDs, can be obtained from measurements of exclusive leptoproduction processes.
-In particular, the exclusive leptoproduction of a single real photon from a nucleon or nucleus that remains intact ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
+In particular, the exclusive leptoproduction of a single real photon from a nucleon or nucleus that remains intact ($e\,N\,\rightarrow\,e\,N\,\gamma$; see figure~\ref{spin}) is the simplest to describe and is the most widely-used reaction channel for such work (see \cite{Ji97b,Air01,Air06,Air08,Air09,Air10,Air10a,Air10b,Air11,Air11a,h101,h105,h107,h109,zeu03,zeu08,Maz07,Cam06,Ste01,Che06,Gir08,Gav09,Com10}).
 
@@
 
-Events were selected if having exactly one photon and one lepton
-track detected within the acceptance of the spectrometer.
+Events in the 2006-2007 data set were selected if having exactly one
+\red{lepton} track detected within the acceptance of the spectrometer and \red{at
+  least one photon depositing $>5$\,GeV in the electromagnetic
+  calorimeter. The latter selection criterion differs from the photon
+  selection criterion used for the 1996-2005 data set as an intermittent
+  hardware fault in 2006-2007 can cause spurious noise signals in the
+  calorimeter that are misinterpreted as very low energy photons.}
 The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
@@
   2006-2007 Data}
-The extracted asymmetry amplitudes are subject to systematic uncertainties that result from a combination of background processes, shifts in the missing-mass distributions, and various detector and binning effects determined in the same manner as used in refs.~\cite{Air08,Air09} in order to maintain consistency with the results published in ref.~\cite{Air09} and therefore facilitate the combination of the two data sets.
+The extracted asymmetry amplitudes are subject to systematic uncertainties
+that result from a combination of background processes, shifts in the
+missing-mass distributions, and various detector and binning effects
+determined in the same manner as used in refs.~\cite{Air08,Air09} in order to
+maintain consistency with the results published in ref.~\cite{Air09} and
+therefore facilitate the combination of the two data sets. \red{No systematic
+  uncertainty is assigned from the intermittent fault in the calorimeter
+  mentioned in section 2; the percentage of events affected by the issue is
+  small for the 2006-2007 data sample and completely negligible in the context
+of the combined data sets.}
 
@@
 production is predominantly due to the failure to identify one of
-  the two photons from the decay of these neutral mesons. The procedure for estimating the corresponding
+  the two photons from the decay of these neutral mesons. \red{The
+    $\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}$ amplitudes are corrected for
+  inclfuences from semi-inclusive pion production and an uncertainty is
+  assigned to the affected amplitudes. A further uncertainty is assigned to
+  these amplitudes for the influence of photons produced in decays of
+  exclusively produced pions.} The procedure for estimating the corresponding
 uncertainty on the measured amplitude values is described in detail in
@@
   centre of the relevant kinematic bin and included as part of the
-  total systematic uncertainty.
+  total systematic uncertainty. \red{No correction is applied or uncertainty
+    assigned to the amplitudes for the
+    $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}$ or $\mathcal{A}_{\textrm{C}}$
+    asymmetries because influences from meson production are expected to
+    vanish when considering the difference between beam charges.}
 
@@
 
-The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
+The first and second harmonics of $\mathcal{A}^{\textrm{I}}_{\textrm{LU}}$, which are sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of figure~\ref{bsa_xbjrange}.
 The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set.
@@
 
-In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}.
-These figures represent the kinematic dependences of the amplitudes in a less-correlated manner than the one-dimensional projections: within experimental uncertainty, there is no evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependences for any of the amplitudes.
+In order to provide more detailed information that can be used in future fits,
+in particular for the determination of the entanglement of the skewness and
+$-t$ dependences of GPDs, the amplitudes already presented in
+figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of
+$-t$ for three different ranges of $x_{\textrm{B}}$ in
+figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. These figures represent
+the kinematic dependences of the amplitudes in a less-correlated manner than
+the one-dimensional projections: within experimental uncertainty, there is no
+evidence of a correlation between the $-t$ and $x_{\textrm{B}}$ dependences
+for any of the amplitudes.
+
 The results from this paper will be made available in the Durham Database.
@@
 Beam-helicity and beam-charge asymmetries in the azimuthal
-distribution of real photons from leptoproduction on an unpolarised
+distribution of real photons from \red{hard exclusive} leptoproduction on an unpolarised
 hydrogen target have been presented. These asymmetries were extracted
@@
 Figure~\ref{pic:covmat} shows the covariance matrix for the 13 parameter fit for all amplitudes extracted in a single bin across the entire kinematic range.
-The covariance matrix for the fit in each of the kinematic bins presented in figures~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2} will be made available in the Durham database.
+The covariance matrix for the fit in each of the kinematic bins presented in figures~\ref{bsa_xbjrange} to~\ref{bca_xbjrange2} will be made available in the Durham database.
 \begin{figure}[tbh]
@@
 \includegraphics[width=\textwidth]{CovMat.pdf}
-\caption{The covariance matrix results for the asymmetries extracted in a single bin across the whole kinematic range.}
+\caption{The covariance matrix results for the asymmetries extracted in a
+  single bin across the whole kinematic range. \red{The size of the symbols in
+the chart reflect the magnitude of the corresponding correlation. Closed
+(open) symbols represent positive (negative) correlations.}}
 \label{pic:covmat}
@@
 
-X.~Ji, \emph{Deeply virtual Compton scattering}
-\\Phys. Rev. D \textbf{55} (1997) 7114 [arxiv:hep-ph/9609381].
-
 \bibitem{Rad97}
@@
 
+\bibitem{Ji97b}
+X.~Ji, \emph{Deeply virtual Compton scattering}
+\\Phys. Rev. D \textbf{55} (1997) 7114 [arxiv:hep-ph/9609381].
+
 \bibitem{Air01}
@@
 \bibitem{Maz07}
-JLab Hall A Collaboration, M. Mazouz et al., \emph{Deeply virtual Compton scattering off the neutron}
+Jefferson Lab Hall A Collaboration, M. Mazouz et al., \emph{Deeply virtual Compton scattering off the neutron}
 \\Phys. Rev. Lett. {\bf 99} (2007) 242501 [arxiv:0709.0450].
@@
 \bibitem{Cam06}
-JLab Hall A Collaboration,  C. Camacho et al., \emph{Scaling Tests of the Cross Section for Deeply Virtual Compton Scattering}
+Jefferson Lab Hall A Collaboration,  C. Camacho et al., \emph{Scaling Tests of the Cross Section for Deeply Virtual Compton Scattering}
 \\Phys. Rev. Lett. \textbf{97} (2006) 262002 [arxiv:nucl-ex/0607029].
@@
 \bibitem{Ste01}
-JLab C{\sc las} Collaboration, S. Stepanyan et al., \emph{Observation of exclusive DVCS in polarized electron beam asymmetry measurements}
+C{\sc las} Collaboration, S. Stepanyan et al., \emph{Observation of exclusive DVCS in polarized electron beam asymmetry measurements}
 \\Phys. Rev. Lett. {\bf 87} (2001) 182002 [arxiv:hep-ex/0107043].
@@
 \bibitem{Che06}
-JLab C{\sc las} Collaboration, S. Chen et al., \emph{Measurement of Deeply Virtual Compton Scattering with a Polarized Proton Target}
+C{\sc las} Collaboration, S. Chen et al., \emph{Measurement of Deeply Virtual Compton Scattering with a Polarized Proton Target}
 \\Phys. Rev. Lett. {\bf 97} (2006) 072002 [arxiv:hep-ex/0605012].
@@
 \bibitem{Gir08}
-JLab C{\sc las} Collaboration, F. X. Girod et al., \emph{Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries}
+C{\sc las} Collaboration, F. X. Girod et al., \emph{Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries}
 \\Phys. Rev. Lett. \textbf{100} (2008) 162002 [arxiv:0711.4805].
@@
 \bibitem{Gav09}
-JLab C{\sc las} Collaboration, G. Gavalian et al., \emph{Beam Spin Asymmetries in DVCS with CLAS with 4.8GeV}
+C{\sc las} Collaboration, G. Gavalian et al., \emph{Beam Spin Asymmetries in DVCS with CLAS with 4.8GeV}
 \\Phys. Rev. C {\bf 80} (2009) 035206 [arxiv:0812.2950].
@@
 
+\bibitem{Bra76}
+F. W. Brasse et al., \emph{Parametrization of the $Q^2$ dependence of $\gamma_V p$ total cross sections in the resonance region}
+\\Nucl. Phys. B {\bf 110} (1976) 413.
+
 \bibitem{Bar90}
@@
 \\Phys. Lett. B \textbf{72} (1977) 195.
-
-\bibitem{Bra76}
-F. W. Brasse et al., \emph{Parametrization of the $Q^2$ dependence of $\gamma_V p$ total cross sections in the resonance region}
-\\Nucl. Phys. B {\bf 110} (1976) 413.
 
@@
 \bibitem{Kum09}
-K. Kumericki and D. M\"uller, \emph{Deeply virtual Compton scattering at small $x_B$ and the access to the GPD H}
+K. Kumeri\v{c}ki and D. M\"uller, \emph{Deeply virtual Compton scattering at small $x_B$ and the access to the GPD H}
 \\Nucl. Phys. B {\bf 841} (2010) 1 [arxiv:0904.0458].
@@
 \bibitem{Kum07}
-K. Kumericki, D. M\"uller and K. Passek-Kumericki, \emph{Towards a fitting procedure for deeply virtual Compton scattering at next-to-leading order and beyond}
+K. Kumeri\v{c}ki, D. M\"uller and K. Passek-Kumeri\v{c}ki, \emph{Towards a fitting procedure for deeply virtual Compton scattering at next-to-leading order and beyond}
 \\Nucl. Phys. B \textbf{794} (2008) 244 [arxiv:hep-ph/0703179].
@@
 \bibitem{Kum08}
-K. Kumericki, D. M\"uller and K. Passek-Kumericki, \emph{Sum rules and dualities for generalized parton distributions: is there a holographic principle?}
+K. Kumeri\v{c}ki, D. M\"uller and K. Passek-Kumeri\v{c}ki, \emph{Sum rules and dualities for generalized parton distributions: is there a holographic principle?}
 \\Eur. Phys. J. C \textbf{58} (2008) 193 [arxiv:0805.0152].

### 2012-03-08 macros/bcaplots_tc_xbjrange_withfracs.C

@@ -166,12 +166,12 @@
    gre->Draw("p");
    TLatex *   tex = new TLatex(0.04,0.16,"0.03 < x_{B} < 0.08 ");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.04,0.06,"<Q^{2}> = 1.56 GeV^{2}");
+      tex = new TLatex(0.04,0.06,"#LTQ^{2}#GT = 1.56 GeV^{2}");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_1->Modified();
@@ -797,12 +797,12 @@
    gre->Draw("p");
       tex = new TLatex(0.04,0.16,"0.08 < x_{B} < 0.12");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.04,0.06,"<Q^{2}> = 2.52 GeV^{2}");
+      tex = new TLatex(0.04,0.06,"#LTQ^{2}#GT = 2.52 GeV^{2}");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_2->Modified();
@@ -1405,12 +1405,12 @@
    gre->Draw("p");
       tex = new TLatex(0.04,0.16,"0.12 < x_{B} < 0.35");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.04,0.06,"<Q^{2}> = 4.34 GeV^{2}");
+      tex = new TLatex(0.04,0.06,"#LTQ^{2}#GT = 4.34 GeV^{2}");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
    pad1_3->Modified();

### 2012-03-08 macros/bsadvcsplots_tc_xbjrange_withfracs.C

@@ -70,29 +70,12 @@
    TLine *line = new TLine(0,0,0.8,0);
    line->SetLineStyle(2);
    line->Draw();
-   
+
    Double_t *dum = 0;
-   TPolyLine *pline = new TPolyLine(14,dum,dum,"");
-   pline->SetFillColor(5);
-   pline->SetPoint(0,0.011,-0.4);
-   pline->SetPoint(1,0.011,-0.38052);
-   pline->SetPoint(2,0.03,-0.38052);
-   pline->SetPoint(3,0.03,-0.375742);
-   pline->SetPoint(4,0.06,-0.375742);
-   pline->SetPoint(5,0.06,-0.381611);
-   pline->SetPoint(6,0.11,-0.381611);
-   pline->SetPoint(7,0.11,-0.380414);
-   pline->SetPoint(8,0.2,-0.380414);
-   pline->SetPoint(9,0.2,-0.385927);
-   pline->SetPoint(10,0.3,-0.385927);
-   pline->SetPoint(11,0.3,-0.391618);
-   pline->SetPoint(12,0.7,-0.391618);
-   pline->SetPoint(13,0.7,-0.4);
-   pline->Draw("f");
-   
-   Double_t *dum = 0;
-   pline = new TPolyLine(14,dum,dum,"");
-   pline->SetFillColor(1);
+   pline = new TPolyLine(15,dum,dum,"");
+   //   pline->SetFillColor(2);
+   pline->SetLineWidth(1);
+   pline->SetLineColor(2);
    pline->SetFillStyle(0);
    pline->SetPoint(0,0.011,-0.4);
    pline->SetPoint(1,0.011,-0.38052);
@@ -108,7 +91,9 @@
    pline->SetPoint(11,0.3,-0.391618);
    pline->SetPoint(12,0.7,-0.391618);
    pline->SetPoint(13,0.7,-0.4);
-   pline->Draw("fsame");
+   pline->SetPoint(14,0.011,-0.4);
+   pline->Draw("l same");
+
    
    TGraphErrors *gre = new TGraphErrors(6);
    gre->SetName("Graph");
@@ -140,12 +125,12 @@
    gre->Draw("p");
    TLatex *   tex = new TLatex(0.04,0.15,"0.03 < x_{B} < 0.08");
    tex->SetTextFont(43);
-   tex->SetTextSize(18);
+   tex->SetTextSize(22);
    tex->SetLineWidth(2);
[…]

### 2012-03-08 macros/covMat.C

@@ -1,5 +1,5 @@
 
-c(){
+covMat(){
  
   int i,j;
   TCanvas *c = new TCanvas("c","",5);
@@ -84,14 +84,14 @@ c(){
   hp->GetXaxis()->SetBinLabel(3,"A^{sin#phi}_{C}");
   hp->GetXaxis()->SetBinLabel(4,"A^{cos(2#phi)}_{C}");
   hp->GetXaxis()->SetBinLabel(5,"A^{cos(3#phi)}_{C}");
-  hp->GetXaxis()->SetBinLabel(6,"A^{cos(0#phi)}_{DVCS}");
-  hp->GetXaxis()->SetBinLabel(7,"A^{sin#phi}_{DVCS}");
-  hp->GetXaxis()->SetBinLabel(8,"A^{cos#phi}_{DVCS}");
-  hp->GetXaxis()->SetBinLabel(9,"A^{sin(2#phi)}_{DVCS}");
-  hp->GetXaxis()->SetBinLabel(10,"A^{cos(0#phi)}_{I}");
-  hp->GetXaxis()->SetBinLabel(11,"A^{sin#phi}_{I}");
-  hp->GetXaxis()->SetBinLabel(12,"A^{cos#phi}_{I}");
-  hp->GetXaxis()->SetBinLabel(13,"A^{sin(2#phi)}_{I}");
+  hp->GetXaxis()->SetBinLabel(6,"A^{cos(0#phi)}_{LU, DVCS}");
+  hp->GetXaxis()->SetBinLabel(7,"A^{sin#phi}_{LU, DVCS}");
+  hp->GetXaxis()->SetBinLabel(8,"A^{cos#phi}_{LU, DVCS}");
+  hp->GetXaxis()->SetBinLabel(9,"A^{sin(2#phi)}_{LU, DVCS}");
+  hp->GetXaxis()->SetBinLabel(10,"A^{cos(0#phi)}_{LU, I}");
+  hp->GetXaxis()->SetBinLabel(11,"A^{sin#phi}_{LU, I}");
+  hp->GetXaxis()->SetBinLabel(12,"A^{cos#phi}_{LU, I}");
+  hp->GetXaxis()->SetBinLabel(13,"A^{sin(2#phi)}_{LU, I}");
   hp->GetXaxis()->SetBit(TAxis::kLabelsVert);
   hp->GetXaxis()->RotateTitle(true);
[…]

### 2012-03-08 macros/bcaplots_tc_xbjrange_withfracs.C
fixed some of the issues related to the plot axes. requires refinement

@@ -48,8 +48,8 @@
    pad1_1->SetFrameBorderMode(0);
    
    TH1F *hframe__1__1__1__16__46__1 = new TH1F("hframe__1__1__1__16__46__1","",21,0.009,0.8);
-   hframe__1__1__1__16__46__1->SetMinimum(-0.35);
-   hframe__1__1__1__16__46__1->SetMaximum(0.25);
+   hframe__1__1__1__16__46__1->SetMinimum(-0.29);
+   hframe__1__1__1__16__46__1->SetMaximum(0.06);
    hframe__1__1__1__16__46__1->SetDirectory(0);
    hframe__1__1__1__16__46__1->SetStats(0);
    hframe__1__1__1__16__46__1->GetXaxis()->SetTitle("-t_{c} (GeV^{2})");
@@ -99,42 +99,27 @@
    
    Double_t *dum = 0;
    TPolyLine *pline = new TPolyLine(14,dum,dum,"");
-   pline->SetFillColor(5);
-   pline->SetPoint(0,0.011,-0.3);
-   pline->SetPoint(1,0.011,-0.294099);
-   pline->SetPoint(2,0.03,-0.294099);
-   pline->SetPoint(3,0.03,-0.292338);
-   pline->SetPoint(4,0.06,-0.292338);
-   pline->SetPoint(5,0.06,-0.282681);
-   pline->SetPoint(6,0.11,-0.282681);
-   pline->SetPoint(7,0.11,-0.281254);
-   pline->SetPoint(8,0.2,-0.281254);
-   pline->SetPoint(9,0.2,-0.276571);
-   pline->SetPoint(10,0.3,-0.276571);
-   pline->SetPoint(11,0.3,-0.274479);
-   pline->SetPoint(12,0.7,-0.274479);
-   pline->SetPoint(13,0.7,-0.3);
-   pline->Draw("f");
    
    Double_t *dum = 0;
-   pline = new TPolyLine(14,dum,dum,"");
-   pline->SetFillColor(1);
-   pline->SetFillStyle(0);
-   pline->SetPoint(0,0.011,-0.3);
-   pline->SetPoint(1,0.011,-0.294099);
-   pline->SetPoint(2,0.03,-0.294099);
-   pline->SetPoint(3,0.03,-0.292338);
-   pline->SetPoint(4,0.06,-0.292338);
-   pline->SetPoint(5,0.06,-0.282681);
[…]

### 2012-03-09 macros/bcaplots_tc_xbjrange_withfracs.C
Made changes to fig.7 as proposed by Gunar

@@ -60,9 +60,12 @@
    hframe__1__1__1__16__46__1->GetYaxis()->SetTitle("A_{C}^{cos (0#phi)}");
    hframe__1__1__1__16__46__1->GetYaxis()->SetNdivisions(205);
    hframe__1__1__1__16__46__1->GetYaxis()->SetLabelOffset(0.02);
-   hframe__1__1__1__16__46__1->GetYaxis()->SetLabelSize(0.17);
-   hframe__1__1__1__16__46__1->GetYaxis()->SetTitleSize(0.25);
-   hframe__1__1__1__16__46__1->GetYaxis()->SetTitleOffset(0.6);
+   hframe__1__1__1__16__46__1->GetYaxis()->SetLabelFont(63);
+   hframe__1__1__1__16__46__1->GetYaxis()->SetLabelSize(23);
+   hframe__1__1__1__16__46__1->GetYaxis()->SetTitleFont(63);
+   hframe__1__1__1__16__46__1->GetYaxis()->SetTitleSize(36);
+   hframe__1__1__1__16__46__1->GetYaxis()->SetTitleOffset(3.5);
+   hframe__1__1__1__16__46__1->GetYaxis()->CenterTitle();
    hframe__1__1__1__16__46__1->Draw(" ");
    TLine *line = new TLine(0,0,0.8,0);
    line->SetLineStyle(2);
@@ -149,12 +152,12 @@
    gre->SetHistogram(Graph2222650742);
    
    gre->Draw("p");
-   TLatex *   tex = new TLatex(0.04,0.16,"0.03 < x_{B} < 0.08 ");
+   TLatex *   tex = new TLatex(0.04,-0.12,"0.03 < x_{B} < 0.08 ");
    tex->SetTextFont(43);
    tex->SetTextSize(22);
    tex->SetLineWidth(2);
    tex->Draw();
-      tex = new TLatex(0.04,0.06,"#LTQ^{2}#GT = 1.56 GeV^{2}");
+      tex = new TLatex(0.04,-0.18,"#LTQ^{2}#GT = 1.56 GeV^{2}");
    tex->SetTextFont(43);
    tex->SetTextSize(22);
    tex->SetLineWidth(2);
@@ -183,7 +186,7 @@
    
    TH1F *hframe__2__2__2__17__47__2 = new TH1F("hframe__2__2__2__17__47__2","",21,0.009,0.8);
    hframe__2__2__2__17__47__2->SetMinimum(-0.19);
[…]

### 2012-03-21 paper.tex
Made the changes requested by Gunar and Klaus post-submission to the DESY directorate.

@@
     $\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}$ amplitudes are corrected for
-  inclfuences from semi-inclusive pion production and an uncertainty is
+  influences from semi-inclusive pion production and an uncertainty is
   assigned to the affected amplitudes. A further uncertainty is assigned to
@@
 single, overall kinematic bin), the contribution of the various
-systematic uncertainties.
-The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period.
-These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
+systematic uncertainties. The beam polarisation measurements have
+total uncertainties of 2.8\% for the 1996-2005 data-taking period and
+3.4\% for the 2006-2007 data taking period. These uncertainties are
+present in the beam-helicity amplitudes and are\red{, as independent
+  scale uncertainties, not included} in the other presented uncertainties.
 \begin{table}
@@
 & 4.50-10.0 &  0.218 & 0.200 &  5.82 &  -0.200  $\pm$  0.074 $\pm$    0.004 &
--0.036  $\pm$  0.074  $\pm$   0.007 & 0.069 $\pm$  0.071$ \pm$  0.013\\
+-0.036  $\pm$  0.074  $\pm$ 0.007 & 0.069 $\pm$  0.071 $\pm$  0.013\\
 \hline
@@
 M.~Burkardt, \emph{Impact Parameter Dependent Parton Distributions and Off-Forward Parton Distributions for $\zeta\to 0$}
-\\Phys. Rev. D \textbf{62} (2000) 071503 [ariv:hep-ph/0005108].
+\\Phys. Rev. D \textbf{62} (2000) 071503 [arxiv:hep-ph/0005108].
 \\Erratum-ibid Phys. Rev. D \textbf{66} (2002) 119903.

### 2012-04-24 submission/paper.tex
Updated some plotting macros and added the submitted paper directory to the repo

--- 2012-03-21 paper.tex
@@
 Events in the 2006-2007 data set were selected if having exactly one
-\red{lepton} track detected within the acceptance of the spectrometer and \red{at
+lepton track detected within the acceptance of the spectrometer and at
   least one photon depositing $>5$\,GeV in the electromagnetic
@@
   hardware fault in 2006-2007 can cause spurious noise signals in the
-  calorimeter that are misinterpreted as very low energy photons.}
+  calorimeter that are misinterpreted as very low energy photons.
 The event selection is subject to the kinematic constraints 1\,GeV$^{2}$ $<$
@@
 maintain consistency with the results published in ref.~\cite{Air09} and
-therefore facilitate the combination of the two data sets. \red{No systematic
+therefore facilitate the combination of the two data sets. No systematic
   uncertainty is assigned from the intermittent fault in the calorimeter
-  mentioned in section 2; the percentage of events affected by the issue is
-  small for the 2006-2007 data sample and completely negligible in the context
-of the combined data sets.}
+  mentioned in section 2; the number of events in which the fault
+  occurred is very small for the 2006-2007 data sample and completely negligible in the context
+of the combined data sets.
 
@@
 production is predominantly due to the failure to identify one of
-  the two photons from the decay of these neutral mesons. \red{The
+  the two photons from the decay of these neutral mesons. The
     $\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}$ amplitudes are corrected for
-  influences from semi-inclusive pion production and an uncertainty is
-  assigned to the affected amplitudes. A further uncertainty is assigned to
+  the fraction of the data sample and the magnitude of the asymmetry
+  due to semi-inclusive pion production. A further uncertainty is assigned to
   these amplitudes for the influence of photons produced in decays of
-  exclusively produced pions.} The procedure for estimating the corresponding
-uncertainty on the measured amplitude values is described in detail in
+  exclusively produced pions. Corrections for dilution of the amplitudes for the
+    $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}$ and $\mathcal{A}_{\textrm{C}}$
+    asymmetries are applied. No asymmetry value is assigned to the
+    influence of the dilution because influences from meson production are expected to
+    vanish when considering the difference between beam charges.
+The procedure for estimating the
+uncertainty and correction factor for each measured amplitude value is described in detail in
 refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
@@
   centre of the relevant kinematic bin and included as part of the
-  total systematic uncertainty. \red{No correction is applied or uncertainty
-    assigned to the amplitudes for the
-    $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}$ or $\mathcal{A}_{\textrm{C}}$
-    asymmetries because influences from meson production are expected to
-    vanish when considering the difference between beam charges.}
+  total systematic uncertainty.
 
@@
 3.4\% for the 2006-2007 data taking period. These uncertainties are
-present in the beam-helicity amplitudes and are\red{, as independent
-  scale uncertainties, not included} in the other presented uncertainties.
+present in the beam-helicity amplitudes and are, as independent
+  scale uncertainties, not included in the other presented uncertainties.
 \begin{table}
@@
 Beam-helicity and beam-charge asymmetries in the azimuthal
-distribution of real photons from \red{hard exclusive} leptoproduction on an unpolarised
+distribution of real photons from hard exclusive leptoproduction on an unpolarised
 hydrogen target have been presented. These asymmetries were extracted
@@
 \caption{The covariance matrix results for the asymmetries extracted in a
-  single bin across the whole kinematic range. \red{The size of the symbols in
+  single bin across the whole kinematic range. The size of the symbols in
 the chart reflect the magnitude of the corresponding correlation. Closed
-(open) symbols represent positive (negative) correlations.}}
+(open) symbols represent positive (negative) correlations.}
 \label{pic:covmat}

### 2012-04-24 macros/bcaplots_eml_par13_bin6_all_release_pic_cluster_update_withassoc_dual.C

@@ -63,10 +63,10 @@
    hframe__17__1->GetYaxis()->SetNdivisions(205);
    hframe__17__1->GetYaxis()->SetLabelFont(63);
    hframe__17__1->GetYaxis()->SetLabelOffset(0.05);
-   hframe__17__1->GetYaxis()->SetLabelSize(25);
-   hframe__17__1->GetYaxis()->SetTitleSize(35);
-   hframe__17__1->GetYaxis()->SetTitleOffset(5);
+   hframe__17__1->GetYaxis()->SetLabelSize(20);
    hframe__17__1->GetYaxis()->SetTitleFont(63);
+   hframe__17__1->GetYaxis()->SetTitleSize(30);
+   hframe__17__1->GetYaxis()->SetTitleOffset(4);
    hframe__17__1->Draw(" ");
    TLine *line = new TLine(0,0,2,0);
    line->SetLineStyle(2);
@@ -100,24 +100,15 @@
    line->Draw();
    
    Double_t *dum = 0;
-   TPolyLine *pline = new TPolyLine(4,dum,dum,"");
-   pline->SetFillColor(5);
+   TPolyLine *pline = new TPolyLine(5,dum,dum,"");
+   pline->SetLineColor(2);
    pline->SetPoint(0,0.5,-0.12);
    pline->SetPoint(1,0.5,-0.109248);
    pline->SetPoint(2,1.5,-0.109248);
    pline->SetPoint(3,1.5,-0.12);
-   pline->Draw("f");
-   
-   Double_t *dum = 0;
-   pline = new TPolyLine(4,dum,dum,"");
-   pline->SetFillColor(1);
-   pline->SetFillStyle(0);
-   pline->SetPoint(0,0.5,-0.12);
-   pline->SetPoint(1,0.5,-0.109248);
-   pline->SetPoint(2,1.5,-0.109248);
-   pline->SetPoint(3,1.5,-0.12);
-   pline->Draw("fsame");
-   
+   pline->SetPoint(4,0.5,-0.12);
+   pline->Draw("L");
+    
    gre = new TGraphErrors(1);
    gre->SetName("Graph");
    gre->SetTitle("Graph");
@@ -160,7 +151,7 @@
    
    TH1F *hframe__18__2 = new TH1F("hframe__18__2","",3,0,2);
    hframe__18__2->SetMinimum(-0.075);
-   hframe__18__2->SetMaximum(0.35);
[…]

### 2012-04-24 macros/bcaplots_tc_xbjrange_withfracs.C

@@ -654,7 +654,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(0.9);
    gre->SetPoint(0,0.018761,0.0201682);
    gre->SetPointError(0,0,0.0150053);
    gre->SetPoint(1,0.04394,-0.0130729);
@@ -704,7 +704,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(0.9);
    gre->SetPoint(0,0.018761,0.0201682);
    gre->SetPointError(0,0,0.0150053);
    gre->SetPoint(1,0.04394,-0.0130729);
@@ -780,7 +780,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(0.9);
    gre->SetPoint(0,0.018761,0.0485);
    gre->SetPointError(0,0,0.0214823);
    gre->SetPoint(1,0.04394,-0.00154069);
@@ -830,7 +830,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(0.9);
    gre->SetPoint(0,0.018761,0.0485);
    gre->SetPointError(0,0,0.0214823);
    gre->SetPoint(1,0.04394,-0.00154069);
@@ -896,7 +896,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(0.9);
    gre->SetPoint(0,0.018761,-0.00180144);
    gre->SetPointError(0,0,0.0208018);
    gre->SetPoint(1,0.04394,0.0367917);
@@ -946,7 +946,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
[…]

### 2012-04-24 macros/bsadvcsplots_eml_par13_bin6_release_all_pic_cluster_dual.C

@@ -48,8 +48,8 @@
    pad1_1->SetFrameBorderMode(0);
    
    TH1F *hframe__1__1__1 = new TH1F("hframe__1__1__1","",3,0,2);
-   hframe__1__1__1->SetMinimum(-0.65);
-   hframe__1__1__1->SetMaximum(0.25);
+   hframe__1__1__1->SetMinimum(-0.435);
+   hframe__1__1__1->SetMaximum(0.235);
    hframe__1__1__1->SetDirectory(0);
    hframe__1__1__1->SetStats(0);
    hframe__1__1__1->GetXaxis()->SetBinLabel(2,"Integrated Over All Kinematics");
@@ -63,10 +63,11 @@
    hframe__1__1__1->GetYaxis()->SetNdivisions(205);
    hframe__1__1__1->GetYaxis()->SetLabelFont(63);
    hframe__1__1__1->GetYaxis()->SetLabelOffset(0.05);
-   hframe__1__1__1->GetYaxis()->SetLabelSize(25);
-   hframe__1__1__1->GetYaxis()->SetTitleSize(35);
-   hframe__1__1__1->GetYaxis()->SetTitleOffset(4.5);
+   hframe__1__1__1->GetYaxis()->SetLabelSize(20);
    hframe__1__1__1->GetYaxis()->SetTitleFont(63);
+   hframe__1__1__1->GetYaxis()->SetTitleSize(30);
+   hframe__1__1__1->GetYaxis()->SetTitleOffset(4);
+
    hframe__1__1__1->Draw(" ");
    TLine *line = new TLine(0,0,2,0);
    line->SetLineStyle(2);
@@ -82,25 +83,18 @@
    line->SetLineColor(8);
    line->SetLineStyle(4);
    line->Draw();
-   
+
+   float offset = 0.21;
    Double_t *dum = 0;
-   TPolyLine *pline = new TPolyLine(4,dum,dum,"");
-   pline->SetFillColor(5);
-   pline->SetPoint(0,0.5,-0.6);
-   pline->SetPoint(1,0.5,-0.576469);
-   pline->SetPoint(2,1.5,-0.576469);
-   pline->SetPoint(3,1.5,-0.6);
-   pline->Draw("f");
-   
-   Double_t *dum = 0;
-   pline = new TPolyLine(4,dum,dum,"");
-   pline->SetFillColor(1);
+   pline = new TPolyLine(5,dum,dum,"");
[…]

### 2012-04-24 macros/bsadvcsplots_tc_xbjrange_withfracs.C

@@ -54,8 +54,12 @@
    hframe__1__1__1->SetStats(0);
    hframe__1__1__1->GetXaxis()->SetTitle("-t_{c} (GeV^{2})");
    hframe__1__1__1->GetXaxis()->SetNdivisions(505);
-   hframe__1__1__1->GetXaxis()->SetLabelSize(0.1);
-   hframe__1__1__1->GetXaxis()->SetTitleSize(0.1);
+   hframe__1__1__1->GetXaxis()->SetLabelFont(63); 
+   hframe__1__1__1->GetXaxis()->SetLabelSize(23);
+   //   hframe__1__1__1->GetXaxis()->SetTitleSize(0.07);
+   hframe__1__1__1->GetXaxis()->SetTitleFont(63); 
+   hframe__1__1__1->GetXaxis()->SetTitleSize(25);
+
    hframe__1__1__1->GetXaxis()->SetTitleOffset(1.1);
    hframe__1__1__1->GetYaxis()->SetTitle("A_{LU,I}^{sin #phi}");
    hframe__1__1__1->GetYaxis()->CenterTitle(true);
@@ -101,7 +105,7 @@
    gre->SetFillColor(1);
    gre->SetLineColor(2);
    gre->SetMarkerColor(2);
-   gre->SetMarkerStyle(21);
+   gre->SetMarkerStyle(21); gre->SetMarkerSize(1);
    gre->SetPoint(0,0.018761,-0.253368);
    gre->SetPointError(0,0,0.0463085);
    gre->SetPoint(1,0.04394,-0.187844);
@@ -162,8 +166,11 @@
    hframe__2__2__2->SetStats(0);
    hframe__2__2__2->GetXaxis()->SetTitle("-t_{c} (GeV^{2})");
    hframe__2__2__2->GetXaxis()->SetNdivisions(505);
-   hframe__2__2__2->GetXaxis()->SetLabelSize(0.1);
-   hframe__2__2__2->GetXaxis()->SetTitleSize(0.1);
+   hframe__2__2__2->GetXaxis()->SetLabelFont(63); 
+   hframe__2__2__2->GetXaxis()->SetLabelSize(23);
+   //hframe__2__2__2->GetXaxis()->SetTitleSize(0.07);
+   hframe__2__2__2->GetXaxis()->SetTitleFont(63); 
+   hframe__2__2__2->GetXaxis()->SetTitleSize(25);
    hframe__2__2__2->GetXaxis()->SetTitleOffset(1.1);
[…]
